### 2020-09-15 paper/agujournaltemplate.tex
debugged version

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% AGUJournalTemplate.tex: this template file is for articles formatted with LaTeX
%
% This file includes commands and instructions
% given in the order necessary to produce a final output that will
% satisfy AGU requirements, including customized APA reference formatting.
%
% You may copy this file and give it your
% article name, and enter your text.
%
%
% Step 1: Set the \documentclass
%
% There are two options for article format:
%
% PLEASE USE THE DRAFT OPTION TO SUBMIT YOUR PAPERS.
% The draft option produces double spaced output.
%

%% To submit your paper:
\documentclass[draft]{agujournal2019}
\usepackage{url} %this package should fix any errors with URLs in refs.
\usepackage{lineno}
\linenumbers
%%%%%%%
% As of 2018 we recommend use of the TrackChanges package to mark revisions.
% The trackchanges package adds five new LaTeX commands:
%
%  \note[editor]{The note}
%  \annote[editor]{Text to annotate}{The note}
%  \add[editor]{Text to add}
%  \remove[editor]{Text to remove}
%  \change[editor]{Text to remove}{Text to add}
%
% complete documentation is here: http://trackchanges.sourceforge.net/
%%%%%%%

\draftfalse

%% Enter journal name below.
%% Choose from this list of Journals:
%
% JGR: Atmospheres
% JGR: Biogeosciences
% JGR: Earth Surface
% JGR: Oceans
% JGR: Planets
% JGR: Solid Earth
% JGR: Space Physics
% Global Biogeochemical Cycles
% Geophysical Research Letters
% Paleoceanography and Paleoclimatology
% Radio Science
% Reviews of Geophysics
% Tectonics
% Space Weather
% Water Resources Research
% Geochemistry, Geophysics, Geosystems
% Journal of Advances in Modeling Earth Systems (JAMES)
% Earth's Future
% Earth and Space Science
% Geohealth
%
% ie, \journalname{Water Resources Research}

\journalname{Geophysical Research Letters}

\begin{document}

%% ------------------------------------------------------------------------ %%
%  Title
%
% (A title should be specific, informative, and brief. Use
% abbreviations only if they are defined in the abstract. Titles that
% start with general keywords then specific terms are optimized in
% searches)
%
%% ------------------------------------------------------------------------ %%

% Example: \title{This is a test title}

\title{A twelve-year-long low-frequency earthquake catalog for Northern California}

%% ------------------------------------------------------------------------ %%
%
%  AUTHORS AND AFFILIATIONS
%
%% ------------------------------------------------------------------------ %%

% Authors are individuals who have significantly contributed to the
% research and preparation of the article. Group authors are allowed, if
% each author in the group is separately identified in an appendix.)

% List authors by first name or initial followed by last name and
% separated by commas. Use \affil{} to number affiliations, and
% \thanks{} for author notes.
% Additional author notes should be indicated with \thanks{} (for
% example, for current addresses).

% Example: \authors{A. B. Author\affil{1}\thanks{Current address, Antartica}, B. C. Author\affil{2,3}, and D. E.
% Author\affil{3,4}\thanks{Also funded by Monsanto.}}

\authors{Ariane Ducellier\affil{1}, Kenneth Creager\affil{1}}

% \affiliation{1}{First Affiliation}
% \affiliation{2}{Second Affiliation}
% \affiliation{3}{Third Affiliation}
% \affiliation{4}{Fourth Affiliation}

\affiliation{1}{University of Washington}
%(repeat as many times as is necessary)

%% Corresponding Author:
% Corresponding author mailing address and e-mail address:

% (include name and email addresses of the corresponding author.  More
% than one corresponding author is allowed in this LaTeX file and for
% publication; but only one corresponding author is allowed in our
% editorial system.)

% Example: \correspondingauthor{First and Last Name}{email@address.edu}

\correspondingauthor{Ariane Ducellier}{ducela@uw.edu}

%% Keypoints, final entry on title page.

%  List up to three key points (at least one is required)
%  Key Points summarize the main points and conclusions of the article
%  Each must be 100 characters or less with no special characters or punctuation and must be complete sentences

% Example:
% \begin{keypoints}
% \item	List up to three key points (at least one is required)
% \item	Key Points summarize the main points and conclusions of the article
% \item	Each must be 100 characters or less with no special characters or punctuation and must be complete sentences
% \end{keypoints}

\begin{keypoints}
\item enter point 1 here
\item enter point 2 here
\item enter point 3 here
\end{keypoints}

%% ------------------------------------------------------------------------ %%
%
%  ABSTRACT
%
% A good abstract will begin with a short description of the problem
% being addressed, briefly describe the new data or analyses, then
% briefly states the main conclusion(s) and how they are supported and
% uncertainties.
%% ------------------------------------------------------------------------ %%

%% \begin{abstract} starts the second page

\begin{abstract}
enter abstract here

\end{abstract}

%% ------------------------------------------------------------------------ %%
%
%  TEXT
%
%% ------------------------------------------------------------------------ %%

%%% Suggested section heads:
% \section{Introduction}
%
% The main text should start with an introduction. Except for short
% manuscripts (such as comments and replies), the text should be divided
% into sections, each with its own heading.

% Headings should be sentence fragments and do not begin with a
% lowercase letter or number. Examples of good headings are:

% \section{Materials and Methods}
% Here is text on Materials and Methods.
%
% \subsection{A descriptive heading about methods}
% More about Methods.
%
% \section{Data} (Or section title might be a descriptive heading about data)
%
% \section{Results} (Or section title might be a descriptive heading about the
% results)
%
% \section{Conclusions}

\section{Introduction}
%Text here ===>>>

Tectonic tremor is a weak but persistent shaking of the Earth that has been discovered in many subduction zones and some strike-slip faults throughout the world. Tremor is observed on seismograms as apparent noise whose amplitude is modulated in time in a similar manner at stations that are dozens of kilometers apart from each other. It is characterized by a long (several seconds to many minutes), low amplitude seismic signal, emergent onsets, and an absence of clear impulsive phases. Tremor can be explained as a swarm of low-frequency earthquakes (LFEs), that is small magnitude earthquakes (M $\sim$ 1) which dominant frequency is clearly low (1-10 Hz) compared with that of ordinary tiny earthquakes (up to 20 Hz). The source of the tremor and the LFEs is located on the plate boundary, and their focal mechanisms represent shear slip on a low-angle thrust fault dipping in the same direction as the plate interface ~\cite{IDE_2007_GRL}. LFEs are usually grouped into families of events, with all the earthquakes of a given family originating from the same small patch on the plate interface, and recurring more or less episodically in a bursty manner. In subduction zones such as Nankai and Cascadia, tectonic tremor and LFE observations are spatially and temporally correlated with slow slip observations ~\cite{OBA_2002, ROG_2003}. Due to this correlation, these paired phenomena have been called Episodic Tremor and Slip (ETS). \\

The relatively short recurrence of slow slip and tremor events results in a rich history both in space and time and reveals potential patterns.  These event histories have allowed scientists to see complete event cycles, which is typically not possible to explore in traditional earthquake catalogs. However, most of the work on low-frequency earthquakes (LFEs) has been focused on detecting LFEs during periods of high tremor activity, grouping them into families of events, and locating the source of the LFE families. Longer catalogs (several years) have been established for LFE families in Mexico (two-year long catalog by ~\citeA{FRA_2014}), the San Andreas Fault (fifteen-year-long catalog by ~\citeA{SHE_2017}), Washington State (five-year-long catalog by ~\citeA{SWE_2019} and two-year-long catalog by ~\citeA{CHE_2017_JGR, CHE_2017_G3}), New Zealand (eight-year-long catalog by ~\citeA{BAR_2018}), and Japan (twelve-year-long catalog by ~\citeA{NAK_2017} and eight-year-long catalog by ~\citeA{OHT_2017}). These studies have shown that the recurrence behavior of LFE families varies a lot between seismic regions, and inside the same seismic region. In northern Washington, ~\citeA{SWE_2019} have identified and characterized four different LFE families that span the width of the transition zone in the Cascadia Subduction Zone beneath western Washington State. They found that the LFEs swarm duration, recurrence interval, and event size decrease systematically with increasing depth. On the San Andreas Fault, ~\citeA{SHE_2017}) observed a large diversity of recurrence behaviors among the LFE families, from semicontinuous to highly episodic. Particularly, two families exhibited bimodal recurrence patterns (about 3 and 6 days for the first one, and about 2 and 4 days for the second one). Moreover, he observed an increase in the LFE event rate after the 2004 Parkfield earthquake. \\

~\citeA{PLO_2015}) have detected LFEs in southern Cascadia during the April 2008 ETS event using seismic data from the EarthScope Flexible Array Mendocino Experiment (FAME). They used a combination of autodetection methods and visual identification to obtain the initial templates. Then, they recovered higher signal-to-noise LFE signals using iterative network cross-correlation. They found that the LFE families on the southern Cascadia Subduction Zone were located above the plate boundary, with a large distribution of depths (28-47 km). Three additional LFE families were found on two strike-slip faults, the Maacama and Bucknell Creek faults, which are part of the San Andreas Fault zone. \\

When the hard work of detecting LFEs and identifying LFE families has been carried out, and enough (a few hundred) LFEs have been identified for a given family, a template waveform can be obtained by stacking all the waveforms corresponding to all the LFEs identified. Once a template is available, additional LFEs can be found by cross-correlating seismic data with the template, and assuming that an LFE is occurring whenever the value of the cross-correlation is higher than a chosen threshold.  The signal-to-noise ratios are low, so LFEs can be best identified by stacking the cross-correlation functions of multiple stations. In this study, we first use the catalog established by ~\citeA{PLO_2015} for the months of March and April 2008 to create templates for the temporary seismic stations of the FAME experiment. We then use these templates to extend the catalog to the whole period when the FAME experiment was running, between July 2007 and June 2009. Next, we use the LFEs detections from the 2007-2009 periods to create templates for the permanent stations of three seismic network in northern California. These new templates allow us to extend the LFE catalog to the period XXX-XXX.

\textcolor{red}{Add something about the conclusions}

\section{Data}

We used both seismic data from the temporary EarthScope Flexible Array Mendocino Experiment (FAME) distributed by Incorporated Research Institutions for Seismology (IRIS), and seismic data from three permanent seismic networks distributed by the Northern California Earthquake Data Center (NCEDC). The FAME network was installed in northern California between July 2007 and June 2009. The three permanent networks are Berkeley Digital Seismic Network (BK), Northern California Seismic Network (NC), and Plate Boundary Observatory Strain and Seismic Data (PB). We used both one-component and three-components seismic stations. Depending on availability, we used channels BHZ, EHZ, HHZ, or SHZ as we are mainly interested in the frequency band 1-10Hz. We restricted ourselves to seismic stations less than 100 kilometers away from the epicenter of an LFE family, as we do not expect to have good signal-to-noise ratio for stations located farther away. The complete list of seismic stations and channels used in this study is given in the Supplementary Material. Figure XXX shows a map of the locations of the LFE families, and of the locations of the seismic stations. We can see that we have a good coverage of the area, and most LFE families are surrounded by several seismic stations. \\

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={1.5cm 4cm 1cm 10cm},clip]{figures/map_LFEs.eps}
\caption{Map showing the location of the LFE families (back dots) and the seismic stations used in this study. Red triangles are the stations from the FAME experiment, green triangles are one-component permanent stations, blue triangles are three components permanent stations. Red stars are moderate ($M > 5$) nearby earthquakes.}
\label{pngfiguresample}
\end{figure}

\citeA{PLO_2015} have kindly accepted to share their LFE catalog with us. They have provided a list of 66 LFE families with, for each family, the location of the hypocenter of the family, the list of stations and channels used to detect LFEs for this family, and the timing of LFE detections. ~\citeA{PLO_2015} have later reduced the number of LFE families to 37, by grouping together families with many common detections, but we chose to use the initial detections to extend the catalog. Using this dataset, we have created LFE templates for each LFE family and each seismic station and channel. For a given LFE family, a given station and a given channel, we downloaded an 80-second-long seismic waveform starting 10 seconds before the LFE detection time, we detrended the data, tapered the first and last 5 seconds of the data with a Hann window, removed the instrument response, bandpassed filter between 1.5 and 9 Hz, resampled the data to 20 Hz, and cut the first and last 10 seconds of data to obtain a one-minute-long template. All these preprocessing operations are done with the Python package obspy. We then stacked linearly all the waveforms after normalizing each waveform with the root mean square (RMS) to obtain a waveform template for each station and each channel.

\section{Method}

We used a matched-filter algorithm to detect LFEs. For a given LFE family, we download one hour of seismic data. Then for each station and each channel, we cross-correlate the one-hour long signal with the one-minute-long template for the given station and channel. As the signal-to-noise ratio of the seismic data is low, we may not see obvious peaks in the cross-correlation signal. However, if we stack the cross-correlation signals for all the channels and all the stations, we can see peaks appearing. Whenever the value of the average cross-correlation is higher than a threshold (we chose a threshold equal to eight times the median absolute deviation of the stacked cross-correlation), we assumed that there is an LFE. As two peaks separated by a short period of time may actually correspond to the same LFE, we kept only LFEs that are separated by at least one second and, when two LFEs are separated by less than one second, we keep only the one with the higher value of the stacked cross-correlation. \\

We first looked for LFEs during the months of March and April 2008, which correspond to the period covered by the catalog from ~\citeA{PLO_2015}, and compared our detections with the initial detections from the original catalog of 66 families. For 19 families, we recovered all the LFE detections initially present in the ~\citeA{PLO_2015}'s catalog. For 61 families, we recovered more than 90 \% of the initial LFE detections. We also added 74 \% more LFEs to the catalog, but most of added LFEs have a low cross-correlation value and may be false detections. Figure XXX shows the cross-correlation values for the LFEs in the original catalog, and for the LFEs that we added to the catalog for family \textcolor{red}{080413.07.023}.

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={7.5cm 1cm 28cm 2cm},clip]{figures/hist.eps}
\caption{Cross-correlation values for LFEs added in the catalog for family \textcolor{red}{080413.07.023} (left) and cross-correlation values for LFEs in the original catalog from ~\citeA{PLO_2015} (right). There were no missing LFEs for this family.}
\label{pngfiguresample}
\end{figure}

We then looked for LFEs during the period from July 2007 to June 2009, which correspond to the period when the FAME experiment was operating. Using a threshold equal to eight times the median absolute deviation of the stacked cross-correlation may produce false detections, therefore we filtered the LFE detection times before visualizing the two-year-long catalog. As the number of seismic stations recording may change with time as the stations were progressively installed during Summer and Fall 2007, and then progressively removed during May and June 2009, we kept only LFE detections for which the product of the cross-correlation value by the number of stations recording at that time is higher than a threshold (equal to 0.1 times the number of stations used to detect LFEs for the given LFE family). The threshold is thus different for each LFE family. The resulting LFE catalog for the period 2007-2009 is shown in Figure XXX. For comparison, we also plotted the tremor detection times from ~\citeA{BOY_2015}. \\

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/tremor_nb.eps}
\caption{LFE and tremor detections as a function of time and latitude. Red dots represent tremor detections from the catalog of ~\citeA{BOY_2015}. Black dots represent days where LFEs are detected for a given LFE family. The size of the black dots are proportional to the number of LFEs detected during this day. The double-headed grey arrow represents the time period when the FAME experiment was operating at full capacity. LFE families south of 40° N latitude are on the San Andreas fault system.}
\label{pngfiguresample}
\end{figure}

We note that there is a good spatial and temporal agreement between tremor and LFEs, with LFEs detected during the main tremor episodes. Additional small LFE episodes are also detected between bigger tremor episodes. The LFE families located south on the strike-slip fault from the San Andreas Fault system are much more active than the LFE families located on the subduction zone. Additionally, one LFE family located on the southern end of the subduction zone is also more active than families located farther north, and behaves more similarly to the strike-slip fault families. \\

We then used the LFE detections from the 2007-2009 catalog to make new templates for the permanent stations of the three seismic networks: Berkeley Digital Seismic Network (BK), Northern California Seismic Network (NC), and Plate Boundary Observatory Strain and Seismic Data (PB). For a given LFE family, we took the 150 LFE detection times with the best cross-correlation value, we downloaded one minute of seismic data around each detection, and linearly stacked the waveforms to obtain the templates. We looked for templates for both one-component stations and three-component stations. \\

For most families, we find that we can obtain good templates with signal-to-noise ratio for several stations. Only nine families have four or less seismic stations with good templates. Examples of templates are given in Figure XXX for station WDC and family \textcolor{red}{080401.05.050}. To obtain the above catalog, we used one-minute-long templates, which included noise before and after the seismic wave arrivals. To increase the cross-correlation values between the templates and the data, we thus reduced the length of the templates to 25 to 40 seconds, depending on the maximum distance from the source to the stations. We did not use stations more than 100 kilometers away from the epicenter of an LFE family, as the template would be unlikely to have a good signal-to-noise ratio.

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/templates.eps}
\caption{Low-frequency earthquake template for station WDC and family \textcolor{red}{080401.05.050} for the three channels BHE, BHN and BHZ (left to right). We can clearly see a P-wave arrival and an S-wave arrival about 7 seconds later. The P-wave has a higher amplitude on the vertical component, and the S-wave has a higher amplitude on the horizontal components.}
\label{pngfiguresample}
\end{figure}

First comparison with 2007-2009 catalog with FAME data

\section{Results}

Now extension of the catalog, we will try 1995-2011.

New templates? New catalog? probably no time (or money)

\section{Discussion}

Section on effects of nearby earthquakes. Possible rapid tremor reversals

\section{Conclusion}

%%

%  Numbered lines in equations:
%  To add line numbers to lines in equations,
%  \begin{linenomath*}
%  \begin{equation}
%  \end{equation}
%  \end{linenomath*}

%% Enter Figures and Tables near as possible to where they are first mentioned:
%
% DO NOT USE \psfrag or \subfigure commands.
%
% Figure captions go below the figure.
% Table titles go above tables;  other caption information
%  should be placed in last line of the table, using
% \multicolumn2l{$^a$ This is a table note.}
%
%----------------
% EXAMPLE FIGURE
%
%
% Giving latex a width will help it to scale the figure properly. A simple trick is to use \textwidth. Try this if large figures run off the side of the page.
% \begin{figure}
% \noindent\includegraphics[width=\textwidth]{anothersample.png}
%\caption{caption}
%\label{pngfiguresample}
%\end{figure}
%
%
%
% If you get an error about an unknown bounding box, try specifying the width and height of the figure with the natwidth and natheight options.
% \begin{figure}
% \noindent\includegraphics[natwidth=800px,natheight=600px]{samplefigure.pdf}
%\caption{caption}
%\label{pdffiguresample}
%\end{figure}
%
%
% PDFLatex does not seem to be able to process EPS figures. You may want to try the epstopdf package.
%
%
%
% ---------------
% EXAMPLE TABLE
%
% \begin{table}
% \caption{Time of the Transition Between Phase 1 and Phase 2$^{a}$}
% \centering
% \begin{tabular}{l c}
% \hline
%  Run  & Time (min)  \\
% \hline
%   $l1$  & 260   \\
%   $l2$  & 300   \\
%   $l3$  & 340   \\
%   $h1$  & 270   \\
%   $h2$  & 250   \\
%   $h3$  & 380   \\
%   $r1$  & 370   \\
%   $r2$  & 390   \\
% \hline
% \multicolumn{2}{l}{$^{a}$Footnote text here.}
% \end{tabular}
% \end{table}

%% SIDEWAYS FIGURE and TABLE
% AGU prefers the use of {sidewaystable} over {landscapetable} as it causes fewer problems.
%
% \begin{sidewaysfigure}
% \includegraphics[width=20pc]{figsamp}
% \caption{caption here}
% \label{newfig}
% \end{sidewaysfigure}
%
%  \begin{sidewaystable}
%  \caption{Caption here}
% \label{tab:signif_gap_clos}
%  \begin{tabular}{ccc}
% one&two&three\\
% four&five&six
%  \end{tabular}
%  \end{sidewaystable}

%% If using numbered lines, please surround equations with \begin{linenomath*}...\end{linenomath*}
%\begin{linenomath*}
%\begin{equation}
%y|{f} \sim g(m, \sigma),
%\end{equation}
%\end{linenomath*}

%%% End of body of article

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional Appendix goes here
%
% The \appendix command resets counters and redefines section heads
%
% After typing \appendix
%
%\section{Here Is Appendix Title}
% will show
% A: Here Is Appendix Title
%
%\appendix
%\section{Here is a sample appendix}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Optional Glossary, Notation or Acronym section goes here:
%
%%%%%%%%%%%%%%
% Glossary is only allowed in Reviews of Geophysics
%  \begin{glossary}
%  \term{Term}
%   Term Definition here
%  \term{Term}
%   Term Definition here
%  \term{Term}
%   Term Definition here
%  \end{glossary}

%
%%%%%%%%%%%%%%
% Acronyms
%   \begin{acronyms}
%   \acro{Acronym}
%   Definition here
%   \acro{EMOS}
%   Ensemble model output statistics
%   \acro{ECMWF}
%   Centre for Medium-Range Weather Forecasts
%   \end{acronyms}

%
%%%%%%%%%%%%%%
% Notation
%   \begin{notation}
%   \notation{$a+b$} Notation Definition here
%   \notation{$e=mc^2$}
%   Equation in German-born physicist Albert Einstein's theory of special
%  relativity that showed that the increased relativistic mass ($m$) of a
%  body comes from the energy of motion of the body—that is, its kinetic
%  energy ($E$)—divided by the speed of light squared ($c^2$).
%   \end{notation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  ACKNOWLEDGMENTS
%
% The acknowledgments must list:
%
% >>>>	A statement that indicates to the reader where the data
% 	supporting the conclusions can be obtained (for example, in the
% 	references, tables, supporting information, and other databases).
%
% 	All funding sources related to this work from all authors
%
% 	Any real or perceived financial conflicts of interests for any
%	author
%
% 	Other affiliations for any author that may be perceived as
% 	having a conflict of interest with respect to the results of this
% 	paper.
%
%
% It is also the appropriate place to thank colleagues and other contributors.
% AGU does not normally allow dedications.

\acknowledgments
The authors would like to thank A. Plourde for sharing his low-frequency earthquake catalog. This project was funded by NSF grant XXX. A.D. would like to thank the Integral Environmental Big Data Research Fund from the College of the Environment of University of Washington, which funded cloud computing resources to carry out the data analyses. The seismic recordings used for this analysis can be downloaded from the IRIS and NCEDC websites.

%% ------------------------------------------------------------------------ %%
%% References and Citations

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% \bibliography{<name of your .bib file>} don't specify the file extension
%
% don't specify bibliographystyle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliography{bibliography}

%Reference citation instructions and examples:
%
% Please use ONLY \cite and \citeA for reference citations.
% \cite for parenthetical references
% ...as shown in recent studies (Simpson et al., 2019)
% \citeA for in-text citations
% ...Simpson et al. (2019) have shown...
%
%
%...as shown by \citeA{jskilby}.
%...as shown by \citeA{lewin76}, \citeA{carson86}, \citeA{bartoldy02}, and \citeA{rinaldi03}.
%...has been shown \cite{jskilbye}.
%...has been shown \cite{lewin76,carson86,bartoldy02,rinaldi03}.
%...has been shown \cite [e.g.,][]{lewin76,carson86,bartoldy02,rinaldi03}.
%
% DO NOT use other cite commands (e.g., \citet, \citep, \citeyear, \nocite, \citealp, etc.).
%

\end{document}

More Information and Advice:

%% ------------------------------------------------------------------------ %%
%
%  SECTION HEADS
%
%% ------------------------------------------------------------------------ %%

% Capitalize the first letter of each word (except for
% prepositions, conjunctions, and articles that are
% three or fewer letters).

% AGU follows standard outline style; therefore, there cannot be a section 1 without
% a section 2, or a section 2.3.1 without a section 2.3.2.
% Please make sure your section numbers are balanced.
% ---------------
% Level 1 head
%
% Use the \section{} command to identify level 1 heads;
% type the appropriate head wording between the curly
% brackets, as shown below.
%
%An example:
%\section{Level 1 Head: Introduction}
%
% ---------------
% Level 2 head
%
% Use the \subsection{} command to identify level 2 heads.
%An example:
%\subsection{Level 2 Head}
%
% ---------------
% Level 3 head
%
% Use the \subsubsection{} command to identify level 3 heads
%An example:
%\subsubsection{Level 3 Head}
%
%---------------
% Level 4 head
%
% Use the \subsubsubsection{} command to identify level 3 heads
% An example:
%\subsubsubsection{Level 4 Head} An example.
%
%% ------------------------------------------------------------------------ %%
%
%  IN-TEXT LISTS
%
%% ------------------------------------------------------------------------ %%
%
% Do not use bulleted lists; enumerated lists are okay.
% \begin{enumerate}
% \item
% \item
% \item
% \end{enumerate}
%
%% ------------------------------------------------------------------------ %%
%
%  EQUATIONS
%
%% ------------------------------------------------------------------------ %%

% Single-line equations are centered.
% Equation arrays will appear left-aligned.

Math coded inside display math mode \[ ...\]
 will not be numbered, e.g.,:
 \[ x^2=y^2 + z^2\]

 Math coded inside \begin{equation} and \end{equation} will
 be automatically numbered, e.g.,:
 \begin{equation}
 x^2=y^2 + z^2
 \end{equation}

% To create multiline equations, use the
% \begin{eqnarray} and \end{eqnarray} environment
% as demonstrated below.
\begin{eqnarray}
  x_{1} & = & (x - x_{0}) \cos \Theta \nonumber \\
        && + (y - y_{0}) \sin \Theta  \nonumber \\
  y_{1} & = & -(x - x_{0}) \sin \Theta \nonumber \\
        && + (y - y_{0}) \cos \Theta.
\end{eqnarray}

%If you don't want an equation number, use the star form:
%\begin{eqnarray*}...\end{eqnarray*}

% Break each line at a sign of operation
% (+, -, etc.) if possible, with the sign of operation
% on the new line.

% Indent second and subsequent lines to align with
% the first character following the equal sign on the
% first line.

% Use an \hspace{} command to insert horizontal space
% into your equation if necessary. Place an appropriate
% unit of measure between the curly braces, e.g.
% \hspace{1in}; you may have to experiment to achieve
% the correct amount of space.

%% ------------------------------------------------------------------------ %%
%
%  EQUATION NUMBERING: COUNTER
%
%% ------------------------------------------------------------------------ %%

% You may change equation numbering by resetting
% the equation counter or by explicitly numbering
% an equation.

% To explicitly number an equation, type \eqnum{}
% (with the desired number between the brackets)
% after the \begin{equation} or \begin{eqnarray}
% command.  The \eqnum{} command will affect only
% the equation it appears with; LaTeX will number
% any equations appearing later in the manuscript
% according to the equation counter.
%

% If you have a multiline equation that needs only
% one equation number, use a \nonumber command in
% front of the double backslashes (\\) as shown in
% the multiline equation above.

% If you are using line numbers, remember to surround
% equations with \begin{linenomath*}...\end{linenomath*}

%  To add line numbers to lines in equations:
%  \begin{linenomath*}
%  \begin{equation}
%  \end{equation}
%  \end{linenomath*}

### 2020-09-15 data/Ducellier/cumulative_LFEs.py

@@ -1,0 +1,79 @@
+"""
+Script to plot cumulative number of LFEs
+"""
+
+import matplotlib.pylab as pylab
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+import pickle
+
+from datetime import datetime, timedelta
+
+# List of LFE families
+templates = np.loadtxt('../Plourde_2015/templates_list.txt', \
+    dtype={'names': ('name', 'family', 'lat', 'lon', 'depth', 'eH', \
+    'eZ', 'nb'), \
+         'formats': ('S13', 'S3', np.float, np.float, np.float, \
+    np.float, np.float, np.int)}, \
+    skiprows=1)
+
+tbegin = datetime(2007, 7, 1)
+nb_days = 731
+
+# Loop on templates
+for i in range(0, np.shape(templates)[0]):
+
+    # Open LFE catalog (FAME data)
+    namedir = 'catalogs/' + templates[i][0].astype(str)
+    namefile = namedir + '/catalog_2007_2009.pkl'
+    df_FAME = pickle.load(open(namefile, 'rb'))
+
+    # Open LFE catalog (permanent networks)
+    namefile = namedir + '/catalog_2006_2011.pkl'
+    df_perm = pickle.load(open(namefile, 'rb'))
+
+    # Filter LFEs
+    maxc = np.max(df_FAME['nchannel'])
+    df_FAME = df_FAME.loc[df_FAME['cc'] * df_FAME['nchannel'] >= 0.07 * maxc]
+    df_perm = df_perm.loc[df_perm['cc'] * df_perm['nchannel'] >= 0.07 * maxc]
+
+    # Add date column
+    df = pd.DataFrame({'year': df_FAME['year'], 'month': df_FAME['month'], 'day': df_FAME['day']})
+    df = pd.to_datetime(df)
+    df_FAME['date'] = df
+
+    df = pd.DataFrame({'year': df_perm['year'], 'month': df_perm['month'], 'day': df_perm['day']})
+    df = pd.to_datetime(df)
+    df_perm['date'] = df
+
+    # Cumulative number of LFEs
+    cum_FAME = np.zeros(nb_days)
+    cum_perm = np.zeros(nb_days)
+    for j in range(0, nb_days):
+        df_sub = df_FAME[df_FAME['date'] < tbegin + timedelta(j + 1)]
+        cum_FAME[j] = len(df_sub)
[…]

### 2020-09-15 data/Ducellier/make_catalogs.py

@@ -1,0 +1,144 @@
+"""
+Script to read monthly catalogs and put them
+into a single file
+"""
+import numpy as np
+import os
+import pandas as pd
+import pickle
+
+# List of LFE families
+templates = np.loadtxt('../Plourde_2015/templates_list.txt', \
+    dtype={'names': ('name', 'family', 'lat', 'lon', 'depth', 'eH', \
+    'eZ', 'nb'), \
+         'formats': ('S13', 'S3', np.float, np.float, np.float, \
+    np.float, np.float, np.int)}, \
+    skiprows=1)
+
+for i in range(0, np.shape(templates)[0]):
+
+    # Create directory to store the catalog
+    namedir = 'catalogs/' + templates[i][0].astype(str)
+    if not os.path.exists(namedir):
+        os.makedirs(namedir)
+
+    # Read monthly catalogs
+    df_2002_01 = pickle.load(open('new/catalog_2002_01/' + templates[i][0].astype(str) + '/catalog_2002_01.pkl', 'rb'))
+    df_2004_01 = pickle.load(open('new/catalog_2004_01/' + templates[i][0].astype(str) + '/catalog_2004_01.pkl', 'rb'))
+    df_2004_02 = pickle.load(open('new/catalog_2004_02/' + templates[i][0].astype(str) + '/catalog_2004_02.pkl', 'rb'))
+    df_2004_04 = pickle.load(open('new/catalog_2004_04/' + templates[i][0].astype(str) + '/catalog_2004_04.pkl', 'rb'))
+    df_2004_05 = pickle.load(open('new/catalog_2004_05/' + templates[i][0].astype(str) + '/catalog_2004_05.pkl', 'rb'))
+    df_2004_08 = pickle.load(open('new/catalog_2004_08/' + templates[i][0].astype(str) + '/catalog_2004_08.pkl', 'rb'))
+    df_2004_09 = pickle.load(open('new/catalog_2004_09/' + templates[i][0].astype(str) + '/catalog_2004_09.pkl', 'rb'))
+    df_2005_02 = pickle.load(open('new/catalog_2005_02/' + templates[i][0].astype(str) + '/catalog_2005_02.pkl', 'rb'))
[…]

### 2020-09-15 data/Ducellier/plot_all_daily_LFEs.py

@@ -1,0 +1,96 @@
+"""
+This script looks at the catalog from southern Cascadia (2007-2009) and plots
+the hourly number of LFEs in function of time in function of latitude
+"""
+
+import matplotlib.pylab as pylab
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+import pickle
+
+from datetime import datetime, timedelta
+from math import floor
+
+params = {'legend.fontsize': 24, \
+          'xtick.labelsize':24, \
+          'ytick.labelsize':24}
+pylab.rcParams.update(params)
+
+# List of LFE families
+templates = np.loadtxt('../Plourde_2015/templates_list.txt', \
+    dtype={'names': ('name', 'family', 'lat', 'lon', 'depth', 'eH', \
+    'eZ', 'nb'), \
+         'formats': ('S13', 'S3', np.float, np.float, np.float, \
+    np.float, np.float, np.int)}, \
+    skiprows=1)
+
+# Beginning and end of the period we are looking at
+tbegin = datetime(2002, 1, 1, 0, 0, 0)
+tend = datetime(2012, 1, 1, 0, 0, 0)
+
+# We construct the time series by counting the number of LFEs
+# per one-day-long time window
+window = 86400.0
+
+# Length of the time series
+dt = tend - tbegin
+duration = dt.days * 86400.0 + dt.seconds + dt.microseconds * 0.000001
+nw = int(duration / window)
+
+# Amplitude coefficients
+amp = 0.01
+
+# Start figure
+plt.figure(1, figsize=(20, 10))
+
+# Loop on templates
+for i in range(0, np.shape(templates)[0]):
+
+    # Get latitude
+    latitude = templates[i][2]
+
+    # Open LFE catalog
+    namedir = 'catalogs/' + templates[i][0].astype(str)
+    namefile = namedir + '/catalog_2002_2011.pkl'
+    df = pickle.load(open(namefile, 'rb'))
+
+    # Filter LFEs
+#    maxc = np.max(df['nchannel'])
+#    df = df.loc[df['cc'] * df['nchannel'] >= 0.1 * maxc]
+    df = df.loc[df['cc'] * df['nchannel'] >= 1.8]
+
+    # Get time series
+    X = np.zeros(nw, dtype=int)
+    # Loop on LFEs
+    for j in range(0, len(df)):
+        myYear = df['year'].iloc[j]
+        myMonth = df['month'].iloc[j]
[…]

### 2020-09-15 data/Ducellier/plot_comparison.py

@@ -1,0 +1,115 @@
+"""
+This script looks at the catalog from southern Cascadia (2007-2009) and plots
+for each family the daily number of LFEs in function of time
+"""
+
+import matplotlib.pylab as pylab
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+import pickle
+
+from datetime import datetime, timedelta
+from math import floor
+
+params = {'legend.fontsize': 24, \
+          'xtick.labelsize':24, \
+          'ytick.labelsize':24}
+pylab.rcParams.update(params)
+
+# List of LFE families
+templates = np.loadtxt('../Plourde_2015/templates_list.txt', \
+    dtype={'names': ('name', 'family', 'lat', 'lon', 'depth', 'eH', \
+    'eZ', 'nb'), \
+         'formats': ('S13', 'S3', np.float, np.float, np.float, \
+    np.float, np.float, np.int)}, \
+    skiprows=1)
+
+# Beginning and end of the period we are looking at
+tbegin = datetime(2007, 7, 1, 0, 0, 0)
+tend = datetime(2009, 7, 1, 0, 0, 0)
+
+# We construct the time series by counting the number of LFEs
+# per one-day-long time window
+window = 86400.0
+
+# Length of the time series
+dt = tend - tbegin
+duration = dt.days * 86400.0 + dt.seconds + dt.microseconds * 0.000001
+nw = int(duration / window)
+
+# Loop on templates
+for i in range(0, 1): #np.shape(templates)[0]):
+
+    # Open LFE catalog
+    namedir = 'catalogs/' + templates[i][0].astype(str)
+    namefile1 = namedir + '/catalog_2007_2009.pkl'
+    namefile2 = namedir + '/catalog_2002_2011.pkl'
+    df1 = pickle.load(open(namefile1, 'rb'))
+    df2 = pickle.load(open(namefile2, 'rb'))
+
+    # Filter LFE
+    df1 = df1.loc[df1['cc'] * df1['nchannel'] >= 1.1]
+    df2 = df2.loc[df2['cc'] * df2['nchannel'] >= 1.5]
+    # Get time series
+    X1 = np.zeros(nw, dtype=int)
+    # Loop on LFEs
+    for j in range(0, len(df1)):
+        myYear = df1['year'].iloc[j]
+        myMonth = df1['month'].iloc[j]
+        myDay = df1['day'].iloc[j]
+        myHour = df1['hour'].iloc[j]
[…]

### 2020-09-15 data/Ducellier/plot_daily_LFEs.py

@@ -1,0 +1,90 @@
+"""
+This script looks at the catalog from southern Cascadia (2007-2009) and plots
+for each family the daily number of LFEs in function of time
+"""
+
+import matplotlib.pylab as pylab
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+import pickle
+
+from datetime import datetime, timedelta
+from math import floor
+
+params = {'legend.fontsize': 24, \
+          'xtick.labelsize':24, \
+          'ytick.labelsize':24}
+pylab.rcParams.update(params)
+
+# List of LFE families
+templates = np.loadtxt('../Plourde_2015/templates_list.txt', \
+    dtype={'names': ('name', 'family', 'lat', 'lon', 'depth', 'eH', \
+    'eZ', 'nb'), \
+         'formats': ('S13', 'S3', np.float, np.float, np.float, \
+    np.float, np.float, np.int)}, \
+    skiprows=1)
+
+# Threshold for filtering the catalog
+threshold = pd.read_csv('threshold_cc.txt', sep=r'\s{1,}', header=None, engine='python')
+threshold.columns = ['family', 'threshold_FAME', 'threshold_perm']
+
+# Beginning and end of the period we are looking at
+#tbegin = datetime(2002, 1, 1, 0, 0, 0)
+#tend = datetime(2012, 1, 1, 0, 0, 0)
+tbegin = datetime(2010, 7, 1, 0, 0, 0)
+tend = datetime(2011, 1, 1, 0, 0, 0)
+
+# We construct the time series by counting the number of LFEs
+# per one-day-long time window
+window = 86400.0
+
+# Length of the time series
+dt = tend - tbegin
+duration = dt.days * 86400.0 + dt.seconds + dt.microseconds * 0.000001
+nw = int(duration / window)
+
+# Loop on templates
+for i in range(0, np.shape(templates)[0]):
+
+    # Open LFE catalog
+#    namedir = 'catalogs/' + templates[i][0].astype(str)
+#    namefile = namedir + '/catalog_2002_2011.pkl'
+    namedir = 'new/LFEs/' + templates[i][0].astype(str)
+    namefile = namedir + '/catalog.pkl'
+    df = pickle.load(open(namefile, 'rb'))
+
+    # Filter LFEs
+#    df = df.loc[df['cc'] * df['nchannel'] >= threshold['threshold_perm'].iloc[i]]
+
+    # Get time series
[…]

### 2020-09-15 data/Ducellier/plot_hist_cc.py

@@ -1,0 +1,63 @@
+"""
+This script looks at the catalog from southern Cascadia (2007-2009) and plots
+for each family the daily number of LFEs in function of time
+"""
+
+import matplotlib.pylab as pylab
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+import pickle
+
+from datetime import datetime, timedelta
+from math import floor
+
+params = {'legend.fontsize': 24, \
+          'xtick.labelsize':24, \
+          'ytick.labelsize':24}
+pylab.rcParams.update(params)
+
+# List of LFE families
+templates = np.loadtxt('../Plourde_2015/templates_list.txt', \
+    dtype={'names': ('name', 'family', 'lat', 'lon', 'depth', 'eH', \
+    'eZ', 'nb'), \
+         'formats': ('S13', 'S3', np.float, np.float, np.float, \
+    np.float, np.float, np.int)}, \
+    skiprows=1)
+
+# Loop on templates
+for i in range(0, np.shape(templates)[0]):
+
+    # Open LFE catalog
+    namedir = 'catalogs/' + templates[i][0].astype(str)
+    namefile = namedir + '/catalog_2002_2011.pkl'
+    df = pickle.load(open(namefile, 'rb'))
+    time = pd.DataFrame({'year':df['year'], 'month':df['month'], 'day':df['day']})
+    time = pd.to_datetime(time)
+    df['time'] = time
+
+    print(templates[i][0].astype(str), np.quantile(df['cc'] * df['nchannel'], 0.8))
+
+    # Plot figure
+    plt.figure(1, figsize=(15, 5))
+    ax1 = plt.subplot(131)
+    plt.hist(df['cc'])
+    plt.xlabel('Cross-correlation value', fontsize=24)
+    plt.ylabel('Number of LFEs', fontsize=24)
+    plt.title('Cross-correlation', fontsize=30)
+    ax2 = plt.subplot(132)
+    plt.hist(df['cc'] * df['nchannel'])
+    plt.xlabel('CC x nb channels', fontsize=24)
+    plt.ylabel('Number of LFEs', fontsize=24)
+    plt.title('CC x nb channels', fontsize=30)
+    ax3 = plt.subplot(133)
+    plt.plot(df['time'], df['nchannel'], 'ko')
+    plt.xlabel('Time', fontsize=24)
+    plt.ylabel('Number of channels', fontsize=24)
[…]

### 2020-09-15 data/Ducellier/plot_tremor_nbLFEs.py

@@ -1,0 +1,91 @@
+"""
+Script to plot tremor and LFEs as a function of latitude
+"""
+
+import matplotlib.pylab as pylab
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+import pickle
+
+from math import floor
+
+from date import ymdhms2day
+
+# Time boundaries
+xmin = 2010.85
+xmax = 2010.95
+
+# Space boundaries
+latmin = 39.4
+latmax = 41.8
+
+# Read tremor file
+tremor = pd.read_csv('../tremor/tremor.xyddtt', sep=' ', header=None)
+tremor.columns = ['longitude', 'latitude', 'downdip', 'alongstrike', 'year', 'epoch']
+year_tremor = tremor['year']
+lat_tremor = tremor['latitude']
+
+# Start figure and plot tremor
+params = {'legend.fontsize': 24, \
+          'xtick.labelsize':24, \
+          'ytick.labelsize':24}
+pylab.rcParams.update(params)
+plt.figure(1, figsize=(20, 10))
+plt.scatter(year_tremor, lat_tremor, c='r')
+
+# List of LFE families
+templates = np.loadtxt('../Plourde_2015/templates_list.txt', \
+    dtype={'names': ('name', 'family', 'lat', 'lon', 'depth', 'eH', \
+    'eZ', 'nb'), \
+         'formats': ('S13', 'S3', np.float, np.float, np.float, \
+    np.float, np.float, np.int)}, \
+    skiprows=1)
+
+# Loop on templates
+for i in range(0, np.shape(templates)[0]):
+    # Get latitude
+    latitude = templates[i][2]
+
+    # Open LFE catalog
+#    namedir = 'catalogs/' + templates[i][0].astype(str)
+#    namefile = namedir + '/catalog_2002_2011.pkl'
+    namefile = 'new/LFEs/' + templates[i][0].astype(str) + '/catalog.pkl'
+    df = pickle.load(open(namefile, 'rb'))
+
+    # Filter LFEs
+#    maxc = np.max(df['nchannel'])
+#    df = df.loc[df['cc'] * df['nchannel'] >= 0.1 * maxc]
+#    df = df.loc[df['cc'] >= 0.2]
+
+    time = np.arange(xmin, xmax, 1.0/365.5)
+    nbLFEs = np.zeros(np.shape(time)[0])
+    # Loop on LFEs
[…]

### 2020-09-15 paper/figures/plot_templates.py

@@ -1,0 +1,30 @@
+import obspy
+
+import matplotlib.pylab as pylab
+import matplotlib.pyplot as plt
+import numpy as np
+
+import pickle
+
+params = {'xtick.labelsize':20, \
+          'ytick.labelsize':20}
+pylab.rcParams.update(params)
+plt.figure(1, figsize=(24, 6))
+namedir = '../../src/templates_2007_2009/080401.05.050/'
+station = 'WDC'
+channels = ['BHE', 'BHN', 'BHZ']
+for (i, channel) in enumerate(channels):
+    filename = namedir + station + '_' + channel + '.pkl'
+    stack = pickle.load(open(filename, 'rb'))[0]
+    dt = stack.stats.delta
+    nt = stack.stats.npts
+    t = dt * np.arange(0, nt)
+    plt.subplot2grid((1, len(channels)), (0, i))
+    plt.plot(t, stack.data, 'k')
+    plt.xlim([15.0, 35.0])
+    plt.ylim([-1.5, 1.5])
+    plt.title('{} - {}'.format(station, channel), fontsize=20)
+    plt.xlabel('Time (s)', fontsize=20)
+plt.tight_layout()
+plt.savefig('templates.eps', format='eps')
+plt.close(1)

### 2020-11-10 paper/agujournaltemplate.tex
Update paper with figures

@@
 
-\title{A twelve-year-long low-frequency earthquake catalog for Northern California}
+\title{An eight-year-long low-frequency earthquake catalog for Southern Cascadia}
 
@@
 \begin{figure}
-\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/tremor_nb.eps}
+\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/tremor_nb_FAME.eps}
 \caption{LFE and tremor detections as a function of time and latitude.
@@
 
-First comparison with 2007-2009 catalog with FAME data
-
 \section{Results}
 
-Now extension of the catalog, we will try 1995-2011.
+Once we have obtained a catalog for the period 2007-2009 using the data from the permanent seismic networks, we compare the LFE detections between the two catalogs: the FAME catalog (obtained with data from the FAME experiment) and the networks catalog (obtained from data from the permanent networks).
+As we may have many false detections, we try to eliminate some of them by assuming that LFEs present in both catalogs are always true detections.
+Then we define two thresholds: the first threshold is chosen such that at least half the LFE detections above the threshold in the FAME catalog are also in the network catalog, the second threshold is chosen such that at least half the LFE detections above the threshold in the network catalog are also in the FAME catalog.
+If we filter the catalogs and keep only detections above the thresholds, we are now confident that at least half of the LFE detections are true detections.
+As the number of stations recording may vary over time (especially for the network catalog), we keep only the LFE detections such that the associated cross correlation multiplied by the number of channels recording at that time is higher than the threshold.
+Thus, if there are few stations recordings at some time, the cross correlation must be higher for the LFE to be considered as a true detection.
+We then compared the normalized number of LFEs obtained with the two catalogs.
+Examples are given in Figures XXX and XXX for families \textcolor{red}{080413.07.023} and \textcolor{red}{080401.05.050}.
+Although the number of LFEs during each event may not be the same, we clearly see for family \textcolor{red}{080413.07.023} that the timing of the events are the same for both catalogs.
+Family \textcolor{red}{080401.05.050} is much more active but most events seem to be present in both catalogs as well.
 
-New templates? New catalog? probably no time (or money)
+\begin{figure}
+\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/080413_07_023.eps}
+\caption{Normalize cumulative number of LFEs over the period July 2007-July 2009 for the FAME catalog (red) and the network catalog (blue) for family \textcolor{red}{080413.07.023}.}
+\label{pngfiguresample}
+\end{figure}
+
+\begin{figure}
+\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/080401_05_050.eps}
+\caption{Normalize cumulative number of LFEs over the period July 2007-July 2009 for the FAME catalog (red) and the network catalog (blue) for family \textcolor{red}{080401.05.050}.}
+\label{pngfiguresample}
+\end{figure}
+
+For most of the families located on the subduction zone, we obtained a good agreement between both catalogs.
+We eliminate two families for which too few permanent stations have good templates, and it was not possible to detect LFEs with the available templates.
+However, we were able to detect most LFEs events even without the presence of the temporary stations from the FAME network.
+We are thus confident that we can detect LFEs before 2007 and after 2009.
+In the following, we focus on the period 2004-2011.
+In November 2011, several 1D stations stopped recording and the number of available stations started decreasing, each is why we did not look for LFEs event after that date.
+The resulting LFE catalog for the period 2004-2011 is shown in Figure XXX.
+For comparison, we also plotted the tremor detection times from ~\citeA{BOY_2015}.
+
+\begin{figure}
+\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/tremor_nb_perm.eps}
+\caption{LFE and tremor detections as a function of time and latitude.
+Red dots represent tremor detections from the catalog of ~\citeA{BOY_2015}.
+Black dots represent days where LFEs are detected for a given LFE family.
+The size of the black dots are proportional to the number of LFEs detected during this day.}
+\label{pngfiguresample}
+\end{figure}
 
@@
 
-Section on effects of nearby earthquakes. Possible rapid tremor reversals
+We were able to detect LFE events propagation \textcolor{red}{ from North to South or from South to North} whenever there is a tremor episode in the ~\citeA{BOY_2015} catalog.
+We were also able to detect several LFE episodes in 2004-2005 before the beginning of the ~\citeA{BOY_2015} catalog.
+It is known than tectonic tremor can be triggered by surface waves from distant and regional earthquakes, as has been observed in Cascadia ~\cite{RUB_2009}, the San Andreas ~\cite{PEN_2009, GUI_2010}, and Nankai ~\cite{HAN_2014}.
+Low-frequency earthquake activity on the San Andreas fault also increased during several months after the 2004 Parafield earthquake ~\cite{SHE_2017}.
+We looked for regional earthquakes with magnitude higher than 5 during the period covered by the catalog to verify whether this phenomenon is also verified in southern Cascadia.
+The characteristics of the earthquakes we looked at are given in Table 1.
+
+\begin{table}
+\caption{Nearby regional earthquakes between 2004 and 2011}
+\centering
+\begin{tabular}{c c c c c}
+\hline
+Magnitude & Time & Latitude & Longitude & Depth (km) \\
+\hline
+7.2 & 2005-06-15 02:50:54 & 41.292N & 125.953W & 16.0 \\
+6.6 & 2005-06-17 06:21:42 & 40.773N & 126.574W & 12.0 \\
+6.5 & 2010-01-10 00:27:39 & 40.652N & 124.693W & 28.7 \\
+5.9 & 2010-02-04 20:20:21 & 40.412N & 124.961W & 23.0 \\
+5.4 & 2008-04-30 03:03:06 & 40.836N & 123.497W & 27.8 \\
+5.0 & 2006-07-19 11:41:43 & 40.281N & 124.433W & 20.1 \\
+\hline
+\end{tabular}
+\end{table}
+
+Although, we observe an increase in LFE activity for some families several days after the earthquakes (except the 2008 one where no activity is observed after the earthquake), it does not seem that this activity is linked to the earthquake.
+Indeed, the LFE events occur a few days after the earthquake and not immediately after as is the case for the Parkfield earthquake, and they affect only a few families.
+The reason may be due to the distance between the LFE families and the epicenters of the regional earthquakes.
+Indeed, for the Parafield earthquake, an increase in LFE activity was observed for LFE families up to 45km away from the epicenter, but not farther away.
+For southern Cascadia, the closest epicenter (2008) is located 50 km away from the closest LFE families.
 

### 2020-11-10 data/Ducellier/cumulative_LFEs.py

@@ -26,7 +26,7 @@ threshold = pd.read_csv('threshold_cc.txt', sep=r'\s{1,}', header=None, engine='
 threshold.columns = ['family', 'threshold_FAME', 'threshold_perm']
 
 # Loop on templates
-for i in range(63, 64): #np.shape(templates)[0]):
+for i in range(0, np.shape(templates)[0]):
 
     # Open LFE catalog (FAME data)
     namedir = 'catalogs/' + templates[i][0].astype(str)

### 2020-11-10 data/Ducellier/date_keep.py

@@ -1,0 +1,161 @@
+"""
+This module contains function to convert dates in appropriate format
+"""
+
+from datetime import datetime, timedelta
+from math import floor
+
+def matlab2ymdhms(time, roundsec=True):
+    """
+    Convert Matlab format to year/month/day/hour/minute/second
+
+    Input:
+        type time =  float
+        time = Number of days since January 1, 0000 (Matlab format)
+    Output:
+        type output = tuple of 6 integers
+        output = year, month, day, hour, minute, second, (microsecond)
+    """    
+    myday = datetime.fromordinal(int(time)) + \
+        timedelta(days=time % 1) - timedelta(days=366)
+    year = myday.year
+    month = myday.month
+    day = myday.day
+    hour = myday.hour
+    minute = myday.minute
+    second = myday.second
+    microsecond = myday.microsecond
+    if (roundsec==True):
+        rsecond = int(round(second + microsecond / 1000000.0))
+        if (rsecond == 60):
+            minute = minute + 1
+            rsecond = 0
+        if (minute == 60):
+            hour = hour + 1
+            minute = 0
+        if (hour == 24):
+            day = day + 1
+            hour = 0
+        if ((month in [1, 3, 5, 7, 8, 10, 12]) and (day == 32)):
+            month = month + 1
+            day = 1
+        elif ((month in [4, 6, 9, 11]) and (day == 31)):
+            month = month + 1
+            day = 1
+        else:
+            if (((year % 4 == 0) and (year % 100 != 0)) or (year % 400 == 0)):
+                if (day == 30):
+                    month = month + 1
+                    day = 1
+            else:
+                if (day == 29):
+                    month = month + 1
+                    day = 1
+        if (month == 13):
+            year = year + 1
+            month = 1
+        return (year, month, day, hour, minute, rsecond)
+    else:
+        return (year, month, day, hour, minute, second, microsecond)
+
+def ymdhms2matlab(year, month, day, hour, minute, second):
+    """
+    Convert year/month/day/hour/minute/second to Matlab format
+
+    Input:
+        type intput = 6 integers
+        input = year, month, day, hour, minute, second
+    Output:
+        type time = float
+        time = Number of days since January 1, 0000 (Matlab format)
+    """
[…]

### 2020-11-10 data/Ducellier/map_earthquakes.py

@@ -1,0 +1,104 @@
+import cartopy.crs as ccrs
+import cartopy.io.shapereader as shapereader
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+import pickle
+
+from datetime import datetime, timedelta
+from math import floor
+
+# Get the names of the template detection files
+templates = np.loadtxt('../Plourde_2015/templates_list.txt', \
+    dtype={'names': ('name', 'family', 'lat', 'lon', 'depth', 'eH', \
+    'eZ', 'nb'), \
+         'formats': ('S13', 'S3', np.float, np.float, np.float, \
+    np.float, np.float, np.int)}, \
+    skiprows=1)
+
+# Threshold for filtering the catalog
+threshold = pd.read_csv('threshold_cc.txt', sep=r'\s{1,}', header=None, engine='python')
+threshold.columns = ['family', 'threshold_FAME', 'threshold_perm']
+
+# Name of catalog
+catalog = 'catalog_2004_2011'
+
+latitude = np.zeros(np.shape(templates)[0])
+longitude = np.zeros(np.shape(templates)[0])
+number_LFEs = np.zeros(np.shape(templates)[0])
+
+t1 = datetime(2005, 6, 15, 2, 50, 54)
+t2 = t1 + timedelta(days=15)
+
+EQ1 = (-125.953, 41.292)
+EQ2 = (-126.57, 40.773)
+        
+# Loop on templates
+for i in range(0, np.shape(templates)[0]):
+
+    # Plot only good data
+    if threshold['threshold_perm'].iloc[i] > 0.0:
+
+        # Get the time of LFE detections
+        filename = 'catalogs/' + templates[i][0].astype(str)
+        latitude[i] = templates[i][2]
+        longitude[i] = templates[i][3]
+        
+        # Open LFE catalog
+        namedir = 'catalogs/' + templates[i][0].astype(str)
+        namefile = namedir + '/' + catalog + '.pkl'
+        df = pickle.load(open(namefile, 'rb'))
+
+        # Filter LFEs
+        df = df.loc[df['cc'] * df['nchannel'] >= threshold['threshold_perm'].iloc[i]]
+
+        # Keep only time interval
+        df_date = pd.DataFrame({'year':df['year'], 'month':df['month'], 'day':df['day']})
+        df_date = pd.to_datetime(df_date)
[…]

### 2020-11-10 data/Ducellier/plot_all_daily_LFEs.py

@@ -30,8 +30,8 @@ threshold = pd.read_csv('threshold_cc.txt', sep=r'\s{1,}', header=None, engine='
 threshold.columns = ['family', 'threshold_FAME', 'threshold_perm']
 
 # Beginning and end of the period we are looking at
-tbegin = datetime(2004, 1, 1, 0, 0, 0)
-tend = datetime(2012, 1, 1, 0, 0, 0)
+tbegin = datetime(2007, 7, 1, 0, 0, 0)
+tend = datetime(2009, 7, 1, 0, 0, 0)
 
 # We construct the time series by counting the number of LFEs
 # per one-day-long time window
@@ -52,18 +52,18 @@ plt.figure(1, figsize=(20, 10))
 for i in range(0, np.shape(templates)[0]):
 
     # Plot only good data
-    if threshold['threshold_perm'].iloc[i] > 0.0:
+    if threshold['threshold_FAME'].iloc[i] > 0.0:
 
         # Get latitude
         latitude = templates[i][2]
 
         # Open LFE catalog
         namedir = 'catalogs/' + templates[i][0].astype(str)
-        namefile = namedir + '/catalog_2004_2011.pkl'
+        namefile = namedir + '/catalog_2007_2009.pkl'
         df = pickle.load(open(namefile, 'rb'))
 
         # Filter LFEs
-        df = df.loc[df['cc'] * df['nchannel'] >= threshold['threshold_perm'].iloc[i]]
+        df = df.loc[df['cc'] * df['nchannel'] >= threshold['threshold_FAME'].iloc[i]]
 
         # Get time series
         X = np.zeros(nw, dtype=int)
@@ -93,9 +93,9 @@ for i in range(0, np.shape(templates)[0]):
         plt.axhline(latitude, linewidth=1, color='k')
 
 plt.xlim([-0.5, len(X) - 0.5])
-plt.xlabel('Time (days) since 2004/01/01', fontsize=24)
+plt.xlabel('Time (days) since 2007/07/01', fontsize=24)
 plt.ylabel('Number of LFEs', fontsize=24)
 plt.title('Daily LFEs for all families', fontsize=24)
-plt.savefig('LFEdistribution_perm/all_families.eps', format='eps')
+plt.savefig('LFEdistribution_FAME/all_families.eps', format='eps')
 plt.close(1)
     

### 2020-11-10 data/Ducellier/plot_comparison.py

@@ -43,7 +43,7 @@ duration = dt.days * 86400.0 + dt.seconds + dt.microseconds * 0.000001
 nw = int(duration / window)
 
 # Loop on templates
-for i in range(63, 64): #np.shape(templates)[0]):
+for i in range(0, np.shape(templates)[0]):
 
     # Open LFE catalog
     namedir = 'catalogs/' + templates[i][0].astype(str)

### 2020-11-10 data/Ducellier/plot_daily_LFEs.py

@@ -30,8 +30,8 @@ threshold = pd.read_csv('threshold_cc.txt', sep=r'\s{1,}', header=None, engine='
 threshold.columns = ['family', 'threshold_FAME', 'threshold_perm']
 
 # Beginning and end of the period we are looking at
-tbegin = datetime(2007, 7, 1, 0, 0, 0)
-tend = datetime(2009, 7, 1, 0, 0, 0)
+tbegin = datetime(2004, 1, 1, 0, 0, 0)
+tend = datetime(2012, 1, 1, 0, 0, 0)
 
 # We construct the time series by counting the number of LFEs
 # per one-day-long time window
@@ -43,15 +43,15 @@ duration = dt.days * 86400.0 + dt.seconds + dt.microseconds * 0.000001
 nw = int(duration / window)
 
 # Loop on templates
-for i in range(63, 64): #np.shape(templates)[0]):
+for i in range(0, np.shape(templates)[0]):
 
     # Open LFE catalog
     namedir = 'catalogs/' + templates[i][0].astype(str)
-    namefile = namedir + '/catalog_2007_2009.pkl'
+    namefile = namedir + '/catalog_2004_2011.pkl'
     df = pickle.load(open(namefile, 'rb'))
 
     # Filter LFEs
-    df = df.loc[df['cc'] * df['nchannel'] >= threshold['threshold_FAME'].iloc[i]]
+    df = df.loc[df['cc'] * df['nchannel'] >= threshold['threshold_perm'].iloc[i]]
 
     # Get time series
     X = np.zeros(nw, dtype=int)
@@ -78,9 +78,9 @@ for i in range(63, 64): #np.shape(templates)[0]):
     plt.figure(1, figsize=(20, 10))
     plt.stem(np.arange(0, len(X)), X, 'k-', markerfmt=' ', basefmt=' ')
     plt.xlim([-0.5, len(X) - 0.5])
-    plt.xlabel('Time (days) since 2007/07/01', fontsize=24)
+    plt.xlabel('Time (days) since 2004/01/01', fontsize=24)
     plt.ylabel('Number of LFEs', fontsize=24)
     plt.title('Family {} ({:d} LFEs)'.format(templates[i][0].astype(str), np.sum(X)), \
         fontsize=24)
-    plt.savefig('LFEdistribution_FAME/' + templates[i][0].astype(str) + '.eps', format='eps')
+    plt.savefig('LFEdistribution_perm/' + templates[i][0].astype(str) + '.eps', format='eps')
     plt.close(1)

### 2020-11-10 data/Ducellier/plot_hourly_LFEs.py

@@ -1,0 +1,112 @@
+"""
+This script looks at the catalog from southern Cascadia (2007-2009) and plots
+for each family the daily number of LFEs in function of time
+"""
+
+import matplotlib.pylab as pylab
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+import pickle
+
+from datetime import datetime, timedelta
+from math import cos, floor, pi, sin, sqrt
+
+params = {'legend.fontsize': 24, \
+          'xtick.labelsize':24, \
+          'ytick.labelsize':24}
+pylab.rcParams.update(params)
+
+# Earth's radius and ellipticity
+a = 6378.136
+e = 0.006694470
+
+# Conversion lat-lon into kilometers
+lat0 = 40.281
+lon0 = -124.433
+dx = (pi / 180.0) * a * cos(lat0 * pi / 180.0) / sqrt(1.0 - e * e * \
+    sin(lat0 * pi / 180.0) * sin(lat0 * pi / 180.0))
+dy = (3.6 * pi / 648.0) * a * (1.0 - e * e) / ((1.0 - e * e * sin(lat0 * \
+    pi / 180.0) * sin(lat0 * pi / 180.0)) ** 1.5)
+
+# List of LFE families
+templates = np.loadtxt('../Plourde_2015/templates_list.txt', \
+    dtype={'names': ('name', 'family', 'lat', 'lon', 'depth', 'eH', \
+    'eZ', 'nb'), \
+         'formats': ('S13', 'S3', np.float, np.float, np.float, \
+    np.float, np.float, np.int)}, \
+    skiprows=1)
+
+# Threshold for filtering the catalog
+threshold = pd.read_csv('threshold_cc.txt', sep=r'\s{1,}', header=None, engine='python')
+threshold.columns = ['family', 'threshold_FAME', 'threshold_perm']
+
+# Beginning and end of the period we are looking at
+tbegin = datetime(2006, 7, 4, 11, 41, 43)
+tend = datetime(2006, 8, 3, 11, 41, 43)
+
+# We construct the time series by counting the number of LFEs
+# per one-day-long time window
+window = 3600.0
+
+# Length of the time series
+dt = tend - tbegin
+duration = dt.days * 86400.0 + dt.seconds + dt.microseconds * 0.000001
+nw = int(duration / window)
+
+# Loop on templates
+for i in range(0, np.shape(templates)[0]):
+
+    # Distance to epicenter
[…]

### 2020-11-10 data/Ducellier/plot_tremor_nbLFEs.py

@@ -13,8 +13,8 @@ from math import floor
 from date import ymdhms2day
 
 # Time boundaries
-xmin = 2007.5
-xmax = 2009.5
+xmin = 2004.0
+xmax = 2012.0
 
 # Space boundaries
 latmin = 39.4
@@ -50,18 +50,18 @@ threshold.columns = ['family', 'threshold_FAME', 'threshold_perm']
 for i in range(0, np.shape(templates)[0]):
 
     # Plot only good data
-    if threshold['threshold_FAME'].iloc[i] > 0.0:
+    if threshold['threshold_perm'].iloc[i] > 0.0:
 
         # Get latitude
         latitude = templates[i][2]
 
         # Open LFE catalog
         namedir = 'catalogs/' + templates[i][0].astype(str)
-        namefile = namedir + '/catalog_2007_2009.pkl'
+        namefile = namedir + '/catalog_2004_2011.pkl'
         df = pickle.load(open(namefile, 'rb'))
 
         # Filter LFEs
-        df = df.loc[df['cc'] * df['nchannel'] >= threshold['threshold_FAME'].iloc[i]]
+        df = df.loc[df['cc'] * df['nchannel'] >= threshold['threshold_perm'].iloc[i]]
 
         time = np.arange(xmin, xmax, 1.0/365.5)
         nbLFEs = np.zeros(np.shape(time)[0])
@@ -86,13 +86,13 @@ for i in range(0, np.shape(templates)[0]):
 #        plt.scatter(time, np.repeat(latitude, np.shape(time)[0]), c=nbLFEs, cmap='autumn')
 
 # Plot time line
-tbegin = ymdhms2day(2007, 9, 25, 0, 0, 0)
-tend = ymdhms2day(2009, 5, 14, 0, 0, 0)
-plt.arrow(tbegin, 39.2, tend - tbegin, 0, head_width=0.05, \
-    head_length=0.03, linewidth=4, color='grey', length_includes_head=True)
-plt.arrow(tend, 39.2, tbegin - tend, 0, head_width=0.05, \
-    head_length=0.03, linewidth=4, color='grey', length_includes_head=True)
-plt.annotate('FAME operating', (2008.35, 39.25), fontsize=24, color='grey')
+#tbegin = ymdhms2day(2007, 9, 25, 0, 0, 0)
+#tend = ymdhms2day(2009, 5, 14, 0, 0, 0)
[…]

### 2020-11-11 paper/agujournaltemplate.tex
First draft of paper

@@
 Next, we use the LFEs detections from the 2007-2009 periods to create templates for the permanent stations of three seismic network in northern California.
-These new templates allow us to extend the LFE catalog to the period XXX-XXX.
-
-\textcolor{red}{Add something about the conclusions}
+These new templates allow us to extend the LFE catalog to the period 2004-2011.
 
@@
 The complete list of seismic stations and channels used in this study is given in the Supplementary Material.
-Figure XXX shows a map of the locations of the LFE families, and of the locations of the seismic stations.
+Figure 1 shows a map of the locations of the LFE families, and of the locations of the seismic stations.
 We can see that we have a good coverage of the area, and most LFE families are surrounded by several seismic stations.
@@
 We also added 74 \% more LFEs to the catalog, but most of added LFEs have a low cross-correlation value and may be false detections.
-Figure XXX shows the cross-correlation values for the LFEs in the original catalog, and for the LFEs that we added to the catalog for family \textcolor{red}{080413.07.023}.
+Figure 2 shows the cross-correlation values for the LFEs in the original catalog, and for the LFEs that we added to the catalog for family \textcolor{red}{080413.07.023}.
 
@@
 The threshold is thus different for each LFE family.
-The resulting LFE catalog for the period 2007-2009 is shown in Figure XXX.
+The resulting LFE catalog for the period 2007-2009 is shown in Figure 3.
 For comparison, we also plotted the tremor detection times from ~\citeA{BOY_2015}.
@@
 Only nine families have four or less seismic stations with good templates.
-Examples of templates are given in Figure XXX for station WDC and family \textcolor{red}{080401.05.050}.
+Examples of templates are given in Figure 4 for station WDC and family \textcolor{red}{080401.05.050}.
 To obtain the above catalog, we used one-minute-long templates, which included noise before and after the seismic wave arrivals.
@@
 We did not use stations more than 100 kilometers away from the epicenter of an LFE family, as the template would be unlikely to have a good signal-to-noise ratio.
+We then used this new, shorter templates for the permanent stations to make an LFE catalog for the period 2007-2009.
 
@@
 We then compared the normalized number of LFEs obtained with the two catalogs.
-Examples are given in Figures XXX and XXX for families \textcolor{red}{080413.07.023} and \textcolor{red}{080401.05.050}.
+Examples are given in Figures 5 and 6 for families \textcolor{red}{080413.07.023} and \textcolor{red}{080401.05.050}.
 Although the number of LFEs during each event may not be the same, we clearly see for family \textcolor{red}{080413.07.023} that the timing of the events are the same for both catalogs.
@@
 In the following, we focus on the period 2004-2011.
-In November 2011, several 1D stations stopped recording and the number of available stations started decreasing, each is why we did not look for LFEs event after that date.
-The resulting LFE catalog for the period 2004-2011 is shown in Figure XXX.
+In November 2011, several one-component stations stopped recording and the number of available stations started decreasing, each is why we did not look for LFEs event after that date.
+The resulting LFE catalog for the period 2004-2011 is shown in Figure 7.
 For comparison, we also plotted the tremor detection times from ~\citeA{BOY_2015}.
@@
 
-We were able to detect LFE events propagation \textcolor{red}{ from North to South or from South to North} whenever there is a tremor episode in the ~\citeA{BOY_2015} catalog.
+We were able to detect LFE events propagating from North to South or from South to North whenever there is a tremor episode in the ~\citeA{BOY_2015} catalog.
 We were also able to detect several LFE episodes in 2004-2005 before the beginning of the ~\citeA{BOY_2015} catalog.
@@
 
-Although, we observe an increase in LFE activity for some families several days after the earthquakes (except the 2008 one where no activity is observed after the earthquake), it does not seem that this activity is linked to the earthquake.
+Although we observe an increase in LFE activity for some families several days after the earthquakes (except the 2008 one where no activity is observed after the earthquake), it does not seem that this activity is linked to the earthquake.
 Indeed, the LFE events occur a few days after the earthquake and not immediately after as is the case for the Parkfield earthquake, and they affect only a few families.
 The reason may be due to the distance between the LFE families and the epicenters of the regional earthquakes.
-Indeed, for the Parafield earthquake, an increase in LFE activity was observed for LFE families up to 45km away from the epicenter, but not farther away.
+Indeed, for the Parkfield earthquake, an increase in LFE activity was observed for LFE families up to 45km away from the epicenter, but not farther away.
 For southern Cascadia, the closest epicenter (2008) is located 50 km away from the closest LFE families.
+\\
+
+Finally, we want to verify whether we can an increase of lFE activity for the downdip LFE families compared to the updip LFE families.
+Most families in the northern and central part of the study area are well aligned along the strike direction, however families in the southern part of the subduction zone are more distant from each other.
+We first look at five families aligned at latitude about 40.7N and show the number of LFEs per day in Figure 8.
+We then look at three families aligned at latitude about 40.4N and show the number of LFEs per day in Figure 9.
+For both sets of families, LFE events are more frequent for the easternmost family than for the westernmost family, as was also the case in northern Cascade ~\cite{SWE_2019}.
+It is more difficult to compare event size and swarm duration as the number of stations and the quality of the templates are different from each family, and may have a strong influence on the number of LFEs detected.
+
+\begin{figure}
+\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/set1_daily_LFEs.eps}
+\caption{Daily number of LFEs over the period 2004-2011 for five LFE families aligned at about 40.7N.}
+\label{pngfiguresample}
+\end{figure}
+
+\begin{figure}
+\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/set2_daily_LFEs.eps}
+\caption{Daily number of LFEs over the period 2004-2011 for three LFE families aligned at about 40.4N.}
+\label{pngfiguresample}
+\end{figure}
 
 \section{Conclusion}
+
+In this study, we used the templates obtained by Plourde et al.
+(2015) using data recorded by the FAME network in Northern California during an episode of high tremor activity in April 2008, and we extended their catalog to the whole two years (2007-2009) during which the seismic stations were installed.
+We then used the two-year-long catalog to create templates for stations from the permanent seismic networks, and used the seismic data recorded by these stations to extend the catalog before and after the FAME experiment.
+We observe LFEs every time that there is tectonic tremor on the tremor catalog from Boyarko et al.
+(2015), and several additional smaller LFE episodes.
+Whereas the LFE families from the subduction zone are mainly active during the big Episodic Tremor and Slip events, the southernmost family is more active, with repeating events about once a month.
+Downdip families are also more active than up dip families.
 

### 2020-11-11 paper/supplement.tex
First draft of paper

\documentclass{article}
\usepackage[lmargin=1 in, rmargin=1 in, tmargin=1 in, bmargin=1 in]{geometry}
\usepackage{lineno}
\linenumbers

\begin{document}

\title{Supplementary Material}
\date{}
\maketitle

\begin{table}
\caption{Temporary stations used for the 2007-2009 catalog}
\centering
\begin{tabular}{c c c c c c c c c}
\hline
Station & Network & Channels & Location & Data center & Latitude & Longitude & Begin time & End time \\
\hline
B039 & PB & EH1,EH2,EHZ & -- & IRIS & 41.4667 & -122.4847 & 2007-10-15 & 3000-01-01 \\
KCPB & NC & HHE,HHN,HHZ & -- & NCEDC & 39.6863 & -123.5824 & 2002-10-17 & 3000-01-01 \\
KHBB & NC & HHE,HHN,HHZ & -- & NCEDC & 40.6599 & -123.2197 & 2003-09-11 & 3000-01-01 \\
KRMB & NC & HHE,HHN,HHZ & -- & NCEDC & 41.5230 & -123.9080 & 2001-06-16 & 3000-01-01 \\
KSXB & NC & HHE,HHN,HHZ & -- & NCEDC & 41.8304 & -123.8769 & 2001-07-13 & 3000-01-01 \\
ME01 & XQ & BHE,BHN,BHZ & 01 & IRIS & 41.7752 & -123.4034 & 2007-07-31 & 2009-06-12 \\
ME02 & XQ & BHE,BHN,BHZ & 01 & IRIS & 41.6898 & -122.3372 & 2007-07-22 & 2009-05-20 \\
ME03 & XQ & BHE,BHN,BHZ & 01 & IRIS & 41.702 & -123.881 & 2007-09-27 & 2009-06-13 \\
ME04 & XQ & BHE,BHN,BHZ & 01 & IRIS & 41.355 & -123.514 & 2007-07-23 & 2009-06-12 \\
ME08 & XQ & BHE,BHN,BHZ & 01 & IRIS & 40.222 & -123.305 & 2007-07-22 & 2009-06-03 \\
ME09 & XQ & BHE,BHN,BHZ & 01 & IRIS & 41.086 & -122.726 & 2007-07-21 & 2009-05-14 \\
ME10 & XQ & BHE,BHN,BHZ & 01 & IRIS & 40.9591 & -122.4619 & 2007-10-31 & 2009-06-12 \\
ME12 & XQ & BHE,BHN,BHZ & 01 & IRIS & 40.104 & -122.498 & 2007-07-20 & 2009-06-12 \\
ME13 & XQ & BHE,BHN,BHZ & 01 & IRIS & 40.764 & -122.918 & 2007-07-22 & 2009-06-12 \\
ME16 & XQ & BHE,BHN,BHZ & 01 & IRIS & 40.577 &  -122.087 & 2007-07-20 & 2008-10-14 \\
ME24 & XQ & BHE,BHN,BHZ & 01 & IRIS & 40.359 & -122.047 & 2007-07-19 & 2009-05-15 \\
ME26 & XQ & BHE,BHN,BHZ & 01 & IRIS & 40.157 & -122.099 & 2007-07-26 & 2009-02-17 \\
ME27 & XQ & BHE,BHN,BHZ & 01 & IRIS & 40.453 & -123.155 & 2008-01-01 & 2009-06-13 \\
ME28 & XQ & BHE,BHN,BHZ & 01 & IRIS & 40.327 & -122.471 & 2007-07-20 & 2009-05-14 \\
ME29 & XQ & BHE,BHN,BHZ & 01 & IRIS & 41.142 & -123.1408 & 2007-09-21 & 2009-06-13 \\
ME30 & XQ & BHE,BHN,BHZ & 01 & IRIS & 40.843 & -123.565 & 2007-07-24 & 2009-06-22 \\
ME42 & XQ & BHE,BHN,BHZ & 01 & IRIS & 39.7145 & -123.273 & 2007-07-15 & 2009-06-16 \\
ME43 & XQ & BHE,BHN,BHZ & 01 & IRIS & 39.5703 & -123.175 & 2007-09-16 & 2009-06-16 \\
ME44 & XQ & BHE,BHN,BHZ & 01 & IRIS & 39.4928 & -123.187 & 2007-09-16 & 2009-06-15 \\
ME45 & XQ & BHE,BHN,BHZ & 01 & IRIS & 39.4666 & -122.9595 & 2007-09-12 & 2009-06-09 \\
ME46 & XQ & BHE,BHN,BHZ & 01 & IRIS & 39.196 & -122.968 & 2007-09-25 & 2009-06-11 \\
ME47 & XQ & BHE,BHN,BHZ & 01 & IRIS & 39.1124 & -122.8106 & 2007-09-25 & 2008-09-17 \\
ME49 & XQ & BHE,BHN,BHZ & 01 & IRIS & 39.8633 & -123.7194 & 2007-09-25 & 2009-06-08 \\
ME52 & XQ & BHE,BHN,BHZ & 01 & IRIS & 39.3228 & -123.2191 & 2008-02-21 & 2009-07-08 \\
ME54 & XQ & BHE,BHN,BHZ & 01 & IRIS & 39.0132 & -123.3779 & 2007-09-24 & 2009-03-03 \\
ME57 & XQ & BHE,BHN,BHZ & 01 & IRIS & 39.9118 & -122.5676 & 2007-10-24 & 2009-06-11 \\
WDC & BK & BHE,BHN,BHZ & -- & NCEDC & 40.5799 & -122.5411 &1992-09-17 & 2011-05-06 \\
YBH &  BK & BHE,BHN,BHZ & -- & NCEDC & 41.7320 & -122.7104 & 1993-07-24 & 2011-06-03 \\
\hline
\end{tabular}
\end{table}

\begin{table}
\caption{Permanent stations used for the 2004-2011 catalog}
\centering
\begin{tabular}{c c c c c c c c c}
\hline
Station & Network & Channels & Location & Data center & Latitude & Longitude & Begin time & End time \\
\hline
B039 & PB & EH1,EH2,EHZ & -- & IRIS & 41.4667 &  -122.4847 & 2007-10-15 & 3000-01-01 \\
B040 & PB & EH1,EH2,EHZ & -- & IRIS & 41.8308 &  -122.4205 & 2007-10-16 & 3000-01-01 \\
B933 & PB & EH1,EH2,EHZ & -- & IRIS & 40.0600 &  -123.9690 & 2008-09-13 & 3000-01-01 \\
B935 & PB & EH1,EH2,EHZ & -- & IRIS & 40.4787 &  -123.5732 & 2008-10-29 & 3000-01-01 \\
GASB & BK & BHE,BHN,BHZ & -- & NCEDC & 39.65471 & -122.71595 & 2005-09-22 & 2011-06-16 \\
GASB & BK & BHE,BHN,BHZ & 0 & NCEDC & 39.65471 & -122.71595 & 2011-06-16 & 3000-01-01 \\
GBB & NC & EHZ & -- & NCEDC & 39.80127 & -122.34550 & 2000-12-06 & 3000-01-01 \\
GHM & NC & EHZ & -- & NCEDC & 39.49545 & -122.93096 & 1984-01-01 & 3000-01-01 \\
GRO & NC & EHZ & -- & NCEDC & 39.91684 & -122.67117 & 1990-12-13 & 3000-01-01 \\
GSN & NC & EHZ & -- & NCEDC & 38.94040 & -123.19245 & 1984-01-01 & 2018-12-11 \\
GTC & NC & SHZ & -- & NCEDC & 39.39944 & -123.55532 & 1996-08-01 & 2011-10-27 \\
GVV & NC & EHZ & -- & NCEDC & 39.77510 & -122.67551 & 2002-04-28 & 3000-01-01 \\
HOPS & BK & BHE,BHN,BHZ & -- & NCEDC & 38.99349 & -123.07234 & 1994-10-21 & 2010-06-16 \\
HOPS & BK & BHE,BHN,BHZ & 0 & NCEDC & 38.99349 & -123.07234 & 2010-06-16 & 3000-01-01 \\
JCC & BK & BHE,BHN,BHZ & -- & NCEDC & 40.81745 & -124.02955 & 2001-04-11 & 2010-08-19 \\
JCC & BK & BHE,BHN,BHZ & 0 & NCEDC & 40.81745 & -124.02955 & 2010-08-19 & 3000-01-01 \\
KBN & NC & SHZ & -- & NCEDC & 39.89237 & -123.19503 & 1994-11-28 & 2011-10-27 \\
KBS & NC & SHZ & -- & NCEDC & 39.91719 & -123.59561 & 2002-10-17 & 2011-10-27 \\
KCPB & NC & HHE,HHN,HHZ & -- & NCEDC & 39.68631 & -123.58242 & 2002-10-17 & 3000-01-01 \\\
KCS & NC & SHZ & -- & NCEDC & 40.53791 & -123.51394 & 1994-11-28 & 2011-11-01 \\
KFP & NC & SHZ & -- & NCEDC & 39.63889 & -123.42514 & 1994-11-28 & 2011-10-27 \\
KHBB & NC & HHE,HHN,HHZ & -- & NCEDC & 40.65990 & -123.21966 & 2003-09-11 & 3000-01-01 \\
KHMB & NC & HHE,HHN,HHZ & -- & NCEDC & 40.87475 & -123.73259 & 2002-06-13 & 3000-01-01 \\
KIP & NC & SHZ & -- & NCEDC & 39.80841 & -123.48130 & 1994-11-28 & 2011-10-27 \\
KKP & NC & SHZ & -- & NCEDC & 40.14579 & -123.46965 & 1994-11-28 & 2011-11-01 \\
KOM & NC & SHZ & -- & NCEDC & 41.27872 & -123.45315 & 1994-11-28 & 2011-11-02 \\
KPP & NC & SHZ & -- & NCEDC & 40.34579 & -123.36328 & 1994-11-28 & 2011-11-01 \\
KRK & NC & SHZ & -- & NCEDC & 39.56315 & -123.18367 & 1994-11-28 & 2011-10-27 \\
KRMB & NC & HHE,HHN,HHZ & -- & NCEDC & 41.52296 & -123.90797 & 2001-06-16 & 3000-01-01 \\
KRP & NC & HHE,HHN,HHZ & -- & NCEDC & 41.15765 & -124.02330 & 2002-06-12 & 3000-01-01 \\
KSXB & NC & HHE,HHN,HHZ & -- & NCEDC & 41.83038 & -123.87688 & 2001-07-13 & 3000-01-01 \\
KTR & NC & SHZ & -- & NCEDC & 41.90847 & -123.37755 & 1994-11-28 & 2011-11-02 \\
LAM & NC & SHZ & -- & NCEDC & 41.60987 & -122.62559 & 1994-11-28 & 2011-09-30 \\
LBF & NC & SHZ & -- & NCEDC & 41.34707 & -121.89098 & 1994-11-28 & 2011-11-03 \\
LBK & NC & SHZ & -- & NCEDC & 41.08382 & -122.66731 & 1994-11-28 & 2011-12-08 \\
LBP & NC & SHZ & -- & NCEDC & 40.31671 & -122.88193 & 1994-11-28 & 2011-12-08 \\
LDB & NC & SHZ & -- & NCEDC & 40.43105 & -121.78632 & 1994-11-28 & 2011-12-08 \\
LGB & NC & SHZ & -- & NCEDC & 41.33418 & -122.18771 & 2001-10-20 & 2011-11-03 \\
LGP & NC & SHZ & -- & NCEDC & 40.91228 & -122.82949 & 1994-11-28 & 2011-12-08 \\
LPG & NC & SHZ & -- & NCEDC & 40.14514 & -122.68788 & 1994-11-28 & 2011-12-08 \\
LRB & NC & SHZ & -- & NCEDC & 40.14323 & -122.55772 & 1994-11-28 & 2011-12-08 \\
LRR & NC & SHZ & -- & NCEDC & 40.46630 & -121.62230 & 1994-11-28 & 2011-12-08 \\
LSF & NC & SHZ & -- & NCEDC & 40.65817 & -122.52371 & 1994-11-28 & 2011-12-08 \\
LSH & NC & SHZ & -- & NCEDC & 40.79294 & -122.03943 & 2002-03-28 & 2011-12-08 \\
LSR & NC & SHZ & -- & NCEDC & 41.10696 & -122.27062 & 1994-11-28 & 2011-12-08 \\
LTC & NC & SHZ & -- & NCEDC & 40.20842 & -122.12548 & 2002-03-28 & 2011-12-08 \\
LVR & NC & SHZ & -- & NCEDC & 40.03937 & -122.67250 & 1994-11-28 & 2011-12-08 \\
LWH & NC & SHZ & -- & NCEDC & 40.64180 & -121.94857 & 1994-11-28 & 2011-12-08 \\
WDC & BK & BHE,BHN,BHZ & -- & NCEDC & 40.57988 & -122.54113 & 1992-09-17 & 2011-05-06 \\
WDC & BK & BHE,BHN,BHZ & 0 & NCEDC & 40.57988 & -122.54113 & 2011-05-06 & 3000-01-01 \\
YBH & BK & BHE,BHN,BHZ & -- & NCEDC & 41.73204 & -122.71039 & 1993-07-24 & 2011-06-03 \\
YBH & BK & BHE,BHN,BHZ & 0 & NCEDC & 41.73204 & -122.71039 & 2011-06-03 & 3000-01-01 \\
\hline
\end{tabular}
\end{table}

\end{document}

### 2020-11-11 data/Ducellier/cumulative_LFEs.py

@@ -26,7 +26,7 @@ threshold = pd.read_csv('threshold_cc.txt', sep=r'\s{1,}', header=None, engine='
 threshold.columns = ['family', 'threshold_FAME', 'threshold_perm']
 
 # Loop on templates
-for i in range(0, np.shape(templates)[0]):
+for i in range(19, 20): #np.shape(templates)[0]):
 
     # Open LFE catalog (FAME data)
     namedir = 'catalogs/' + templates[i][0].astype(str)
@@ -78,5 +78,5 @@ for i in range(0, np.shape(templates)[0]):
     plt.ylabel('Normalized number of LFEs', fontsize=24)
     plt.title('Cumulative number of LFEs', fontsize=24)
     plt.legend(loc=4, fontsize=20)
-    plt.savefig('cumulative/' + templates[i][0].astype(str) + '.eps', format='eps')
+    plt.savefig('cumulative/' + templates[i][0].astype(str) + '.png', format='png')
     plt.close(1)

### 2020-11-11 data/Ducellier/plot_daily_LFEs_longitude.py

@@ -1,0 +1,106 @@
+"""
+This script looks at the catalog from southern Cascadia (2007-2009) and plots
+the hourly number of LFEs in function of time in function of latitude
+"""
+
+import matplotlib.pylab as pylab
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+import pickle
+
+from datetime import datetime, timedelta
+from math import floor
+
+params = {'legend.fontsize': 24, \
+          'xtick.labelsize':24, \
+          'ytick.labelsize':24}
+pylab.rcParams.update(params)
+
+# List of LFE families
+templates = np.loadtxt('../Plourde_2015/templates_list.txt', \
+    dtype={'names': ('name', 'family', 'lat', 'lon', 'depth', 'eH', \
+    'eZ', 'nb'), \
+         'formats': ('S13', 'S3', np.float, np.float, np.float, \
+    np.float, np.float, np.int)}, \
+    skiprows=1)
+
+# Threshold for filtering the catalog
+threshold = pd.read_csv('threshold_cc.txt', sep=r'\s{1,}', header=None, engine='python')
+threshold.columns = ['family', 'threshold_FAME', 'threshold_perm']
+
+# Beginning and end of the period we are looking at
+tbegin = datetime(2004, 1, 1, 0, 0, 0)
+tend = datetime(2012, 1, 1, 0, 0, 0)
+
+# We construct the time series by counting the number of LFEs
+# per one-day-long time window
+window = 86400.0
+
+# Length of the time series
+dt = tend - tbegin
+duration = dt.days * 86400.0 + dt.seconds + dt.microseconds * 0.000001
+nw = int(duration / window)
+
+# Amplitude coefficients
+amp = 0.005
+
+# Start figure
+plt.figure(1, figsize=(20, 10))
+
+# Loop on templates
+for i in [12, 13, 20, 23, 25]: #range(0, np.shape(templates)[0]):
+
+    # Plot only good data
+    if threshold['threshold_perm'].iloc[i] > 0.0:
+
+        # Get latitude
+        latitude = templates[i][2]
+        longitude = templates[i][3]
+
+        # Filter geography
+        if (latitude >= 40.2) and (latitude <= 40.8):
+            print(templates[i][0].astype(str))
+
+            # Open LFE catalog
+            namedir = 'catalogs/' + templates[i][0].astype(str)
+            namefile = namedir + '/catalog_2004_2011.pkl'
+            df = pickle.load(open(namefile, 'rb'))
+
[…]

### 2020-11-11 data/Ducellier/plot_nbLFEs_longitude.py

@@ -1,0 +1,93 @@
+"""
+Script to plot tremor and LFEs as a function of latitude
+"""
+
+import matplotlib.pylab as pylab
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+import pickle
+
+from math import floor
+
+from date import ymdhms2day
+
+# Time boundaries
+xmin = 2004.0
+xmax = 2012.0
+
+# Space boundaries
+lonmin = -123.1
+lonmax = -122.2
+
+# Start figure
+params = {'legend.fontsize': 24, \
+          'xtick.labelsize':24, \
+          'ytick.labelsize':24}
+pylab.rcParams.update(params)
+plt.figure(1, figsize=(20, 10))
+
+# List of LFE families
+templates = np.loadtxt('../Plourde_2015/templates_list.txt', \
+    dtype={'names': ('name', 'family', 'lat', 'lon', 'depth', 'eH', \
+    'eZ', 'nb'), \
+         'formats': ('S13', 'S3', np.float, np.float, np.float, \
+    np.float, np.float, np.int)}, \
+    skiprows=1)
+
+# Threshold for filtering the catalog
+threshold = pd.read_csv('threshold_cc.txt', sep=r'\s{1,}', header=None, engine='python')
+threshold.columns = ['family', 'threshold_FAME', 'threshold_perm']
+
+# Loop on templates
+for i in [12, 13, 20, 23, 25]: #range(0, np.shape(templates)[0]):
+
+    # Plot only good data
+    if threshold['threshold_perm'].iloc[i] > 0.0:
+
+        # Get latitude
+        latitude = templates[i][2]
+        longitude = templates[i][3]
+
+        # Filter geography
+        if (latitude >= 40.2) and (latitude <= 40.8):
+            print(templates[i][0].astype(str))
+
+            # Open LFE catalog
+            namedir = 'catalogs/' + templates[i][0].astype(str)
+            namefile = namedir + '/catalog_2004_2011.pkl'
+            df = pickle.load(open(namefile, 'rb'))
+
+            # Filter LFEs
+            df = df.loc[df['cc'] * df['nchannel'] >= threshold['threshold_perm'].iloc[i]]
+
+            time = np.arange(xmin, xmax, 1.0/365.5)
+            nbLFEs = np.zeros(np.shape(time)[0])
+            # Loop on LFEs
+            for j in range(0, len(df)):
[…]

### 2020-11-11 data/Ducellier/plot_several_families.py

@@ -1,0 +1,96 @@
+"""
+This script looks at the catalog from southern Cascadia (2007-2009) and plots
+for each family the daily number of LFEs in function of time
+"""
+
+import matplotlib.pylab as pylab
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+import pickle
+
+from datetime import datetime, timedelta
+from math import floor
+
+params = {'legend.fontsize': 24, \
+          'xtick.labelsize':24, \
+          'ytick.labelsize':24}
+pylab.rcParams.update(params)
+
+# List of LFE families
+templates = np.loadtxt('../Plourde_2015/templates_list.txt', \
+    dtype={'names': ('name', 'family', 'lat', 'lon', 'depth', 'eH', \
+    'eZ', 'nb'), \
+         'formats': ('S13', 'S3', np.float, np.float, np.float, \
+    np.float, np.float, np.int)}, \
+    skiprows=1)
+
+# Beginning and end of the period we are looking at
+tbegin = datetime(2004, 1, 1, 0, 0, 0)
+tend = datetime(2012, 1, 1, 0, 0, 0)
+
+# Threshold for filtering the catalog
+threshold = pd.read_csv('threshold_cc.txt', sep=r'\s{1,}', header=None, engine='python')
+threshold.columns = ['family', 'threshold_FAME', 'threshold_perm']
+
+# We construct the time series by counting the number of LFEs
+# per one-day-long time window
+window = 86400.0
+
+# Length of the time series
+dt = tend - tbegin
+duration = dt.days * 86400.0 + dt.seconds + dt.microseconds * 0.000001
+nw = int(duration / window)
+
+# Indices of LFE families
+indices = [12, 13, 25, 20, 23]
+#indices = [2, 5, 6]
+
+plt.figure(1, figsize=(16, 4 * len(indices)))
+
+# Loop on templates
+for (count, i) in enumerate(indices):
+    longitude = templates[i][3]
+
+    # Open LFE catalog
+    namedir = 'catalogs/' + templates[i][0].astype(str)
+    namefile = namedir + '/catalog_2004_2011.pkl'
+    df = pickle.load(open(namefile, 'rb'))
+
+    # Filter LFE
+    df = df.loc[df['cc'] * df['nchannel'] >= threshold['threshold_perm'].iloc[i]]
+
+    # Get time series
+    X = np.zeros(nw, dtype=int)
+    # Loop on LFEs
[…]

### 2020-11-11 data/Ducellier/plot_tremor_nbLFEs.py

@@ -61,6 +61,8 @@ for i in range(0, np.shape(templates)[0]):
         df = pickle.load(open(namefile, 'rb'))
 
         # Filter LFEs
+#        maxc = np.max(df['nchannel'])
+#        df = df.loc[df['cc'] * df['nchannel'] >= 0.1 * maxc]
         df = df.loc[df['cc'] * df['nchannel'] >= threshold['threshold_perm'].iloc[i]]
 
         time = np.arange(xmin, xmax, 1.0/365.5)
@@ -101,5 +103,5 @@ plt.xlabel('Time (years)', fontsize=24)
 plt.ylabel('Latitude', fontsize=24)
 plt.title('Tremor and LFEs', fontsize=24)
 plt.tight_layout()
-plt.savefig('LFEdistribution_perm/tremor_nb.eps', format='eps')
+plt.savefig('LFEdistribution_perm/tremor_nb.png', format='png')
 plt.close(1)

### 2020-11-11 paper/figures/plot_templates.py

@@ -26,5 +26,5 @@ for (i, channel) in enumerate(channels):
     plt.title('{} - {}'.format(station, channel), fontsize=20)
     plt.xlabel('Time (s)', fontsize=20)
 plt.tight_layout()
-plt.savefig('templates.eps', format='eps')
+plt.savefig('templates.png', format='png')
 plt.close(1)

### 2021-07-10 paper/agujournaltemplate.tex
Compute tidal stress

@@
 It is known than tectonic tremor can be triggered by surface waves from distant and regional earthquakes, as has been observed in Cascadia ~\cite{RUB_2009}, the San Andreas ~\cite{PEN_2009, GUI_2010}, and Nankai ~\cite{HAN_2014}.
-Low-frequency earthquake activity on the San Andreas fault also increased during several months after the 2004 Parafield earthquake ~\cite{SHE_2017}.
-We looked for regional earthquakes with magnitude higher than 5 during the period covered by the catalog to verify whether this phenomenon is also verified in southern Cascadia.
+Low-frequency earthquake activity on the San Andreas fault also increased during several months after the 2004 Parkfield earthquake ~\cite{SHE_2017}.
+We looked for regional earthquakes with magnitude higher than 5 during the period covered by the catalog to verify whether this phenomenon is also observed in southern Cascadia.
 The characteristics of the earthquakes we looked at are given in Table 1.
+We also looked at distant earthquakes with large magnitude, which  characteristics are given in Table 2.
 
@@
 
+\begin{table}
+\caption{Teleseismic earthquakes between 2004 and 2011}
+\centering
+\begin{tabular}{c c c c c}
+\hline
+Magnitude & Time & Latitude & Longitude & Depth (km) \\
+\hline
+9.1 & 2011-03-11 05:46:24 & 38.297N & 142.373E & 29.0 \\
+9.1 & 2004-12-26 00:58:53 & 3.295N & 95.982E & 30.0 \\
+8.8 & 2010-02-27 06:34:11 & 36.122S & 72.898W & 22.9 \\ 
+8.6 & 2005-03-28 16:09:36 & 2.085N & 97.108E & 30.0 \\ 
+7.9 & 2008-05-12 06:28:01 & 31.002N & 103.322E & 19.0 \\ 
+\hline
+\end{tabular}
+\end{table}
+
 Although we observe an increase in LFE activity for some families several days after the earthquakes (except the 2008 one where no activity is observed after the earthquake), it does not seem that this activity is linked to the earthquake.
@@
 Indeed, for the Parkfield earthquake, an increase in LFE activity was observed for LFE families up to 45km away from the epicenter, but not farther away.
+Moreover, the Parkfield earthquake was more shallower (8.1km deep) than the regional earthquakes used in this study.
+For the 2003 M6.5 San Simeon earthquake, no increase in LFE activity in the San Andreas LFE families was observed in the hours following the earthquake.
+This was also a shallow earthquake (8.4km deep) but the epicenter was farther away from the LFE families (60 to 100 km).
 For southern Cascadia, the closest epicenter (2008) is located 50 km away from the closest LFE families.
+Based on what was observed for the San Andreas LFE families, this distance may be too large for a regional earthquake to trigger an increase in LFE activity.
+We do not see any change in LFE activity after the large teleseismic earthquakes.
+There was not any change in LFE activity for the San Andreas LFE families either.
 \\

### 2021-07-10 src/get_tidal_stress.py

@@ -1,0 +1,52 @@
+"""
+Script to read tidal stress file from H. Houston and
+interpolate the values at the LFE locations
+"""
+
+import numpy as np
+import pickle
+
+from math import cos, pi, sin, sqrt
+from scipy.io import loadmat
+
+# Earth's radius and ellipticity
+a = 6378.136
+e = 0.006694470
+
+# List of LFE families
+templates = np.loadtxt('../data/Plourde_2015/templates_list.txt', \
+    dtype={'names': ('name', 'family', 'lat', 'lon', 'depth', 'eH', \
+    'eZ', 'nb'), \
+         'formats': ('S13', 'S3', np.float, np.float, np.float, \
+    np.float, np.float, np.int)}, \
+    skiprows=1)
+
+# Read tidal stress file
+data = loadmat('../data/For_Ken_California_LFE/stressonfp_4Ken_extended.mat')
+xmnr = data['xmnr']
+ymnr = data['ymnr']
+
+# Loop on templates
+for i in range(0, np.shape(templates)[0]):
+
+    lat0 = templates[i][2]
+    lon0 = templates[i][3]
+    dx = (pi / 180.0) * a * cos(lat0 * pi / 180.0) / sqrt(1.0 - e * e * \
+        sin(lat0 * pi / 180.0) * sin(lat0 * pi / 180.0))
+    dy = (3.6 * pi / 648.0) * a * (1.0 - e * e) / ((1.0 - e * e * sin(lat0 * \
+        pi / 180.0) * sin(lat0 * pi / 180.0)) ** 1.5)
+    x = (xmnr - lon0) * dx
+    y = (ymnr - lat0 ) * dy
+    dist = np.sqrt(np.power(x, 2.0) + np.power(y, 2.0))
+    closest_dists = np.sort(dist, axis=None)[0:4]
+    indices = np.argsort(dist, axis=None)[0:4]
+    indices = np.unravel_index(indices, dist.shape)
+    ind1 = indices[0]
+    ind2 = indices[1]
+    weights = np.reshape(closest_dists / np.sum(closest_dists), (4, 1))
+    norm = np.sum(weights * data['gridnorm'][ind1, ind2, :], axis=0)
+    shear = np.sum(weights * data['gridshear'][ind1, ind2, :], axis=0)
+    vol = np.sum(weights * data['gridvol'][ind1, ind2, :], axis=0)
+    time = data['tvec']
[…]

### 2021-07-10 src/tidal_stress.py
Plot tidal stress

@@ -17,9 +17,6 @@ pylab.rcParams.update(params)
 # Number of boxes for plotting
 nbox = 20
 
-# Tidal stress file
-data = loadmat('../data/For_Ken_California_LFE/LFEs2.mat')
-
 # List of LFE families
 templates = np.loadtxt('../data/Plourde_2015/templates_list.txt', \
     dtype={'names': ('name', 'family', 'lat', 'lon', 'depth', 'eH', \
@@ -39,15 +36,13 @@ for i in range(0, np.shape(templates)[0]):
     # Look only at good data
     if threshold['threshold_perm'].iloc[i] > 0.0:
 
-        # Look for corresponding location of tidal stress
-        latitude = templates[i][2]
-        longitude = templates[i][3]
-        for k in range(0, len(data['LFE']['TempLabel'][0][0])):
-            if ((data['LFE']['lat'][0][0][k] == latitude) & \
-                (data['LFE']['lon'][0][0][k] == longitude)):
-                namefile = data['LFE']['TempLabel'][0][0][k][0][0]
-                j = k
-        print(templates[i][0].astype(str), namefile, i, j)
+        # Load data
+        filename = '../data/tidal_stress/' + templates[i][0].astype(str) + '.pkl'
+        tidal_stress = pickle.load(open(filename, 'rb'))
+        time = tidal_stress[0]
+        norm = tidal_stress[1]
+        shear = tidal_stress[2]
+        vol = tidal_stress[3]
 
         # Open LFE catalog
         namedir = '../data/Ducellier/catalogs/' + templates[i][0].astype(str)
@@ -70,72 +65,97 @@ for i in range(0, np.shape(templates)[0]):
         df['date'] = date
 
         # Look for value of tidal stress at the time of each LFE 
-        shear = np.repeat(np.nan, len(df))
-        norm = np.repeat(np.nan, len(df))
-        vol = np.repeat(np.nan, len(df))
+        shear_LFE = np.repeat(np.nan, len(df))
+        norm_LFE = np.repeat(np.nan, len(df))
+        vol_LFE = np.repeat(np.nan, len(df))
         for k in range(len(df)):
-            indices = np.where(24 * 4 * np.abs(data['LFE']['tvec'][0][0][0, j] - df.date.loc[k]) <= 1)[1]
[…]

### 2021-07-15 paper/agujournaltemplate.tex
Remake map

@@
 We also added 74 \% more LFEs to the catalog, but most of added LFEs have a low cross-correlation value and may be false detections.
-Figure 2 shows the cross-correlation values for the LFEs in the original catalog, and for the LFEs that we added to the catalog for family \textcolor{red}{080413.07.023}.
+Figure 2 shows the cross-correlation values for the LFEs in the original catalog, and for the LFEs that we added to the catalog for family B (inverted triangle in Figure 1).
 
@@
 \noindent\includegraphics[width=\textwidth, trim={7.5cm 1cm 28cm 2cm},clip]{figures/hist.eps}
-\caption{Cross-correlation values for LFEs added in the catalog for family \textcolor{red}{080413.07.023} (left) and cross-correlation values for LFEs in the original catalog from ~\citeA{PLO_2015} (right).
+\caption{Cross-correlation values for LFEs added in the catalog for family B (inverted triangle in Figure 1) (left) and cross-correlation values for LFEs in the original catalog from ~\citeA{PLO_2015} (right).
 There were no missing LFEs for this family.}
@@
 Only nine families have four or less seismic stations with good templates.
-Examples of templates are given in Figure 4 for station WDC and family \textcolor{red}{080401.05.050}.
+Examples of templates are given in Figure 4 for station WDC and family A (square in Figure 1).
 To obtain the above catalog, we used one-minute-long templates, which included noise before and after the seismic wave arrivals.
@@
 \noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/templates.eps}
-\caption{Low-frequency earthquake template for station WDC and family \textcolor{red}{080401.05.050} for the three channels BHE, BHN and BHZ (left to right).
+\caption{Low-frequency earthquake template for station WDC and family A (square in Figure 1) for the three channels BHE, BHN and BHZ (left to right).
 We can clearly see a P-wave arrival and an S-wave arrival about 7 seconds later.
@@
 We then compared the normalized number of LFEs obtained with the two catalogs.
-Examples are given in Figures 5 and 6 for families \textcolor{red}{080413.07.023} and \textcolor{red}{080401.05.050}.
-Although the number of LFEs during each event may not be the same, we clearly see for family \textcolor{red}{080413.07.023} that the timing of the events are the same for both catalogs.
-Family \textcolor{red}{080401.05.050} is much more active but most events seem to be present in both catalogs as well.
+Examples are given in Figures 5 and 6 for families B (inverted triangle in Figure 1) and A (square in Figure 1).
+Although the number of LFEs during each event may not be the same, we clearly see for family B that the timing of the events are the same for both catalogs.
+Family A is much more active but most events seem to be present in both catalogs as well.
 
@@
 \noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/080413_07_023.eps}
-\caption{Normalize cumulative number of LFEs over the period July 2007-July 2009 for the FAME catalog (red) and the network catalog (blue) for family \textcolor{red}{080413.07.023}.}
+\caption{Normalize cumulative number of LFEs over the period July 2007-July 2009 for the FAME catalog (red) and the network catalog (blue) for family B (inverted triangle in Figure 1).}
 \label{pngfiguresample}
@@
 \noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/080401_05_050.eps}
-\caption{Normalize cumulative number of LFEs over the period July 2007-July 2009 for the FAME catalog (red) and the network catalog (blue) for family \textcolor{red}{080401.05.050}.}
+\caption{Normalize cumulative number of LFEs over the period July 2007-July 2009 for the FAME catalog (red) and the network catalog (blue) for family A (square in Figure 1).}
 \label{pngfiguresample}
@@
 
-Finally, we want to verify whether we can an increase of lFE activity for the downdip LFE families compared to the updip LFE families.
+In northern Cascadia, it has been observed that there is an increase in activity downdip of the plate boundary compared to up dip, both for tremor ~\cite{WEC_2011} and LFEs ~\cite{SWE_2019}.
+We want to verify whether we can an increase of LFE activity for the downdip LFE families compared to the updip LFE families.
 Most families in the northern and central part of the study area are well aligned along the strike direction, however families in the southern part of the subduction zone are more distant from each other.
-We first look at five families aligned at latitude about 40.7N and show the number of LFEs per day in Figure 8.
-We then look at three families aligned at latitude about 40.4N and show the number of LFEs per day in Figure 9.
+We first look at five families aligned at latitude about 40.7N (group D, diamonds in Figure 1) and show the number of LFEs per day in Figure 8.
+We then look at three families aligned at latitude about 40.4N (group C, triangles in Figure 1) and show the number of LFEs per day in Figure 9.
 For both sets of families, LFE events are more frequent for the easternmost family than for the westernmost family, as was also the case in northern Cascade ~\cite{SWE_2019}.
@@
 \noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/set1_daily_LFEs.eps}
-\caption{Daily number of LFEs over the period 2004-2011 for five LFE families aligned at about 40.7N.}
+\caption{Daily number of LFEs over the period 2004-2011 for the five LFE families in group D (diamonds in Figure 1).}
 \label{pngfiguresample}
@@
 \noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/set2_daily_LFEs.eps}
-\caption{Daily number of LFEs over the period 2004-2011 for three LFE families aligned at about 40.4N.}
+\caption{Daily number of LFEs over the period 2004-2011 for the three LFE families in group C (triangles in Figure 1).}
 \label{pngfiguresample}
@@
 The authors would like to thank A.
-Plourde for sharing his low-frequency earthquake catalog.
+Plourde for sharing his low-frequency earthquake catalog, and D.
+Boyarko for sharing his tremor catalog.
 This project was funded by NSF grant XXX.
@@
 The seismic recordings used for this analysis can be downloaded from the IRIS and NCEDC websites.
+The first figure was done using GMT ~\cite{WES_1991}.
+The Python scripts used to analyze the data and make the figures can be found on the first author's Github account \url{https://github.com/ArianeDucellier/catalog}.
 

### 2021-07-15 data/Ducellier/plot_several_families.py

@@ -43,8 +43,12 @@ duration = dt.days * 86400.0 + dt.seconds + dt.microseconds * 0.000001
 nw = int(duration / window)
 
 # Indices of LFE families
-indices = [12, 13, 25, 20, 23]
-#indices = [2, 5, 6]
+#indices = [12, 13, 25, 20, 23]
+indices = [2, 5, 6]
+
+# Names of LFE families
+#names = ['D1', 'D2', 'D3', 'D4', 'D5']
+names = ['C1', 'C2', 'C3']
 
 plt.figure(1, figsize=(16, 4 * len(indices)))
 
@@ -88,9 +92,9 @@ for (count, i) in enumerate(indices):
     plt.xlim([-0.5, len(X) - 0.5])
     plt.xlabel('Time (days) since 2004/01/01', fontsize=24)
     plt.ylabel('Number of LFEs', fontsize=24)
-    plt.title('Family {} at {}'.format(templates[i][0].astype(str), longitude), \
+    plt.title('Family {} at {}'.format(names[count], longitude), \
         fontsize=24)
 
 plt.tight_layout()
-plt.savefig('LFEdistribution_perm/set1_daily_LFEs.png', format='png')
+plt.savefig('LFEdistribution_perm/set2_daily_LFEs.eps', format='eps')
 plt.close(1)

### 2021-07-17 paper/agujournaltemplate.tex
Add abstarct to paper

@@
 \begin{keypoints}
-\item enter point 1 here
-\item enter point 2 here
-\item enter point 3 here
+\item We establish an eight-year-long low-frequency earthquake catalog for southern Cascadia.
+\item Families from the subduction zone are mainly active during the big tremor events, with down dip families more active than up dip families.
+\item The southernmost family is more active and sensitive to tidal stress changes.
 \end{keypoints}
@@
 \begin{abstract}
-enter abstract here
-
+Low-frequency earthquakes (LFEs) are small magnitude earthquakes, with typical magnitude less than 2, and reduced amplitudes at frequencies greater than 10 Hz relative to ordinary small earthquakes.
+Their occurrence is often associated with tectonic tremor and slow slip events along the plate boundary in subduction zones and occasionally transform fault zones.
+They are usually grouped into families of events, with all the earthquakes of a given family originating from the same small patch on the plate interface and recurring more or less episodically in a bursty manner.
+In this study, we extend the LFE catalog obtained by Plourde et al.
+(2015) during an episode of high tremor activity in April 2008, to the period 2004-2011.
+LFE activity is well correlated with tremor activity.
+Down dip families are more active than up dip families.
+The southernmost LFE family is also very active, and sensitive to tidal stress changes.
 \end{abstract}
@@
 These event histories have allowed scientists to see complete event cycles, which is typically not possible to explore in traditional earthquake catalogs.
-However, most of the work on low-frequency earthquakes (LFEs) has been focused on detecting LFEs during periods of high tremor activity, grouping them into families of events, and locating the source of the LFE families.
+However, most of the work on LFEs has been focused on detecting LFEs during periods of high tremor activity, grouping them into families of events, and locating the source of the LFE families.
 Longer catalogs (several years) have been established for LFE families in Mexico (two-year long catalog by ~\citeA{FRA_2014}), the San Andreas Fault (fifteen-year-long catalog by ~\citeA{SHE_2017}), Washington State (five-year-long catalog by ~\citeA{SWE_2019} and two-year-long catalog by ~\citeA{CHE_2017_JGR, CHE_2017_G3}), New Zealand (eight-year-long catalog by ~\citeA{BAR_2018}), and Japan (twelve-year-long catalog by ~\citeA{NAK_2017} and eight-year-long catalog by ~\citeA{OHT_2017}).
@@
 We then use these templates to extend the catalog to the whole period when the FAME experiment was running, between July 2007 and June 2009.
-Next, we use the LFEs detections from the 2007-2009 periods to create templates for the permanent stations of three seismic network in northern California.
+Next, we use the LFEs detections from the 2007-2009 period to create templates for the permanent stations of three seismic networks in northern California.
 These new templates allow us to extend the LFE catalog to the period 2004-2011.
@@
 Figure 2 shows the cross-correlation values for the LFEs in the original catalog, and for the LFEs that we added to the catalog for family B (inverted triangle in Figure 1).
+\\
 
@@
 We then used this new, shorter templates for the permanent stations to make an LFE catalog for the period 2007-2009.
+\\
 
@@
 Family A is much more active but most events seem to be present in both catalogs as well.
+\\
 
@@
 \noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/080413_07_023.eps}
-\caption{Normalize cumulative number of LFEs over the period July 2007-July 2009 for the FAME catalog (red) and the network catalog (blue) for family B (inverted triangle in Figure 1).}
+\caption{Normalized cumulative number of LFEs over the period July 2007-July 2009 for the FAME catalog (red) and the network catalog (blue) for family B (inverted triangle in Figure 1).}
 \label{pngfiguresample}
@@
 \noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/080401_05_050.eps}
-\caption{Normalize cumulative number of LFEs over the period July 2007-July 2009 for the FAME catalog (red) and the network catalog (blue) for family A (square in Figure 1).}
+\caption{Normalized cumulative number of LFEs over the period July 2007-July 2009 for the FAME catalog (red) and the network catalog (blue) for family A (square in Figure 1).}
 \label{pngfiguresample}
@@
 In the following, we focus on the period 2004-2011.
-In November 2011, several one-component stations stopped recording and the number of available stations started decreasing, each is why we did not look for LFEs event after that date.
+In November 2011, several one-component stations stopped recording and the number of available stations started decreasing, which is why we did not look for LFEs event after that date.
 The resulting LFE catalog for the period 2004-2011 is shown in Figure 7.
 For comparison, we also plotted the tremor detection times from ~\citeA{BOY_2015}.
+\\
 
@@
 We also looked at distant earthquakes with large magnitude, which  characteristics are given in Table 2.
+\\
 
@@
 In northern Cascadia, it has been observed that there is an increase in activity downdip of the plate boundary compared to up dip, both for tremor ~\cite{WEC_2011} and LFEs ~\cite{SWE_2019}.
-We want to verify whether we can an increase of LFE activity for the downdip LFE families compared to the updip LFE families.
+We want to verify whether we can see an increase of LFE activity for the downdip LFE families compared to the updip LFE families.
 Most families in the northern and central part of the study area are well aligned along the strike direction, however families in the southern part of the subduction zone are more distant from each other.
@@
 We then look at three families aligned at latitude about 40.4N (group C, triangles in Figure 1) and show the number of LFEs per day in Figure 9.
-For both sets of families, LFE events are more frequent for the easternmost family than for the westernmost family, as was also the case in northern Cascade ~\cite{SWE_2019}.
+For both sets of families, LFE events are more frequent for the easternmost family than for the westernmost family, as was also the case in northern Cascadia ~\cite{SWE_2019}.
 It is more difficult to compare event size and swarm duration as the number of stations and the quality of the templates are different from each family, and may have a strong influence on the number of LFEs detected.
+\\
 
@@
 
+The occurrence and amplitude of tectonic tremor can be modulated by small stress changes (about 1 kPa) associated with ocean or solid earth tides ~\cite{HOU_2015}.
+Sensitivity of LFE families activity to tidal stress changes has also been observed in northern Cascadia ~\cite{ROY_2015}, and on the San Andreas fault ~\cite{THO_2012}.
+We used calculated stresses from elastic deformations due to both water loads and bodily tides in the solid Earth along the Cascadia subduction zone (H.
+Houston, personal communication).
+The stress computation is done following the method described in ~\citeA{HOU_2015}.
+The resulting full stress tensors are projected to normal and shear (in the plate convergence direction) stresses on the interface, as well as mean stress (one-third the tensor trace).
+We then divided the values of tidal stress change into 20 stress bins and computed for each LFE family the number of LFEs occurring at a time when the value of the stress was in a given bin.
+We also computed what would be the expected number of LFEs occurring if the tidal stress changes have no influence on LFE activity.
+For most LFE families, we did not notice any evidence of influence of tidal stress on LFE activity.
+However, the LFE activity on family A seems to be correlated with tidal stress changes.
+Figure 10 shows the number of LFEs occurring during each stress bin (blue bars) and the expected number of LFEs (black line) for shear, normal, and mean stress.
+We also normalized the number of LFEs by the time during which the stress takes values in each bin.
+We note that LFE activity is triggered by negative shear stress and positive normal stress.
+This sensitivity of LE activity to tidal stress changes may explain while this family is much more active than the other families on the subduction zone.
+
+\begin{figure}
+\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/tidal_stress.eps}
+\caption{Left: Number of LFEs for family A (square in Figure 1) observed (blue bars) and expected (black line) for each stress bin for shear (top), normal (middle) and mean (bottom) tidal stress change.
+Right: Normalized number of LFEs observed (blue bars) and expected (black line).
+As the number of LFEs is normalized by the time spent in each stress bin, the expected number of LFEs is constant.}
+\label{pngfiguresample}
+\end{figure}
+
 \section{Conclusion}
@@
 Downdip families are also more active than up dip families.
+Tidal stress changes seem to be correlated with LFE activity on the southernmost family, which may explain why it is more active.
 
@@
 The authors would like to thank A.
-Plourde for sharing his low-frequency earthquake catalog, and D.
-Boyarko for sharing his tremor catalog.
+Plourde for sharing his low-frequency earthquake catalog, D.
+Boyarko for sharing his tremor catalog, and H.
+Houston for the tidal stress calculation in the Cascadia subduction zone.
 This project was funded by NSF grant XXX.

### 2021-07-27 paper/agujournaltemplate.tex
Update figures

@@
 We then compared the normalized number of LFEs obtained with the two catalogs.
-Examples are given in Figures 5 and 6 for families B (inverted triangle in Figure 1) and A (square in Figure 1).
+Examples are given in Figures 5 and 6 for families A (square in Figure 1) and B (inverted triangle in Figure 1).
 Although the number of LFEs during each event may not be the same, we clearly see for family B that the timing of the events are the same for both catalogs.
@@
 \begin{figure}
-\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/080413_07_023.eps}
-\caption{Normalized cumulative number of LFEs over the period July 2007-July 2009 for the FAME catalog (red) and the network catalog (blue) for family B (inverted triangle in Figure 1).}
+\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/080401_05_050.eps}
+\caption{Normalized cumulative number of LFEs over the period July 2007-July 2009 for the FAME catalog (red) and the network catalog (blue) for family A (square in Figure 1).
+The cumulative number of LFEs has been divided by the total number of LFEs so that both curves start at 0 and end at 1, in order to get a better match between the LFE bursts in both catalogs.}
 \label{pngfiguresample}
@@
 \begin{figure}
-\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/080401_05_050.eps}
-\caption{Normalized cumulative number of LFEs over the period July 2007-July 2009 for the FAME catalog (red) and the network catalog (blue) for family A (square in Figure 1).}
+\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/080413_07_023.eps}
+\caption{Normalized cumulative number of LFEs over the period July 2007-July 2009 for the FAME catalog (red) and the network catalog (blue) for family B (inverted triangle in Figure 1).
+The cumulative number of LFEs has been divided by the total number of LFEs so that both curves start at 0 and end at 1, in order to get a better match between the LFE bursts in both catalogs.}
 \label{pngfiguresample}
@@
 Most families in the northern and central part of the study area are well aligned along the strike direction, however families in the southern part of the subduction zone are more distant from each other.
-We first look at five families aligned at latitude about 40.7N (group D, diamonds in Figure 1) and show the number of LFEs per day in Figure 8.
-We then look at three families aligned at latitude about 40.4N (group C, triangles in Figure 1) and show the number of LFEs per day in Figure 9.
-For both sets of families, LFE events are more frequent for the easternmost family than for the westernmost family, as was also the case in northern Cascadia ~\cite{SWE_2019}.
+We first look at three families aligned at latitude about 40.4N (group C, triangles in Figure 1) and show the number of LFEs per day in Figure 8.
+We then look at five families aligned at latitude about 40.7N (group D, diamonds in Figure 1) and show the number of LFEs per day in Figure 9.
+Finally, we look at five families aligned at latitude about 41.05N (group E, pentagons in Figure 1) and show the number of LFEs per day in Figure 10.
+For all three sets of families, LFE events are more frequent for the easternmost family than for the westernmost family, as was also the case in northern Cascadia ~\cite{SWE_2019}.
 It is more difficult to compare event size and swarm duration as the number of stations and the quality of the templates are different from each family, and may have a strong influence on the number of LFEs detected.
@@
 \noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/set1_daily_LFEs.eps}
+\caption{Daily number of LFEs over the period 2004-2011 for the three LFE families in group C (triangles in Figure 1).}
+\label{pngfiguresample}
+\end{figure}
+
+\begin{figure}
+\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/set2_daily_LFEs.eps}
 \caption{Daily number of LFEs over the period 2004-2011 for the five LFE families in group D (diamonds in Figure 1).}
@@
 \begin{figure}
-\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/set2_daily_LFEs.eps}
-\caption{Daily number of LFEs over the period 2004-2011 for the three LFE families in group C (triangles in Figure 1).}
+\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/set3_daily_LFEs.eps}
+\caption{Daily number of LFEs over the period 2004-2011 for the five LFE families in group E (pentagons in Figure 1).}
 \label{pngfiguresample}
@@
 However, the LFE activity on family A seems to be correlated with tidal stress changes.
-Figure 10 shows the number of LFEs occurring during each stress bin (blue bars) and the expected number of LFEs (black line) for shear, normal, and mean stress.
+Figure 11 shows the number of LFEs occurring during each stress bin (blue bars) and the expected number of LFEs (black line) for shear, normal, and mean stress.
 We also normalized the number of LFEs by the time during which the stress takes values in each bin.

### 2021-07-27 data/Ducellier/cumulative_LFEs.py

@@ -26,7 +26,7 @@ threshold = pd.read_csv('threshold_cc.txt', sep=r'\s{1,}', header=None, engine='
 threshold.columns = ['family', 'threshold_FAME', 'threshold_perm']
 
 # Loop on templates
-for i in range(19, 20): #np.shape(templates)[0]):
+for i in range(0, np.shape(templates)[0]):
 
     # Open LFE catalog (FAME data)
     namedir = 'catalogs/' + templates[i][0].astype(str)
@@ -54,14 +54,16 @@ for i in range(19, 20): #np.shape(templates)[0]):
     cum_FAME = np.zeros(nb_days)
     cum_perm = np.zeros(nb_days)
     for j in range(0, nb_days):
-        df_sub = df_FAME[df_FAME['date'] < tbegin + timedelta(j + 1)]
+        df_sub = df_FAME[(df_FAME['date'] >= tbegin) & (df_FAME['date'] < tbegin + timedelta(j + 1))]
         cum_FAME[j] = len(df_sub)
-        df_sub = df_perm[df_perm['date'] < tbegin + timedelta(j + 1)]
+        df_sub = df_perm[(df_perm['date'] >= tbegin) & (df_perm['date'] < tbegin + timedelta(j + 1))]
         cum_perm[j] = len(df_sub)
 
     # Normalize
-    cum_FAME = cum_FAME / np.max(cum_FAME)
-    cum_perm = cum_perm / np.max(cum_perm)
+    nb_FAME = int(np.max(cum_FAME))
+    nb_perm = int(np.max(cum_perm))
+    cum_FAME = cum_FAME / nb_FAME
+    cum_perm = cum_perm / nb_perm
 
     # Plot
     params = {'legend.fontsize': 24, \
@@ -69,14 +71,13 @@ for i in range(19, 20): #np.shape(templates)[0]):
               'ytick.labelsize':24}
     pylab.rcParams.update(params)
     plt.figure(1, figsize=(10, 10))
-    plt.plot(np.arange(0, nb_days), cum_FAME, 'r-', label='FAME ({:d} LFEs)'.format(len(df_FAME)))
-    plt.plot(np.arange(0, nb_days), cum_perm + 0.1, 'b-', label='networks ({:d} LFEs)'.format(len(df_perm)))
+    plt.plot(np.arange(0, nb_days), cum_FAME, 'r-', label='FAME ({:d} LFEs)'.format(nb_FAME))
[…]

### 2021-07-27 data/Ducellier/plot_several_families.py

@@ -43,12 +43,16 @@ duration = dt.days * 86400.0 + dt.seconds + dt.microseconds * 0.000001
 nw = int(duration / window)
 
 # Indices of LFE families
+#indices = [2, 5, 6]
 #indices = [12, 13, 25, 20, 23]
-indices = [2, 5, 6]
+#indices = [40, 29, 33, 36, 41]
+indices = [0, 2, 12, 40]
 
 # Names of LFE families
+#names = ['C1', 'C2', 'C3']
 #names = ['D1', 'D2', 'D3', 'D4', 'D5']
-names = ['C1', 'C2', 'C3']
+#names = ['E1', 'E2', 'E3', 'E4', 'E5']
+names = ['A', 'C1', 'D1', 'E1']
 
 plt.figure(1, figsize=(16, 4 * len(indices)))
 
@@ -88,13 +92,13 @@ for (count, i) in enumerate(indices):
     # Plot figure
     plt.subplot2grid((len(indices), 1), (count, 0))
     plt.plot((1, 1))
-    plt.stem(np.arange(0, len(X)), X, 'k-', markerfmt=' ', basefmt=' ')
-    plt.xlim([-0.5, len(X) - 0.5])
-    plt.xlabel('Time (days) since 2004/01/01', fontsize=24)
+    plt.stem(2004 + np.arange(0, len(X)) / 365.25, X, 'k-', markerfmt=' ', basefmt=' ')
+    plt.xlim([2004, 2012])
+    plt.xlabel('Time (years)', fontsize=24)
     plt.ylabel('Number of LFEs', fontsize=24)
     plt.title('Family {} at {}'.format(names[count], longitude), \
         fontsize=24)
 
 plt.tight_layout()
-plt.savefig('LFEdistribution_perm/set2_daily_LFEs.eps', format='eps')
+plt.savefig('LFEdistribution_perm/set4_daily_LFEs.eps', format='eps')
 plt.close(1)

### 2021-07-27 data/Ducellier/plot_tremor_nbLFEs.py

@@ -13,8 +13,8 @@ from math import floor
 from date import ymdhms2day
 
 # Time boundaries
-xmin = 2004.0
-xmax = 2012.0
+xmin = 2007.5
+xmax = 2009.5
 
 # Space boundaries
 latmin = 39.4
@@ -50,20 +50,20 @@ threshold.columns = ['family', 'threshold_FAME', 'threshold_perm']
 for i in range(0, np.shape(templates)[0]):
 
     # Plot only good data
-    if threshold['threshold_perm'].iloc[i] > 0.0:
+    if threshold['threshold_FAME'].iloc[i] > 0.0:
 
         # Get latitude
         latitude = templates[i][2]
 
         # Open LFE catalog
         namedir = 'catalogs/' + templates[i][0].astype(str)
-        namefile = namedir + '/catalog_2004_2011.pkl'
+        namefile = namedir + '/catalog_2007_2009.pkl'
         df = pickle.load(open(namefile, 'rb'))
 
         # Filter LFEs
 #        maxc = np.max(df['nchannel'])
 #        df = df.loc[df['cc'] * df['nchannel'] >= 0.1 * maxc]
-        df = df.loc[df['cc'] * df['nchannel'] >= threshold['threshold_perm'].iloc[i]]
+        df = df.loc[df['cc'] * df['nchannel'] >= threshold['threshold_FAME'].iloc[i]]
 
         time = np.arange(xmin, xmax, 1.0/365.5)
         nbLFEs = np.zeros(np.shape(time)[0])
@@ -82,19 +82,19 @@ for i in range(0, np.shape(templates)[0]):
                 nbLFEs[index] = nbLFEs[index] + 1
 
         # Plot LFEs
-        time = time[nbLFEs > 0]
-        nbLFEs = nbLFEs[nbLFEs > 0]
+        time = time[nbLFEs > 1]
+        nbLFEs = nbLFEs[nbLFEs > 1]
         plt.scatter(time, np.repeat(latitude, np.shape(time)[0]), s=1 + nbLFEs * 5, c='k')
 #        plt.scatter(time, np.repeat(latitude, np.shape(time)[0]), c=nbLFEs, cmap='autumn')
 
 # Plot time line
-#tbegin = ymdhms2day(2007, 9, 25, 0, 0, 0)
-#tend = ymdhms2day(2009, 5, 14, 0, 0, 0)
[…]

### 2021-08-05 paper/agujournaltemplate.tex
Last version fo paper

@@
 
-\journalname{Geophysical Research Letters}
+\journalname{JGR: Solid Earth}
 
@@
 \item Families from the subduction zone are mainly active during the big tremor events, with down dip families more active than up dip families.
-\item The southernmost family is more active and sensitive to tidal stress changes.
+\item LFE activity is sensitive to tidal stress changes.
 \end{keypoints}
@@
 They are usually grouped into families of events, with all the earthquakes of a given family originating from the same small patch on the plate interface and recurring more or less episodically in a bursty manner.
-In this study, we extend the LFE catalog obtained by Plourde et al.
-(2015) during an episode of high tremor activity in April 2008, to the period 2004-2011.
-LFE activity is well correlated with tremor activity.
-Down dip families are more active than up dip families.
-The southernmost LFE family is also very active, and sensitive to tidal stress changes.
+In this study, we extend the LFE catalog obtained by ~\citeA{PLO_2015} during an episode of high tremor activity in  April 2008, to the 8-year period 2004-2011.
+All of the tremor in the ~\citeA{BOY_2015} catalog south of 42 degrees North has associated LFE activity, but we have identified several other, mostly smaller, clusters of LFEs, and extend their catalog forward and backward by a total of about 3 years.
+As in northern Cascadia, the down-dip LFE families have recurrence intervals several times smaller than the up-dip families.
+For the April, 2008 Episodic Tremor and Slip event, the best recorded LFE families exhibit a strong tidal Coulomb stress sensitivity starting 1.5 days after the rupture front passes by each LFE family.
+The southernmost LFE family, which has been interpreted to be on the subduction plate boundary, near the up-dip limit of tremor, has a very short recurrence time.
+Also, these LFEs tend to occur during times when predicted tidal Coulomb stress is discouraging slip on the plate boundary.
+Both observations suggest this LFE family may be on a different fault.
 \end{abstract}
@@
 We then use these templates to extend the catalog to the whole period when the FAME experiment was running, between July 2007 and June 2009.
-Next, we use the LFEs detections from the 2007-2009 period to create templates for the permanent stations of three seismic networks in northern California.
+Next, we use the LFE detections from the 2007-2009 period to create templates for the permanent stations of three seismic networks in northern California.
 These new templates allow us to extend the LFE catalog to the period 2004-2011.
@@
 
-\citeA{PLO_2015} have kindly accepted to share their LFE catalog with us.
-They have provided a list of 66 LFE families with, for each family, the location of the hypocenter of the family, the list of stations and channels used to detect LFEs for this family, and the timing of LFE detections.
+\citeA{PLO_2015} have kindly shared their LFE catalog with us.
+For each of 66 LFE families they provided hypocentral locations, lists of stations and channels used to detect LFEs, and the timing of all LFE detections.
 ~\citeA{PLO_2015} have later reduced the number of LFE families to 37, by grouping together families with many common detections, but we chose to use the initial detections to extend the catalog.
@@
 All these preprocessing operations are done with the Python package obspy.
-We then stacked linearly all the waveforms after normalizing each waveform with the root mean square (RMS) to obtain a waveform template for each station and each channel.
+We then linearly stacked all the waveforms after normalizing each waveform with the root mean square (RMS) to obtain a waveform template for each station and each channel.
 
@@
 Then for each station and each channel, we cross-correlate the one-hour long signal with the one-minute-long template for the given station and channel.
+We scale the correlation coefficient by the standard deviation so the value is 1 if the correlation is perfect.
 As the signal-to-noise ratio of the seismic data is low, we may not see obvious peaks in the cross-correlation signal.
 However, if we stack the cross-correlation signals for all the channels and all the stations, we can see peaks appearing.
-Whenever the value of the average cross-correlation is higher than a threshold (we chose a threshold equal to eight times the median absolute deviation of the stacked cross-correlation), we assumed that there is an LFE.
+Whenever the value of the average cross-correlation is higher than a threshold (we chose a threshold equal to eight times the median absolute deviation of the stacked cross-correlation), we inferred that there is an LFE.
 As two peaks separated by a short period of time may actually correspond to the same LFE, we kept only LFEs that are separated by at least one second and, when two LFEs are separated by less than one second, we keep only the one with the higher value of the stacked cross-correlation.
@@
 We also added 74 \% more LFEs to the catalog, but most of added LFEs have a low cross-correlation value and may be false detections.
-Figure 2 shows the cross-correlation values for the LFEs in the original catalog, and for the LFEs that we added to the catalog for family B (inverted triangle in Figure 1).
+Figure 2 shows the cross-correlation values for the LFEs in the original catalog, and for the LFEs that we added to the catalog for family E (inverted triangle in Figure 1).
 \\
@@
 \noindent\includegraphics[width=\textwidth, trim={7.5cm 1cm 28cm 2cm},clip]{figures/hist.eps}
-\caption{Cross-correlation values for LFEs added in the catalog for family B (inverted triangle in Figure 1) (left) and cross-correlation values for LFEs in the original catalog from ~\citeA{PLO_2015} (right).
+\caption{Cross-correlation values for LFEs added in the catalog for family E (inverted triangle in Figure 1) (left) and cross-correlation values for LFEs in the original catalog from ~\citeA{PLO_2015} (right).
 There were no missing LFEs for this family.}
@@
 Using a threshold equal to eight times the median absolute deviation of the stacked cross-correlation may produce false detections, therefore we filtered the LFE detection times before visualizing the two-year-long catalog.
-As the number of seismic stations recording may change with time as the stations were progressively installed during Summer and Fall 2007, and then progressively removed during May and June 2009, we kept only LFE detections for which the product of the cross-correlation value by the number of stations recording at that time is higher than a threshold (equal to 0.1 times the number of stations used to detect LFEs for the given LFE family).
+As the number of seismic stations recording may change with time as the stations were progressively installed during Summer and Fall 2007, and then progressively removed during May and June 2009, we kept only LFE detections for which the product of the cross-correlation value by the number of stations recording at that time is higher than a threshold.
 The threshold is thus different for each LFE family.
@@
 \begin{figure}
-\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/tremor_nb_FAME.eps}
+\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/tremor_nb_FAME_3.eps}
 \caption{LFE and tremor detections as a function of time and latitude.
@@
 The double-headed grey arrow represents the time period when the FAME experiment was operating at full capacity.
-LFE families south of 40° N latitude are on the San Andreas fault system.}
+LFE families south of 40° N latitude are on the San Andreas fault system.
+For clarity, we do not show the LFEs for the days when there are less than three LFEs.}
 \label{pngfiguresample}
@@
 Additional small LFE episodes are also detected between bigger tremor episodes.
-The LFE families located south on the strike-slip fault from the San Andreas Fault system are much more active than the LFE families located on the subduction zone.
-Additionally, one LFE family located on the southern end of the subduction zone is also more active than families located farther north, and behaves more similarly to the strike-slip fault families.
+The LFE families located south on the strike-slip fault from the San Andreas Fault system have much shorter recurrence intervals than the LFE families located on the subduction zone.
+Additionally, one LFE family located on the southern end of the subduction zone has also shorter recurrence intervals than families located farther north, and behaves more similarly to the strike-slip fault families.
 \\
@@
 We then compared the normalized number of LFEs obtained with the two catalogs.
-Examples are given in Figures 5 and 6 for families A (square in Figure 1) and B (inverted triangle in Figure 1).
-Although the number of LFEs during each event may not be the same, we clearly see for family B that the timing of the events are the same for both catalogs.
-Family A is much more active but most events seem to be present in both catalogs as well.
+Examples are given in Figure 5 for families A (square in Figure 1) and E (inverted triangle in Figure 1).
+Although the number of LFEs during each event may not be the same, we clearly see for family E that the timing of the events are the same for both catalogs.
+Family A has much shorter recurrence times but most events seem to be present in both catalogs as well.
 \\
@@
 \begin{figure}
-\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/080401_05_050.eps}
-\caption{Normalized cumulative number of LFEs over the period July 2007-July 2009 for the FAME catalog (red) and the network catalog (blue) for family A (square in Figure 1).
-The cumulative number of LFEs has been divided by the total number of LFEs so that both curves start at 0 and end at 1, in order to get a better match between the LFE bursts in both catalogs.}
-\label{pngfiguresample}
-\end{figure}
-
-\begin{figure}
-\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/080413_07_023.eps}
-\caption{Normalized cumulative number of LFEs over the period July 2007-July 2009 for the FAME catalog (red) and the network catalog (blue) for family B (inverted triangle in Figure 1).
+\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/cumulative.eps}
+\caption{Normalized cumulative number of LFEs over the period July 2007-July 2009 for the FAME catalog (red) and the network catalog (blue) for family A (square in Figure 1) and family E (inverted triangle in Figure 1).
 The cumulative number of LFEs has been divided by the total number of LFEs so that both curves start at 0 and end at 1, in order to get a better match between the LFE bursts in both catalogs.}
@@
 We eliminate two families for which too few permanent stations have good templates, and it was not possible to detect LFEs with the available templates.
-However, we were able to detect most LFEs events even without the presence of the temporary stations from the FAME network.
+However, we were able to detect most LFE events even without the presence of the temporary stations from the FAME network.
 We are thus confident that we can detect LFEs before 2007 and after 2009.
 In the following, we focus on the period 2004-2011.
-In November 2011, several one-component stations stopped recording and the number of available stations started decreasing, which is why we did not look for LFEs event after that date.
-The resulting LFE catalog for the period 2004-2011 is shown in Figure 7.
+In November 2011, several one-component stations stopped recording and the number of available stations started decreasing, which is why we did not look for LFE event after that date.
+The resulting LFE catalog for the period 2004-2011 is shown in Figure 6.
 For comparison, we also plotted the tremor detection times from ~\citeA{BOY_2015}.
+Figure 7 shows the details of four big ETS events in 2205, 2006, 2007 and 2008.
 \\
@@
 \begin{figure}
-\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/tremor_nb_perm.eps}
+\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/tremor_nb_perm_3.eps}
 \caption{LFE and tremor detections as a function of time and latitude.
@@
 Black dots represent days where LFEs are detected for a given LFE family.
-The size of the black dots are proportional to the number of LFEs detected during this day.}
+The size of the black dots are proportional to the number of LFEs detected during this day.
+For clarity, we do not show the LFEs for the days when there are less than three LFEs.}
+\label{pngfiguresample}
+\end{figure}
+
+\begin{figure}
+\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/zoom_ETS_events.eps}
+\caption{LFE and tremor detections as a function of time and latitude for four ETS events.
+Red dots represent tremor detections from the catalog of ~\citeA{BOY_2015}.
+Black dots represent days where LFEs are detected for a given LFE family.
+The size of the black dots are proportional to the number of LFEs detected during this day.
+For clarity, we do not show the LFEs for the days when there are less than three LFEs.}
 \label{pngfiguresample}
@@
 We were also able to detect several LFE episodes in 2004-2005 before the beginning of the ~\citeA{BOY_2015} catalog.
+In particular, the LFE event in January 2005 propagating South to North from latitude 40.1 to latitude 41.2 is also present in the ETS catalog from ~\citeA{BRU_2007}.
+We also see one LFE event in May-June 2004, propagating South to North from latitude 40.1 to 41.6, and one LFE event in October-November 2004, propagating North to South from latitude 41.6 to 40.4.
+One on these events is also in the ETS catalog from ~\citeA{BRU_2007}.
 It is known than tectonic tremor can be triggered by surface waves from distant and regional earthquakes, as has been observed in Cascadia ~\cite{RUB_2009}, the San Andreas ~\cite{PEN_2009, GUI_2010}, and Nankai ~\cite{HAN_2014}.
-Low-frequency earthquake activity on the San Andreas fault also increased during several months after the 2004 Parkfield earthquake ~\cite{SHE_2017}.
+LFE activity on the San Andreas fault also increased during several months after the 2004 Parkfield earthquake ~\cite{SHE_2017}.
 We looked for regional earthquakes with magnitude higher than 5 during the period covered by the catalog to verify whether this phenomenon is also observed in southern Cascadia.
@@
 Indeed, for the Parkfield earthquake, an increase in LFE activity was observed for LFE families up to 45km away from the epicenter, but not farther away.
-Moreover, the Parkfield earthquake was more shallower (8.1km deep) than the regional earthquakes used in this study.
+Moreover, the Parkfield earthquake was more shallow (8.1km deep) than the regional earthquakes used in this study.
 For the 2003 M6.5 San Simeon earthquake, no increase in LFE activity in the San Andreas LFE families was observed in the hours following the earthquake.
@@
 Most families in the northern and central part of the study area are well aligned along the strike direction, however families in the southern part of the subduction zone are more distant from each other.
-We first look at three families aligned at latitude about 40.4N (group C, triangles in Figure 1) and show the number of LFEs per day in Figure 8.
-We then look at five families aligned at latitude about 40.7N (group D, diamonds in Figure 1) and show the number of LFEs per day in Figure 9.
-Finally, we look at five families aligned at latitude about 41.05N (group E, pentagons in Figure 1) and show the number of LFEs per day in Figure 10.
+We first look at three families aligned at latitude about 40.4N (group B, triangles in Figure 1) and show the number of LFEs per day in the left column of Figure 8.
+We then look at five families aligned at latitude about 40.7N (group C, diamonds in Figure 1) and show the number of LFEs per day in the middle column of Figure 8.
+Finally, we look at five families aligned at latitude about 41.05N (group G, pentagons in Figure 1) and show the number of LFEs per day in the right column of Figure 8.
 For all three sets of families, LFE events are more frequent for the easternmost family than for the westernmost family, as was also the case in northern Cascadia ~\cite{SWE_2019}.
 It is more difficult to compare event size and swarm duration as the number of stations and the quality of the templates are different from each family, and may have a strong influence on the number of LFEs detected.
+To summarize the findings, we plot in Figure 9 the number of LFE events as a function of the distance in the eastern direction from the upper limit of the tremor.
+We clearly see that the number of events increases with the down dip distance.
 \\
@@
 \begin{figure}
-\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/set1_daily_LFEs.eps}
-\caption{Daily number of LFEs over the period 2004-2011 for the three LFE families in group C (triangles in Figure 1).}
+\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/set_daily_LFEs.eps}
+\caption{Left: Daily number of LFEs over the period 2004-2011 for the three LFE families in group C (triangles in Figure 1).
+Middle: Daily number of LFEs for the five LFE families in group D (diamonds in Figure 1).
+Right: Daily number of LFEs for the five LFE families in group E (pentagons in Figure 1).}
 \label{pngfiguresample}
@@
 \begin{figure}
-\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/set2_daily_LFEs.eps}
-\caption{Daily number of LFEs over the period 2004-2011 for the five LFE families in group D (diamonds in Figure 1).}
-\label{pngfiguresample}
-\end{figure}
-
-\begin{figure}
-\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/set3_daily_LFEs.eps}
-\caption{Daily number of LFEs over the period 2004-2011 for the five LFE families in group E (pentagons in Figure 1).}
+\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/nb_LFE_events.eps}
+\caption{Number of LFE events as a function of distance in the eastern direction from the upper limit of tremor for the three LFE families in group B (triangles in Figure 1), the five LFE families in group C (diamonds in Figure 1), and the five LFE families in group G (pentagons in Figure 1).
+Family A (square in Figure 1) has much more LFE events and is shown by an arrow.}
 \label{pngfiguresample}
@@
 Sensitivity of LFE families activity to tidal stress changes has also been observed in northern Cascadia ~\cite{ROY_2015}, and on the San Andreas fault ~\cite{THO_2012}.
-We used calculated stresses from elastic deformations due to both water loads and bodily tides in the solid Earth along the Cascadia subduction zone (H.
+We used calculated stresses from elastic deformations due to both water loads and body tides in the solid Earth along the Cascadia subduction zone (H.
 Houston, personal communication).
@@
 The resulting full stress tensors are projected to normal and shear (in the plate convergence direction) stresses on the interface, as well as mean stress (one-third the tensor trace).
-We then divided the values of tidal stress change into 20 stress bins and computed for each LFE family the number of LFEs occurring at a time when the value of the stress was in a given bin.
+The change in Coulomb stress (positive promotes shear failure) $\Delta CFF$ is then computed:
+
+\begin{linenomath*}
+\begin{equation}
+\Delta CFF = \Delta \tau + \mu \left( \Delta \sigma - B \Delta \sigma_m \right)
+\end{equation}
+\end{linenomath*}
+
+where $\Delta \tau$ is the change in shear stress on the fault plane in the slip direction, $\Delta \sigma$ is the change in fault normal stress (positive is tensile), $\mu$ is the coefficient of intrinsic friction, $\Delta \sigma_m$ is the change in mean stress and $B$ is the Skempton's coefficient ~\cite{HOU_2015}.
+We take the values $\mu = 0.1$ and $B = 0.5$ for the friction and the Skempton's coefficient.
+We then divided the values of tidal Coulomb stress change into 20 stress bins and computed for each LFE family the number of LFEs occurring at a time when the value of the stress was in a given bin.
 We also computed what would be the expected number of LFEs occurring if the tidal stress changes have no influence on LFE activity.
-For most LFE families, we did not notice any evidence of influence of tidal stress on LFE activity.
-However, the LFE activity on family A seems to be correlated with tidal stress changes.
-Figure 11 shows the number of LFEs occurring during each stress bin (blue bars) and the expected number of LFEs (black line) for shear, normal, and mean stress.
-We also normalized the number of LFEs by the time during which the stress takes values in each bin.
-We note that LFE activity is triggered by negative shear stress and positive normal stress.
-This sensitivity of LE activity to tidal stress changes may explain while this family is much more active than the other families on the subduction zone.
+As noted by ~\citeA{HOU_2015}, tremor sensitivity to stress perturbations changes during an ETS event, with an increase in sensitivity to tidal stress as slip accumulates over several days.
+We thus choose to only consider the later part of the 2008 ETS event, using only LFEs that occurred between 1.5 and 11.5 days after the arrival of the tremor front.
+As there are only a few LFEs, it is not always obvious to see the influence of tidal stress on LFE activity.
+However, Figure 10 shows the number of LFEs occurring during each stress bin (blue bars) and the expected number of LFEs (black line) for six families with a relatively high number of LFEs.
+For most of the families, a positive Coulomb stress change (promoting shear failure) is associated with an increase in LFE activity.
+However, this is not the case for the southernmost LFE family A, for which a negative Coulomb stress change is associated with an increase in LFE activity.
+To better highlight the behavior of family A, we also consider the whole LFE catalog and plot the observed and expected number of LFEs as a function of tidal stress.
+We clearly see that these LFEs tend to occur during times when predicted tidal Coulomb stress is discouraging slip on the plate boundary.
+We hypothesize that LFE family A may not be located on the subduction zone, and may be on a different fault instead.
 
 \begin{figure}
-\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/tidal_stress.eps}
-\caption{Left: Number of LFEs for family A (square in Figure 1) observed (blue bars) and expected (black line) for each stress bin for shear (top), normal (middle) and mean (bottom) tidal stress change.
-Right: Normalized number of LFEs observed (blue bars) and expected (black line).
-As the number of LFEs is normalized by the time spent in each stress bin, the expected number of LFEs is constant.}
+\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/coulomb.eps}
+\caption{Number of LFEs for families A, B2, D, C4, F and G1 observed (blue bars) and expected (black line) for each stress bin of tidal Coulomb stress change.}
 \label{pngfiguresample}
@@
 Downdip families are also more active than up dip families.
-Tidal stress changes seem to be correlated with LFE activity on the southernmost family, which may explain why it is more active.
+Tidal stress changes seem to be correlated with LFE activity in the later part of the 2008 ETS event.
 

### 2021-08-05 data/Ducellier/plot_nb_events.py

@@ -1,0 +1,50 @@
+"""
+This script plots the number of events as a function
+of distance from the up-dip limit of tremor
+"""
+
+import matplotlib.pylab as pylab
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+
+from itertools import cycle
+
+params = {'legend.fontsize': 24, \
+          'xtick.labelsize':24, \
+          'ytick.labelsize':24}
+pylab.rcParams.update(params)
+
+events = pd.read_csv('LFEdistribution_perm/nb_LFE_events.txt', sep=r'\s{1,}', header=None, engine='python')
+events.columns = ['group', 'name', 'lon', 'lat', 'x', 'y', 'nb']
+
+groups = events['group'].unique()
+
+plt.figure(1, figsize=(8, 8))
+cycol = cycle('bgrcmk')
+
+for group in groups:
+    events_sub = events.loc[events['group'] == group]
+    color = next(cycol)
+    if group == 'A':
+        plt.arrow(events_sub['x'].iloc[0], 50, 0, 2, width=0.3, color=color)
+        plt.annotate(events_sub['name'].iloc[0] + ' (' + str(int(events_sub['nb'].iloc[0])) + ')', \
+            (events_sub['x'].iloc[0] + 1, 50), fontsize=24, color=color)
+    else:
+        plt.scatter(events_sub['x'], events_sub['nb'], c=color, s=100)
+        for i in range(0, len(events_sub)):
+            if events_sub['name'].iloc[i] == 'G2':
+                plt.annotate(events_sub['name'].iloc[i], \
+                    (events_sub['x'].iloc[i] - 5, events_sub['nb'].iloc[i]), \
+                    fontsize=24, color=color)
+            else:
+                plt.annotate(events_sub['name'].iloc[i], \
+                    (events_sub['x'].iloc[i] + 1, events_sub['nb'].iloc[i]), \
+                    fontsize=24, color=color)
+
+plt.xlabel('Distance in the east direction (km)', fontsize=24)
+plt.ylabel('Number of LFE events', fontsize=24)
+plt.xlim([2, 52])
+plt.ylim([5, 54])
+plt.savefig('LFEdistribution_perm/nb_LFE_events.eps', format='eps')
+plt.close(1)

### 2021-08-05 data/Ducellier/plot_several_cumulative.py

@@ -1,0 +1,92 @@
+"""
+Script to plot cumulative number of LFEs
+"""
+
+import matplotlib.pylab as pylab
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+import pickle
+
+from datetime import datetime, timedelta
+
+# List of LFE families
+templates = np.loadtxt('../Plourde_2015/templates_list.txt', \
+    dtype={'names': ('name', 'family', 'lat', 'lon', 'depth', 'eH', \
+    'eZ', 'nb'), \
+         'formats': ('S13', 'S3', np.float, np.float, np.float, \
+    np.float, np.float, np.int)}, \
+    skiprows=1)
+
+tbegin = datetime(2007, 7, 1)
+nb_days = 731
+
+families = [0, 19]
+names = ['A', 'E']
+
+# Threshold for filtering the catalog
+threshold = pd.read_csv('threshold_cc.txt', sep=r'\s{1,}', header=None, engine='python')
+threshold.columns = ['family', 'threshold_FAME', 'threshold_perm']
+
+# Start plot
+params = {'legend.fontsize': 16, \
+          'xtick.labelsize':16, \
+          'ytick.labelsize':16}
+pylab.rcParams.update(params)
+plt.figure(1, figsize=(5 * len(families), 5))
+
+# Loop on templates
+for i in range(0, len(families)):
+
+    # Open LFE catalog (FAME data)
+    namedir = 'catalogs/' + templates[families[i]][0].astype(str)
+    namefile = namedir + '/catalog_2007_2009.pkl'
+    df_FAME = pickle.load(open(namefile, 'rb'))
+
+    # Open LFE catalog (permanent networks)
+    namefile = namedir + '/catalog_2004_2011.pkl'
+    df_perm = pickle.load(open(namefile, 'rb'))
+
+    # Filter LFEs
+    df_FAME = df_FAME.loc[df_FAME['cc'] * df_FAME['nchannel'] >= threshold['threshold_FAME'].iloc[families[i]]]
+    df_perm = df_perm.loc[df_perm['cc'] * df_perm['nchannel'] >= threshold['threshold_perm'].iloc[families[i]]]
+
+    # Add date column
+    df = pd.DataFrame({'year': df_FAME['year'], 'month': df_FAME['month'], 'day': df_FAME['day']})
+    df = pd.to_datetime(df)
[…]

### 2021-08-05 data/Ducellier/plot_several_families.py

@@ -43,62 +43,63 @@ duration = dt.days * 86400.0 + dt.seconds + dt.microseconds * 0.000001
 nw = int(duration / window)
 
 # Indices of LFE families
-#indices = [2, 5, 6]
-#indices = [12, 13, 25, 20, 23]
-#indices = [40, 29, 33, 36, 41]
-indices = [0, 2, 12, 40]
+indices = [[2, 5, 6], \
+           [12, 13, 25, 20, 23], \
+           [40, 29, 33, 36, 41]]
 
 # Names of LFE families
-#names = ['C1', 'C2', 'C3']
-#names = ['D1', 'D2', 'D3', 'D4', 'D5']
-#names = ['E1', 'E2', 'E3', 'E4', 'E5']
-names = ['A', 'C1', 'D1', 'E1']
+names = [['B1', 'B2', 'B3'], \
+         ['C1', 'C2', 'C3', 'C4', 'C5'], \
+         ['G1', 'G2', 'G3', 'G4', 'G5']]
 
-plt.figure(1, figsize=(16, 4 * len(indices)))
+plt.figure(1, figsize=(24, 15))
 
 # Loop on templates
-for (count, i) in enumerate(indices):
-    longitude = templates[i][3]
+for column in range(0, len(indices)):
+    for (count, i) in enumerate(indices[column]):
+        longitude = templates[i][3]
 
-    # Open LFE catalog
-    namedir = 'catalogs/' + templates[i][0].astype(str)
-    namefile = namedir + '/catalog_2004_2011.pkl'
-    df = pickle.load(open(namefile, 'rb'))
+        # Open LFE catalog
+        namedir = 'catalogs/' + templates[i][0].astype(str)
+        namefile = namedir + '/catalog_2004_2011.pkl'
+        df = pickle.load(open(namefile, 'rb'))
 
-    # Filter LFE
-    df = df.loc[df['cc'] * df['nchannel'] >= threshold['threshold_perm'].iloc[i]]
+        # Filter LFE
+        df = df.loc[df['cc'] * df['nchannel'] >= threshold['threshold_perm'].iloc[i]]
 
-    # Get time series
-    X = np.zeros(nw, dtype=int)
-    # Loop on LFEs
-    for j in range(0, len(df)):
-        myYear = df['year'].iloc[j]
-        myMonth = df['month'].iloc[j]
-        myDay = df['day'].iloc[j]
-        myHour = df['hour'].iloc[j]
[…]

### 2021-08-05 data/Ducellier/plot_tremor_nbLFEs.py

@@ -13,8 +13,8 @@ from math import floor
 from date import ymdhms2day
 
 # Time boundaries
-xmin = 2007.5
-xmax = 2009.5
+xmin = 2004.0
+xmax = 2006.0
 
 # Space boundaries
 latmin = 39.4
@@ -50,20 +50,20 @@ threshold.columns = ['family', 'threshold_FAME', 'threshold_perm']
 for i in range(0, np.shape(templates)[0]):
 
     # Plot only good data
-    if threshold['threshold_FAME'].iloc[i] > 0.0:
+    if threshold['threshold_perm'].iloc[i] > 0.0:
 
         # Get latitude
         latitude = templates[i][2]
 
         # Open LFE catalog
         namedir = 'catalogs/' + templates[i][0].astype(str)
-        namefile = namedir + '/catalog_2007_2009.pkl'
+        namefile = namedir + '/catalog_2004_2011.pkl'
         df = pickle.load(open(namefile, 'rb'))
 
         # Filter LFEs
 #        maxc = np.max(df['nchannel'])
 #        df = df.loc[df['cc'] * df['nchannel'] >= 0.1 * maxc]
-        df = df.loc[df['cc'] * df['nchannel'] >= threshold['threshold_FAME'].iloc[i]]
+        df = df.loc[df['cc'] * df['nchannel'] >= threshold['threshold_perm'].iloc[i]]
 
         time = np.arange(xmin, xmax, 1.0/365.5)
         nbLFEs = np.zeros(np.shape(time)[0])
@@ -82,26 +82,35 @@ for i in range(0, np.shape(templates)[0]):
                 nbLFEs[index] = nbLFEs[index] + 1
 
         # Plot LFEs
-        time = time[nbLFEs > 1]
-        nbLFEs = nbLFEs[nbLFEs > 1]
+        time = time[nbLFEs > 3]
+        nbLFEs = nbLFEs[nbLFEs > 3]
         plt.scatter(time, np.repeat(latitude, np.shape(time)[0]), s=1 + nbLFEs * 5, c='k')
 #        plt.scatter(time, np.repeat(latitude, np.shape(time)[0]), c=nbLFEs, cmap='autumn')
 
 # Plot time line
-tbegin = ymdhms2day(2007, 9, 25, 0, 0, 0)
-tend = ymdhms2day(2009, 5, 14, 0, 0, 0)
[…]

### 2021-08-05 data/Ducellier/plot_zoom_ETS.py

@@ -1,0 +1,110 @@
+"""
+Script to plot tremor and LFEs as a function of latitude
+"""
+
+import matplotlib.pylab as pylab
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+import pickle
+
+from math import floor
+
+from date import ymdhms2day
+
+# Time boundaries
+xmin = [2005.66, 2006.36, 2007.48, 2008.25]
+xmax = [2005.73, 2006.43, 2007.59, 2008.35]
+years = [2005, 2006, 2007, 2008]
+
+# Space boundaries
+latmin = 39.4
+latmax = 41.8
+
+# Read tremor file
+tremor = pd.read_csv('../tremor/tremor.xyddtt', sep=' ', header=None)
+tremor.columns = ['longitude', 'latitude', 'downdip', 'alongstrike', 'year', 'epoch']
+year_tremor = tremor['year']
+lat_tremor = tremor['latitude']
+
+# List of LFE families
+templates = np.loadtxt('../Plourde_2015/templates_list.txt', \
+    dtype={'names': ('name', 'family', 'lat', 'lon', 'depth', 'eH', \
+    'eZ', 'nb'), \
+         'formats': ('S13', 'S3', np.float, np.float, np.float, \
+    np.float, np.float, np.int)}, \
+    skiprows=1)
+
+# Threshold for filtering the catalog
+threshold = pd.read_csv('threshold_cc.txt', sep=r'\s{1,}', header=None, engine='python')
+threshold.columns = ['family', 'threshold_FAME', 'threshold_perm']
+
+# Start figure and plot tremor
+params = {'legend.fontsize': 24, \
+          'xtick.labelsize':24, \
+          'ytick.labelsize':24}
+pylab.rcParams.update(params)
+plt.figure(1, figsize=(20, 10))
+
+for event in range(0, 4):
+    ax = plt.subplot2grid((1, 4), (0, event))
+    plt.scatter(year_tremor - years[event], lat_tremor, c='r')
+
+    # Loop on templates
+    for i in range(0, np.shape(templates)[0]):
+
+        # Plot only good data
+        if threshold['threshold_perm'].iloc[i] > 0.0:
+
+            # Get latitude
+            latitude = templates[i][2]
+
+            # Open LFE catalog
+            namedir = 'catalogs/' + templates[i][0].astype(str)
+            namefile = namedir + '/catalog_2004_2011.pkl'
[…]

### 2021-08-05 src/plot_several_tidal_stress.py

@@ -1,0 +1,148 @@
+import matplotlib.pylab as pylab
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+import pickle
+
+from math import floor
+from scipy.io import loadmat
+
+from date import ymdhms2matlab, matlab2ymdhms
+
+params = {'legend.fontsize': 24, \
+          'xtick.labelsize':24, \
+          'ytick.labelsize':24}
+pylab.rcParams.update(params)
+
+# Number of boxes for plotting
+nbox = 20
+
+# Friction
+mu = 0.1
+B = 0.5
+
+# LFE families
+families = [0, 0, 5, 14, 20, 28, 40]
+names = ['A (all LFEs)', 'A', 'B2', 'D', 'C4', 'F', 'G1']
+
+# List of LFE families
+templates = np.loadtxt('../data/Plourde_2015/templates_list.txt', \
+    dtype={'names': ('name', 'family', 'lat', 'lon', 'depth', 'eH', \
+    'eZ', 'nb'), \
+         'formats': ('S13', 'S3', np.float, np.float, np.float, \
+    np.float, np.float, np.int)}, \
+    skiprows=1)
+
+# Threshold for filtering the catalog
+threshold = pd.read_csv('../data/Ducellier/threshold_cc.txt', sep=r'\s{1,}', \
+    header=None, engine='python')
+threshold.columns = ['family', 'threshold_FAME', 'threshold_perm']
+
+# Arrival time of 2008 ETS event
+begin_time = pd.read_csv('../data/For_Ken_California_LFE/begin_time.txt', sep=' ', header=None)
+begin_time.columns = ['latitude', 'longitude', 'begin_time']
+
+plt.figure(1, figsize=(28, 10))
+
+# Loop on templates
+for i in range(0, len(families)):
+
+    # Look for beginning time of ETS
+    latitude = templates[families[i]][2]
+    longitude = templates[families[i]][3]
+    subset = begin_time.loc[(begin_time['latitude'] == latitude) & \
+        (begin_time['longitude'] == longitude)]
+    time_ETS = subset.iloc[0]['begin_time']
+
+    # Load data
+    filename = '../data/tidal_stress/' + templates[families[i]][0].astype(str) + '.pkl'
+    tidal_stress = pickle.load(open(filename, 'rb'))
+    time = tidal_stress[0]
+    norm = tidal_stress[1]
+    shear = tidal_stress[2]
[…]

### 2021-08-05 src/tidal_stress.py

@@ -17,6 +17,9 @@ pylab.rcParams.update(params)
 # Number of boxes for plotting
 nbox = 20
 
+# Friction
+mu = 0.1
+
 # List of LFE families
 templates = np.loadtxt('../data/Plourde_2015/templates_list.txt', \
     dtype={'names': ('name', 'family', 'lat', 'lon', 'depth', 'eH', \
@@ -77,6 +80,7 @@ for i in range(0, np.shape(templates)[0]):
         df['shear'] = shear_LFE
         df['norm'] = norm_LFE
         df['vol'] = vol_LFE
+        df['coulomb'] = shear_LFE + mu * (norm_LFE + vol_LFE)
 
         # Plot
         plt.figure(1, figsize=(20, 18))
@@ -167,4 +171,40 @@ for i in range(0, np.shape(templates)[0]):
         ax4.clear()
         ax5.clear()
         ax6.clear()
+        plt.close(1)
+
+        # Plot Coulomb stress
+        plt.figure(1, figsize=(20, 6))
+
+        coulomb = shear + mu * (norm + vol)
+        min_stress = np.min(coulomb)
+        max_stress = np.max(coulomb)
+        boxes = np.linspace(min_stress, max_stress, nbox + 1)
+        size_box = (max_stress - min_stress) / (4 * nbox)
+
+        count = np.zeros(nbox)
+        count_coulomb = np.zeros(nbox)
+        for k in range(0, nbox):
+            count[k] = len(df.loc[(df.coulomb >= boxes[k]) & (df.coulomb <= boxes[k + 1])])
+            count_coulomb[k] = np.sum((coulomb >= boxes[k]) & (coulomb <= boxes[k + 1]))
+        normalize = np.sum(count) / np.sum(count / count_coulomb)
+
+        ax1 = plt.subplot(121)
+        expected = len(df) * count_coulomb/ np.sum(count_coulomb)
+        plt.plot(0.5 * (boxes[1:] + boxes[:-1]), expected, color='black')
+        plt.bar(0.5 * (boxes[1:] + boxes[:-1]), count, size_box)
+        plt.xlabel('Coulomb stress (kPa)', fontsize=24)
+        plt.ylabel('Number of LFEs', fontsize=24)
+
+        ax2 = plt.subplot(122)
+        plt.plot(0.5 * (boxes[1:] + boxes[:-1]), normalize * expected / count_coulomb, color='black')
[…]

### 2021-08-05 src/tidal_stress_ETS.py

@@ -1,0 +1,277 @@
+import matplotlib.pylab as pylab
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+import pickle
+
+from math import floor
+from scipy.io import loadmat
+
+from date import ymdhms2matlab, matlab2ymdhms
+
+params = {'legend.fontsize': 24, \
+          'xtick.labelsize':24, \
+          'ytick.labelsize':24}
+pylab.rcParams.update(params)
+
+# Number of boxes for plotting
+nbox = 20
+
+# Friction
+mu = 0.1
+
+# List of LFE families
+templates = np.loadtxt('../data/Plourde_2015/templates_list.txt', \
+    dtype={'names': ('name', 'family', 'lat', 'lon', 'depth', 'eH', \
+    'eZ', 'nb'), \
+         'formats': ('S13', 'S3', np.float, np.float, np.float, \
+    np.float, np.float, np.int)}, \
+    skiprows=1)
+
+# Threshold for filtering the catalog
+threshold = pd.read_csv('../data/Ducellier/threshold_cc.txt', sep=r'\s{1,}', \
+    header=None, engine='python')
+threshold.columns = ['family', 'threshold_FAME', 'threshold_perm']
+
+# Arrival time of 2008 ETS event
+begin_time = pd.read_csv('../data/For_Ken_California_LFE/begin_time.txt', sep=' ', header=None)
+begin_time.columns = ['latitude', 'longitude', 'begin_time']
+
+# Loop on templates
+for i in range(0, np.shape(templates)[0] - 5):
+
+    # Look only at good data
+    if threshold['threshold_perm'].iloc[i] > 0.0:
+
+        # Look for beginning time of ETS
+        latitude = templates[i][2]
+        longitude = templates[i][3]
+        subset = begin_time.loc[(begin_time['latitude'] == latitude) & \
+            (begin_time['longitude'] == longitude)]
+        time_ETS = subset.iloc[0]['begin_time']
+
+        # Load data
+        filename = '../data/tidal_stress/' + templates[i][0].astype(str) + '.pkl'
+        tidal_stress = pickle.load(open(filename, 'rb'))
+        time = tidal_stress[0]
+        norm = tidal_stress[1]
+        shear = tidal_stress[2]
+        vol = tidal_stress[3]
+
+        # Open LFE catalog
[…]

### 2021-08-07 paper/agujournaltemplate.tex
Last version of apaper

@@
 For comparison, we also plotted the tremor detection times from ~\citeA{BOY_2015}.
-Figure 7 shows the details of four big ETS events in 2205, 2006, 2007 and 2008.
+Figure 7 shows the details of six big ETS events in 2004, 2005, 2006, 2007 and 2008.
 \\
@@
 \noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/zoom_ETS_events.eps}
-\caption{LFE and tremor detections as a function of time and latitude for four ETS events.
+\caption{LFE and tremor detections as a function of time and latitude for six ETS events.
 Red dots represent tremor detections from the catalog of ~\citeA{BOY_2015}.
@@
 In particular, the LFE event in January 2005 propagating South to North from latitude 40.1 to latitude 41.2 is also present in the ETS catalog from ~\citeA{BRU_2007}.
-We also see one LFE event in May-June 2004, propagating South to North from latitude 40.1 to 41.6, and one LFE event in October-November 2004, propagating North to South from latitude 41.6 to 40.4.
-One on these events is also in the ETS catalog from ~\citeA{BRU_2007}.
+We also see one LFE event in May-June 2004, propagating South to North from latitude 40.1 to 41.6, and one LFE event in November 2004, propagating North to South from latitude 41.6 to 40.4.
+The first of these events is also in the ETS catalog from ~\citeA{BRU_2007}.
+The main characteristics of the six biggest events shown in Figure 7 are given in Table 1.
+\\
+
+\begin{table}
+\caption{Main LFEs events between 2004 and 2011}
+\centering
+\begin{tabular}{c c c c c}
+\hline
+Begin time & End time & Direction & Southern limit & Northern limit \\
+\hline
+End May 2004 & Mid June 2004 & South to North & 40.1 & 41.6 \\
+Early November 2004 & End November 2004 & North to South & 40.4 & 41.6 \\
+Early September 2005 & End September 2005 & South to North & 40.1 & 41.6 \\
+Mid April 2006 & End April 2006 & South to North & 40.1 & 41.5 \\
+Early July 2007 & End July 2007 & North to South & 40.1 & 41.6 \\
+Early April 2008 & End April 2008 & South to North & 40.1 & 41.7 \\
+\hline
+\end{tabular}
+\end{table}
+
 It is known than tectonic tremor can be triggered by surface waves from distant and regional earthquakes, as has been observed in Cascadia ~\cite{RUB_2009}, the San Andreas ~\cite{PEN_2009, GUI_2010}, and Nankai ~\cite{HAN_2014}.
@@
 We looked for regional earthquakes with magnitude higher than 5 during the period covered by the catalog to verify whether this phenomenon is also observed in southern Cascadia.
-The characteristics of the earthquakes we looked at are given in Table 1.
-We also looked at distant earthquakes with large magnitude, which  characteristics are given in Table 2.
+The characteristics of the earthquakes we looked at are given in Table 2.
+We also looked at distant earthquakes with large magnitude, which  characteristics are given in Table 3.
 \\
@@
 We clearly see that the number of events increases with the down dip distance.
-\\
+The southernmost family A is also added in Figure 9, but does not fit the general trend.\\
 
@@
 Middle: Daily number of LFEs for the five LFE families in group D (diamonds in Figure 1).
-Right: Daily number of LFEs for the five LFE families in group E (pentagons in Figure 1).}
+Right: Daily number of LFEs for the five LFE families in group E (pentagons in Figure 1).
+Down-dip families (lower rows) typically have far more LFE swarms that up-dip families (upper rows).}
 \label{pngfiguresample}

### 2021-08-07 data/Ducellier/plot_several_cumulative.py

@@ -84,9 +84,11 @@ for i in range(0, len(families)):
         format(tbegin.month, tbegin.day, tbegin.year), fontsize=16)
     if i == 0:
         plt.ylabel('Normalized number of LFEs', fontsize=16)
-    plt.title('Cumulative number of LFEs (family ' + names[i] + ')', fontsize=16)
+    plt.title('Cumulative number of LFEs' \
+        # (family ' + names[i] + ')'
+        , fontsize=16)
     plt.legend(loc=4, fontsize=12)
 
 plt.tight_layout()
-plt.savefig('cumulative.eps', format='eps')
+plt.savefig('Figure5.eps', format='eps')
 plt.close(1)

### 2021-08-07 data/Ducellier/plot_tremor_nbLFEs.py

@@ -13,8 +13,8 @@ from math import floor
 from date import ymdhms2day
 
 # Time boundaries
-xmin = 2004.0
-xmax = 2006.0
+xmin = 2005.0
+xmax = 2005.1
 
 # Space boundaries
 latmin = 39.4

### 2021-08-07 data/Ducellier/plot_zoom_ETS.py

@@ -13,9 +13,9 @@ from math import floor
 from date import ymdhms2day
 
 # Time boundaries
-xmin = [2005.66, 2006.36, 2007.48, 2008.25]
-xmax = [2005.73, 2006.43, 2007.59, 2008.35]
-years = [2005, 2006, 2007, 2008]
+xmin = [2004.39, 2004.81, 2005.66, 2006.36, 2007.48, 2008.25]
+xmax = [2004.45, 2004.88, 2005.73, 2006.43, 2007.59, 2008.35]
+years = [2004, 2004, 2005, 2006, 2007, 2008]
 
 # Space boundaries
 latmin = 39.4
@@ -44,10 +44,10 @@ params = {'legend.fontsize': 24, \
           'xtick.labelsize':24, \
           'ytick.labelsize':24}
 pylab.rcParams.update(params)
-plt.figure(1, figsize=(20, 10))
+plt.figure(1, figsize=(30, 10))
 
-for event in range(0, 4):
-    ax = plt.subplot2grid((1, 4), (0, event))
+for event in range(0, 6):
+    ax = plt.subplot2grid((1, 6), (0, event))
     plt.scatter(year_tremor - years[event], lat_tremor, c='r')
 
     # Loop on templates

### 2021-08-07 data/Ducellier/date_keep.py
Clean repository

@@ -1,161 +1,0 @@
-"""
-This module contains function to convert dates in appropriate format
-"""
-
-from datetime import datetime, timedelta
-from math import floor
-
-def matlab2ymdhms(time, roundsec=True):
-    """
-    Convert Matlab format to year/month/day/hour/minute/second
-
-    Input:
-        type time =  float
-        time = Number of days since January 1, 0000 (Matlab format)
-    Output:
-        type output = tuple of 6 integers
-        output = year, month, day, hour, minute, second, (microsecond)
-    """    
-    myday = datetime.fromordinal(int(time)) + \
-        timedelta(days=time % 1) - timedelta(days=366)
-    year = myday.year
-    month = myday.month
-    day = myday.day
-    hour = myday.hour
-    minute = myday.minute
-    second = myday.second
-    microsecond = myday.microsecond
-    if (roundsec==True):
-        rsecond = int(round(second + microsecond / 1000000.0))
-        if (rsecond == 60):
-            minute = minute + 1
-            rsecond = 0
-        if (minute == 60):
-            hour = hour + 1
-            minute = 0
-        if (hour == 24):
-            day = day + 1
-            hour = 0
-        if ((month in [1, 3, 5, 7, 8, 10, 12]) and (day == 32)):
-            month = month + 1
-            day = 1
-        elif ((month in [4, 6, 9, 11]) and (day == 31)):
-            month = month + 1
-            day = 1
-        else:
-            if (((year % 4 == 0) and (year % 100 != 0)) or (year % 400 == 0)):
-                if (day == 30):
-                    month = month + 1
-                    day = 1
-            else:
-                if (day == 29):
-                    month = month + 1
-                    day = 1
-        if (month == 13):
-            year = year + 1
-            month = 1
-        return (year, month, day, hour, minute, rsecond)
-    else:
-        return (year, month, day, hour, minute, second, microsecond)
-
-def ymdhms2matlab(year, month, day, hour, minute, second):
-    """
-    Convert year/month/day/hour/minute/second to Matlab format
-
-    Input:
-        type intput = 6 integers
-        input = year, month, day, hour, minute, second
-    Output:
-        type time = float
-        time = Number of days since January 1, 0000 (Matlab format)
-    """
[…]

### 2021-08-17 paper/agujournaltemplate.tex
Cover letter
Corrected submission

@@
 \end{abstract}
+
+\section*{Plain language summary}
+
+Low-frequency earthquakes (LFEs) are small magnitude earthquakes, with typical magnitude less than 2, and reduced amplitudes at frequencies greater than 10 Hz relative to ordinary small earthquakes.
+Their occurrence is often associated with tectonic tremor and slow slip events along the plate boundary in subduction zones and occasionally transform fault zones.
+They are usually grouped into families of events, with all the earthquakes of a given family originating from the same small patch on the plate interface and recurring more or less episodically in a bursty manner.
+In this study, we extend the LFE catalog obtained by ~\citeA{PLO_2015} to the 8-year period 2004-2011.
+As in northern Cascadia, the down-dip LFE families have recurrence intervals smaller than the up-dip families.
+For the April 2008 Episodic Tremor and Slip event, the best recorded LFE families exhibit a strong tidal stress sensitivity.
+The southernmost LFE family, which has been interpreted to be on the subduction plate boundary has a short recurrence time.
+Also, these LFEs tend to occur during times when tidal stress discourages slip on the plate boundary.
+Both observations suggest this LFE family may be on a different fault.
 
@@
 Sensitivity of LFE families activity to tidal stress changes has also been observed in northern Cascadia ~\cite{ROY_2015}, and on the San Andreas fault ~\cite{THO_2012}.
-We used calculated stresses from elastic deformations due to both water loads and body tides in the solid Earth along the Cascadia subduction zone (H.
-Houston, personal communication).
+We used calculated stresses from elastic deformations due to both water loads and body tides in the solid Earth along the Cascadia subduction zone.
 The stress computation is done following the method described in ~\citeA{HOU_2015}.
@@
 
-In this study, we used the templates obtained by Plourde et al.
-(2015) using data recorded by the FAME network in Northern California during an episode of high tremor activity in April 2008, and we extended their catalog to the whole two years (2007-2009) during which the seismic stations were installed.
+In this study, we used the templates obtained by ~\citeA{PLO_2015} using data recorded by the FAME network in Northern California during an episode of high tremor activity in April 2008, and we extended their catalog to the whole two years (2007-2009) during which the seismic stations were installed.
 We then used the two-year-long catalog to create templates for stations from the permanent seismic networks, and used the seismic data recorded by these stations to extend the catalog before and after the FAME experiment.
@@
 Houston for the tidal stress calculation in the Cascadia subduction zone.
-This project was funded by NSF grant XXX.
+This project was funded by NSF grant EAR-1358512.
 A.D.
 would like to thank the Integral Environmental Big Data Research Fund from the College of the Environment of University of Washington, which funded cloud computing resources to carry out the data analyses.
-The seismic recordings used for this analysis can be downloaded from the IRIS and NCEDC websites.
+The seismic recordings from the FAME experiment used for this analysis can be downloaded from the IRIS website \cite{https://doi.org/10.7914/sn/xq_2007}.
+Waveform data from the permanent networks were accessed through the Northern California Earthquake Data Center (NCEDC), doi:10.7932/NCEDC.
 The first figure was done using GMT ~\cite{WES_1991}.
-The Python scripts used to analyze the data and make the figures can be found on the first author's Github account \url{https://github.com/ArianeDucellier/catalog}.
+The Python scripts used to analyze the data and make the figures can be found on the first author's Github account, accessible through Zenodo ~\cite{ariane_ducellier_2021_5168867}.
 

### 2022-01-01 paper/answer_reviewers.tex
Work on answers

\documentclass[letterpaper, 12pt]{article}

\usepackage{caption}
\usepackage{float}
\usepackage[T1]{fontenc}
\usepackage[lmargin=1 in, rmargin=1 in, tmargin=1 in, bmargin=1 in]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{times}
\usepackage{xcolor}

\begin{document}

\textbf{Associate editor}

\bigskip

\textit{In addition to the reviewer's comments, the following references should be cited:
\begin{itemize}
\item L48. Study of LFE has been continuing for about two decades, and it may be difficult to cite all the important previous studies. The review of Beroza and Ide (2011, Annual Rev. Earth Planet. Sci.) covers the first decade.
\item L53. Tremor can be explained as a swarm of LFEs (Shelly et al., 2007, Nature).
\item L56. The source of the tremor and the LFEs is located on the plate boundary (Shelly et al., 2006, Nature; Bostock et al., 2012, G-cubed). Or as a summary by Audet and Kim (2016, Tectonophysics).
\item L58. In addition to the currently cited Ide et al. (2007, GRL), Bostock et al. (2012, G-cubed) and Royer and Bostock (2014, EPSL) are also appropriate for the mechanism study in Cascadia.
\item L63. Obara (2002, Science) should obviously be cited, but is inappropriate as a basis for a correlation study between tectonic tremor and slow slip. Obara et al. (2004, GRL) is better.
\end{itemize}}

\bigskip

We have added these references in the text.

\bigskip

\textbf{Reviewer 1}

\bigskip

\textit{Figure 1: Depth contour of subducting plate and surface traces of the San Andreas fault zones (SAF) should be in the figure for easier understanding because authors mentioned about LFE families are on SAF and in the subduction zones (Lines 176 - 183). It should be also helpful to include a figure of depth cross section for LFE hypocenters.}

\bigskip

\textit{Lines 73 - 74: Bostock (2015, https://doi.org/10.1002/2015JB012195) provides 10-year catalog of LFES at the Vancouver Island.}

\bigskip

We added the reference in the text.

\bigskip

\textit{Lines 75 - 76: Japan Meteorological Agency (JMA) provides LFE catalog in Japan since 2004. Kato and Nakagawa (2020, https://doi.org/10.1186/s40623-020-01257-4) also provides LFE catalogs in Japan between 2004 - 2015.}

\bigskip

We added the references in the text.

\bigskip

\textit{Line 138: Why did authors used such a long (1 min) time window for matched filter analysis. I think it is common to use time windows of 5 - 10 seconds around the arrival time at each seismic station (e.g., Shelly et al., 2007, https://doi.org/10.1038/nature05666; Kato and Nakagawa, 2020, https://doi.org/10.1186/s40623-020-01257-4).}

\bigskip

The templates from Plourde et al. (2015) have a low signal-to-noise ratio and generally do not show clear P- and S-wave arrivals. Moreover, the wave arrivals can be located close to the beginning or close to the end of the time window, depending on the LFE family considered. We have chosen to keep the whole one-minute time window to be sure to include both the P- and the S-wave arrivals. The templates obtained using LFE detections from the 2-year-long catalog show clearer P- and S-wave arrivals and we have reduced the length of the time window to 30 seconds on average, depending on the LFE family considered. We have remade the templates using only LFEs that were present in both catalogs (FAME and permanent networks). The wave arrivals are now clearer and, to extend farther in time our catalog, we could reduce the size of the time window by using a different starting time for each station, depending on whether it is close or farther away from the LFE source location.

\bigskip

\textit{Figure 2: It is helpful to show the value of the detection threshold in this figure.}

\bigskip

\textit{Lines 165 - 175: How second thresholds (CC values vs stations numbers) were chosen for each seismic station? If it is done manually, please provide a list of the threshold as the supplementary table. In addition, how many events did this selection step remove from the catalog? (A figure comparing before and after the selection step will be useful.)}

\bigskip

\textit{Lines 204 - 207: How much are two catalogs (the FAME catalog and the network catalog) different originally? As the station density of FAME stations seems to be equivalent to that of permanent stations, I expect two catalogs do not show significant differences. If there are severe differences between two catalogs, detection process and/or event selection procedure needs to be reconsidered. In addition, I think it is also good to show event catalog detected using both FAME stations and permanent stations. Comparing "FAME + network" catalog and the network catalog at the same period, we can evaluate how much the resolution of LFE detection only with the permanent stations becomes worse than that with additional FAME stations. This is important information to evaluate completeness of the LFE catalog in the periods without FAME stations.}

\bigskip

\textit{Line 209: "two thresholds" for what?}

\bigskip

\textit{Line 215: It will be helpful to visually show temporal changes of the number of available seismic stations.}

\bigskip

\textit{Line 249: Surface wave triggering of LFEs at the Nankai trough was reported in Miyazawa et al. (2008, https://doi.org/10.1186/BF03352858) and references therein before Han et al. (2014).}

\bigskip

We added the reference in the text.

\bigskip

\textit{Lines 271 - 273: Is there no evidence for dynamic triggering as well?}

\bigskip

\textit{Lines 290 - 294: I think the vertical axis of Figure 9 should be average recurrence interval rather than the number of events.}

\bigskip

\textit{Line 296: Tidal triggering of tremors was reported in many studies before Houston (2015), including Shelly et al. (2007, https://doi.org/10.1029/2007GC001640) and Houston et al. (2011, https://doi.org/10.1038/ngeo1157).}

\bigskip

We added these references.

\bigskip

Line 306: Which fault plane did authors assume to calculate tidal stress?

Lines 323 - 324: Is it possible that this negative sensitivity for family A is due to incorrect fault geometry? As family A is located at the southern edge of the subduction zone, fault geometry could be complex, which might be different from the assumed one.

\bigskip

\textbf{Reviewer 2}

\bigskip

\textit{The southern-most LFE family is very interesting! I agree with your assessments that the tidal stress modulation and rapid recurrence intervals suggest this family is on a different fault. With that in mind, I find the lack of further discussion about it unsastisfying. Did you try to re-stack and re-locate this family? It would be great if you could. Even if you conclude that you can’t get a reliable depth estimate, I would suggest it’s worth showing the template waveforms and discussing a few potential source regions, even if it’s highly speculative.}

\bigskip

Line 290 / Figure 9: I’m a bit confused here. The number of LFE events shown on Figure 9 (< 50) are much too small to be total numbers of events, as made clear by the daily event counts in Figure 8 … Are these LFE numbers normalised somehow? Please clarify this.

Minor points

Line 22: what does “other” refer to? Not associated with tremor detections?

I think the plain-language summary could be more “plain”. Even words/phrases like “episodically”, “recurrence intervals”, “tidal stress sensitivity” could be expressed in

simpler/more-common words. Things like “tectonic tremor”, “slow slip” are certainly not familiar to most people, so that’s not plain language.

Line 41: “…recurrence intervals smaller…” → shorter recurrence intervals

Line 61: “…in a bursty manner.” Maybe you can follow this up with a more explicit description of what “bursty” means…something like “tens to hundreds of events in short period, often lasting a few hours”?

Line 92: “…were located above the plate boundary.” We found that they were shallower than the McCrory model, but we actually assumed that this meant the McCrory model was biased deep. A minor rephrase would be good here (even though we might have just been wrong).

Figure 1: it would be nice to have the trench, the San Andreas Fault, (+ the Maacama and Bucknell Creek faults?) and/or plate interface contours on this map

Line 139: “All these preprocessing operations are done with the Python package obspy”. I think it is fine to leave this to the acknowledgements if you prefer to shorten here.

\bigskip

\textit{Line 151: maybe a reference to that Shelly (2007, Nature) paper is warranted here for the somewhat standard 8*MAD threshold}

We added the reference.

\bigskip

Line 161: does the 74\% apply to the total number of LFEs (all families)? Or still the 61 families of the previous sentence?

Line 173: “The threshold is thus different for each LFE family”. I’m not sure what you mean here. Is the threshold constant for each family, or does it vary as stations become active/inactive? Is the threshold consistent for a given number of active stations (on that day), or does it vary between templates? Please try to clarify.

Line 180: “Additionally, one LFE family located on the southern end of the subduction zone has also shorter recurrence intervals than families located farther north, and behaves more similarly to the strike-slip fault families.” What locations are you using here? Also, maybe for clarity you can put (40.1⁰ N), or whatever the precise latitude is after “…on the southern end”. It may be good to specify the depth here too, since it may not be surprising to see frequent bursts if the family is at 45 km depth.

Line 223: I think it would be nice to quantify the number of shared (between FAME and network catalogs) events, for each family here instead of just saying “…most events seem to be present…”

Figure 7: Did the Boyarko et al. study include 2004? I found in your discussion that it does not, but I think it’s worth repeating this information in the figure caption. Also, the font size is quite tiny here, it would be nice to ensure that there is no text below size 6-7 on any of the figures.

Figure 9: Does the “upper limit of tremor” mean the westward limit?

Line 309: Can you provide references to justify these coefficient values (0.1, 0.5)?

Line 312: “We also computed what would be the expected number of LFEs occurring if the tidal stress changes have no influence on LFE activity.” It’s not clear to me why this (the black lines in Figure 10) varies so dramatically between families, could you explain a bit further?

Supplementary Material: it might be worth repeating the acronym explanations (IRIS, NDEDC) as well as the links to the data sources in this document

\end{document}

### 2022-01-01 paper/agujournaltemplate_highlighted.tex
Work on answers

--- 2021-08-17 paper/agujournaltemplate.tex
@@
 
-Tectonic tremor is a weak but persistent shaking of the Earth that has been discovered in many subduction zones and some strike-slip faults throughout the world.
-Tremor is observed on seismograms as apparent noise whose amplitude is modulated in time in a similar manner at stations that are dozens of kilometers apart from each other.
+Tectonic tremor is a weak but persistent shaking of the Earth that has been discovered in many subduction zones and some strike-slip faults throughout the world \textbf{~\cite{BER_2011}}.
+Tremor is observed on seismograms as apparent noise whose amplitude is modulated in time in a similar manner at stations that are dozens of kilometers apart from each other \textbf{~\cite{OBA_2002}}.
 It is characterized by a long (several seconds to many minutes), low amplitude seismic signal, emergent onsets, and an absence of clear impulsive phases.
-Tremor can be explained as a swarm of low-frequency earthquakes (LFEs), that is small magnitude earthquakes (M $\sim$ 1) which dominant frequency is clearly low (1-10 Hz) compared with that of ordinary tiny earthquakes (up to 20 Hz).
-The source of the tremor and the LFEs is located on the plate boundary, and their focal mechanisms represent shear slip on a low-angle thrust fault dipping in the same direction as the plate interface ~\cite{IDE_2007_GRL}.
+Tremor can be explained as a swarm of low-frequency earthquakes (LFEs) \textbf{~\cite{SHE_2007_nature}}, that is small magnitude earthquakes (M $\sim$ 1) which dominant frequency is clearly low (1-10 Hz) compared with that of ordinary tiny earthquakes (up to 20 Hz).
+The source of the tremor and the LFEs is located on the plate boundary \textbf{~\cite{SHE_2006,BOS_2012,AUD_2016}}, and their focal mechanisms represent shear slip on a low-angle thrust fault dipping in the same direction as the plate interface ~\textbf{\cite{IDE_2007_GRL,BOS_2012,ROY_2014}}.
 LFEs are usually grouped into families of events, with all the earthquakes of a given family originating from the same small patch on the plate interface, and recurring more or less episodically in a bursty manner.
-In subduction zones such as Nankai and Cascadia, tectonic tremor and LFE observations are spatially and temporally correlated with slow slip observations ~\cite{OBA_2002, ROG_2003}.
+In subduction zones such as Nankai and Cascadia, tectonic tremor and LFE observations are spatially and temporally correlated with slow slip observations \textbf{~\cite{ROG_2003,OBA_2004}}.
 Due to this correlation, these paired phenomena have been called Episodic Tremor and Slip (ETS).
@@
 However, most of the work on LFEs has been focused on detecting LFEs during periods of high tremor activity, grouping them into families of events, and locating the source of the LFE families.
-Longer catalogs (several years) have been established for LFE families in Mexico (two-year long catalog by ~\citeA{FRA_2014}), the San Andreas Fault (fifteen-year-long catalog by ~\citeA{SHE_2017}), Washington State (five-year-long catalog by ~\citeA{SWE_2019} and two-year-long catalog by ~\citeA{CHE_2017_JGR, CHE_2017_G3}), New Zealand (eight-year-long catalog by ~\citeA{BAR_2018}), and Japan (twelve-year-long catalog by ~\citeA{NAK_2017} and eight-year-long catalog by ~\citeA{OHT_2017}).
+Longer catalogs (several years) have been established for LFE families in Mexico (two-year long catalog by ~\citeA{FRA_2014}), the San Andreas Fault (fifteen-year-long catalog by ~\citeA{SHE_2017}), Washington State (five-year-long catalog by ~\citeA{SWE_2019} and two-year-long catalog by ~\citeA{CHE_2017_JGR, CHE_2017_G3}), \textbf{Vancouver Island (ten-year-long catalog by ~\citeA{BOS_2015})}, New Zealand (eight-year-long catalog by ~\citeA{BAR_2018}), and Japan (twelve-year-long catalog by ~\citeA{NAK_2017}, eight-year-long catalog by ~\citeA{OHT_2017}, \textbf{eleven-year-long catalog by ~\citeA{KAT_2020}, and Japan Meteorological Agency (JMA) catalog since 1999 ~\cite{KAT_2003}}).
 These studies have shown that the recurrence behavior of LFE families varies a lot between seismic regions, and inside the same seismic region.
@@
 However, if we stack the cross-correlation signals for all the channels and all the stations, we can see peaks appearing.
-Whenever the value of the average cross-correlation is higher than a threshold (we chose a threshold equal to eight times the median absolute deviation of the stacked cross-correlation), we inferred that there is an LFE.
+Whenever the value of the average cross-correlation is higher than a threshold (we chose a threshold equal to eight times the median absolute deviation of the stacked cross-correlation \textbf{as was done by ~\citeA{SHE_2007_nature}}), we inferred that there is an LFE.
 As two peaks separated by a short period of time may actually correspond to the same LFE, we kept only LFEs that are separated by at least one second and, when two LFEs are separated by less than one second, we keep only the one with the higher value of the stacked cross-correlation.
@@
 
-It is known than tectonic tremor can be triggered by surface waves from distant and regional earthquakes, as has been observed in Cascadia ~\cite{RUB_2009}, the San Andreas ~\cite{PEN_2009, GUI_2010}, and Nankai ~\cite{HAN_2014}.
+It is known than tectonic tremor can be triggered by surface waves from distant and regional earthquakes, as has been observed in Cascadia ~\cite{RUB_2009}, the San Andreas ~\cite{PEN_2009, GUI_2010}, and Nankai \textbf{~\cite{MIY_2008,HAN_2014}}.
 LFE activity on the San Andreas fault also increased during several months after the 2004 Parkfield earthquake ~\cite{SHE_2017}.
@@
 
-The occurrence and amplitude of tectonic tremor can be modulated by small stress changes (about 1 kPa) associated with ocean or solid earth tides ~\cite{HOU_2015}.
+The occurrence and amplitude of tectonic tremor can be modulated by small stress changes (about 1 kPa) associated with ocean or solid earth tides \textbf{~\cite{SHE_2007_G3,HOU_2011,HOU_2015}}.
 Sensitivity of LFE families activity to tidal stress changes has also been observed in northern Cascadia ~\cite{ROY_2015}, and on the San Andreas fault ~\cite{THO_2012}.

### 2022-01-01 src/compute_templates_both.py

@@ -67,8 +67,7 @@ def rotate_stream(D, orientation, reference):
     return Drot
 
 def compute_new_templates(family, latitude, longitude, catalog1, catalog2, diff, \
-    directory, max_dist, max_LFEs, TDUR, filt, dt, nattempts, \
-    waittime, method='RMS'):
+    directory, max_dist, max_LFEs, TDUR, filt, dt, nattempts, waittime, method='RMS'):
     """
     This function take only the best LFEs that are present
     in both LFE catalogs (FAME and networks),
@@ -175,16 +174,16 @@ def compute_new_templates(family, latitude, longitude, catalog1, catalog2, diff,
         location = stations['Lo'].iloc[ir]
         starttime = stations['Start time'].iloc[ir]
         endtime = stations['End time'].iloc[ir]
-        if (network == 'PB'):
+        if (network in ['PB', 'XQ']):
             server = 'IRIS'
         else:
             server = 'NCEDC'
 
         # Filter LFEs for the period where the station was recording
-        df = pd.DataFrame({'year': LFEsort['year'], 'month': LFEsort['month'], 'day': LFEsort['day']})
-        date = pd.to_datetime(df)
+        df_sub = pd.DataFrame({'year': df['year'], 'month': df['month'], 'day': df['day']})
+        date = pd.to_datetime(df_sub)
         mask = (date >= starttime) & (date <= endtime)
-        LFEsub = LFEsort.loc[mask]
+        df_sub = df.loc[mask]
 
         # Download instrument response
         if (server == 'IRIS'):
@@ -204,13 +203,13 @@ def compute_new_templates(family, latitude, longitude, catalog1, catalog2, diff,
         complete = False
         index = 0
         # Loop on LFEs
-        while ((index < len(LFEsub)) and (complete == False)):
-            mySecond = int(floor(LFEsub['second'].iloc[index]))
+        while ((index < len(df_sub)) and (complete == False)):
+            mySecond = int(floor(df_sub['second'].iloc[index]))
             myMicrosecond = int(1000000.0 * \
-                (LFEsub['second'].iloc[index] - floor(LFEsub['second'].iloc[index])))
-            Tori = UTCDateTime(year=LFEsub['year'].iloc[index], \
-                month=LFEsub['month'].iloc[index], day=LFEsub['day'].iloc[index], \
-                hour=LFEsub['hour'].iloc[index], minute=LFEsub['minute'].iloc[index], \
[…]

### 2022-01-02 paper/agujournaltemplate_highlighted.tex
Work on answers

@@
 In this study, we extend the LFE catalog obtained by ~\citeA{PLO_2015} during an episode of high tremor activity in  April 2008, to the 8-year period 2004-2011.
-All of the tremor in the ~\citeA{BOY_2015} catalog south of 42 degrees North has associated LFE activity, but we have identified several other, mostly smaller, clusters of LFEs, and extend their catalog forward and backward by a total of about 3 years.
+All of the tremor in the ~\citeA{BOY_2015} catalog south of 42 degrees North has associated LFE activity, but we have identified several \textbf{smaller clusters of LFEs without associated tremor activity}, and extend their catalog forward and backward by a total of about 3 years.
 As in northern Cascadia, the down-dip LFE families have recurrence intervals several times smaller than the up-dip families.
@@
 In this study, we extend the LFE catalog obtained by ~\citeA{PLO_2015} to the 8-year period 2004-2011.
-As in northern Cascadia, the down-dip LFE families have recurrence intervals smaller than the up-dip families.
+As in northern Cascadia, the down-dip LFE families have \textbf{shorter recurrence intervals} than the up-dip families.
 For the April 2008 Episodic Tremor and Slip event, the best recorded LFE families exhibit a strong tidal stress sensitivity.
@@
 LFEs are usually grouped into families of events, with all the earthquakes of a given family originating from the same small patch on the plate interface, and recurring more or less episodically in a bursty manner.
-In subduction zones such as Nankai and Cascadia, tectonic tremor and LFE observations are spatially and temporally correlated with slow slip observations \textbf{~\cite{ROG_2003,OBA_2004}}.
+\textbf{Tens of events are thus recorded within a few hours or days during a burst of LFE activity, followed by weeks or months of quiet, with very few events.} In subduction zones such as Nankai and Cascadia, tectonic tremor and LFE observations are spatially and temporally correlated with slow slip observations \textbf{~\cite{ROG_2003,OBA_2004}}.
 Due to this correlation, these paired phenomena have been called Episodic Tremor and Slip (ETS).
@@
 Then, they recovered higher signal-to-noise LFE signals using iterative network cross-correlation.
-They found that the LFE families on the southern Cascadia Subduction Zone were located above the plate boundary, with a large distribution of depths (28-47 km).
-Three additional LFE families were found on two strike-slip faults, the Maacama and Bucknell Creek faults, which are part of the San Andreas Fault zone.
+They found that the LFE families on the southern Cascadia Subduction Zone were located above the \textbf{plate boundary model of ~\citeA{MCC_2006}, with a large distribution of depths (28-47 km).
+However, they suggested that this may be because the model is biased deep.} Three additional LFE families were found on two strike-slip faults, the Maacama and Bucknell Creek faults, which are part of the San Andreas Fault zone.
 \\
@@
 For a given LFE family, a given station and a given channel, we downloaded an 80-second-long seismic waveform starting 10 seconds before the LFE detection time, we detrended the data, tapered the first and last 5 seconds of the data with a Hann window, removed the instrument response, bandpassed filter between 1.5 and 9 Hz, resampled the data to 20 Hz, and cut the first and last 10 seconds of data to obtain a one-minute-long template.
-All these preprocessing operations are done with the Python package obspy.
 We then linearly stacked all the waveforms after normalizing each waveform with the root mean square (RMS) to obtain a waveform template for each station and each channel.
@@
 Although the number of LFEs during each event may not be the same, we clearly see for family E that the timing of the events are the same for both catalogs.
-Family A has much shorter recurrence times but most events seem to be present in both catalogs as well.
-\\
+Family A has much shorter recurrence times but most events \textbf{are present in both catalogs as well: forty events are present in both catalogs, three events are present in the FAME catalog but not in the networks catalog and one event is present in the networks catalog but not in the FAME catalog.} \\
 
@@
 The size of the black dots are proportional to the number of LFEs detected during this day.
-For clarity, we do not show the LFEs for the days when there are less than three LFEs.}
+For clarity, we do not show the LFEs for the days when there are less than three LFEs.
+\textbf{The tremor catalog of ~\citeA{BOY_2015} starts in 2005.
+This is why no tremor detections can be shown or the two events in 2004.}}
 \label{pngfiguresample}
@@
 where $\Delta \tau$ is the change in shear stress on the fault plane in the slip direction, $\Delta \sigma$ is the change in fault normal stress (positive is tensile), $\mu$ is the coefficient of intrinsic friction, $\Delta \sigma_m$ is the change in mean stress and $B$ is the Skempton's coefficient ~\cite{HOU_2015}.
-We take the values $\mu = 0.1$ and $B = 0.5$ for the friction and the Skempton's coefficient.
+We take the values $\mu = 0.1$ and $B = 0.5$ for the friction and the Skempton's coefficient \textbf{, as was done by ~\citeA{HOU_2015}}.
 We then divided the values of tidal Coulomb stress change into 20 stress bins and computed for each LFE family the number of LFEs occurring at a time when the value of the stress was in a given bin.
@@
 The first figure was done using GMT ~\cite{WES_1991}.
-The Python scripts used to analyze the data and make the figures can be found on the first author's Github account, accessible through Zenodo ~\cite{ariane_ducellier_2021_5168867}.
+\textbf{All the downloading and preprocessing operations on the seismic waveforms are done with the Python package obspy.} The Python scripts used to analyze the data and make the figures can be found on the first author's Github account, accessible through Zenodo ~\cite{ariane_ducellier_2021_5168867}.
 

### 2022-01-04 src/compute_templates_both.py
Work on templates

@@ -136,9 +136,9 @@ def compute_new_templates(family, latitude, longitude, catalog1, catalog2, diff,
     stations_BK = filter_stations('BK')
     stations_NC = filter_stations('NC')
     stations_PB = filter_stations('PB')
-    stations = pd.concat([stations_BK, stations_NC, stations_PB], ignore_index=True)
-#    stations = pd.concat([stations_BK, stations_NC], ignore_index=True)
-#    stations = stations_PB
+    stations_XQ = filter_stations('FAME')
+    stations = pd.concat([stations_BK, stations_NC, stations_PB, \
+        stations_FAME], ignore_index=True)
 
     # Create directory to store the waveforms
     namedir = directory + '/' + family
@@ -186,12 +186,14 @@ def compute_new_templates(family, latitude, longitude, catalog1, catalog2, diff,
         df_sub = df.loc[mask]
 
         # Download instrument response
-        if (server == 'IRIS'):
-            get_responses.get_from_IRIS(station, network)
-        elif (server == 'NCEDC'):
-            get_responses.get_from_NCEDC(station, network)
-        else:
-            raise ValueError('You can only download data from IRIS and NCEDC')
+        path = '../data/response/' + network + '_' + station + '.xml'
+        if !os.path.isfile(path):
+            if (server == 'IRIS'):
+                get_responses.get_from_IRIS(station, network)
+            elif (server == 'NCEDC'):
+                get_responses.get_from_NCEDC(station, network)
+            else:
+                raise ValueError('You can only download data from IRIS and NCEDC')
         # Create streams
         cha_list = channels.split(',')
         streams = []

### 2022-01-04 src/compute_templates_both.py
Start new templates

@@ -69,7 +69,7 @@ def rotate_stream(D, orientation, reference):
 def compute_new_templates(family, latitude, longitude, catalog1, catalog2, diff, \
     directory, max_dist, max_LFEs, TDUR, filt, dt, nattempts, waittime, method='RMS'):
     """
-    This function take only the best LFEs that are present
+    This function take only the LFEs that are present
     in both LFE catalogs (FAME and networks),
     downloads every one-minute time window where there is an LFE recorded,
     and stacks the signal over all the LFEs to get the template
@@ -77,14 +77,22 @@ def compute_new_templates(family, latitude, longitude, catalog1, catalog2, diff,
     Input:
         type family = string
         family = Name of the LFE family
+        type latitude = float
+        latitude = Latitude of the epicenter of the family
+        type longitude = float
+        longitude = Longitude of the epicenter of the family
         type catalog1 = string
         catalog1 = Name of the first catalog containing the LFEs (FAME)
         type catalog2 = string
         catalog2 = Name of the second catalog containing the LFEs (networks)
-        type threshold = float
-        threshold = Minimun value of cross correlation to keep LFE
-        type stations = list of strings
-        stations = Name of the stations where we want a template
+        type diff = float
+        diff = Time difference between two catalogs
+        type directory = string
+        directory = Directory where to store the templates
+        type max_dist = float
+        max_dist = Maximum distance from station to epicenter
+        type max_LFEs = integer
+        max_LFEs = Number of LFEs used to make template
         type TDUR = float
         TDUR = Time to add before and after the time window for tapering
         type filt = tuple of floats
@@ -138,7 +146,7 @@ def compute_new_templates(family, latitude, longitude, catalog1, catalog2, diff,
     stations_PB = filter_stations('PB')
     stations_XQ = filter_stations('FAME')
     stations = pd.concat([stations_BK, stations_NC, stations_PB, \
-        stations_FAME], ignore_index=True)
+        stations_XQ], ignore_index=True)
 
     # Create directory to store the waveforms
     namedir = directory + '/' + family
@@ -180,27 +188,37 @@ def compute_new_templates(family, latitude, longitude, catalog1, catalog2, diff,
             server = 'NCEDC'
 
         # Filter LFEs for the period where the station was recording
-        df_sub = pd.DataFrame({'year': df['year'], 'month': df['month'], 'day': df['day']})
-        date = pd.to_datetime(df_sub)
+        date = pd.DataFrame({'year': df['year'], 'month': df['month'], 'day': df['day']})
[…]

### 2022-01-05 paper/answer_reviewers.tex
Work on reviews

@@
 
-We have added these references in the text.
+We added these references in the text.
 
@@
 
-Line 306: Which fault plane did authors assume to calculate tidal stress?
+\textit{Line 306: Which fault plane did authors assume to calculate tidal stress?}
 
-Lines 323 - 324: Is it possible that this negative sensitivity for family A is due to incorrect fault geometry?
-As family A is located at the southern edge of the subduction zone, fault geometry could be complex, which might be different from the assumed one.
+\bigskip
+
+\textit{Lines 323 - 324: Is it possible that this negative sensitivity for family A is due to incorrect fault geometry?
+As family A is located at the southern edge of the subduction zone, fault geometry could be complex, which might be different from the assumed one.}
 
@@
 I agree with your assessments that the tidal stress modulation and rapid recurrence intervals suggest this family is on a different fault.
-With that in mind, I find the lack of further discussion about it unsastisfying.
+With that in mind, I find the lack of further discussion about it unsatisfying.
 Did you try to re-stack and re-locate this family?
 It would be great if you could.
-Even if you conclude that you can’t get a reliable depth estimate, I would suggest it’s worth showing the template waveforms and discussing a few potential source regions, even if it’s highly speculative.}
+Even if you conclude that you can't get a reliable depth estimate, I would suggest it's worth showing the template waveforms and discussing a few potential source regions, even if it's highly speculative.}
 
@@
 
-Line 290 / Figure 9: I’m a bit confused here.
-The number of LFE events shown on Figure 9 (< 50) are much too small to be total numbers of events, as made clear by the daily event counts in Figure 8 … Are these LFE numbers normalised somehow?
-Please clarify this.
+\textit{Line 290 / Figure 9: I'm a bit confused here.
+The number of LFE events shown on Figure 9 (< 50) are much too small to be total numbers of events, as made clear by the daily event counts in Figure 8...
+Are these LFE numbers normalized somehow?
+Please clarify this.}
 
-Minor points
+\bigskip
 
-Line 22: what does “other” refer to? Not associated with tremor detections?
+\textit{Line 22: what does "other" refer to? Not associated with tremor detections?}
 
-I think the plain-language summary could be more “plain”. Even words/phrases like “episodically”, “recurrence intervals”, “tidal stress sensitivity” could be expressed in
+\bigskip
 
-simpler/more-common words. Things like “tectonic tremor”, “slow slip” are certainly not familiar to most people, so that’s not plain language.
+We meant other smaller episodes of LFE activity in between the big tremor episodes. We modified this sentence.
 
-Line 41: “…recurrence intervals smaller…” → shorter recurrence intervals
+\bigskip
 
-Line 61: “…in a bursty manner.” Maybe you can follow this up with a more explicit description of what “bursty” means…something like “tens to hundreds of events in short period, often lasting a few hours”?
+\textit{I think the plain-language summary could be more "plain".
+Even words/phrases like "episodically", "recurrence intervals", "tidal stress sensitivity" could be expressed in  simpler/more-common words.
+Things like "tectonic tremor", "slow slip" are certainly not familiar to most people, so that's not plain language.}
 
-Line 92: “…were located above the plate boundary.” We found that they were shallower than the McCrory model, but we actually assumed that this meant the McCrory model was biased deep.
-A minor rephrase would be good here (even though we might have just been wrong).
+\bigskip
 
-Figure 1: it would be nice to have the trench, the San Andreas Fault, (+ the Maacama and Bucknell Creek faults?) and/or plate interface contours on this map
+\textit{Line 41: "...recurrence intervals smaller..." $\rightarrow$ shorter recurrence intervals}
 
-Line 139: “All these preprocessing operations are done with the Python package obspy”. I think it is fine to leave this to the acknowledgements if you prefer to shorten here.
+\bigskip
+
+We modified this sentence.
+
+\bigskip
+
+\textit{Line 61: "...in a bursty manner." Maybe you can follow this up with a more explicit description of what "bursty" means...something like "tens to hundreds of events in short period, often lasting a few hours"?}
+
+\bigskip
+
+We added a sentence.
+
+\bigskip
+
+\textit{Line 92: "...were located above the plate boundary." We found that they were shallower than the McCrory model, but we actually assumed that this meant the McCrory model was biased deep.
+A minor rephrase would be good here (even though we might have just been wrong).}
+
+\bigskip
+
+We modified the sentence.
+
+\bigskip
+
+\textit{Figure 1: it would be nice to have the trench, the San Andreas Fault, (+ the Maacama and Bucknell Creek faults?) and/or plate interface contours on this map}
+
+\bigskip
+
+\textit{Line 139: "All these preprocessing operations are done with the Python package obspy". I think it is fine to leave this to the acknowledgements if you prefer to shorten here.}
+
+\bigskip
+
+We move this sentence to the acknowledgements.
 
@@
 
+\bigskip
+
 We added the reference.
@@
 
-Line 161: does the 74\% apply to the total number of LFEs (all families)? Or still the 61 families of the previous sentence?
+\textit{Line 161: does the 74\% apply to the total number of LFEs (all families)? Or still the 61 families of the previous sentence?}
 
-Line 173: “The threshold is thus different for each LFE family”.
-I’m not sure what you mean here.
+\bigskip
+
+It applies to the total number of LFEs for all the 66 families. We modified the text
+
+\bigskip
+
+\textit{Line 173: "The threshold is thus different for each LFE family".
+I'm not sure what you mean here.
 Is the threshold constant for each family, or does it vary as stations become active/inactive?
 Is the threshold consistent for a given number of active stations (on that day), or does it vary between templates?
-Please try to clarify.
+Please try to clarify.}
 
-Line 180: “Additionally, one LFE family located on the southern end of the subduction zone has also shorter recurrence intervals than families located farther north, and behaves more similarly to the strike-slip fault families.” What locations are you using here?
-Also, maybe for clarity you can put (40.1⁰ N), or whatever the precise latitude is after “…on the southern end”.
-It may be good to specify the depth here too, since it may not be surprising to see frequent bursts if the family is at 45 km depth.
+\bigskip
 
-Line 223: I think it would be nice to quantify the number of shared (between FAME and network catalogs) events, for each family here instead of just saying “…most events seem to be present…”
+\textit{Line 180: "Additionally, one LFE family located on the southern end of the subduction zone has also shorter recurrence intervals than families located farther north, and behaves more similarly to the strike-slip fault families." What locations are you using here?
+Also, maybe for clarity you can put (40.1N), or whatever the precise latitude is after "...on the southern end".
+It may be good to specify the depth here too, since it may not be surprising to see frequent bursts if the family is at 45 km depth.}
 
-Figure 7: Did the Boyarko et al.
+\bigskip
+
+\textit{Line 223: I think it would be nice to quantify the number of shared (between FAME and network catalogs) events, for each family here instead of just saying "...most events seem to be present..."}
+
+\bigskip
+
+We added a sentence.
+
+\bigskip
+
+\textit{Figure 7: Did the Boyarko et al.
 study include 2004?
-I found in your discussion that it does not, but I think it’s worth repeating this information in the figure caption.
-Also, the font size is quite tiny here, it would be nice to ensure that there is no text below size 6-7 on any of the figures.
+I found in your discussion that it does not, but I think it's worth repeating this information in the figure caption.
+Also, the font size is quite tiny here, it would be nice to ensure that there is no text below size 6-7 on any of the figures.}
 
-Figure 9: Does the “upper limit of tremor” mean the westward limit?
+\bigskip
 
-Line 309: Can you provide references to justify these coefficient values (0.1, 0.5)?
+The Boyarko et al. tremor catalog starts in 2005. That is why we do not show the tremor for the two 2004 LFE events.
 
-Line 312: “We also computed what would be the expected number of LFEs occurring if the tidal stress changes have no influence on LFE activity.” It’s not clear to me why this (the black lines in Figure 10) varies so dramatically between families, could you explain a bit further?
+\bigskip
 
-Supplementary Material: it might be worth repeating the acronym explanations (IRIS, NDEDC) as well as the links to the data sources in this document
+\textit{Figure 9: Does the "upper limit of tremor" mean the westward limit?}
+
+\bigskip
+
+Yes, it is the westward limit of the tremor. We modified the caption.
+
+\bigskip
+
+\textit{Line 309: Can you provide references to justify these coefficient values (0.1, 0.5)?}
+
+\bigskip
+
+We took the same values as Houston (2015) for the friction and the Skempton's coefficient.
+
+\bigskip
+
+\textit{Line 312: "We also computed what would be the expected number of LFEs occurring if the tidal stress changes have no influence on LFE activity." It's not clear to me why this (the black lines in Figure 10) varies so dramatically between families, could you explain a bit further?}
+
+\bigskip
+
+\textit{Supplementary Material: it might be worth repeating the acronym explanations (IRIS, NDEDC) as well as the links to the data sources in this document}
+
+\bigskip
+
+We added the acronym explanations and the reference for the data sources.
 

### 2022-01-05 paper/agujournaltemplate_highlighted.tex
Work on reviews

@@
 For 61 families, we recovered more than 90 \% of the initial LFE detections.
-We also added 74 \% more LFEs to the catalog, but most of added LFEs have a low cross-correlation value and may be false detections.
+We also added 74 \% more LFEs to the \textbf{initial number of LFEs in the catalog (when considering all 66 families)}, but most of added LFEs have a low cross-correlation value and may be false detections.
 Figure 2 shows the cross-correlation values for the LFEs in the original catalog, and for the LFEs that we added to the catalog for family E (inverted triangle in Figure 1).
@@
 \noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/nb_LFE_events.eps}
-\caption{Number of LFE events as a function of distance in the eastern direction from the upper limit of tremor for the three LFE families in group B (triangles in Figure 1), the five LFE families in group C (diamonds in Figure 1), and the five LFE families in group G (pentagons in Figure 1).
+\caption{Number of LFE events as a function of distance in the eastern direction from the \textbf{westward} limit of tremor for the three LFE families in group B (triangles in Figure 1), the five LFE families in group C (diamonds in Figure 1), and the five LFE families in group G (pentagons in Figure 1).
 Family A (square in Figure 1) has much more LFE events and is shown by an arrow.}

### 2022-01-07 src/compute_templates_both.py
Stations s fn of time

@@ -297,7 +297,7 @@ if __name__ == '__main__':
     # Merge dataframes
     families = pd.merge(locations, differences, on=['family'])
 
-    for i in range(0, 1): #len(families)):
+    for i in range(1, len(families)):
         family = families['family'].iloc[i]
         latitude = families['lat'].iloc[i]
         longitude = families['lon'].iloc[i]

### 2022-01-07 src/plot_new_templates.py

@@ -9,6 +9,8 @@ import pickle
 
 from math import cos, pi, sin, sqrt
 
+from get_stations import filter_stations
+
 def plot_new_templates(family, directory, timearrival, latitude, longitude, \
     ie, tbegin, tend):
     """
@@ -23,15 +25,23 @@ def plot_new_templates(family, directory, timearrival, latitude, longitude, \
             sep=r'\s{1,}', header=None, engine='python')
         staloc.columns = ['station', 'network', 'channels', 'location', \
             'server', 'latitude', 'longitude', 'time_on', 'time_off', 'dt']
-        a = 6378.136
-        e = 0.006694470
+    else:
+        # Get the network, channels, and location of the stations
+        stations_BK = filter_stations('BK')
+        stations_NC = filter_stations('NC')
+        stations_PB = filter_stations('PB')
+        stations_XQ = filter_stations('FAME')
+        stations = pd.concat([stations_BK, stations_NC, stations_PB, \
+            stations_XQ], ignore_index=True)
+    a = 6378.136
+    e = 0.006694470
 
+    # Start figure    
     params = {'xtick.labelsize':20, \
               'ytick.labelsize':20}
     pylab.rcParams.update(params)
     namedir = directory + '/' + family
     templates = os.listdir(namedir)
-#    templates = ['WDC_BHN.pkl']
     for template in templates:
         name = template.split('.')[0]
         station = name.split('_')[0]
@@ -41,6 +51,7 @@ def plot_new_templates(family, directory, timearrival, latitude, longitude, \
         RMS = np.sqrt(np.mean(np.square(stack.data)))
         maximum = np.max(np.abs(stack.data))
         SNR = maximum / RMS
+        plot_time = False
         if timearrival == True:
             subdf = staloc.loc[staloc['station'] == station]
             distance = 0.0
@@ -61,10 +72,21 @@ def plot_new_templates(family, directory, timearrival, latitude, longitude, \
 #                tS = 23.5 # for WDC and 16.5 for LRB
 #                tP = 16.5 # for WDC and 13.0 for LRB 
                 plot_time = True
-            else:
-                plot_time = False
+        else:
+            subdf = stations.loc[stations['Stat'] == station]
+            distance = 0.0
+            if (len(subdf) > 0):
+                lat = subdf['Lat'].iloc[0]
[…]

### 2022-01-07 src/timeline.py

@@ -1,0 +1,63 @@
+import matplotlib.pylab as pylab
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+
+from datetime import datetime, timedelta
+
+station_file = '../data/Ducellier/stations_temporary.txt'
+
+tmin = datetime(2007, 7, 1)
+tmax = datetime(2009, 7, 1)
+ticks_time = [datetime(2007, 7, 1), datetime(2008, 1, 1), \
+    datetime(2008, 7, 1), datetime(2009, 1, 1), datetime(2009, 7, 1)]
+ticks_labels = ['2007-07-01', '2008-01-01', '2008-07-01',\
+    '2009-01-01', '2009-07-01']
+
+#tmin = datetime(2004, 1, 1)
+#tmax = datetime(2012, 1, 1)
+#ticks_time = [datetime(2004, 1, 1), datetime(2006, 1, 1), \
+#    datetime(2008, 1, 1), datetime(2010, 1, 1), datetime(2012, 1, 1)]
+#ticks_labels = ['2004-01-01', '2006-01-01', '2008-01-01',\
+#    '2010-01-01', '2012-01-01']
+
+staloc = pd.read_csv(station_file, sep=r'\s{1,}', header=None, \
+    engine='python')
+staloc.columns = ['station', 'network', 'channels', 'location', 'server', \
+    'latitude', 'longitude', 'time_on', 'time_off']
+
+staloc['time_on']= pd.to_datetime(staloc['time_on'])
+staloc['time_off']= pd.to_datetime(staloc['time_off'])
+
+staloc['channels'] = staloc.apply(lambda x: len(x['channels'].split(',')), axis=1)
+staloc['channels'] = staloc['channels'].astype(int)
+
+staloc = staloc.groupby(['station', 'network', 'channels', 'server', \
+    'latitude', 'longitude']).agg({ \
+    'time_on':lambda x: min(x), \
+    'time_off':lambda x: max(x)}).reset_index()
+
+t = np.arange(tmin, tmax, timedelta(days=1)).astype(datetime)
+nstations = np.zeros(len(t))
+
+for i in range(0, len(t)):
+    df = staloc.loc[(staloc['time_on'] <= t[i]) & (staloc['time_off'] >= t[i])]
+    nstations[i] = int(df['channels'].sum())
+
+# Figure
+params = {'legend.fontsize': 20, \
+          'xtick.labelsize':20, \
[…]

### 2022-01-15 data/Ducellier/plot_several_families.py
Work on figures

@@ -43,16 +43,19 @@ duration = dt.days * 86400.0 + dt.seconds + dt.microseconds * 0.000001
 nw = int(duration / window)
 
 # Indices of LFE families
-indices = [[2, 5, 6], \
-           [12, 13, 25, 20, 23], \
-           [40, 29, 33, 36, 41]]
+#indices = [[2, 5, 6], \
+#           [12, 13, 25, 20, 23], \
+#           [40, 29, 33, 36, 41]]
+indices = [[40, 29, 33, 36, 41]]
 
 # Names of LFE families
-names = [['B1', 'B2', 'B3'], \
-         ['C1', 'C2', 'C3', 'C4', 'C5'], \
-         ['G1', 'G2', 'G3', 'G4', 'G5']]
+#names = [['B1', 'B2', 'B3'], \
+#         ['C1', 'C2', 'C3', 'C4', 'C5'], \
+#         ['G1', 'G2', 'G3', 'G4', 'G5']]
+names = [['G1', 'G2', 'G3', 'G4', 'G5']]
 
-plt.figure(1, figsize=(24, 15))
+#plt.figure(1, figsize=(24, 15))
+plt.figure(1, figsize=(8, 15))
 
 # Loop on templates
 for column in range(0, len(indices)):
@@ -101,5 +104,6 @@ for column in range(0, len(indices)):
             fontsize=24)
 
 plt.tight_layout()
-plt.savefig('LFEdistribution_perm/set_daily_LFEs.eps', format='eps')
+#plt.savefig('LFEdistribution_perm/set_daily_LFEs.eps', format='eps')
+plt.savefig('LFEdistribution_perm/set_daily_LFEs_seriesG.eps', format='eps')
 plt.close(1)

### 2022-01-15 src/get_waveforms.py

@@ -8,6 +8,7 @@ import obspy
 from obspy import UTCDateTime
 from obspy.core.stream import Stream
 
+import matplotlib.pylab as pylab
 import matplotlib.pyplot as plt
 import numpy as np
 import os
@@ -72,10 +73,14 @@ def get_waveform(filename, TDUR, filt, nattempts, waittime, method='RMS'):
         os.makedirs(namedir)
 
     # File to write error messages
-    errorfile = 'error/' + filename + '.txt'
+    errorfile = 'error_waveform/' + filename + '.txt'
+
+    params = {'xtick.labelsize':30, \
+              'ytick.labelsize':30}
+    pylab.rcParams.update(params)
 
     # Loop over stations
-    for station in staNames:
+    for station in ['ME57']: #staNames:
         # Create streams
         EW = Stream()
         NS = Stream()
@@ -154,47 +159,48 @@ def get_waveform(filename, TDUR, filt, nattempts, waittime, method='RMS'):
             nt = EWstack[0].stats.npts
             t = dt * np.arange(0, nt)
             norm = np.max(np.abs(EWstack[0].data))
-            plt.plot(t, EWstack[0].data / norm, 'r', label='Stack')
+            plt.plot(t, EWstack[0].data / norm, 'k', label='Stack')
             t0 = ndt * np.arange(0, np.shape(uk)[1])
             norm = np.max(np.abs(uk[ns + index, :]))
-            plt.plot(t0, uk[ns + index, :] / norm, 'k', label='Waveform')
+#            plt.plot(t0, uk[ns + index, :] / norm, 'k', label='Waveform')
             plt.xlim(0.0, 60.0)
-            plt.title('East component', fontsize=16)
-            plt.xlabel('Time (s)', fontsize=16)
-            plt.ylabel('Velocity (m/s)', fontsize=16)
-            plt.legend(loc=1)
+            plt.title('East component', fontsize=30)
+#            plt.xlabel('Time (s)', fontsize=30)
+            plt.ylabel('Velocity (m/s)', fontsize=30)
+#            plt.legend(loc=1)
             # NS component
             ax2 = plt.subplot(312)
             dt = NSstack[0].stats.delta
             nt = NSstack[0].stats.npts
             t = dt * np.arange(0, nt)
             norm = np.max(np.abs(NSstack[0].data))
-            plt.plot(t, NSstack[0].data / norm, 'r', label='Stack')
[…]

### 2022-01-15 src/plot_several_tidal_stress.py

@@ -22,8 +22,12 @@ mu = 0.1
 B = 0.5
 
 # LFE families
-families = [0, 0, 5, 14, 20, 28, 40]
-names = ['A (all LFEs)', 'A', 'B2', 'D', 'C4', 'F', 'G1']
+#families = [0, 0, 5, 14, 20, 28, 40]
+#names = ['A (all LFEs)', 'A', 'B2', 'D', 'C4', 'F', 'G1']
+#families = [0, 5, 14, 20, 28, 40]
+#names = ['A', 'B2', 'D', 'C4', 'F', 'G1']
+families = [0, 0]
+names = ['A (2008 ETS event)', 'A (all LFEs)']
 
 # List of LFE families
 templates = np.loadtxt('../data/Plourde_2015/templates_list.txt', \
@@ -42,7 +46,9 @@ threshold.columns = ['family', 'threshold_FAME', 'threshold_perm']
 begin_time = pd.read_csv('../data/For_Ken_California_LFE/begin_time.txt', sep=' ', header=None)
 begin_time.columns = ['latitude', 'longitude', 'begin_time']
 
-plt.figure(1, figsize=(28, 10))
+#plt.figure(1, figsize=(28, 10))
+#plt.figure(1, figsize=(14, 15))
+plt.figure(1, figsize=(14, 5))
 
 # Loop on templates
 for i in range(0, len(families)):
@@ -83,7 +89,8 @@ for i in range(0, len(families)):
     df['date'] = date
 
     # Divide catalog between first and last part of ETS event
-    if i == 0:
+#    if i == 0:
+    if i == 1:
         df2 = df.copy(deep=True)
     else:
         t2 = ymdhms2matlab(2008, 4, 1, 0, 0, 0) + time_ETS
@@ -120,29 +127,52 @@ for i in range(0, len(families)):
                 count[k] = len(df2.loc[(df2.coulomb >= boxes[k]) & (df2.coulomb <= boxes[k + 1])])
             count_coulomb[k] = np.sum((coulomb >= boxes[k]) & (coulomb <= boxes[k + 1]))
 
+#        if i == 0:
+#            plt.subplot2grid((2, 4), (0, 3))
+#        elif i == 1:
+#            plt.subplot2grid((2, 4), (0, 0))
+#        elif i == 2:
+#            plt.subplot2grid((2, 4), (0, 1))
+#        elif i == 3:
+#            plt.subplot2grid((2, 4), (0, 2))
[…]

### 2022-01-15 src/find_LFEs.py
New figure

@@ -188,7 +188,7 @@ def find_LFEs(filename, stations, tbegin, tend, TDUR, filt, \
     """
 
     # Get the network, channels, and location of the stations
-    staloc = pd.read_csv('../data/Ducellier/stations_permanent.txt', \
+    staloc = pd.read_csv('../data/Ducellier/stations_temporary.txt', \
         sep=r'\s{1,}', header=None, engine='python')
     staloc.columns = ['station', 'network', 'channels', 'location', \
         'server', 'latitude', 'longitude', 'time_on', 'time_off']
@@ -207,7 +207,7 @@ def find_LFEs(filename, stations, tbegin, tend, TDUR, filt, \
     # Read the templates
     templates = Stream()
     for station in stations:
-        data = pickle.load(open('templates_new/' + filename + \
+        data = pickle.load(open('templates/' + filename + \
             '/' + station + '.pkl', 'rb'))
         if (len(data) == 3):
             EW = data[0]
@@ -266,7 +266,7 @@ def find_LFEs(filename, stations, tbegin, tend, TDUR, filt, \
         for channel in mychannels:
             angle = inventory.get_orientation(network + '.' + \
                 station + '.' + mylocation + '.' + channel, \
-                UTCDateTime(2012, 1, 1, 0, 0, 0))
+                UTCDateTime(2008, 4, 1, 0, 0, 0))
             reference.append(angle)
 
         # First case: we can get the data from IRIS
@@ -353,8 +353,9 @@ def find_LFEs(filename, stations, tbegin, tend, TDUR, filt, \
 
             # Draw figure
             if (draw == True):
-                params = {'xtick.labelsize':16,
-                          'ytick.labelsize':16}
+                params = {'legend.fontsize':30, \
+                          'xtick.labelsize':30,
+                          'ytick.labelsize':30}
                 pylab.rcParams.update(params) 
                 plt.figure(1, figsize=(20, 8))
                 if np.shape(index)[1] > 0:
@@ -372,11 +373,12 @@ def find_LFEs(filename, stations, tbegin, tend, TDUR, filt, \
                     raise ValueError( \
                         'Type of threshold must be MAD or Threshold')
                 plt.xlim(0.0, (np.shape(meancc)[0] - 1) * dt)
-                plt.xlabel('Time (s)', fontsize=24)
[…]

### 2022-01-16 src/compute_traveltimes.py
Work on travel times

@@ -1,0 +1,142 @@
+"""
+This module convert horizontal components into radial and transverse,
+cross-correlate templates between components and between stations
+and returns the relative travel times
+"""
+
+import numpy as np
+import obspy
+import os
+import pandas as pd
+import pickle
+
+from math import atan2, cos, pi, sin, sqrt
+
+def compute_traveltimes(family, stations, channels, latitudes, longitudes, \
+        nt, dt, lat0, lon0):
+    """
+    type family = String
+    family = Name of the LFE family
+    type stations = List of strings
+    stations = Names of the stations to be used
+    type channels = List of strings
+    channels = Channels to be used
+    type latitudes = List of floats
+    latitudes = List of latitudes of the stations
+    type longitudes = List of floats
+    longitudes = List of longitudes of the stations
+    type nt = Integer
+    nt = Length of templates
+    type dt = Float
+    dt = Time step for templates
+    type lat0 = Float
+    lat0 = Latitude of the epicenter of the LFE family
+    type lon0 = Float
+    lon0 = Longitude of the epicenter of the LFE family
+    """
+    # To compute distances
+    a = 6378.136
+    e = 0.006694470
+    # Get the number of stations with horizontal and vertical components
+    nsta3 = 0
+    nsta1 = 0
+    for (station, channel) in zip(stations, channels):
+        if len(channel.split(',')) == 3:
+            nsta3 = nsta3 + 1
+        else:
+            nsta1 = nsta1 + 1
+    # Initialization
+    vertical = np.zeros((nt, nsta1 + nsta3))
+    radial = np.zeros((nt, nsta3))
+    transverse = np.zeros((nt, nsta3))
+    sta_V = []
+    sta_H = []
+    index_V = 0
+    index_H = 0
+    df_SP = pd.DataFrame(columns=['station', 't_SP_R', 't_SP_T'])
+    # Fill the arrays
+    for station, channel, latitude, longitude in zip(stations, channels, latitudes, longitudes):
+        channel = channel.split(',')
+        # Get vertical component
+        filename = 'templates_both/' + family + '/' + station + '_' + channel[-1] + '.pkl'
[…]

### 2022-01-16 paper/answer_reviewers.tex
Finished draft of revisions

@@
 
+We added the depth contours of the plate boundary model from McCrory et al. (2006) and fault lines. We added a cross section with the depth of the LFE families.
+
+\bigskip
+
 \textit{Lines 73 - 74: Bostock (2015, https://doi.org/10.1002/2015JB012195) provides 10-year catalog of LFES at the Vancouver Island.}
@@
 
+We analyzed the seismic data one hour a time.
+For each hour of data, we assumed that there was an LFE each time the average cross-correlation over all stations and channels is higher than 8 times the median absolute deviation.
+The threshold is thus different for each hour of data and it is difficult to show its values in the figure.
+
+\bigskip
+
 \textit{Lines 165 - 175: How second thresholds (CC values vs stations numbers) were chosen for each seismic station?
@@
 (A figure comparing before and after the selection step will be useful.)}
+
+\bigskip
+
+The choice of the threshold is explained in more detail later in the text, when we explain how we cleaned the longer catalog (2004-2011).
+The main idea is that if an LFE is present both in the 2007-2009 FAME catalog and in the 2004-2011 permanent networks catalog, then it is unlikely to be a false detection.
+We assumed that all LFEs present in both catalogs are true detections.
+The LFEs recorded during the period 2007-2009 that are present in only one catalog are then assumed to be false detections.
+We then chose a threshold such that at least 50 \% of the LFE detections are true detections.
+There is thus one threshold per family.
+The thresholds are also different for the two catalogs 2007-2009 and 2004-2011 because the stations and the quality of the templates are different for both catalogs.
+We added in a supplement a table with the values of the thresholds.
+\\
+
+Our filtering method kept 37 \% of the LFEs for the 2004-2011 catalog and 16 \% of the LFEs for the 2007-2009 catalog.
+We have added in the supplements figures of the catalogs without filtering the LFEs.
 
@@
 
+We have computed the catalog with only the FAME stations and the catalog with only the permanent stations.
+We have not computed a catalog using both FAME and permanent stations.
+We agree that it would be interesting to compute this third catalog and study how many LFEs are missed when removing the FAME stations, but this is beyond the scope of this paper.
+
+\bigskip
+
 \textit{Line 209: "two thresholds" for what?}
@@
 
+One threshold to filter the 2007-2009 catalog computed with the FAME stations and one threshold to filter the 2004-2011 catalog computed with the permanent stations.
+We use two different thresholds because the quality of the templates is not the same for the two catalogs.
+
+\bigskip
+
 \textit{Line 215: It will be helpful to visually show temporal changes of the number of available seismic stations.}
+
+\bigskip
+
+We have added two figures in the supplement with number of channels available as a function of time.
 
@@
 
+We did not see any burst of LFEs coincident with the arrival of seismic waves from regional or distant earthquakes.
+
+\bigskip
+
 \textit{Lines 290 - 294: I think the vertical axis of Figure 9 should be average recurrence interval rather than the number of events.}
+
+\bigskip
+
+We changed the figure and plotted recurrence time instead of number of events.
 
@@
 \textit{Line 306: Which fault plane did authors assume to calculate tidal stress?}
+
+\bigskip
+
+The fault plane is the plate boundary model of McCrory et al. (2006).
 
@@
 
+To define the number of events, we assume that there is an event each time that there are at least five LFEs during a single day.
+If two events are separated by less than five days, we assume that this is a single event.
+We remade the figure to plot average recurrence time instead of number of events.
+
+\bigskip
+
 \textit{Line 22: what does "other" refer to? Not associated with tremor detections?}
@@
 Things like "tectonic tremor", "slow slip" are certainly not familiar to most people, so that's not plain language.}
+
+\bigskip
+
+We modified the plain language summary.
 
@@
 \textit{Figure 1: it would be nice to have the trench, the San Andreas Fault, (+ the Maacama and Bucknell Creek faults?) and/or plate interface contours on this map}
+
+\bigskip
+
+We added plate contours and faults to the map.
 
@@
 
+To keep an LFE in the filtered catalog, we require that the product of the cross-correlation by the number of channels recording at that time is higher than a threshold.
+We thus require a higher cross-correlation value to keep the LFE in the catalog if some stations are inactive.
+The threshold is different for each LFE family and applied to the stacked cross-correlation over all channels.
+
+\bigskip
+
 \textit{Line 180: "Additionally, one LFE family located on the southern end of the subduction zone has also shorter recurrence intervals than families located farther north, and behaves more similarly to the strike-slip fault families." What locations are you using here?
@@
 It may be good to specify the depth here too, since it may not be surprising to see frequent bursts if the family is at 45 km depth.}
+
+\bigskip
+
+We use the same locations as Pourde et al. (2015). We have not tried to relocate the families using the new templates. We specified the latitude and depth of the family in the text.
 
@@
 
+We divided possible values of the Coulomb stress changes into bins and computed the number of hours for which the Coulomb stress change takes values in each bins.
+As Coulomb stress change often takes small values and rarely takes high values, the expected number of LFEs is higher around 0 and smaller for big negative or positive values.
+We did not normalize the results, so the expected number of LFEs is proportional to the total number of LFEs occurring for each family.
+
+\bigskip
+
 \textit{Supplementary Material: it might be worth repeating the acronym explanations (IRIS, NDEDC) as well as the links to the data sources in this document}

### 2022-01-16 paper/agujournaltemplate_highlighted.tex
Finished draft of revisions

@@
 
-\authors{Ariane Ducellier\affil{1}, Kenneth Creager\affil{1}}
+\authors{Ariane Ducellier\affil{1}, Kenneth C. Creager\affil{1}}
 
@@
 Low-frequency earthquakes (LFEs) are small magnitude earthquakes, with typical magnitude less than 2, and reduced amplitudes at frequencies greater than 10 Hz relative to ordinary small earthquakes.
-Their occurrence is often associated with tectonic tremor and slow slip events along the plate boundary in subduction zones and occasionally transform fault zones.
-They are usually grouped into families of events, with all the earthquakes of a given family originating from the same small patch on the plate interface and recurring more or less episodically in a bursty manner.
+They are usually grouped into families of events, with all the earthquakes of a given family originating from the same small patch on the plate interface.
+\textbf{LFEs tend to happen in bursts, with dozen of earthquakes occurring within a few days, followed by weeks or months of quiet}.
 In this study, we extend the LFE catalog obtained by ~\citeA{PLO_2015} to the 8-year period 2004-2011.
-As in northern Cascadia, the down-dip LFE families have \textbf{shorter recurrence intervals} than the up-dip families.
-For the April 2008 Episodic Tremor and Slip event, the best recorded LFE families exhibit a strong tidal stress sensitivity.
-The southernmost LFE family, which has been interpreted to be on the subduction plate boundary has a short recurrence time.
-Also, these LFEs tend to occur during times when tidal stress discourages slip on the plate boundary.
-Both observations suggest this LFE family may be on a different fault.
+As in northern Cascadia, the \textbf{LFE families located at greater depth are more active, with shorter time intervals between two earthquake bursts, than the LFE families located at shallower depth.
+Earth tides have also an influence on LFE activity: LFEs are more likely to occur when the stress changes associated with the tides favor shear failure on the plate boundary}.
 
@@
 
-~\citeA{PLO_2015}) have detected LFEs in southern Cascadia during the April 2008 ETS event using seismic data from the EarthScope Flexible Array Mendocino Experiment (FAME).
+~\citeA{PLO_2015} have detected LFEs in southern Cascadia during the April 2008 ETS event using seismic data from the EarthScope Flexible Array Mendocino Experiment (FAME).
 They used a combination of autodetection methods and visual identification to obtain the initial templates.
@@
 \begin{figure}
-\noindent\includegraphics[width=\textwidth, trim={1.5cm 4cm 1cm 10cm},clip]{figures/map_LFEs.eps}
-\caption{Map showing the location of the LFE families (back dots) and the seismic stations used in this study.
+\noindent\includegraphics[width=\textwidth, trim={0.5cm 7cm 1.5cm 7cm},clip]{figures/map_LFEs.eps}
+\caption{Map showing the location of the LFE families (black dots) and the seismic stations used in this study.
 Red triangles are the stations from the FAME experiment, green triangles are one-component permanent stations, blue triangles are three components permanent stations.
-Red stars are moderate ($M > 5$) nearby earthquakes.}
+Red stars are moderate ($M > 5$) nearby earthquakes.
+\textbf{Contour lines are the depth contours of the plate boundary model from ~\citeA{MCC_2006}.
+The cross section shows the depth of the LFE families.
+The line corresponds to the plate boundary model from ~\citeA{MCC_2006} at latitude 41N.}}
 \label{pngfiguresample}
@@
 Using a threshold equal to eight times the median absolute deviation of the stacked cross-correlation may produce false detections, therefore we filtered the LFE detection times before visualizing the two-year-long catalog.
-As the number of seismic stations recording may change with time as the stations were progressively installed during Summer and Fall 2007, and then progressively removed during May and June 2009, we kept only LFE detections for which the product of the cross-correlation value by the number of stations recording at that time is higher than a threshold.
-The threshold is thus different for each LFE family.
+As the number of seismic stations recording may change with time as the stations were progressively installed during Summer and Fall 2007, and then progressively removed during May and June 2009, we kept only LFE detections for which the product of the \textbf{stacked} cross-correlation value by the number of \textbf{channels} recording at that time is higher than a threshold.
+\textbf{We will explain later in the text how the threshold is chosen}.
+The threshold is different for each LFE family, \textbf{but is constant over time for a given LFE family}.
 The resulting LFE catalog for the period 2007-2009 is shown in Figure 3.
 For comparison, we also plotted the tremor detection times from ~\citeA{BOY_2015}.
-\\
+\textbf{Filtering the catalog has removed about 84 \% of the LFEs.
+As a reference, we plotted in the Supplementary Material the catalog without filtering the LFEs and the number of channels recording as a function of time.} \\
 
@@
 The LFE families located south on the strike-slip fault from the San Andreas Fault system have much shorter recurrence intervals than the LFE families located on the subduction zone.
-Additionally, one LFE family located on the southern end of the subduction zone has also shorter recurrence intervals than families located farther north, and behaves more similarly to the strike-slip fault families.
+Additionally, one LFE family located on the southern end of the subduction zone \textbf{(family A at 40.09N and 34.9km depth)} has also shorter recurrence intervals than families located farther north, and behaves more similarly to the strike-slip fault families.
 \\
@@
 
-For most families, we find that we can obtain good templates with signal-to-noise ratio for several stations.
+For most families, we find that we can obtain good templates with high signal-to-noise ratio for several stations.
 Only nine families have four or less seismic stations with good templates.
@@
 For most of the families located on the subduction zone, we obtained a good agreement between both catalogs.
-We eliminate two families for which too few permanent stations have good templates, and it was not possible to detect LFEs with the available templates.
+We eliminate six families for which too few permanent stations have good templates, and it was not possible to detect LFEs with the available templates.
 However, we were able to detect most LFE events even without the presence of the temporary stations from the FAME network.
@@
 In the following, we focus on the period 2004-2011.
-In November 2011, several one-component stations stopped recording and the number of available stations started decreasing, which is why we did not look for LFE event after that date.
+In November 2011, several one-component stations stopped recording and the number of available stations started decreasing, which is why we did not look for LFE events after that date.
 The resulting LFE catalog for the period 2004-2011 is shown in Figure 6.
@@
 Figure 7 shows the details of six big ETS events in 2004, 2005, 2006, 2007 and 2008.
-\\
+\textbf{The catalog shown in Figure 6 has been filtered using the threshold computed above.
+Filtering the catalog has removed about 63 \% of the LFEs.
+As a reference, we plotted in the Supplementary Material the catalog without filtering the LFEs and the number of channels recording as a function of time.} \\
 
@@
 \textbf{The tremor catalog of ~\citeA{BOY_2015} starts in 2005.
-This is why no tremor detections can be shown or the two events in 2004.}}
+This is why no tremor detections can be shown for the two events in 2004.}}
 \label{pngfiguresample}
@@
 For all three sets of families, LFE events are more frequent for the easternmost family than for the westernmost family, as was also the case in northern Cascadia ~\cite{SWE_2019}.
-It is more difficult to compare event size and swarm duration as the number of stations and the quality of the templates are different from each family, and may have a strong influence on the number of LFEs detected.
-To summarize the findings, we plot in Figure 9 the number of LFE events as a function of the distance in the eastern direction from the upper limit of the tremor.
-We clearly see that the number of events increases with the down dip distance.
+It is more difficult to compare event size and swarm duration as the number of stations and the quality of the templates are different for each family, and may have a strong influence on the number of LFEs detected.
+To summarize the findings, we plot in Figure 9 the \textbf{average time between} LFE events as a function of the distance in the eastern direction from the \textbf{western} limit of the tremor.
+We clearly see that the \textbf{average time between} decreases with the down dip distance.
 The southernmost family A is also added in Figure 9, but does not fit the general trend.\\
@@
 \noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/nb_LFE_events.eps}
-\caption{Number of LFE events as a function of distance in the eastern direction from the \textbf{westward} limit of tremor for the three LFE families in group B (triangles in Figure 1), the five LFE families in group C (diamonds in Figure 1), and the five LFE families in group G (pentagons in Figure 1).
-Family A (square in Figure 1) has much more LFE events and is shown by an arrow.}
+\caption{\textbf{Average time between} LFE events as a function of distance in the eastern direction from the \textbf{westward} limit of tremor for the three LFE families in group B (triangles in Figure 1), the five LFE families in group C (diamonds in Figure 1), and the five LFE families in group G (pentagons in Figure 1).
+Family A (square in Figure 1) has much \textbf{shorter time intervals between } LFE events.}
 \label{pngfiguresample}
@@
 where $\Delta \tau$ is the change in shear stress on the fault plane in the slip direction, $\Delta \sigma$ is the change in fault normal stress (positive is tensile), $\mu$ is the coefficient of intrinsic friction, $\Delta \sigma_m$ is the change in mean stress and $B$ is the Skempton's coefficient ~\cite{HOU_2015}.
-We take the values $\mu = 0.1$ and $B = 0.5$ for the friction and the Skempton's coefficient \textbf{, as was done by ~\citeA{HOU_2015}}.
+We take the values $\mu = 0.1$ and $B = 0.5$ for the friction and the Skempton's coefficient, \textbf{as was done by ~\citeA{HOU_2015}}.
 We then divided the values of tidal Coulomb stress change into 20 stress bins and computed for each LFE family the number of LFEs occurring at a time when the value of the stress was in a given bin.
@@
 Houston for the tidal stress calculation in the Cascadia subduction zone.
+The authors would like to thank Alexandre Plourde, an anonymous reviewer and the associate editor whose comments helped improve the manuscript.
 This project was funded by NSF grant EAR-1358512.

### 2022-01-16 paper/supplement.tex
Work on answers
Finished draft of revisions

@@
-\documentclass{article}
-\usepackage[lmargin=1 in, rmargin=1 in, tmargin=1 in, bmargin=1 in]{geometry}
+\documentclass[draft]{agujournal2019}
+\usepackage{url}
 \usepackage{lineno}
+\usepackage{longtable}
+
 \linenumbers
+
+\draftfalse
+
+\journalname{JGR: Solid Earth}
+
+\renewcommand{\thefigure}{S\arabic{figure}}
+\renewcommand{\thetable}{S\arabic{table}}
 
@@
 
-\title{Supplementary Material}
-\date{}
-\maketitle
+\title{An eight-year-long low-frequency earthquake catalog for Southern Cascadia}
+
+\authors{Ariane Ducellier\affil{1}, Kenneth C. Creager\affil{1}}
+
+\affiliation{1}{University of Washington}
+
+\correspondingauthor{Ariane Ducellier}{ducela@uw.edu}
+
+\begin{figure}
+\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/unfiltered_FAME.eps}
+\caption{Same as Figure 3 from the main text, but without filtering the LFEs.
+They are many false detections at the beginning and the end of the catalog because the FAME stations were not yet installed / already removed.}
+\label{pngfiguresample}
+\end{figure}
+
+\begin{figure}
+\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/unfiltered_perm.eps}
+\caption{Same as Figure 6 from the main text, but without filtering the LFEs.}
+\label{pngfiguresample}
+\end{figure}
+
+\begin{figure}
+\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/timeline_FAME.eps}
+\caption{Evolution of the number of channels available for the computation of the 2007-2009 catalog using the temporary FAME stations.}
+\label{pngfiguresample}
+\end{figure}
+
+\begin{figure}
+\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/timeline_perm.eps}
+\caption{Evolution of the number of channels available for the computation of the 2004-2011 catalog using the permanent stations.}
+\label{pngfiguresample}
+\end{figure}
 
 \begin{table}
-\caption{Temporary stations used for the 2007-2009 catalog}
+\caption{Temporary stations used for the 2007-2009 catalog.}
 \centering
+\footnotesize
 \begin{tabular}{c c c c c c c c c}
@@
 
+\small{
 \begin{table}
-\caption{Permanent stations used for the 2004-2011 catalog}
+\caption{Permanent stations used for the 2004-2011 catalog.}
 \centering
+\footnotesize
 \begin{tabular}{c c c c c c c c c}
@@
 \end{table}
+}
+
+The data centers providing the seismic waveforms are the Incorporated Research Institutions for Seismology (IRIS) (Alan Levander, 2007), and the Northern California Earthquake Data Center (NCEDC), doi:10.7932/NCEDC.
+
+\begin{center}
+\begin{longtable}{c c c}
+\caption{Thresholds used to clean the catalogs.
+An LFE is kept in the catalog if its cross-correlation value multiplied by the number of channels recording when it was detected is higher than the threshold.
+The threshold is missing for the families for which there were not enough permanent stations with good templates to obtain reliable LFE detections.} \\
+\hline
+Family & Threshold 2007-2009 & Threshold 2004-2011 \\
+\hline
+\endfirsthead
+\hline
+Family & Threshold 2007-2009 & Threshold 2004-2011 \\
+\hline
+\endhead
+\endfoot
+\hline
+\endlastfoot\
+080401.05.050 & 1.4 & 1.9 \\
+080405.11.042 & 2.0 & 1.6 \\
+080408.08.007 & 1.7 & 1.5 \\
+080408.15.023 & 2.0 & 1.3 \\
+080408.08.029 & 2.3 & 1.4 \\
+080408.16.026 & 1.8 & 1.4 \\
+080410.01.050 & 3.5 & 1.3 \\
+080410.09.032 & 3.9 & 1.4 \\
+080410.12.039 & 1.9 & 1.3 \\
+080410.12.040 & 5.4 & 2.3 \\
+080411.04.013 & 3.4 & 1.5 \\
+080411.04.023 & 3.6 & 1.5 \\
+080410.13.055 & 1.9 & 1.3 \\
+080412.03.029 & 2.2 & 1.0 \\
+080412.11.038 & 2.2 & 1.3 \\
+080412.22.047 & 3.2 & 1.5 \\
+080413.13.026 & 2.2 & 1.3 \\
+080412.22.040 & 3.5 & 1.6 \\
+080413.07.015 & 2.0 & 1.6 \\
+080413.07.023 & 1.8 & 1.4 \\
+080413.16.058 & 2.2 & 0.1 \\
+080413.18.013 & 2.6 & 1.2 \\
+080413.20.036 & 2.1 & 1.1 \\
+080414.12.016 & 2.0 & 1.2 \\
+080414.12.020 & 1.5 & 1.2 \\
+080414.10.058 & 1.8 & 1.2 \\
+080414.18.003 & NA & NA \\
+080415.11.006 & 4.6 & 1.6 \\
+080415.11.008 & 3.0 & 1.8 \\
+080415.24.028 & 2.5 & 1.7 \\
+080416.15.003 & 2.8 & 1.7 \\
+080418.03.001 & 5.0 & 1.5 \\
+080415.19.030 & 2.9 & 1.9 \\
+080419.24.054 & 3.4 & 2.2 \\
+080416.13.033 & 3.9 & 2.0 \\
+080417.15.043 & 3.3 & 1.7 \\
+080418.02.049 & 3.7 & 1.6 \\
+080419.04.046 & 3.5 & 1.5 \\
+080420.01.019 & 2.3 & 1.6 \\
+080420.04.009 & 2.2 & 1.4 \\
+080420.05.032 & 3.0 & 1.8 \\
+080420.08.042 & 1.8 & 1.5 \\
+080421.14.048 & 2.1 & 1.6 \\
+080421.15.050 & 1.9 & 1.5 \\
+080421.16.053 & 3.0 & 1.4 \\
+080421.16.054 & 2.3 & 1.4 \\
+080421.17.056 & 2.1 & 1.3 \\
+080421.23.033 & 2.7 & 1.4 \\
+080422.13.003 & 3.2 & 1.7 \\
+080422.12.039 & 1.7 & 1.1 \\
+080422.13.043 & 2.7 & 1.6 \\
+080422.15.030 & 2.0 & 1.5 \\
+080424.04.058 & 3.3 & 1.8 \\
+080424.05.060 & 2.2 & 1.7 \\
+080426.05.008 & 1.8 & 1.6 \\
+080426.06.027 & 2.1 & 1.8 \\
+080426.20.030 & 1.5 & 1.7 \\
+080427.04.052 & 2.5 & 1.5 \\
+080427.13.036 & 2.1 & 1.5 \\
+080427.20.043 & 2.5 & 2.0 \\
+080429.15.005 & NA & NA \\
+080326.07.004 & NA & NA \\
+080326.07.048 & NA & NA \\
+080326.08.015 & 2.7 & 1.0 \\
+080326.09.007 & NA & NA \\
+080328.09.029 & NA & NA \\
+\hline
+\end{longtable}
+\end{center}
 

### 2022-01-16 data/Ducellier/compare_catalog.py

@@ -65,10 +65,10 @@ if __name__ == '__main__':
     tend = datetime(2009, 5, 14, 0, 0, 0)
 
     # Thresholds
-    thresh1 = 2.7
-    thresh2 = 1.0
+    thresh1 = 1.4
+    thresh2 = 1.9
 
-    for i in range(63, 64): #len(families)):
+    for i in range(0, 1): #len(families)):
         family = families['family'].iloc[i]
         dt = families['dt'].iloc[i]
         compare_catalog(family, tbegin, tend, dt, thresh1, thresh2)

### 2022-01-16 data/Ducellier/plot_daily_LFEs.py

@@ -43,7 +43,7 @@ duration = dt.days * 86400.0 + dt.seconds + dt.microseconds * 0.000001
 nw = int(duration / window)
 
 # Loop on templates
-for i in range(0, np.shape(templates)[0]):
+for i in range(0, 1): #range(0, np.shape(templates)[0]):
 
     # Open LFE catalog
     namedir = 'catalogs/' + templates[i][0].astype(str)
@@ -73,14 +73,19 @@ for i in range(0, np.shape(templates)[0]):
                 0.000001
             index = int(duration / window)
             X[index] = X[index] + 1
-            
+
+    index = np.where(X >= 5)[0]
+    times = index[1:] - index[:-1]
+    keep = times[times >= 5]
+    print(len(keep), np.mean(keep))
+
     # Plot figure
-    plt.figure(1, figsize=(20, 10))
-    plt.stem(np.arange(0, len(X)), X, 'k-', markerfmt=' ', basefmt=' ')
-    plt.xlim([-0.5, len(X) - 0.5])
-    plt.xlabel('Time (days) since 2004/01/01', fontsize=24)
-    plt.ylabel('Number of LFEs', fontsize=24)
-    plt.title('Family {} ({:d} LFEs)'.format(templates[i][0].astype(str), np.sum(X)), \
-        fontsize=24)
-    plt.savefig('LFEdistribution_perm/' + templates[i][0].astype(str) + '.eps', format='eps')
-    plt.close(1)
+#    plt.figure(1, figsize=(20, 10))
+#    plt.stem(np.arange(0, len(X)), X, 'k-', markerfmt=' ', basefmt=' ')
+#    plt.xlim([-0.5, len(X) - 0.5])
+#    plt.xlabel('Time (days) since 2004/01/01', fontsize=24)
+#    plt.ylabel('Number of LFEs', fontsize=24)
+#    plt.title('Family {} ({:d} LFEs)'.format(templates[i][0].astype(str), np.sum(X)), \
+#        fontsize=24)
+#    plt.savefig('LFEdistribution_perm/' + templates[i][0].astype(str) + '.eps', format='eps')
+#    plt.close(1)

### 2022-01-16 data/Ducellier/plot_nb_events.py

@@ -16,7 +16,7 @@ params = {'legend.fontsize': 24, \
 pylab.rcParams.update(params)
 
 events = pd.read_csv('LFEdistribution_perm/nb_LFE_events.txt', sep=r'\s{1,}', header=None, engine='python')
-events.columns = ['group', 'name', 'lon', 'lat', 'x', 'y', 'nb']
+events.columns = ['group', 'name', 'lon', 'lat', 'x', 'y', 'nb', 'rt']
 
 groups = events['group'].unique()
 
@@ -26,25 +26,29 @@ cycol = cycle('bgrcmk')
 for group in groups:
     events_sub = events.loc[events['group'] == group]
     color = next(cycol)
-    if group == 'A':
-        plt.arrow(events_sub['x'].iloc[0], 50, 0, 2, width=0.3, color=color)
-        plt.annotate(events_sub['name'].iloc[0] + ' (' + str(int(events_sub['nb'].iloc[0])) + ')', \
-            (events_sub['x'].iloc[0] + 1, 50), fontsize=24, color=color)
-    else:
-        plt.scatter(events_sub['x'], events_sub['nb'], c=color, s=100)
-        for i in range(0, len(events_sub)):
-            if events_sub['name'].iloc[i] == 'G2':
-                plt.annotate(events_sub['name'].iloc[i], \
-                    (events_sub['x'].iloc[i] - 5, events_sub['nb'].iloc[i]), \
-                    fontsize=24, color=color)
-            else:
-                plt.annotate(events_sub['name'].iloc[i], \
-                    (events_sub['x'].iloc[i] + 1, events_sub['nb'].iloc[i]), \
-                    fontsize=24, color=color)
+    plt.scatter(events_sub['x'], events_sub['rt'], c=color, s=100)
+    for i in range(0, len(events_sub)):
+        if events_sub['name'].iloc[i] in ['C2', 'C4']:
+            plt.annotate(events_sub['name'].iloc[i], \
+                (events_sub['x'].iloc[i] - 5, events_sub['rt'].iloc[i]), \
+                fontsize=24, color=color)
+        elif events_sub['name'].iloc[i] == 'G2':
+            plt.annotate(events_sub['name'].iloc[i], \
+                (events_sub['x'].iloc[i] + 1, events_sub['rt'].iloc[i] + 10), \
+                fontsize=24, color=color)
+        elif events_sub['name'].iloc[i] == 'G3':
[…]

### 2022-01-16 data/Ducellier/plot_tremor_nbLFEs.py

@@ -13,8 +13,8 @@ from math import floor
 from date import ymdhms2day
 
 # Time boundaries
-xmin = 2005.0
-xmax = 2005.1
+xmin = 2007.5
+xmax = 2009.5
 
 # Space boundaries
 latmin = 39.4
@@ -46,24 +46,29 @@ templates = np.loadtxt('../Plourde_2015/templates_list.txt', \
 threshold = pd.read_csv('threshold_cc.txt', sep=r'\s{1,}', header=None, engine='python')
 threshold.columns = ['family', 'threshold_FAME', 'threshold_perm']
 
+all_LFEs = 0
+kept_LFEs = 0
+
 # Loop on templates
 for i in range(0, np.shape(templates)[0]):
 
     # Plot only good data
-    if threshold['threshold_perm'].iloc[i] > 0.0:
+    if threshold['threshold_FAME'].iloc[i] > 0.0:
 
         # Get latitude
         latitude = templates[i][2]
 
         # Open LFE catalog
         namedir = 'catalogs/' + templates[i][0].astype(str)
-        namefile = namedir + '/catalog_2004_2011.pkl'
+        namefile = namedir + '/catalog_2007_2009.pkl'
         df = pickle.load(open(namefile, 'rb'))
 
+        all_LFEs = all_LFEs + len(df)
+
         # Filter LFEs
-#        maxc = np.max(df['nchannel'])
-#        df = df.loc[df['cc'] * df['nchannel'] >= 0.1 * maxc]
-        df = df.loc[df['cc'] * df['nchannel'] >= threshold['threshold_perm'].iloc[i]]
+#        df = df.loc[df['cc'] * df['nchannel'] >= threshold['threshold_FAME'].iloc[i]]
+
+        kept_LFEs = kept_LFEs + len(df)
 
         time = np.arange(xmin, xmax, 1.0/365.5)
         nbLFEs = np.zeros(np.shape(time)[0])
@@ -88,13 +93,13 @@ for i in range(0, np.shape(templates)[0]):
 #        plt.scatter(time, np.repeat(latitude, np.shape(time)[0]), c=nbLFEs, cmap='autumn')
 
 # Plot time line
-#tbegin = ymdhms2day(2007, 9, 25, 0, 0, 0)
-#tend = ymdhms2day(2009, 5, 14, 0, 0, 0)
-#plt.arrow(tbegin, 39.2, tend - tbegin, 0, head_width=0.05, \
[…]

### 2022-01-16 matlab/makeTTgrid.m

@@ -1,0 +1,83 @@
+function [TTgrid,LAT,LON,DEP] = makeTTgrid(staLat, staLon, grd, model);
+%  makeTTGrid      calculate travel time grid
+% USAGE: [TTgrid,LAT,LON,DEP] = makeTTgrid(staLat, staLon, grd, model);
+%
+% Input:
+%  staLat   vector of station latitudes (geographic degrees)
+%  staLon   vector of station longitudes (geographic degrees)
+%  grd      structure containing 3-D source grid 
+%           grd.lon = vector of source longitudes (geographic degrees)
+%           grd.lat = vector of source latitudes (geographic degrees)
+%           grd.depth = vector of source depths (km positive down)
+%
+% Output:
+%  TTgrid   vector of structures for each station containing containing fields 
+%           TTgrid(ksta).TIM  3-D array of travel time (s)
+%           TTgrid(ksta).XI   2-D array of azimuths (deg)
+%           TTgrid(ksta).DELT 3-D array of horizontal distancd (km)
+%  LAT      3-D array of latitudes (geographic degrees)
+%  LON      3-D array of longitudes (geographic degrees)
+%  DEP      3-D array of depths (km)
+% 
+%
+%G(2).arrayName='SEQ';   G(2).array_loc=[47.99158525; -122.93713188];
+%G(3).arrayName='SOOK';  G(3).array_loc=[48.38379033; -123.80361048];
+%GROUP=G;
+%grd.lat   = [  47.5 : 0.10  :  49.0];
+%grd.lon   = [-125.0 : 0.10 : -122.0];
+%grd.depth = [25:10:65];
+% modified 7/20/07 to optionaly accept a new earth model
+  
+if nargin<4; model=''; end; % use default (PNSN P2 S-wave model) if no model is passed in
+
+[LON,LAT,DEP]          = meshgrid(grd.lon,grd.lat,grd.depth);  % latitude and longitude of grid points
+LAT2  = squeeze(LAT(:,:,1)); 
+LON2  = squeeze(LON(:,:,1));
+[ngrd1,ngrd2,ngrd3]= size(LON);                  % dimensions of the grids 
+ngrd               = ngrd1*ngrd2*ngrd3;          % total number of grid points
+
+for kdepth=1:ngrd3;   % loop over depths
+  
[…]

### 2022-01-16 matlab/search_PNSN_LFE_agu10.m

@@ -1,0 +1,310 @@
+% % Use times of known LFEs to cut windows out of nearCross correlate a reference time event recorded at an array with continuous data to find repeating events
+%clear
+
+home_dir=pwd;
+% tic
+% % Use data for stations in the ascii file containing staCode tab staChannel on each line
+% %station_file='good_stations.txt';   % list of stations that have good, correlated signals for the reference event
+% %[sta_list.staCode,sta_list.staChannel]=textread(station_file,'%s %s','headerlines',0,'delimiter','\t');
+% Filt=[1.5 8]; % 2-8?
+% LFE_list=load('~/UW/IRIS_2008/LFEs/2008.073.09/LFEs2.txt','ascii'); % use LFEs whose times are described in this file
+% RefTime      = LFE_list(1,1:6)'; % column vector if reference time [YY;MM;DD;HH;MM;SS.SSS]
+% Ref_P_window = LFE_list(2,1:2)';
+% Ref_S_window = LFE_list(2,3:4)';
+% LFE_list     = LFE_list(3:end,:); % other events
+% 
+% % read all LFE P and S waves in the LFE_list
+% windowLFE.RefTime = RefTime;
+% P_start           = LFE_list(2:end,1)';
+% P_start=P_start(7:end);
+% Ref_P_window = [-10 20];
+% windowLFE.P       = [P_start + Ref_P_window(1) ;P_start + Ref_P_window(2) ];
+% %windowLFE.S       = [P_start + Ref_S_window(1) ;P_start + Ref_S_window(2) ];
+% 
+% sta = {'2008.073.09.00.00.XU.H05.EHZ..sac' '0803130900.B001.EHZ'	'0803130900.B007.EHZ'	'0803130900.B013.EHZ'	...
+%   '0803130900.B001.EH1' '0803130900.B001.EH2' '0803130900.B013.EH1' '0803130900.B013.EH2' '0803130900.HDW.EHZ' '0803130900.GNW.BHZ' '0803130900.SQM.BHZ' ...
[…]

### 2022-01-16 matlab/trace_ray.m

@@ -1,0 +1,137 @@
+function [X,T,P,vs,vr]=trace_ray(depth, model);
+%   trace_ray    calculate travel time curve by tracing rays
+% USAGE: [X,T,P,vs,vr]=trace_ray(depth, model);
+%
+%  Input: 
+%  depth is earthquake depth (km)
+%  model is an optional velocity model (Nx2 array) with
+%  velocity (km/s) in first column and depth (km) in second
+%  velocity is a layered model, each line of the model gives the
+%  velocity of a layer and depth at the top of the layer
+%  use default (PNSN Puget Sound (P2)) model if model='' or if 
+%  there is only one input argument
+% 
+% Output:
+%  X horizontal distance (km)
+%  T travel time (s)
+%  P ray parameter (dT/dX s/km)
+%  vs velocity at source (km/s)
+%  vr velocity at receiver (surface) (km/s)
+%
+% example:
+% clear; figure(20);clf; depth=[25 35 45 55]; colr = {'k' 'm' 'r' 'b'} ;
+% for k=1:4; [X,T,P]=trace_ray(depth(k));hold on;h(k)=plot(X,T-X/4.5033,['.-' colr{k}]);end;axis([0 300 3 13]); grid on;
+% legend(h,'25 km','35 km','45 km','55 km');xlabel('Range (km)'); ylabel('Travel Time - Range/4.5033 (s)')
+
+%clear;close all;  % clear matlab workspace and close all figures
+
+h0=depth;   % source depth
+
+if nargin<2 || length(model)==0;  % use default model (PNSN model P2 converted to a shear wave model)
+
+  vel_P2=[
+   5.40  0.0
+   6.38  4.0
+   6.59  9.0
+   6.73 16.0
+   6.86 20.0
+   6.95 25.0
+   7.80 51.0;
+   8.00 81.0];
+ 
+  model = [vel_P2(:,1)/sqrt(3) ,  vel_P2(:,2)];
+  
+end
+
+h  = model(:,2);    % column vector of depths corresponding to the tops of layers (km)
+vl = model(:,1);    % velocity within each layer (km/s)
+
+% add a new layer boundary at the source depth without changing the model
+if length(find(h0==h))==0;
+  i=max(find(h0>=h));
+  h = [h(1:i); h0; h(i+1:end)];
+  vl= vl([1:i i:end]);
+else
+  i=find(h0==h);
+end
+i0=i;
+v0= vl(i0);
+vs=v0;
+vr=vl(1); %velocity at surface (receiver).
+
[…]

### 2022-01-25 matlab/delaz.m
Relocate family A

@@ -1,0 +1,65 @@
+function [delta,azeqst,azsteq]=delaz(eqlat,eqlon,stlat,stlon,flag);
+%   delaz         compute earthquake/station distance and azimuth
+% usage: [delta,azeqst,azsteq]=delaz(eqlat,eqlon,stlat,stlon,flag);
+%
+%     compute distance and azimuth from earthquake (eq) to station (st)
+%     delta  = distance between (eq) and (st) in degrees
+%     azeqst = azimuth from (eq) to (st) clockwise from north in degrees
+%     azsteq = azimuth from (st) to (eq) clockwise from north in degrees
+%
+%     if input coordinates are geographic degrees   flag=0
+%     if input coordinates are geocentric radians   flag=1
+%
+%     input latitudes and longitudes can be scalars or vectors
+%     acceptable combinations are one earthquake with many stations,
+%     one station and many earthquakes, or the same number of earthquakes
+%     and stations
+%     output vectors will have same dimensions as input vectors
+%
+%     calls coortr.m
+
+% convert from geographic degrees to geocentric radians if necessary
+% convert to spherical polar coordinates in radians (lat -> colatitude)
+
+if flag==0,   % convert geographic degrees to geocentric radians
+  [eqlat,eqlon]=coortr(eqlat,eqlon,flag); 
+  [stlat,stlon]=coortr(stlat,stlon,flag); 
+end
+eqcolat=pi/2-eqlat;
+stcolat=pi/2-stlat;
+
+cos_eq=cos(eqcolat);
+sin_eq=sin(eqcolat);
+cos_st=cos(stcolat);
+sin_st=sin(stcolat);
+cos_eqst=cos(stlon-eqlon);
+sin_eqst=sin(stlon-eqlon);
+
+cos_delta=cos_eq.*cos_st + sin_eq.*sin_st.*cos_eqst;
+sin_delta=real(sqrt(1-cos_delta.*cos_delta));
+delta=atan2(sin_delta,cos_delta);
+% if sin(delta)=0, set sin(delta)=eps=10**-16
+sin_delta = sin_delta + (sin_delta==0)*eps;
+
+% index is zero if expression is false, 1 if true; 
+% if false, leave unchanged, if true azeqst=pi-azeqst
[…]

### 2022-01-25 matlab/locate_family.m

@@ -1,0 +1,15 @@
+grd.lon = [-123.8:.01:-122.3];
+grd.lat = [39.5:.01:40.8];
+grd.depth = [20:1:70];
+vp_vs = 1.8;
+stations = ['KHBB', 'ME08', 'ME12', 'ME27', 'ME28', 'ME37', 'ME39', 'ME41', 'ME57', 'WDC'];
+lats = [40.65990, 40.222, 40.104, 40.453, 40.327, 40.285, 40.188202, 39.884998, 39.9118, 40.57988];
+lons = [-123.21966, -123.305, -122.498, -123.155, -122.471, -123.653999, -123.594299, -123.361, -122.5676, -122.54113];
+S_P = [14.00, 12.70, 5.50, 12.50, 6.45, 16.40, 17.10, 15.35, 3.50, 7.45];
+[TTgrid, LAT, LON, DEP] = makeTTgrid(lats, lons, grd);
+misfit = abs(TTgrid(1).TIM - S_P(1)) + abs(TTgrid(2).TIM - S_P(2)) + ...
+         abs(TTgrid(3).TIM - S_P(3)) + abs(TTgrid(4).TIM - S_P(4)) + ...
+         abs(TTgrid(5).TIM - S_P(5)) + abs(TTgrid(6).TIM - S_P(6)) + ...
+         abs(TTgrid(7).TIM - S_P(7)) + abs(TTgrid(8).TIM - S_P(8)) + ...
+         abs(TTgrid(9).TIM - S_P(9)) + abs(TTgrid(10).TIM - S_P(10));
+[minmisfit, minindx] = min(misfit(:));

### 2022-01-25 matlab/trace_ray.m

@@ -29,16 +29,27 @@ h0=depth;   % source depth
 
 if nargin<2 || length(model)==0;  % use default model (PNSN model P2 converted to a shear wave model)
 
+%  vel_P2=[
+%   5.40  0.0
+%   6.38  4.0
+%   6.59  9.0
+%   6.73 16.0
+%   6.86 20.0
+%   6.95 25.0
+%   7.80 51.0;
+%   8.00 81.0];
+
   vel_P2=[
-   5.40  0.0
-   6.38  4.0
-   6.59  9.0
-   6.73 16.0
-   6.86 20.0
-   6.95 25.0
-   7.80 51.0;
-   8.00 81.0];
- 
+   5.25  0.0;
+   5.57  5.0;
+   5.18 10.0;
+   6.57 15.0;
+   6.87 20.0;
+   7.74 25.0;
+   7.79 30.0;
+   7.88 35.0;
+   9.16 40.0];
+
   model = [vel_P2(:,1)/sqrt(3) ,  vel_P2(:,2)];
   
 end

### 2022-01-25 src/get_tidal_stress.py

@@ -27,10 +27,12 @@ xmnr = data['xmnr']
 ymnr = data['ymnr']
 
 # Loop on templates
-for i in range(0, np.shape(templates)[0]):
+for i in range(0, 1): #np.shape(templates)[0]):
 
-    lat0 = templates[i][2]
-    lon0 = templates[i][3]
+#    lat0 = templates[i][2]
+#    lon0 = templates[i][3]
+    lat0 = 40.22
+    lon0 = -122.89
     dx = (pi / 180.0) * a * cos(lat0 * pi / 180.0) / sqrt(1.0 - e * e * \
         sin(lat0 * pi / 180.0) * sin(lat0 * pi / 180.0))
     dy = (3.6 * pi / 648.0) * a * (1.0 - e * e) / ((1.0 - e * e * sin(lat0 * \

### 2022-01-25 src/tidal_stress.py

@@ -34,7 +34,7 @@ threshold = pd.read_csv('../data/Ducellier/threshold_cc.txt', sep=r'\s{1,}', \
 threshold.columns = ['family', 'threshold_FAME', 'threshold_perm']
 
 # Loop on templates
-for i in range(0, np.shape(templates)[0]):
+for i in range(0, 1): #np.shape(templates)[0]):
 
     # Look only at good data
     if threshold['threshold_perm'].iloc[i] > 0.0:

### 2022-01-25 src/tidal_stress_ETS.py

@@ -38,7 +38,7 @@ begin_time = pd.read_csv('../data/For_Ken_California_LFE/begin_time.txt', sep=' 
 begin_time.columns = ['latitude', 'longitude', 'begin_time']
 
 # Loop on templates
-for i in range(0, np.shape(templates)[0] - 5):
+for i in range(0, 1): #np.shape(templates)[0] - 5):
 
     # Look only at good data
     if threshold['threshold_perm'].iloc[i] > 0.0:

### 2022-01-26 paper/answer_reviewers.tex
Include revisions

@@
 The templates from Plourde et al.
-(2015) have a low signal-to-noise ratio and generally do not show clear P- and S-wave arrivals.
+(2015) have a low signal-to-noise ratio and generally do not show clear P- and S-wave arrivals, so the 60 seconds window helps be sure it contains the P and S waves.
 Moreover, the wave arrivals can be located close to the beginning or close to the end of the time window, depending on the LFE family considered.
@@
 The LFEs recorded during the period 2007-2009 that are present in only one catalog are then assumed to be false detections.
-We then chose a threshold such that at least 50 \% of the LFE detections are true detections.
-There is thus one threshold per family.
-The thresholds are also different for the two catalogs 2007-2009 and 2004-2011 because the stations and the quality of the templates are different for both catalogs.
+Our goal is to maximize the number of true detections in the filtered catalogs.
+For the FAME catalog, we then chose a threshold such that at least 50 \% of the LFE detections kept in the FAME catalog after filtering with the threshold, are true detections, that is they are also in the networks catalog.
+For the networks catalog, we chose a threshold such that at least 50 \% of the LFE detections kept in the networks catalog after filtering with the threshold (and occurring between 2007 and 2009), are true detections, that i that are also in the FAME catalog.
+There are thus two thresholds per family.
+The filtering is done such that the product of the cross-correlation for a given LFE by the number of channels recording at the time when the LFE occurred is higher than the threshold.
+The thresholds chosen for the FAME and the networks catalog are then different because the stations and the quality of the templates are different for both catalogs.
+For the period 2004-2007 and 2009-2011, we used the same threshold as determined for the period 2007-2009 for the networks catalog.
 We added in a supplement a table with the values of the thresholds.
@@
 
-Our filtering method kept 37 \% of the LFEs for the 2004-2011 catalog and 16 \% of the LFEs for the 2007-2009 catalog.
-We have added in the supplements figures of the catalogs without filtering the LFEs.
+Our filtering method kept 37 \% of the LFEs for the networks catalog and 16 \% of the LFEs for the FAME catalog. We have added in the supplements figures of the catalogs without filtering the LFEs.
 
@@
 
-The fault plane is the plate boundary model of McCrory et al. (2006).
+The fault plane is the plate boundary model of McCrory et al.
+(2012): McCrory, P.
+A., Blair, J.
+L., Waldhauser, F., Oppenheimer, D.
+H.
+(2012) Juan de Fuca slab geometry and its relation to Wadati-Benioff zone seismicity.
+Journal of Geophysical Research: Solid Earth, 2012-09, Vol.117 (B9).
 

### 2022-01-26 paper/agujournaltemplate_highlighted.tex
Include revisions

@@
 As in northern Cascadia, the \textbf{LFE families located at greater depth are more active, with shorter time intervals between two earthquake bursts, than the LFE families located at shallower depth.
-Earth tides have also an influence on LFE activity: LFEs are more likely to occur when the stress changes associated with the tides favor shear failure on the plate boundary}.
+Earth tides also have an influence on LFE activity: LFEs are more likely to occur when the stress changes associated with the tides favor shear failure on the plate boundary}.
 
@@
 \textbf{Contour lines are the depth contours of the plate boundary model from ~\citeA{MCC_2006}.
+MF indicates the Maacama Fault.
 The cross section shows the depth of the LFE families.
@@
 To summarize the findings, we plot in Figure 9 the \textbf{average time between} LFE events as a function of the distance in the eastern direction from the \textbf{western} limit of the tremor.
-We clearly see that the \textbf{average time between} decreases with the down dip distance.
+\textbf{We defined an LFE event as at least five LFEs recorded during a given day.
+If two events are separated by less than five days, we assume that this is a single event.} We clearly see that the \textbf{average time between} decreases with the down dip distance.
 The southernmost family A is also added in Figure 9, but does not fit the general trend.\\

### 2022-01-26 paper/supplement.tex
Include revisions

--- 2020-11-11 paper/supplement.tex
@@
 
-\title{Supplementary Material}
-\date{}
-\maketitle
+\title{An eight-year-long low-frequency earthquake catalog for Southern Cascadia}
 
-\begin{table}
-\caption{Temporary stations used for the 2007-2009 catalog}
+\authors{Ariane Ducellier\affil{1}, Kenneth C. Creager\affil{1}}
+
+\affiliation{1}{University of Washington}
+
+\correspondingauthor{Ariane Ducellier}{ducela@uw.edu}
+
+\begin{figure}[hbt!]
+\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/unfiltered_FAME.eps}
+\caption{Same as Figure 3 from the main text, but without filtering the LFEs.
+They are many false detections at the beginning and the end of the catalog because the FAME stations were not yet installed / already removed.}
+\label{pngfiguresample}
+\end{figure}
+
+\begin{figure}[hbt!]
+\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/unfiltered_perm.eps}
+\caption{Same as Figure 6 from the main text, but without filtering the LFEs.}
+\label{pngfiguresample}
+\end{figure}
+
+\begin{figure}[hbt!]
+\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/timeline_FAME.eps}
+\caption{Evolution of the number of channels available for the computation of the 2007-2009 catalog using the temporary FAME stations.}
+\label{pngfiguresample}
+\end{figure}
+
+\begin{figure}[hbt!]
+\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/timeline_perm.eps}
+\caption{Evolution of the number of channels available for the computation of the 2004-2011 catalog using the permanent stations.}
+\label{pngfiguresample}
+\end{figure}
+
+\newpage
+
+\begin{table}[hbt!]
+\caption{Temporary stations used for the 2007-2009 catalog.
+The data centers providing the seismic waveforms are the Incorporated Research Institutions for Seismology (IRIS) (Alan Levander, 2007), and the Northern California Earthquake Data Center (NCEDC), doi:10.7932/NCEDC.}
 \centering
+\footnotesize
 \begin{tabular}{c c c c c c c c c}
@@
 
-\begin{table}
-\caption{Permanent stations used for the 2004-2011 catalog}
+\newpage
+
+\begin{table}[hbt!]
+\caption{Permanent stations used for the 2004-2011 catalog.
+The data centers providing the seismic waveforms are the Incorporated Research Institutions for Seismology (IRIS) (Alan Levander, 2007), and the Northern California Earthquake Data Center (NCEDC), doi:10.7932/NCEDC.}
 \centering
+\footnotesize
 \begin{tabular}{c c c c c c c c c}
@@
 
+\newpage
+
+\begin{table}[hbt!]
+\caption{Thresholds used to clean the catalogs.
+An LFE is kept in the catalog if its cross-correlation value multiplied by the number of channels recording when it was detected is higher than the threshold.
+The threshold is missing for the families for which there were not enough permanent stations with good templates to obtain reliable LFE detections.}
+\centering
+\scriptsize
+\begin{tabular}{c c c}
+\hline
+Family & Threshold 2007-2009 & Threshold 2004-2011 \\
+\hline
+080401.05.050 & 1.4 & 1.9 \\
+080405.11.042 & 2.0 & 1.6 \\
+080408.08.007 & 1.7 & 1.5 \\
+080408.15.023 & 2.0 & 1.3 \\
+080408.08.029 & 2.3 & 1.4 \\
+080408.16.026 & 1.8 & 1.4 \\
+080410.01.050 & 3.5 & 1.3 \\
+080410.09.032 & 3.9 & 1.4 \\
+080410.12.039 & 1.9 & 1.3 \\
+080410.12.040 & 5.4 & 2.3 \\
+080411.04.013 & 3.4 & 1.5 \\
+080411.04.023 & 3.6 & 1.5 \\
+080410.13.055 & 1.9 & 1.3 \\
+080412.03.029 & 2.2 & 1.0 \\
+080412.11.038 & 2.2 & 1.3 \\
+080412.22.047 & 3.2 & 1.5 \\
+080413.13.026 & 2.2 & 1.3 \\
+080412.22.040 & 3.5 & 1.6 \\
+080413.07.015 & 2.0 & 1.6 \\
+080413.07.023 & 1.8 & 1.4 \\
+080413.16.058 & 2.2 & 0.1 \\
+080413.18.013 & 2.6 & 1.2 \\
+080413.20.036 & 2.1 & 1.1 \\
+080414.12.016 & 2.0 & 1.2 \\
+080414.12.020 & 1.5 & 1.2 \\
+080414.10.058 & 1.8 & 1.2 \\
+080414.18.003 & NA & NA \\
+080415.11.006 & 4.6 & 1.6 \\
+080415.11.008 & 3.0 & 1.8 \\
+080415.24.028 & 2.5 & 1.7 \\
+080416.15.003 & 2.8 & 1.7 \\
+080418.03.001 & 5.0 & 1.5 \\
+080415.19.030 & 2.9 & 1.9 \\
+080419.24.054 & 3.4 & 2.2 \\
+080416.13.033 & 3.9 & 2.0 \\
+080417.15.043 & 3.3 & 1.7 \\
+080418.02.049 & 3.7 & 1.6 \\
+080419.04.046 & 3.5 & 1.5 \\
+080420.01.019 & 2.3 & 1.6 \\
+080420.04.009 & 2.2 & 1.4 \\
+080420.05.032 & 3.0 & 1.8 \\
+080420.08.042 & 1.8 & 1.5 \\
+080421.14.048 & 2.1 & 1.6 \\
+080421.15.050 & 1.9 & 1.5 \\
+080421.16.053 & 3.0 & 1.4 \\
+080421.16.054 & 2.3 & 1.4 \\
+080421.17.056 & 2.1 & 1.3 \\
+080421.23.033 & 2.7 & 1.4 \\
+080422.13.003 & 3.2 & 1.7 \\
+080422.12.039 & 1.7 & 1.1 \\
+080422.13.043 & 2.7 & 1.6 \\
+080422.15.030 & 2.0 & 1.5 \\
+080424.04.058 & 3.3 & 1.8 \\
+080424.05.060 & 2.2 & 1.7 \\
+080426.05.008 & 1.8 & 1.6 \\
+080426.06.027 & 2.1 & 1.8 \\
+080426.20.030 & 1.5 & 1.7 \\
+080427.04.052 & 2.5 & 1.5 \\
+080427.13.036 & 2.1 & 1.5 \\
+080427.20.043 & 2.5 & 2.0 \\
+080429.15.005 & NA & NA \\
+080326.07.004 & NA & NA \\
+080326.07.048 & NA & NA \\
+080326.08.015 & 2.7 & 1.0 \\
+080326.09.007 & NA & NA \\
+080328.09.029 & NA & NA \\
+\hline
+\end{tabular}
+\end{table}
+
 \end{document}

### 2022-01-26 data/Ducellier/plot_zoom_ETS.py

@@ -40,9 +40,9 @@ threshold = pd.read_csv('threshold_cc.txt', sep=r'\s{1,}', header=None, engine='
 threshold.columns = ['family', 'threshold_FAME', 'threshold_perm']
 
 # Start figure and plot tremor
-params = {'legend.fontsize': 24, \
-          'xtick.labelsize':24, \
-          'ytick.labelsize':24}
+params = {'legend.fontsize': 36, \
+          'xtick.labelsize':36, \
+          'ytick.labelsize':36}
 pylab.rcParams.update(params)
 plt.figure(1, figsize=(30, 10))
 
@@ -100,10 +100,12 @@ for event in range(0, 6):
     # End figure
     plt.xlim([xmin[event] - years[event], xmax[event] - years[event]]) # + 0.1 * (xmax - xmin)])
     plt.ylim([39.1, latmax])
-    plt.xlabel('Time (years)', fontsize=24)
+    plt.xlabel('Time (years)', fontsize=36)
     if event == 0:
-        plt.ylabel('Latitude', fontsize=24)
-    plt.title('Year {:d}'.format(years[event]), fontsize=24)
+        plt.ylabel('Latitude', fontsize=36)
+    else:
+        ax.axes.yaxis.set_ticklabels([])
+    plt.title('Year {:d}'.format(years[event]), fontsize=36)
 
 plt.tight_layout()
 plt.savefig('LFEdistribution_perm/zoom_ETS_events.eps', format='eps')

### 2022-01-26 paper/agujournaltemplate_highlighted.tex
Work on revisions

@@
 In this study, we extend the LFE catalog obtained by ~\citeA{PLO_2015} to the 8-year period 2004-2011.
-As in northern Cascadia, the \textbf{LFE families located at greater depth are more active, with shorter time intervals between two earthquake bursts, than the LFE families located at shallower depth.
+As in northern Cascadia, the \textbf{LFE families located at greater depth (down dip) are more active, with shorter time intervals between two earthquake bursts, than the LFE families located at shallower depth (up dip).
 Earth tides also have an influence on LFE activity: LFEs are more likely to occur when the stress changes associated with the tides favor shear failure on the plate boundary}.
@@
 Red stars are moderate ($M > 5$) nearby earthquakes.
-\textbf{Contour lines are the depth contours of the plate boundary model from ~\citeA{MCC_2006}.
-MF indicates the Maacama Fault.
-The cross section shows the depth of the LFE families.
-The line corresponds to the plate boundary model from ~\citeA{MCC_2006} at latitude 41N.}}
+\textbf{The plate boundary from ~\citeA{MCC_2006} is contoured at 10-km intervals starting at 10 km depth.
+The cross section shows the depth of the LFE families ~\cite{PLO_2015} and the plate boundary model from ~\citeA{MCC_2006} at latitude 41 N.
+MF indicates the Maacama Fault.}}
 \label{pngfiguresample}
@@
 
-\citeA{PLO_2015} have kindly shared their LFE catalog with us.
+~\citeA{PLO_2015} have kindly shared their LFE catalog with us.
 For each of 66 LFE families they provided hypocentral locations, lists of stations and channels used to detect LFEs, and the timing of all LFE detections.
@@
 
-We used a matched-filter algorithm to detect LFEs.
+\textbf{Our ultimate goal is to obtain an eight-year-long LFE catalog using data from permanent seismic networks.
+The first step is to use the templates from ~\citeA{PLO_2015} and the data from the FAME experiment to get an LFE catalog for 2007-2009.
+The second step is to use the 2007-2009 FAME catalog to make templates for the seismic stations from the permanent networks.
+The third step is to use the new templates and the data from the permanent networks to get an LFE catalog for 2004-2011.} We used a matched-filter algorithm to detect LFEs.
 For a given LFE family, we download one hour of seismic data.
@@
 To increase the cross-correlation values between the templates and the data, we thus reduced the length of the templates to 25 to 40 seconds, depending on the maximum distance from the source to the stations.
-We did not use stations more than 100 kilometers away from the epicenter of an LFE family, as the template would be unlikely to have a good signal-to-noise ratio.
+\textbf{The 2007-2009 FAME catalog has thus been established with cross correlations over one-minute-long templates while the 2004-2011 networks catalog has been established with cross correlations over shorter templates with average duration equal to 30 seconds.} We did not use stations more than 100 kilometers away from the epicenter of an LFE family, as the template would be unlikely to have a good signal-to-noise ratio.
 We then used this new, shorter templates for the permanent stations to make an LFE catalog for the period 2007-2009.

### 2022-01-26 paper/agujournaltemplate_highlighted.tex
Work on revisions

@@
 For comparison, we also plotted the tremor detection times from ~\citeA{BOY_2015}.
-\textbf{Filtering the catalog has removed about 84 \% of the LFEs.
-As a reference, we plotted in the Supplementary Material the catalog without filtering the LFEs and the number of channels recording as a function of time.} \\
+\textbf{Filtering the catalog has removed about 84 \% of the LFEs, compared to the initial catalog where LFEs were detected using the 8 * MAD threshold for the cross-correlation.
+As a reference, we plotted in the Supplementary Material (Figure S1) the catalog without filtering the LFEs and the number of channels recording as a function of time.} \\
 
@@
 If we filter the catalogs and keep only detections above the thresholds, we are now confident that at least half of the LFE detections are true detections.
-As the number of stations recording may vary over time (especially for the network catalog), we keep only the LFE detections such that the associated cross correlation multiplied by the number of channels recording at that time is higher than the threshold.
+As the number of stations recording may vary over time (especially for the permanent networks catalog), we keep only the LFE detections such that the associated cross correlation multiplied by the number of channels recording at that time is higher than the threshold.
 Thus, if there are few stations recordings at some time, the cross correlation must be higher for the LFE to be considered as a true detection.
@@
 Examples are given in Figure 5 for families A (square in Figure 1) and E (inverted triangle in Figure 1).
-Although the number of LFEs during each event may not be the same, we clearly see for family E that the timing of the events are the same for both catalogs.
-Family A has much shorter recurrence times but most events \textbf{are present in both catalogs as well: forty events are present in both catalogs, three events are present in the FAME catalog but not in the networks catalog and one event is present in the networks catalog but not in the FAME catalog.} \\
+Although the number of LFEs during each \textbf{cluster of LFEs} may not be the same, we clearly see for family E that the timing of the events are the same for both catalogs.
+Family A has much shorter recurrence times but most \textbf{clusters of LFEs are present in both catalogs as well: forty clusters are present in both catalogs, three clusters are present in the FAME catalog but not in the networks catalog and one cluster is present in the networks catalog but not in the FAME catalog.} \\
 
@@
 \textbf{The catalog shown in Figure 6 has been filtered using the threshold computed above.
-Filtering the catalog has removed about 63 \% of the LFEs.
-As a reference, we plotted in the Supplementary Material the catalog without filtering the LFEs and the number of channels recording as a function of time.} \\
+Filtering the catalog has removed about 63 \% of the LFEs, compared to the initial catalog where LFEs were detected using the 8 * MAD threshold for the cross-correlation.
+As a reference, we plotted in the Supplementary Material (Figure S2) the catalog without filtering the LFEs and the number of channels recording as a function of time.} \\
 

### 2022-01-28 paper/answer_reviewers.tex
Incorporate KC comments

@@
 
-We divided possible values of the Coulomb stress changes into bins and computed the number of hours for which the Coulomb stress change takes values in each bins.
+%We divided possible values of the Coulomb stress changes into bins and computed the number of hours for which the Coulomb stress change takes values in each bin.
 As Coulomb stress change often takes small values and rarely takes high values, the expected number of LFEs is higher around 0 and smaller for big negative or positive values.
 We did not normalize the results, so the expected number of LFEs is proportional to the total number of LFEs occurring for each family.
+\\
+
+The shape of the black curves are pretty similar for most of the LFE families.
+The y-axis scale refers to the histograms and not the theoretical stress so theoretical stress for families D, C4, F, and G1 are pretty similar.
+Family A has smaller theoretical stress levels (x axis) and a different shape.
+Family B2 is in a transition between A and the other families.
+These differences may be due to changing slab geometry in the south (Figure 1).
 

### 2022-01-28 paper/agujournaltemplate_highlighted.tex
Incorporate KC comments

@@
 To summarize the findings, we plot in Figure 9 the \textbf{average time between} LFE events as a function of the distance in the eastern direction from the \textbf{western} limit of the tremor.
-\textbf{We defined an LFE event as at least five LFEs recorded during a given day.
-If two events are separated by less than five days, we assume that this is a single event.} We clearly see that the \textbf{average time between} decreases with the down dip distance.
+\textbf{We assume that there is an LFE event avery time that at least five LFEs are recorded during a given day.
+If two events are separated by less than five days, we assume that this is a single event.} We clearly see that the \textbf{average time between LFE events} decreases with the down dip distance.
 The southernmost family A is also added in Figure 9, but does not fit the general trend.\\

### 2022-01-28 data/Ducellier/compare_catalog.py

@@ -16,8 +16,6 @@ def compare_catalog(family, tbegin, tend, dt, thresh1, thresh2):
         'cc': float, 'nchannel': int})
     date = pd.to_datetime(df1.drop(columns=['cc', 'nchannel']))
     df1['date'] = date
-    df1 = df1[(df1['date'] >= tbegin) & (df1['date'] <= tend)]
-    df1_filter = df1.loc[df1['cc'] * df1['nchannel'] >= thresh1]
 
     # Read network catalog
     namefile = 'catalogs/' + family + '/catalog_2004_2011.pkl'
@@ -30,6 +28,14 @@ def compare_catalog(family, tbegin, tend, dt, thresh1, thresh2):
     date = pd.to_datetime(df2.drop(columns=['cc', 'nchannel']))
     df2['date'] = date
     df2['date'] = df2['date'] - timedelta(seconds=dt)
+
+    # LFEs in both catalog
+    df = pd.merge(df1, df2, on=['date'])
+
+    # Filter catalogs with data and thresholds
+    df1 = df1[(df1['date'] >= tbegin) & (df1['date'] <= tend)]
+    df1_filter = df1.loc[df1['cc'] * df1['nchannel'] >= thresh1]
+
     df2 = df2[(df2['date'] >= tbegin) & (df2['date'] <= tend)]
     df2_filter = df2.loc[df2['cc'] * df2['nchannel'] >= thresh2]
 
@@ -48,6 +54,7 @@ def compare_catalog(family, tbegin, tend, dt, thresh1, thresh2):
     df_added_network = df_merge[df_merge['_merge'] == 'left_only']
     
     print(family)
+    print('LFEs in both catalogs: {}'.format(len(df)))
     print('FAME: false detections = {}, total = {}, ratio = {}'.format( \
          len(df_added_FAME), len(df1_filter), len(df_added_FAME) / len(df1_filter)))
     print('Network: false detections = {}, total = {}, ratio = {}'.format( \
@@ -65,10 +72,10 @@ if __name__ == '__main__':
     tend = datetime(2009, 5, 14, 0, 0, 0)
 
     # Thresholds
-    thresh1 = 1.4
-    thresh2 = 1.9
+    thresh1 = 1.8
+    thresh2 = 1.4
 
-    for i in range(0, 1): #len(families)):
+    for i in range(19, 20): #len(families)):
         family = families['family'].iloc[i]
         dt = families['dt'].iloc[i]
         compare_catalog(family, tbegin, tend, dt, thresh1, thresh2)

### 2022-02-01 paper/answer_reviewers.tex
Relocate again

@@
 For the FAME catalog, we then chose a threshold such that at least 50 \% of the LFE detections kept in the FAME catalog after filtering with the threshold, are true detections, that is they are also in the networks catalog.
-For the networks catalog, we chose a threshold such that at least 50 \% of the LFE detections kept in the networks catalog after filtering with the threshold (and occurring between 2007 and 2009), are true detections, that i that are also in the FAME catalog.
+For the networks catalog, we chose a threshold such that at least 50 \% of the LFE detections kept in the networks catalog after filtering with the threshold (and occurring between 2007 and 2009), are true detections, that is they are also in the FAME catalog.
 There are thus two thresholds per family.
@@
 
+We tried to relocate family A using new templates obtained from the LFEs present in both the 2007-2009 FAME catalog and the 2004-2011 networks catalog and S minus P within a station times or P-P times between stations.
+The family may be located 20 to 30 kilometers north or east from the initial location given by Plourde et al.
+(2015).
+There is still a great uncertainty on the depth and this family could be much shallower that the plate boundary.
+It is then possible that the family is located on a nearby crustal fault running west to east.
+If that is the case, the fault geometry used for the tidal stress calculation is not appropriate and that would explain the negative sensitivity.
+We added this comment in the text.
+
+\bigskip
+
 \textbf{Reviewer 2}
@@
 Even if you conclude that you can't get a reliable depth estimate, I would suggest it's worth showing the template waveforms and discussing a few potential source regions, even if it's highly speculative.}
+
+\bigskip
+
+We have remade the templates for both the FAME and the networks stations using the LFEs present in both the 2007-2009 FAME catalog and the 2004-2011 networks catalog.
+We tried to relocate the family A using S minus P times for single stations or P-P times between stations.
+The family A would then be located 20-30 kilometers north or east from the initial location.
+This does not change the pattern of the tidal stress calculations and the negative sensitivity.
+However, there is a great uncertainty on the depth and this LFE family may be much shallower than the plate boundary.
+It is possible that it is located on a nearby crustal fault running west to east.
+In that case, the fault model for the tidal stress calculation is not appropriate.
+
+\begin{figure}[hbt!]
+\centering
+\noindent\includegraphics[width=10cm, trim={1cm 11cm 6cm 4cm},clip]{figures/map_LFEs_answers.eps}
+\caption{Stations used to relocate LFE family A (black triangles).
+Initial location from Plourde et al.
+(2015) (red star) and new locations using S-P times and P-P times (green stars).
+The numbers in parentheses are the corresponding depth.
+The family could be located on the crustal fault near station ME28.}
+\end{figure}
 

### 2022-02-01 paper/agujournaltemplate_highlighted.tex
Relocate again

@@
 They found that the LFEs swarm duration, recurrence interval, and event size decrease systematically with increasing depth.
-On the San Andreas Fault, ~\citeA{SHE_2017}) observed a large diversity of recurrence behaviors among the LFE families, from semicontinuous to highly episodic.
+On the San Andreas Fault, ~\citeA{SHE_2017} observed a large diversity of recurrence behaviors among the LFE families, from semicontinuous to highly episodic.
 Particularly, two families exhibited bimodal recurrence patterns (about 3 and 6 days for the first one, and about 2 and 4 days for the second one).
@@
 They found that the LFE families on the southern Cascadia Subduction Zone were located above the \textbf{plate boundary model of ~\citeA{MCC_2006}, with a large distribution of depths (28-47 km).
-However, they suggested that this may be because the model is biased deep.} Three additional LFE families were found on two strike-slip faults, the Maacama and Bucknell Creek faults, which are part of the San Andreas Fault zone.
+However, they suggested that this may be because the plate boundary model is biased deep.} Three additional LFE families were found on two strike-slip faults, the Maacama and Bucknell Creek faults, which are part of the San Andreas Fault zone.
 \\
@@
 \textbf{Filtering the catalog has removed about 84 \% of the LFEs, compared to the initial catalog where LFEs were detected using the 8 * MAD threshold for the cross-correlation.
-As a reference, we plotted in the Supplementary Material (Figure S1) the catalog without filtering the LFEs and the number of channels recording as a function of time.} \\
+As a reference, we plotted in the Supplementary Material (Figure S1) the catalog without filtering the LFEs and the number of channels recording as a function of time (Figure S3).} \\
 
@@
 Filtering the catalog has removed about 63 \% of the LFEs, compared to the initial catalog where LFEs were detected using the 8 * MAD threshold for the cross-correlation.
-As a reference, we plotted in the Supplementary Material (Figure S2) the catalog without filtering the LFEs and the number of channels recording as a function of time.} \\
+As a reference, we plotted in the Supplementary Material (Figure S2) the catalog without filtering the LFEs and the number of channels recording as a function of time (Figure S4).} \\
 
@@
 To summarize the findings, we plot in Figure 9 the \textbf{average time between} LFE events as a function of the distance in the eastern direction from the \textbf{western} limit of the tremor.
-\textbf{We assume that there is an LFE event avery time that at least five LFEs are recorded during a given day.
+\textbf{We assume that there is an LFE event every time that at least five LFEs are recorded during a given day.
 If two events are separated by less than five days, we assume that this is a single event.} We clearly see that the \textbf{average time between LFE events} decreases with the down dip distance.
@@
 We clearly see that these LFEs tend to occur during times when predicted tidal Coulomb stress is discouraging slip on the plate boundary.
-We hypothesize that LFE family A may not be located on the subduction zone, and may be on a different fault instead.
+\textbf{We tried to relocate this LFE family using the new templates obtained from the best LFEs in the 2004-2011 catalogs and S minus P times within a single stations or P-P times between stations.
+The location is still not very well constrained and the LFE family A may be located 20 to 30 kilometers north or east of the initial location from ~\citeA{PLO_2015}.
+However, this does not change the pattern observed for the correlation between tidal stress changes and LFE activity.
+There is a great uncertainty on the depth and this LFE family may be located much shallower than the plate boundary.
+We hypothesize that LFE family A may not be located on the subduction zone and may be on a nearby crustal fault that runs west to east.
+If this was the case, the fault plane assumed for the tidal stress calculation would not be appropriate, which would explain the different patron for this LFE family.
+In our future work, we plan to invert template waveforms for moment tensor mechanisms, which should help investigate whether the LFE family A is on a crustal fault.}
 

### 2022-02-01 matlab/locate_family.m

@@ -2,14 +2,94 @@ grd.lon = [-123.8:.01:-122.3];
 grd.lat = [39.5:.01:40.8];
 grd.depth = [20:1:70];
 vp_vs = 1.8;
-stations = ['KHBB', 'ME08', 'ME12', 'ME27', 'ME28', 'ME37', 'ME39', 'ME41', 'ME57', 'WDC'];
-lats = [40.65990, 40.222, 40.104, 40.453, 40.327, 40.285, 40.188202, 39.884998, 39.9118, 40.57988];
-lons = [-123.21966, -123.305, -122.498, -123.155, -122.471, -123.653999, -123.594299, -123.361, -122.5676, -122.54113];
+
+% Using S minus P times
+stations = ['KHBB', 'ME08', 'ME12', 'ME28', 'ME37', 'ME39', 'ME41', 'ME57', 'WDC'];
+lats = [40.65990, 40.222, 40.104, 40.327, 40.285, 40.188202, 39.884998, 39.9118, 40.57988];
+lons = [-123.21966, -123.305, -122.498, -122.471, -123.653999, -123.594299, -123.361, -122.5676, -122.54113];
 S_P = [14.00, 12.70, 5.50, 12.50, 6.45, 16.40, 17.10, 15.35, 3.50, 7.45];
 [TTgrid, LAT, LON, DEP] = makeTTgrid(lats, lons, grd);
 misfit = abs(TTgrid(1).TIM - S_P(1)) + abs(TTgrid(2).TIM - S_P(2)) + ...
          abs(TTgrid(3).TIM - S_P(3)) + abs(TTgrid(4).TIM - S_P(4)) + ...
          abs(TTgrid(5).TIM - S_P(5)) + abs(TTgrid(6).TIM - S_P(6)) + ...
          abs(TTgrid(7).TIM - S_P(7)) + abs(TTgrid(8).TIM - S_P(8)) + ...
-         abs(TTgrid(9).TIM - S_P(9)) + abs(TTgrid(10).TIM - S_P(10));
+         abs(TTgrid(9).TIM - S_P(9));
 [minmisfit, minindx] = min(misfit(:));
+LAT0 = LAT(minindx);
+LON0 = LON(minindx);
+DEP0 = DEP(minindx);
+fprintf('%f %f %f', LON0, LAT0, DEP0);
+% Plot cross section of misfit with fixed latitude
+figure(1); clf;
+k = find(grd.lat == LAT0);
[…]

### 2022-02-01 src/compute_traveltimes.py

@@ -4,6 +4,8 @@ cross-correlate templates between components and between stations
 and returns the relative travel times
 """
 
+import matplotlib.pylab as pylab
+import matplotlib.pyplot as plt
 import numpy as np
 import obspy
 import os
@@ -121,6 +123,132 @@ def compute_traveltimes(family, stations, channels, latitudes, longitudes, \
 #    pickle.dump(df_SP, open(namedir + '/t_SP.pkl', 'wb'))
     return(cc_R, cc_T)
 
+def compute_plot_PP(family, stations, channels, ibegins, nt, dt, nkeep):
+    """
+    """
+    namedir = 'traveltimes/' + family
+    if not os.path.exists(namedir):
+        os.makedirs(namedir)
+
+    time = dt * np.arange(0, nt)
+
+    params = {'legend.fontsize': 24, \
+              'xtick.labelsize':24, \
+              'ytick.labelsize':24}
+    pylab.rcParams.update(params)
+
+    df_P = pd.DataFrame(columns=['station1', 'station2', 't_PP'])
+
+    for i in range(0, len(stations) - 1):
+        for j in range(i + 1, len(stations)):
+            filename1 = 'templates_both/' + family + '/' + stations[i] + '_' + channels[i] + '.pkl'
+            filename2 = 'templates_both/' + family + '/' + stations[j] + '_' + channels[j] + '.pkl'
+            trace1 = pickle.load(open(filename1, 'rb'))[0]
+            trace2 = pickle.load(open(filename2, 'rb'))[0]
+            data1 = trace1.data[ibegins[i] : ibegins[i] + nkeep + 1]
+            data2 = trace2.data[ibegins[j] : ibegins[j] + nkeep + 1]
+            cc = np.correlate(data1, data2, mode='full')
+            time_cc = dt * np.arange(- nkeep, nkeep + 1)
+            tlag = dt * (ibegins[j] - ibegins[i] + nkeep - np.argmax(cc))
+            df_P.loc[len(df_P.index)] = [stations[i], stations[j], tlag]
+
+            # Figure
+            plt.figure(1, figsize=(8, 15))
+            plt.subplot2grid((3, 1), (2, 0))
+            plt.plot(time, trace1.data)
[…]

### 2022-02-01 src/get_tidal_stress.py

@@ -31,8 +31,8 @@ for i in range(0, 1): #np.shape(templates)[0]):
 
 #    lat0 = templates[i][2]
 #    lon0 = templates[i][3]
-    lat0 = 40.22
-    lon0 = -122.89
+    lat0 = 40.21
+    lon0 = -122.50
     dx = (pi / 180.0) * a * cos(lat0 * pi / 180.0) / sqrt(1.0 - e * e * \
         sin(lat0 * pi / 180.0) * sin(lat0 * pi / 180.0))
     dy = (3.6 * pi / 648.0) * a * (1.0 - e * e) / ((1.0 - e * e * sin(lat0 * \

### 2022-02-03 paper/answer_reviewers.tex
Ready to submit

--- 2022-01-28 paper/answer_reviewers.tex
@@
 Moreover, the wave arrivals can be located close to the beginning or close to the end of the time window, depending on the LFE family considered.
-We have chosen to keep the whole one-minute time window to be sure to include both the P- and the S-wave arrivals.
-The templates obtained using LFE detections from the 2-year-long catalog show clearer P- and S-wave arrivals and we have reduced the length of the time window to 30 seconds on average, depending on the LFE family considered.
+To make the initial 2007-2009 FAME catalog, we have chosen to keep the whole one-minute time window to be sure to include both the P- and the S-wave arrivals.
+The templates obtained using LFE detections from the 2-year-long catalog show clearer P- and S-wave arrivals.
+To make the 2004-2011 permanent networks catalog, we have reduced the length of the time window to 30 seconds on average, depending on the LFE family considered.
 We have remade the templates using only LFEs that were present in both catalogs (FAME and permanent networks).
@@
 The threshold is thus different for each hour of data and it is difficult to show its values in the figure.
+This is how Shelly et al.
+(2007, Nature) defined the thresholds.
 
@@
 The choice of the threshold is explained in more detail later in the text, when we explain how we cleaned the longer catalog (2004-2011).
-The main idea is that if an LFE is present both in the 2007-2009 FAME catalog and in the 2004-2011 permanent networks catalog, then it is unlikely to be a false detection.
+The main idea is that if an LFE is present both in the 2007-2009 FAME catalog and in the 2007-2009 permanent networks catalog, then it is unlikely to be a false detection.
 We assumed that all LFEs present in both catalogs are true detections.
@@
 Our goal is to maximize the number of true detections in the filtered catalogs.
-For the FAME catalog, we then chose a threshold such that at least 50 \% of the LFE detections kept in the FAME catalog after filtering with the threshold, are true detections, that is they are also in the networks catalog.
-For the networks catalog, we chose a threshold such that at least 50 \% of the LFE detections kept in the networks catalog after filtering with the threshold (and occurring between 2007 and 2009), are true detections, that i that are also in the FAME catalog.
+For the FAME catalog, we then chose a threshold such that 50 \% of the LFE detections kept in the FAME catalog after filtering with the threshold, are true detections, that is they are also in the networks catalog.
+For the networks catalog, we chose a threshold such that 50 \% of the LFE detections kept in the networks catalog after filtering with the threshold (and occurring between 2007 and 2009), are true detections, that is they are also in the FAME catalog.
 There are thus two thresholds per family.
@@
 
-One threshold to filter the 2007-2009 catalog computed with the FAME stations and one threshold to filter the 2004-2011 catalog computed with the permanent stations.
+One threshold to filter the 2007-2009 catalog computed with the FAME stations and one threshold to filter the 2007-2009 catalog computed with the permanent stations.
 We use two different thresholds because the quality of the templates is not the same for the two catalogs.
@@
 
-We changed the figure and plotted recurrence time instead of number of events.
+We changed the figure and plotted recurrence time instead of number of LFE clusters.
 
@@
 
+We tried to relocate family A using new templates obtained from the LFEs present in both the 2007-2009 FAME catalog and the 2004-2011 networks catalog.
+We locate the family using S minus P times for each station, or using P-P times between stations, or using a combination of both.
+The family may be located 30 to 50 kilometers east from the initial location given by Plourde et al.
+(2015).
+The depth is 20-25 kilometers, that is shallower than the location given Plourde et al.
+(2015) and shallower than the plate boundary.
+It is then possible that the family is located on a nearby crustal fault.
+If that is the case, the fault geometry used for the tidal stress calculation is not appropriate and that would explain the negative sensitivity.
+We added this comment in the text.
+
+\bigskip
+
 \textbf{Reviewer 2}
@@
 
+We have remade the templates for both the FAME and the networks stations using the LFEs present in both the 2007-2009 FAME catalog and the 2004-2011 networks catalog.
+We tried to relocate the family A using S minus P times for each station, or using P-P times between stations, or using a combination of both.
+The family may be located 30 to 50 kilometers east from the initial location.
+This does not change the pattern of the tidal stress calculations and the negative sensitivity.
+However, the depth of this LFE family is shallower than the initial location (20-25 kilometers depth) and shallower than the plate boundary.
+It is possible that it is located on a nearby crustal fault.
+In that case, the fault model for the tidal stress calculation is not appropriate.
+
+\begin{figure}[hbt!]
+\centering
+\noindent\includegraphics[width=10cm, trim={1cm 11cm 3cm 4cm},clip]{figures/map_LFEs_answers.eps}
+\caption{Stations used to relocate LFE family A (black triangles).
+Initial location from Plourde et al.
+(2015) (red star) and new locations using S-P times, P-P times and a combination of both (green stars).
+The numbers in parentheses are the corresponding depth.
+The family could be located on one of the crustal faults in the eastern part of the map.}
+\end{figure}
+
+\bigskip
+
 \textit{Line 290 / Figure 9: I'm a bit confused here.
@@
 
-To define the number of events, we assume that there is an event each time that there are at least five LFEs during a single day.
-If two events are separated by less than five days, we assume that this is a single event.
-We remade the figure to plot average recurrence time instead of number of events.
+To define the number of LFE clusters, we assume that there is a cluster each time that there are at least five LFEs during a single day.
+If two clusters are separated by less than five days, we assume that this is a single cluster.
+We remade the figure to plot average recurrence time instead of number of clusters.
 
@@
 
-We move this sentence to the acknowledgements.
+We moved this sentence to the acknowledgements.
 
@@
 
-It applies to the total number of LFEs for all the 66 families. We modified the text
+It applies to the total number of LFEs for all the 66 families. We modified the text.
 
@@
 
-We use the same locations as Pourde et al. (2015). We have not tried to relocate the families using the new templates. We specified the latitude and depth of the family in the text.
+We use the same locations as Pourde et al.
+(2015).
+We have not tried to relocate the families using the new templates, except for family A as discussed in the revised text.
+We specified the latitude and depth of the family in the text.
 
@@
 
-The Boyarko et al. tremor catalog starts in 2005. That is why we do not show the tremor for the two 2004 LFE events.
+The Boyarko et al. tremor catalog starts in 2005. That is why we do not show the tremor for the two 2004 ETS events.
 

### 2022-02-03 paper/agujournaltemplate.tex
Ready to submit

@@
 % You may copy this file and give it your
-% article name, and enter your text.
+% article name, and enter your text.slow-slip
 %
@@
 Low-frequency earthquakes (LFEs) are small magnitude earthquakes, with typical magnitude less than 2, and reduced amplitudes at frequencies greater than 10 Hz relative to  ordinary small earthquakes.
-Their occurrence is often associated with tectonic tremor and slow slip events along the plate boundary in subduction zones and occasionally transform fault zones.
-They are usually grouped into families of events, with all the earthquakes of a given family originating from the same small patch on the plate interface and recurring more or less episodically in a bursty manner.
+Their occurrence is often associated with tectonic tremor and slow-slip events along the plate boundary in subduction zones and occasionally transform fault zones.
+They are usually grouped into families, with all the earthquakes of a given family originating from the same small patch on the plate interface and recurring more or less episodically in a bursty manner.
 In this study, we extend the LFE catalog obtained by ~\citeA{PLO_2015} during an episode of high tremor activity in  April 2008, to the 8-year period 2004-2011.
-All of the tremor in the ~\citeA{BOY_2015} catalog south of 42 degrees North has associated LFE activity, but we have identified several other, mostly smaller, clusters of LFEs, and extend their catalog forward and backward by a total of about 3 years.
+All of the tremor in the ~\citeA{BOY_2015} catalog south of 42 degrees North has associated LFE activity, but we have identified several smaller clusters of LFEs without associated tremor activity, and extend their catalog forward and backward by a total of about 3 years.
 As in northern Cascadia, the down-dip LFE families have recurrence intervals several times smaller than the up-dip families.
@@
 Low-frequency earthquakes (LFEs) are small magnitude earthquakes, with typical magnitude less than 2, and reduced amplitudes at frequencies greater than 10 Hz relative to ordinary small earthquakes.
-Their occurrence is often associated with tectonic tremor and slow slip events along the plate boundary in subduction zones and occasionally transform fault zones.
-They are usually grouped into families of events, with all the earthquakes of a given family originating from the same small patch on the plate interface and recurring more or less episodically in a bursty manner.
+They are usually grouped into families of events, with all the earthquakes of a given family originating from the same small patch on the plate interface.
+LFEs tend to happen in bursts, with dozen of earthquakes occurring within a few days, followed by weeks or months of quiet.
 In this study, we extend the LFE catalog obtained by ~\citeA{PLO_2015} to the 8-year period 2004-2011.
-As in northern Cascadia, the down-dip LFE families have recurrence intervals smaller than the up-dip families.
-For the April 2008 Episodic Tremor and Slip event, the best recorded LFE families exhibit a strong tidal stress sensitivity.
-The southernmost LFE family, which has been interpreted to be on the subduction plate boundary has a short recurrence time.
-Also, these LFEs tend to occur during times when tidal stress discourages slip on the plate boundary.
-Both observations suggest this LFE family may be on a different fault.
+As in northern Cascadia, the LFE families located at greater depth (down dip) are more active, with shorter time intervals between two earthquake bursts, than the LFE families located at shallower depth (up dip).
+Earth tides also have an influence on LFE activity: LFEs are more likely to occur when the stress changes associated with the tides favor shear failure on the plate boundary.
 
@@
 
-Tectonic tremor is a weak but persistent shaking of the Earth that has been discovered in many subduction zones and some strike-slip faults throughout the world.
-Tremor is observed on seismograms as apparent noise whose amplitude is modulated in time in a similar manner at stations that are dozens of kilometers apart from each other.
+Tectonic tremor is a weak but persistent shaking of the Earth that has been discovered in many subduction zones and some strike-slip faults throughout the world ~\cite{BER_2011}.
+Tremor is observed on seismograms as apparent noise whose amplitude is modulated in time in a similar manner at stations that are dozens of kilometers apart from each other ~\cite{OBA_2002}.
 It is characterized by a long (several seconds to many minutes), low amplitude seismic signal, emergent onsets, and an absence of clear impulsive phases.
-Tremor can be explained as a swarm of low-frequency earthquakes (LFEs), that is small magnitude earthquakes (M $\sim$ 1) which dominant frequency is clearly low (1-10 Hz) compared with that of ordinary tiny earthquakes (up to 20 Hz).
-The source of the tremor and the LFEs is located on the plate boundary, and their focal mechanisms represent shear slip on a low-angle thrust fault dipping in the same direction as the plate interface ~\cite{IDE_2007_GRL}.
-LFEs are usually grouped into families of events, with all the earthquakes of a given family originating from the same small patch on the plate interface, and recurring more or less episodically in a bursty manner.
-In subduction zones such as Nankai and Cascadia, tectonic tremor and LFE observations are spatially and temporally correlated with slow slip observations ~\cite{OBA_2002, ROG_2003}.
+Tremor can be explained as a swarm of low-frequency earthquakes (LFEs) ~\cite{SHE_2007_nature}, that is small magnitude earthquakes (M $\sim$ 1) which dominant frequency is clearly low (1-10 Hz) compared with that of ordinary tiny earthquakes (up to 20 Hz).
+The source of the tremor and the LFEs is located on the plate boundary ~\cite{SHE_2006,BOS_2012,AUD_2016}, and their focal mechanisms represent shear slip on a low-angle thrust fault dipping in the same direction as the plate interface ~\cite{IDE_2007_GRL,BOS_2012,ROY_2014}.
+LFEs are usually grouped into families of earthquakes, with all the earthquakes of a given family originating from the same small patch on the plate interface, and recurring more or less episodically in a bursty manner.
+Dozens of earthquakes are thus recorded within a few hours or days during a burst of LFE activity, followed by weeks or months of quiet, with very few earthquakes.
+In subduction zones such as Nankai and Cascadia, tectonic tremor and LFE observations are spatially and temporally correlated with slow-slip observations ~\cite{ROG_2003,OBA_2004}.
 Due to this correlation, these paired phenomena have been called Episodic Tremor and Slip (ETS).
@@
 
-The relatively short recurrence of slow slip and tremor events results in a rich history both in space and time and reveals potential patterns.
+The relatively short recurrence of slow-slip and tremor events results in a rich history both in space and time and reveals potential patterns.
 These event histories have allowed scientists to see complete event cycles, which is typically not possible to explore in traditional earthquake catalogs.
-However, most of the work on LFEs has been focused on detecting LFEs during periods of high tremor activity, grouping them into families of events, and locating the source of the LFE families.
-Longer catalogs (several years) have been established for LFE families in Mexico (two-year long catalog by ~\citeA{FRA_2014}), the San Andreas Fault (fifteen-year-long catalog by ~\citeA{SHE_2017}), Washington State (five-year-long catalog by ~\citeA{SWE_2019} and two-year-long catalog by ~\citeA{CHE_2017_JGR, CHE_2017_G3}), New Zealand (eight-year-long catalog by ~\citeA{BAR_2018}), and Japan (twelve-year-long catalog by ~\citeA{NAK_2017} and eight-year-long catalog by ~\citeA{OHT_2017}).
+However, most of the work on LFEs has been focused on detecting LFEs during periods of high tremor activity, grouping them into families of earthquakes, and locating the source of the LFE families.
+Longer catalogs (several years) have been established for LFE families in Mexico (two-year long catalog by ~\citeA{FRA_2014}), the San Andreas Fault (fifteen-year-long catalog by ~\citeA{SHE_2017}), Washington State (five-year-long catalog by ~\citeA{SWE_2019} and two-year-long catalog by ~\citeA{CHE_2017_JGR, CHE_2017_G3}), Vancouver Island (ten-year-long catalog by ~\citeA{BOS_2015}), New Zealand (eight-year-long catalog by ~\citeA{BAR_2018}), and Japan (twelve-year-long catalog by ~\citeA{NAK_2017}, eight-year-long catalog by ~\citeA{OHT_2017}, eleven-year-long catalog by ~\citeA{KAT_2020}, and Japan Meteorological Agency (JMA) catalog since 1999 ~\cite{KAT_2003}).
 These studies have shown that the recurrence behavior of LFE families varies a lot between seismic regions, and inside the same seismic region.
 In northern Washington, ~\citeA{SWE_2019} have identified and characterized four different LFE families that span the width of the transition zone in the Cascadia Subduction Zone beneath western Washington State.
-They found that the LFEs swarm duration, recurrence interval, and event size decrease systematically with increasing depth.
-On the San Andreas Fault, ~\citeA{SHE_2017}) observed a large diversity of recurrence behaviors among the LFE families, from semicontinuous to highly episodic.
+They found that the LFEs swarm duration, recurrence interval, and cluster size decrease systematically with increasing depth.
+On the San Andreas Fault, ~\citeA{SHE_2017} observed a large diversity of recurrence behaviors among the LFE families, from semicontinuous to highly episodic.
 Particularly, two families exhibited bimodal recurrence patterns (about 3 and 6 days for the first one, and about 2 and 4 days for the second one).
-Moreover, he observed an increase in the LFE event rate after the 2004 Parkfield earthquake.
+Moreover, he observed an increase in the LFE rate after the 2004 Parkfield earthquake.
 \\
 
-~\citeA{PLO_2015}) have detected LFEs in southern Cascadia during the April 2008 ETS event using seismic data from the EarthScope Flexible Array Mendocino Experiment (FAME).
+~\citeA{PLO_2015} have detected LFEs in southern Cascadia during the April 2008 ETS event using seismic data from the EarthScope Flexible Array Mendocino Experiment (FAME).
 They used a combination of autodetection methods and visual identification to obtain the initial templates.
 Then, they recovered higher signal-to-noise LFE signals using iterative network cross-correlation.
-They found that the LFE families on the southern Cascadia Subduction Zone were located above the plate boundary, with a large distribution of depths (28-47 km).
+They found that the LFE families on the southern Cascadia Subduction Zone were located above the plate boundary model of ~\citeA{MCC_2006}, with a large distribution of depths (28-47 km).
+However, they suggested that this may be because the plate boundary model is biased deep.
 Three additional LFE families were found on two strike-slip faults, the Maacama and Bucknell Creek faults, which are part of the San Andreas Fault zone.
@@
 We restricted ourselves to seismic stations less than 100 kilometers away from the epicenter of an LFE family, as we do not expect to have good signal-to-noise ratio for stations located farther away.
-The complete list of seismic stations and channels used in this study is given in the Supplementary Material.
+The complete list of seismic stations and channels used in this study is given in the Supplementary Material (Tables S1 and S2).
 Figure 1 shows a map of the locations of the LFE families, and of the locations of the seismic stations.
@@
 \begin{figure}
-\noindent\includegraphics[width=\textwidth, trim={1.5cm 4cm 1cm 10cm},clip]{figures/map_LFEs.eps}
-\caption{Map showing the location of the LFE families (back dots) and the seismic stations used in this study.
+\noindent\includegraphics[width=\textwidth, trim={0.5cm 7cm 1.5cm 7cm},clip]{figures/map_LFEs.eps}
+\caption{Map showing the location of the LFE families (black dots) and the seismic stations used in this study.
 Red triangles are the stations from the FAME experiment, green triangles are one-component permanent stations, blue triangles are three components permanent stations.
-Red stars are moderate ($M > 5$) nearby earthquakes.}
+Red stars are moderate ($M > 5$) nearby earthquakes.
+The plate boundary from ~\citeA{MCC_2006} is contoured at 10-km intervals starting at 10 km depth.
+The cross section shows the depth of the LFE families ~\cite{PLO_2015} and the plate boundary model from ~\citeA{MCC_2006} at latitude 41 N.
+MF indicates the Maacama Fault.}
 \label{pngfiguresample}
@@
 
+Our ultimate goal is to obtain an eight-year-long LFE catalog using data from permanent seismic networks.
+The first step is to use the templates from ~\citeA{PLO_2015} and the data from the FAME experiment to get an LFE catalog for 2007-2009.
+The second step is to use the 2007-2009 FAME catalog to make templates for the seismic stations from the permanent networks.
+The third step is to use the new templates and the data from the permanent networks to get an LFE catalog for 2004-2011.
 We used a matched-filter algorithm to detect LFEs.
@@
 However, if we stack the cross-correlation signals for all the channels and all the stations, we can see peaks appearing.
-Whenever the value of the average cross-correlation is higher than a threshold (we chose a threshold equal to eight times the median absolute deviation of the stacked cross-correlation), we inferred that there is an LFE.
+Whenever the value of the average cross-correlation is higher than a threshold (we chose a threshold equal to eight times the median absolute deviation of the stacked cross-correlation as was done by ~\citeA{SHE_2007_nature}), we inferred that there is an LFE.
 As two peaks separated by a short period of time may actually correspond to the same LFE, we kept only LFEs that are separated by at least one second and, when two LFEs are separated by less than one second, we keep only the one with the higher value of the stacked cross-correlation.
@@
 For 61 families, we recovered more than 90 \% of the initial LFE detections.
-We also added 74 \% more LFEs to the catalog, but most of added LFEs have a low cross-correlation value and may be false detections.
+We also added 74 \% more LFEs to the initial number of LFEs in the catalog (when considering all 66 families), but most of added LFEs have a low cross-correlation value and may be false detections.
 Figure 2 shows the cross-correlation values for the LFEs in the original catalog, and for the LFEs that we added to the catalog for family E (inverted triangle in Figure 1).
@@
 Using a threshold equal to eight times the median absolute deviation of the stacked cross-correlation may produce false detections, therefore we filtered the LFE detection times before visualizing the two-year-long catalog.
-As the number of seismic stations recording may change with time as the stations were progressively installed during Summer and Fall 2007, and then progressively removed during May and June 2009, we kept only LFE detections for which the product of the cross-correlation value by the number of stations recording at that time is higher than a threshold.
-The threshold is thus different for each LFE family.
+As the number of seismic stations recording may change with time as the stations were progressively installed during Summer and Fall 2007, and then progressively removed during May and June 2009, we kept only LFE detections for which the product of the stacked cross-correlation value by the number of channels recording at that time is higher than a threshold.
+We will explain later in the text how the threshold is chosen.
+The threshold is different for each LFE family, but is constant over time for a given LFE family.
 The resulting LFE catalog for the period 2007-2009 is shown in Figure 3.
 For comparison, we also plotted the tremor detection times from ~\citeA{BOY_2015}.
+Filtering the catalog has removed about 84 \% of the LFEs, compared to the initial catalog where LFEs were detected using the 8 * MAD threshold for the cross-correlation.
+As a reference, we plotted in the Supplementary Material (Figure S1) the catalog without filtering the LFEs and the number of channels recording as a function of time (Figure S3).
 \\
@@
 The LFE families located south on the strike-slip fault from the San Andreas Fault system have much shorter recurrence intervals than the LFE families located on the subduction zone.
-Additionally, one LFE family located on the southern end of the subduction zone has also shorter recurrence intervals than families located farther north, and behaves more similarly to the strike-slip fault families.
+Additionally, one LFE family located on the southern end of the subduction zone (family A at 40.09N and 34.9km depth) has also shorter recurrence intervals than families located farther north, and behaves more similarly to the strike-slip fault families.
 \\
@@
 To increase the cross-correlation values between the templates and the data, we thus reduced the length of the templates to 25 to 40 seconds, depending on the maximum distance from the source to the stations.
+The 2007-2009 FAME catalog has thus been established with cross correlations over one-minute-long templates while the 2004-2011 networks catalog has been established with cross correlations over shorter templates with average duration equal to 30 seconds.
 We did not use stations more than 100 kilometers away from the epicenter of an LFE family, as the template would be unlikely to have a good signal-to-noise ratio.
@@
 As we may have many false detections, we try to eliminate some of them by assuming that LFEs present in both catalogs are always true detections.
-Then we define two thresholds: the first threshold is chosen such that at least half the LFE detections above the threshold in the FAME catalog are also in the network catalog, the second threshold is chosen such that at least half the LFE detections above the threshold in the network catalog are also in the FAME catalog.
+Then we define two thresholds: the first threshold is chosen such that half the LFE detections above the threshold in the FAME catalog are also in the network catalog, the second threshold is chosen such that half the LFE detections above the threshold (and occurring during 2007-2009) in the network catalog are also in the FAME catalog.
 If we filter the catalogs and keep only detections above the thresholds, we are now confident that at least half of the LFE detections are true detections.
-As the number of stations recording may vary over time (especially for the network catalog), we keep only the LFE detections such that the associated cross correlation multiplied by the number of channels recording at that time is higher than the threshold.
+Thus there are two thresholds per LFE family (given in Table S3 of the Supplementary Material).
+As the number of stations recording may vary over time (especially for the permanent networks catalog), we keep only the LFE detections such that the associated cross correlation multiplied by the number of channels recording at that time is higher than the threshold.
 Thus, if there are few stations recordings at some time, the cross correlation must be higher for the LFE to be considered as a true detection.
@@
 Examples are given in Figure 5 for families A (square in Figure 1) and E (inverted triangle in Figure 1).
-Although the number of LFEs during each event may not be the same, we clearly see for family E that the timing of the events are the same for both catalogs.
-Family A has much shorter recurrence times but most events seem to be present in both catalogs as well.
+Although the number of LFEs during each cluster of LFEs may not be the same, we clearly see for family E that the timing of the clusters are the same for both catalogs.
+Family A has much shorter recurrence times but most clusters of LFEs are present in both catalogs as well: forty clusters are present in both catalogs, three clusters are present in the FAME catalog but not in the networks catalog and one cluster is present in the networks catalog but not in the FAME catalog.
 \\
@@
 For most of the families located on the subduction zone, we obtained a good agreement between both catalogs.
-We eliminate two families for which too few permanent stations have good templates, and it was not possible to detect LFEs with the available templates.
-However, we were able to detect most LFE events even without the presence of the temporary stations from the FAME network.
+We eliminate six families for which too few permanent stations have good templates, and it was not possible to detect LFEs with the available templates.
+However, we were able to detect most LFE clusters even without the presence of the temporary stations from the FAME network.
 We are thus confident that we can detect LFEs before 2007 and after 2009.
 In the following, we focus on the period 2004-2011.
-In November 2011, several one-component stations stopped recording and the number of available stations started decreasing, which is why we did not look for LFE event after that date.
+In November 2011, several one-component stations stopped recording and the number of available stations started decreasing, which is why we did not look for LFE after that date.
 The resulting LFE catalog for the period 2004-2011 is shown in Figure 6.
@@
 Figure 7 shows the details of six big ETS events in 2004, 2005, 2006, 2007 and 2008.
+The catalog shown in Figure 6 has been filtered using the threshold computed above.
+Filtering the catalog has removed about 63 \% of the LFEs, compared to the initial catalog where LFEs were detected using the 8 * MAD threshold for the cross-correlation.
+As a reference, we plotted in the Supplementary Material (Figure S2) the catalog without filtering the LFEs and the number of channels recording as a function of time (Figure S4).
 \\
@@
 The size of the black dots are proportional to the number of LFEs detected during this day.
-For clarity, we do not show the LFEs for the days when there are less than three LFEs.}
+For clarity, we do not show the LFEs for the days when there are less than three LFEs.
+The tremor catalog of ~\citeA{BOY_2015} starts in 2005.
+This is why no tremor detections can be shown for the two ETS events in 2004.}
 \label{pngfiguresample}
@@
 
-We were able to detect LFE events propagating from North to South or from South to North whenever there is a tremor episode in the ~\citeA{BOY_2015} catalog.
+We were able to detect LFE clusters propagating from North to South or from South to North whenever there is a tremor episode in the ~\citeA{BOY_2015} catalog.
 We were also able to detect several LFE episodes in 2004-2005 before the beginning of the ~\citeA{BOY_2015} catalog.
-In particular, the LFE event in January 2005 propagating South to North from latitude 40.1 to latitude 41.2 is also present in the ETS catalog from ~\citeA{BRU_2007}.
-We also see one LFE event in May-June 2004, propagating South to North from latitude 40.1 to 41.6, and one LFE event in November 2004, propagating North to South from latitude 41.6 to 40.4.
-The first of these events is also in the ETS catalog from ~\citeA{BRU_2007}.
-The main characteristics of the six biggest events shown in Figure 7 are given in Table 1.
+In particular, the LFE episode in January 2005 propagating South to North from latitude 40.1 to latitude 41.2 is also present in the ETS catalog from ~\citeA{BRU_2007}.
+We also see one LFE episode in May-June 2004, propagating South to North from latitude 40.1 to 41.6, and one LFE episode in November 2004, propagating North to South from latitude 41.6 to 40.4.
+The first of these episodes is also in the ETS catalog from ~\citeA{BRU_2007}.
+The main characteristics of the six biggest episodes shown in Figure 7 are given in Table 1.
 \\
@@
 \begin{table}
-\caption{Main LFEs events between 2004 and 2011}
+\caption{Main LFEs episodes between 2004 and 2011}
 \centering
@@
 
-It is known than tectonic tremor can be triggered by surface waves from distant and regional earthquakes, as has been observed in Cascadia ~\cite{RUB_2009}, the San Andreas ~\cite{PEN_2009, GUI_2010}, and Nankai ~\cite{HAN_2014}.
+It is known than tectonic tremor can be triggered by surface waves from distant and regional earthquakes, as has been observed in Cascadia ~\cite{RUB_2009}, the San Andreas ~\cite{PEN_2009, GUI_2010}, and Nankai ~\cite{MIY_2008,HAN_2014}.
 LFE activity on the San Andreas fault also increased during several months after the 2004 Parkfield earthquake ~\cite{SHE_2017}.
@@
 Although we observe an increase in LFE activity for some families several days after the earthquakes (except the 2008 one where no activity is observed after the earthquake), it does not seem that this activity is linked to the earthquake.
-Indeed, the LFE events occur a few days after the earthquake and not immediately after as is the case for the Parkfield earthquake, and they affect only a few families.
+Indeed, the LFE clusters occur a few days after the earthquake and not immediately after as is the case for the Parkfield earthquake, and they affect only a few families.
 The reason may be due to the distance between the LFE families and the epicenters of the regional earthquakes.
@@
 Finally, we look at five families aligned at latitude about 41.05N (group G, pentagons in Figure 1) and show the number of LFEs per day in the right column of Figure 8.
-For all three sets of families, LFE events are more frequent for the easternmost family than for the westernmost family, as was also the case in northern Cascadia ~\cite{SWE_2019}.
-It is more difficult to compare event size and swarm duration as the number of stations and the quality of the templates are different from each family, and may have a strong influence on the number of LFEs detected.
-To summarize the findings, we plot in Figure 9 the number of LFE events as a function of the distance in the eastern direction from the upper limit of the tremor.
-We clearly see that the number of events increases with the down dip distance.
+For all three sets of families, LFE clusters are more frequent for the easternmost family than for the westernmost family, as was also the case in northern Cascadia ~\cite{SWE_2019}.
+It is more difficult to compare cluster size and swarm duration as the number of stations and the quality of the templates are different for each family, and may have a strong influence on the number of LFEs detected.
+To summarize the findings, we plot in Figure 9 the average time between LFE clusters as a function of the distance in the eastern direction from the western limit of the tremor.
+We assume that there is an LFE cluster every time that at least five LFEs are recorded during a given day.
+If two clusters are separated by less than five days, we assume that this is a single cluster.
+We clearly see that the average time between LFE clusters decreases with the down dip distance.
 The southernmost family A is also added in Figure 9, but does not fit the general trend.\\
@@
 \noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/nb_LFE_events.eps}
-\caption{Number of LFE events as a function of distance in the eastern direction from the upper limit of tremor for the three LFE families in group B (triangles in Figure 1), the five LFE families in group C (diamonds in Figure 1), and the five LFE families in group G (pentagons in Figure 1).
-Family A (square in Figure 1) has much more LFE events and is shown by an arrow.}
+\caption{Average time between LFE clusters as a function of distance in the eastern direction from the westward limit of tremor for the three LFE families in group B (triangles in Figure 1), the five LFE families in group C (diamonds in Figure 1), and the five LFE families in group G (pentagons in Figure 1).
+Family A (square in Figure 1) has much shorter time intervals between LFE clusters.}
 \label{pngfiguresample}
@@
 
-The occurrence and amplitude of tectonic tremor can be modulated by small stress changes (about 1 kPa) associated with ocean or solid earth tides ~\cite{HOU_2015}.
+The occurrence and amplitude of tectonic tremor can be modulated by small stress changes (about 1 kPa) associated with ocean or solid earth tides ~\cite{SHE_2007_G3,HOU_2011,HOU_2015}.
 Sensitivity of LFE families activity to tidal stress changes has also been observed in northern Cascadia ~\cite{ROY_2015}, and on the San Andreas fault ~\cite{THO_2012}.
@@
 where $\Delta \tau$ is the change in shear stress on the fault plane in the slip direction, $\Delta \sigma$ is the change in fault normal stress (positive is tensile), $\mu$ is the coefficient of intrinsic friction, $\Delta \sigma_m$ is the change in mean stress and $B$ is the Skempton's coefficient ~\cite{HOU_2015}.
-We take the values $\mu = 0.1$ and $B = 0.5$ for the friction and the Skempton's coefficient.
+We take the values $\mu = 0.1$ and $B = 0.5$ for the friction and the Skempton's coefficient, as was done by ~\citeA{HOU_2015}.
 We then divided the values of tidal Coulomb stress change into 20 stress bins and computed for each LFE family the number of LFEs occurring at a time when the value of the stress was in a given bin.
@@
 We clearly see that these LFEs tend to occur during times when predicted tidal Coulomb stress is discouraging slip on the plate boundary.
-We hypothesize that LFE family A may not be located on the subduction zone, and may be on a different fault instead.
+We tried to relocate this LFE family using new templates obtained from LFEs present in both the 2007-2009 FAME catalog and the 2004-2011 networks catalog.
+We locate the family using S minus P times for each station, or using P-P times between stations, or using a combination of both.
+The family may be located 30 to 50 kilometers east from the initial location given by ~\citeA{PLO_2015}.
+The depth is 20-25 kilometers, that is shallower than the location given by ~\citeA{PLO_2015} and shallower than the plate boundary.
+However, this does not change the pattern observed for the correlation between tidal stress changes and LFE activity.
+We hypothesize that LFE family A may not be located on the subduction zone and may be on a nearby crustal fault.
+If this was the case, the fault plane assumed for the tidal stress calculation would not be appropriate, which would explain the different pattern for this LFE family.
+The LFE families located on the San Andreas fault by ~\citeA{SHE_2017} have a depth of 15 to 30 kilometers, so the depth of the LFE family A is compatible with a location on a crustal fault.
 
@@
 The first figure was done using GMT ~\cite{WES_1991}.
+All the downloading and preprocessing operations on the seismic waveforms are done with the Python package obspy.
 The Python scripts used to analyze the data and make the figures can be found on the first author's Github account, accessible through Zenodo ~\cite{ariane_ducellier_2021_5168867}.

### 2022-02-03 paper/agujournaltemplate_highlighted.tex
Ready to submit

@@
 Low-frequency earthquakes (LFEs) are small magnitude earthquakes, with typical magnitude less than 2, and reduced amplitudes at frequencies greater than 10 Hz relative to  ordinary small earthquakes.
-Their occurrence is often associated with tectonic tremor and slow slip events along the plate boundary in subduction zones and occasionally transform fault zones.
-They are usually grouped into families of events, with all the earthquakes of a given family originating from the same small patch on the plate interface and recurring more or less episodically in a bursty manner.
+Their occurrence is often associated with tectonic tremor and slow-slip events along the plate boundary in subduction zones and occasionally transform fault zones.
+They are usually grouped into families, with all the earthquakes of a given family originating from the same small patch on the plate interface and recurring more or less episodically in a bursty manner.
 In this study, we extend the LFE catalog obtained by ~\citeA{PLO_2015} during an episode of high tremor activity in  April 2008, to the 8-year period 2004-2011.
@@
 The source of the tremor and the LFEs is located on the plate boundary \textbf{~\cite{SHE_2006,BOS_2012,AUD_2016}}, and their focal mechanisms represent shear slip on a low-angle thrust fault dipping in the same direction as the plate interface ~\textbf{\cite{IDE_2007_GRL,BOS_2012,ROY_2014}}.
-LFEs are usually grouped into families of events, with all the earthquakes of a given family originating from the same small patch on the plate interface, and recurring more or less episodically in a bursty manner.
-\textbf{Tens of events are thus recorded within a few hours or days during a burst of LFE activity, followed by weeks or months of quiet, with very few events.} In subduction zones such as Nankai and Cascadia, tectonic tremor and LFE observations are spatially and temporally correlated with slow slip observations \textbf{~\cite{ROG_2003,OBA_2004}}.
+LFEs are usually grouped into families of earthquakes, with all the earthquakes of a given family originating from the same small patch on the plate interface, and recurring more or less episodically in a bursty manner.
+\textbf{Dozens of earthquakes are thus recorded within a few hours or days during a burst of LFE activity, followed by weeks or months of quiet, with very few earthquakes.} In subduction zones such as Nankai and Cascadia, tectonic tremor and LFE observations are spatially and temporally correlated with slow-slip observations \textbf{~\cite{ROG_2003,OBA_2004}}.
 Due to this correlation, these paired phenomena have been called Episodic Tremor and Slip (ETS).
@@
 
-The relatively short recurrence of slow slip and tremor events results in a rich history both in space and time and reveals potential patterns.
+The relatively short recurrence of slow-slip and tremor events results in a rich history both in space and time and reveals potential patterns.
 These event histories have allowed scientists to see complete event cycles, which is typically not possible to explore in traditional earthquake catalogs.
-However, most of the work on LFEs has been focused on detecting LFEs during periods of high tremor activity, grouping them into families of events, and locating the source of the LFE families.
+However, most of the work on LFEs has been focused on detecting LFEs during periods of high tremor activity, grouping them into families of earthquakes, and locating the source of the LFE families.
 Longer catalogs (several years) have been established for LFE families in Mexico (two-year long catalog by ~\citeA{FRA_2014}), the San Andreas Fault (fifteen-year-long catalog by ~\citeA{SHE_2017}), Washington State (five-year-long catalog by ~\citeA{SWE_2019} and two-year-long catalog by ~\citeA{CHE_2017_JGR, CHE_2017_G3}), \textbf{Vancouver Island (ten-year-long catalog by ~\citeA{BOS_2015})}, New Zealand (eight-year-long catalog by ~\citeA{BAR_2018}), and Japan (twelve-year-long catalog by ~\citeA{NAK_2017}, eight-year-long catalog by ~\citeA{OHT_2017}, \textbf{eleven-year-long catalog by ~\citeA{KAT_2020}, and Japan Meteorological Agency (JMA) catalog since 1999 ~\cite{KAT_2003}}).
@@
 In northern Washington, ~\citeA{SWE_2019} have identified and characterized four different LFE families that span the width of the transition zone in the Cascadia Subduction Zone beneath western Washington State.
-They found that the LFEs swarm duration, recurrence interval, and event size decrease systematically with increasing depth.
+They found that the LFEs swarm duration, recurrence interval, and cluster size decrease systematically with increasing depth.
 On the San Andreas Fault, ~\citeA{SHE_2017} observed a large diversity of recurrence behaviors among the LFE families, from semicontinuous to highly episodic.
 Particularly, two families exhibited bimodal recurrence patterns (about 3 and 6 days for the first one, and about 2 and 4 days for the second one).
-Moreover, he observed an increase in the LFE event rate after the 2004 Parkfield earthquake.
+Moreover, he observed an increase in the LFE rate after the 2004 Parkfield earthquake.
 \\
@@
 As we may have many false detections, we try to eliminate some of them by assuming that LFEs present in both catalogs are always true detections.
-Then we define two thresholds: the first threshold is chosen such that at least half the LFE detections above the threshold in the FAME catalog are also in the network catalog, the second threshold is chosen such that at least half the LFE detections above the threshold in the network catalog are also in the FAME catalog.
+Then we define two thresholds: the first threshold is chosen such that half the LFE detections above the threshold in the FAME catalog are also in the network catalog, the second threshold is chosen such that half the LFE detections above the threshold \textbf{(and occurring during 2007-2009)} in the network catalog are also in the FAME catalog.
 If we filter the catalogs and keep only detections above the thresholds, we are now confident that at least half of the LFE detections are true detections.
-As the number of stations recording may vary over time (especially for the permanent networks catalog), we keep only the LFE detections such that the associated cross correlation multiplied by the number of channels recording at that time is higher than the threshold.
+\textbf{Thus there are two thresholds per LFE family (given in Table S3 of the Supplementary Material).} As the number of stations recording may vary over time (especially for the permanent networks catalog), we keep only the LFE detections such that the associated cross correlation multiplied by the number of channels recording at that time is higher than the threshold.
 Thus, if there are few stations recordings at some time, the cross correlation must be higher for the LFE to be considered as a true detection.
@@
 Examples are given in Figure 5 for families A (square in Figure 1) and E (inverted triangle in Figure 1).
-Although the number of LFEs during each \textbf{cluster of LFEs} may not be the same, we clearly see for family E that the timing of the events are the same for both catalogs.
+Although the number of LFEs during each \textbf{cluster of LFEs} may not be the same, we clearly see for family E that the timing of the clusters are the same for both catalogs.
 Family A has much shorter recurrence times but most \textbf{clusters of LFEs are present in both catalogs as well: forty clusters are present in both catalogs, three clusters are present in the FAME catalog but not in the networks catalog and one cluster is present in the networks catalog but not in the FAME catalog.} \\
@@
 We eliminate six families for which too few permanent stations have good templates, and it was not possible to detect LFEs with the available templates.
-However, we were able to detect most LFE events even without the presence of the temporary stations from the FAME network.
+However, we were able to detect most LFE clusters even without the presence of the temporary stations from the FAME network.
 We are thus confident that we can detect LFEs before 2007 and after 2009.
 In the following, we focus on the period 2004-2011.
-In November 2011, several one-component stations stopped recording and the number of available stations started decreasing, which is why we did not look for LFE events after that date.
+In November 2011, several one-component stations stopped recording and the number of available stations started decreasing, which is why we did not look for LFE after that date.
 The resulting LFE catalog for the period 2004-2011 is shown in Figure 6.
@@
 \textbf{The tremor catalog of ~\citeA{BOY_2015} starts in 2005.
-This is why no tremor detections can be shown for the two events in 2004.}}
+This is why no tremor detections can be shown for the two ETS events in 2004.}}
 \label{pngfiguresample}
@@
 Finally, we look at five families aligned at latitude about 41.05N (group G, pentagons in Figure 1) and show the number of LFEs per day in the right column of Figure 8.
-For all three sets of families, LFE events are more frequent for the easternmost family than for the westernmost family, as was also the case in northern Cascadia ~\cite{SWE_2019}.
-It is more difficult to compare event size and swarm duration as the number of stations and the quality of the templates are different for each family, and may have a strong influence on the number of LFEs detected.
-To summarize the findings, we plot in Figure 9 the \textbf{average time between} LFE events as a function of the distance in the eastern direction from the \textbf{western} limit of the tremor.
-\textbf{We assume that there is an LFE event every time that at least five LFEs are recorded during a given day.
-If two events are separated by less than five days, we assume that this is a single event.} We clearly see that the \textbf{average time between LFE events} decreases with the down dip distance.
+For all three sets of families, LFE clusters are more frequent for the easternmost family than for the westernmost family, as was also the case in northern Cascadia ~\cite{SWE_2019}.
+It is more difficult to compare cluster size and swarm duration as the number of stations and the quality of the templates are different for each family, and may have a strong influence on the number of LFEs detected.
+To summarize the findings, we plot in Figure 9 the \textbf{average time between} LFE clusters as a function of the distance in the eastern direction from the \textbf{western} limit of the tremor.
+\textbf{We assume that there is an LFE cluster every time that at least five LFEs are recorded during a given day.
+If two clusters are separated by less than five days, we assume that this is a single cluster.} We clearly see that the \textbf{average time between LFE clusters} decreases with the down dip distance.
 The southernmost family A is also added in Figure 9, but does not fit the general trend.\\
@@
 \noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/nb_LFE_events.eps}
-\caption{\textbf{Average time between} LFE events as a function of distance in the eastern direction from the \textbf{westward} limit of tremor for the three LFE families in group B (triangles in Figure 1), the five LFE families in group C (diamonds in Figure 1), and the five LFE families in group G (pentagons in Figure 1).
-Family A (square in Figure 1) has much \textbf{shorter time intervals between } LFE events.}
+\caption{\textbf{Average time between} LFE clusters as a function of distance in the eastern direction from the \textbf{westward} limit of tremor for the three LFE families in group B (triangles in Figure 1), the five LFE families in group C (diamonds in Figure 1), and the five LFE families in group G (pentagons in Figure 1).
+Family A (square in Figure 1) has much \textbf{shorter time intervals between } LFE clusters.}
 \label{pngfiguresample}
@@
 We clearly see that these LFEs tend to occur during times when predicted tidal Coulomb stress is discouraging slip on the plate boundary.
-\textbf{We tried to relocate this LFE family using the new templates obtained from the best LFEs in the 2004-2011 catalogs and S minus P times within a single stations or P-P times between stations.
-The location is still not very well constrained and the LFE family A may be located 20 to 30 kilometers north or east of the initial location from ~\citeA{PLO_2015}.
+\textbf{We tried to relocate this LFE family using new templates obtained from LFEs present in both the 2007-2009 FAME catalog and the 2004-2011 networks catalog.
+We locate the family using S minus P times for each station, or using P-P times between stations, or using a combination of both.
+The family may be located 30 to 50 kilometers east from the initial location given by ~\citeA{PLO_2015}.
+The depth is 20-25 kilometers, that is shallower than the location given by ~\citeA{PLO_2015} and shallower than the plate boundary.
 However, this does not change the pattern observed for the correlation between tidal stress changes and LFE activity.
-There is a great uncertainty on the depth and this LFE family may be located much shallower than the plate boundary.
-We hypothesize that LFE family A may not be located on the subduction zone and may be on a nearby crustal fault that runs west to east.
-If this was the case, the fault plane assumed for the tidal stress calculation would not be appropriate, which would explain the different patron for this LFE family.
-In our future work, we plan to invert template waveforms for moment tensor mechanisms, which should help investigate whether the LFE family A is on a crustal fault.}
+We hypothesize that LFE family A may not be located on the subduction zone and may be on a nearby crustal fault.
+If this was the case, the fault plane assumed for the tidal stress calculation would not be appropriate, which would explain the different pattern for this LFE family.
+The LFE families located on the San Andreas fault by ~\citeA{SHE_2017} have a depth of 15 to 30 kilometers, so the depth of the LFE family A is compatible with a location on a crustal fault.}
 

### 2022-02-03 paper/supplement.tex
Work on revisions
Ready to submit

@@
 \caption{Same as Figure 3 from the main text, but without filtering the LFEs.
-They are many false detections at the beginning and the end of the catalog because the FAME stations were not yet installed / already removed.}
+There are many false detections at the beginning and the end of the catalog because the FAME stations were not yet installed / already removed.}
 \label{pngfiguresample}
@@
 \hline
-Family & Threshold 2007-2009 & Threshold 2004-2011 \\
+Family & Threshold 2007-2009 FAME catalog & Threshold 2007-2009 networks catalog\\
 \hline

### 2022-02-03 matlab/locate_family.m

@@ -1,4 +1,4 @@
-grd.lon = [-123.8:.01:-122.3];
+grd.lon = [-123.8:.01:-122.0];
 grd.lat = [39.5:.01:40.8];
 grd.depth = [20:1:70];
 vp_vs = 1.8;
@@ -7,22 +7,22 @@ vp_vs = 1.8;
 stations = ['KHBB', 'ME08', 'ME12', 'ME28', 'ME37', 'ME39', 'ME41', 'ME57', 'WDC'];
 lats = [40.65990, 40.222, 40.104, 40.327, 40.285, 40.188202, 39.884998, 39.9118, 40.57988];
 lons = [-123.21966, -123.305, -122.498, -122.471, -123.653999, -123.594299, -123.361, -122.5676, -122.54113];
-S_P = [14.00, 12.70, 5.50, 12.50, 6.45, 16.40, 17.10, 15.35, 3.50, 7.45];
+S_P = [15.65, 12.70, 2.20, 6.75, 17.90, 16.85, 15.35, 3.85, 7.65];
 [TTgrid, LAT, LON, DEP] = makeTTgrid(lats, lons, grd);
-misfit = abs(TTgrid(1).TIM - S_P(1)) + abs(TTgrid(2).TIM - S_P(2)) + ...
-         abs(TTgrid(3).TIM - S_P(3)) + abs(TTgrid(4).TIM - S_P(4)) + ...
-         abs(TTgrid(5).TIM - S_P(5)) + abs(TTgrid(6).TIM - S_P(6)) + ...
-         abs(TTgrid(7).TIM - S_P(7)) + abs(TTgrid(8).TIM - S_P(8)) + ...
-         abs(TTgrid(9).TIM - S_P(9));
+misfit = abs((vp_vs - 1) * TTgrid(1).TIM - S_P(1)) + abs((vp_vs - 1) * TTgrid(2).TIM - S_P(2)) + ...
+         abs((vp_vs - 1) * TTgrid(3).TIM - S_P(3)) + abs((vp_vs - 1) * TTgrid(4).TIM - S_P(4)) + ...
+         abs((vp_vs - 1) * TTgrid(5).TIM - S_P(5)) + abs((vp_vs - 1) * TTgrid(6).TIM - S_P(6)) + ...
+         abs((vp_vs - 1) * TTgrid(7).TIM - S_P(7)) + abs((vp_vs - 1) * TTgrid(8).TIM - S_P(8)) + ...
[…]

### 2022-02-03 matlab/locate_family_kcc.m

@@ -1,0 +1,160 @@
+clear;
+PPweights=[0 .1 .3 .5 .75 1 2 10];
+PPweight=0.5;  
+% first section finds location for S-P times and plots data and maps
+% second section finds location for P-P times down weighted by PPweight and
+% S-P times and makes plots for S-P times at the location for PP and SP
+grd.lon = [-123.8:.01:-122.3];
+grd.lat = [39.5:.01:40.8];
+grd.depth = [20:1:70];
+vp_vs = 1.8;
+
+% Using S minus P times
+stations = {'KHBB', 'ME08', 'ME12', 'ME28', 'ME37', 'ME39', 'ME41', 'ME57', 'WDC'};
+lats = [40.65990, 40.222, 40.104, 40.327, 40.285, 40.188202, 39.884998, 39.9118, 40.57988];
+lons = [-123.21966, -123.305, -122.498, -122.471, -123.653999, -123.594299, -123.361, -122.5676, -122.54113];
+S_P = [15.65, 12.70, 2.20, 6.75, 17.90, 16.85, 15.35, 3.85, 7.65];
+S_P = S_P(:);
+[TTgrid, LAT, LON, DEP] = makeTTgrid(lats, lons, grd);
+misfit=0;
+for k=1:9;
+  misfit=misfit + abs((vp_vs - 1) * TTgrid(k).TIM - S_P(k));
+end
+misfit_SP=misfit;
+[minmisfit, minindx] = min(misfit(:));
+LAT0 = LAT(minindx);
+LON0 = LON(minindx);
+DEP0 = DEP(minindx);
+fprintf('%f %f %f\n', LON0, LAT0, DEP0);
+% Plot cross section of misfit with fixed latitude
+figure(1); clf;
+k = find(grd.lat == LAT0);
+contour(reshape(LON(k, : , :), 151, 51), reshape(DEP(k, :, :), 151, 51), reshape(misfit(k, :, :), 151, 51),'ShowText','on');
+hold on;
+plot(LON0, DEP0, '*');
+xlabel('Longitude', 'FontSize', 16);
+ylabel('Depth', 'FontSize', 16);
+% Plot cross section of misfit with fixed longitude
+figure(2); clf;
+k = find(grd.lon == LON0);
+contour(reshape(LAT(:, k, :), 131, 51), reshape(DEP(:, k, :), 131, 51), reshape(misfit(:, k, :), 131, 51),'ShowText','on');
+hold on;
[…]

### 2022-02-03 matlab/trace_ray.m

@@ -50,7 +50,7 @@ if nargin<2 || length(model)==0;  % use default model (PNSN model P2 converted t
    7.88 35.0;
    9.16 40.0];
 
-  model = [vel_P2(:,1)/sqrt(3) ,  vel_P2(:,2)];
+  model = [vel_P2(:,1) ,  vel_P2(:,2)];
   
 end
 

### 2022-02-03 src/get_tidal_stress.py

@@ -31,8 +31,8 @@ for i in range(0, 1): #np.shape(templates)[0]):
 
 #    lat0 = templates[i][2]
 #    lon0 = templates[i][3]
-    lat0 = 40.21
-    lon0 = -122.50
+    lat0 = 40.18
+    lon0 = -122.24
     dx = (pi / 180.0) * a * cos(lat0 * pi / 180.0) / sqrt(1.0 - e * e * \
         sin(lat0 * pi / 180.0) * sin(lat0 * pi / 180.0))
     dy = (3.6 * pi / 648.0) * a * (1.0 - e * e) / ((1.0 - e * e * sin(lat0 * \

### 2022-02-03 paper/agujournaltemplate.tex
Revision submitted

@@
 All the downloading and preprocessing operations on the seismic waveforms are done with the Python package obspy.
-The Python scripts used to analyze the data and make the figures can be found on the first author's Github account, accessible through Zenodo ~\cite{ariane_ducellier_2021_5168867}.
+The Python scripts used to analyze the data and make the figures can be found on the first author's Github account, accessible through Zenodo ~\cite{ariane_ducellier_2022_5962414}.
 

### 2022-02-03 paper/agujournaltemplate_highlighted.tex
Revision submitted

@@
 The first figure was done using GMT ~\cite{WES_1991}.
-\textbf{All the downloading and preprocessing operations on the seismic waveforms are done with the Python package obspy.} The Python scripts used to analyze the data and make the figures can be found on the first author's Github account, accessible through Zenodo ~\cite{ariane_ducellier_2021_5168867}.
+\textbf{All the downloading and preprocessing operations on the seismic waveforms are done with the Python package obspy.} The Python scripts used to analyze the data and make the figures can be found on the first author's Github account, accessible through Zenodo ~\cite{ariane_ducellier_2022_5962414}.
 

### 2022-03-09 paper/agujournaltemplate_highlighted.tex
Last revision

@@
 \item We establish an eight-year-long low-frequency earthquake catalog for southern Cascadia.
-\item Families from the subduction zone are mainly active during the big tremor events, with down dip families more active than up dip families.
+\item Families from the subduction zone are mainly active during the big tremor episodes, with down dip families more active than up dip families.
 \item LFE activity is sensitive to tidal stress changes.
@@
 In this study, we extend the LFE catalog obtained by ~\citeA{PLO_2015} during an episode of high tremor activity in  April 2008, to the 8-year period 2004-2011.
-All of the tremor in the ~\citeA{BOY_2015} catalog south of 42 degrees North has associated LFE activity, but we have identified several \textbf{smaller clusters of LFEs without associated tremor activity}, and extend their catalog forward and backward by a total of about 3 years.
+All of the tremor in the ~\citeA{BOY_2015} catalog south of 42 degrees North has associated LFE activity, but we have identified several smaller episodes of LFEs without associated tremor activity, and extend their catalog forward and backward by a total of about 3 years.
 As in northern Cascadia, the down-dip LFE families have recurrence intervals several times smaller than the up-dip families.
-For the April, 2008 Episodic Tremor and Slip event, the best recorded LFE families exhibit a strong tidal Coulomb stress sensitivity starting 1.5 days after the rupture front passes by each LFE family.
+For the April 2008 Episodic Tremor and Slip event, the best recorded LFE families exhibit a strong tidal Coulomb stress sensitivity starting 1.5 days after the rupture front passes by each LFE family.
 The southernmost LFE family, which has been interpreted to be on the subduction plate boundary, near the up-dip limit of tremor, has a very short recurrence time.
@@
 Low-frequency earthquakes (LFEs) are small magnitude earthquakes, with typical magnitude less than 2, and reduced amplitudes at frequencies greater than 10 Hz relative to ordinary small earthquakes.
-They are usually grouped into families of events, with all the earthquakes of a given family originating from the same small patch on the plate interface.
-\textbf{LFEs tend to happen in bursts, with dozen of earthquakes occurring within a few days, followed by weeks or months of quiet}.
+They are usually grouped into families, with all the earthquakes of a given family originating from the same small patch on the plate interface.
+LFEs tend to happen in bursts, with dozen of earthquakes occurring within a few days, followed by weeks or months of quiet.
 In this study, we extend the LFE catalog obtained by ~\citeA{PLO_2015} to the 8-year period 2004-2011.
-As in northern Cascadia, the \textbf{LFE families located at greater depth (down dip) are more active, with shorter time intervals between two earthquake bursts, than the LFE families located at shallower depth (up dip).
-Earth tides also have an influence on LFE activity: LFEs are more likely to occur when the stress changes associated with the tides favor shear failure on the plate boundary}.
+As in northern Cascadia, the LFE families located at greater depth (down dip) are more active, with shorter time intervals between two earthquake bursts, than the LFE families located at shallower depth (up dip).
+Earth tides also have an influence on LFE activity: LFEs are more likely to occur when the stress changes associated with the tides favor shear failure on the plate boundary.
 
@@
 
-Tectonic tremor is a weak but persistent shaking of the Earth that has been discovered in many subduction zones and some strike-slip faults throughout the world \textbf{~\cite{BER_2011}}.
-Tremor is observed on seismograms as apparent noise whose amplitude is modulated in time in a similar manner at stations that are dozens of kilometers apart from each other \textbf{~\cite{OBA_2002}}.
+Tectonic tremor is a weak but persistent shaking of the Earth that has been discovered in many subduction zones and some strike-slip faults throughout the world ~\cite{BER_2011}.
+Tremor is observed on seismograms as apparent noise whose amplitude is modulated in time in a similar manner at stations that are dozens of kilometers apart from each other ~\cite{OBA_2002}.
 It is characterized by a long (several seconds to many minutes), low amplitude seismic signal, emergent onsets, and an absence of clear impulsive phases.
-Tremor can be explained as a swarm of low-frequency earthquakes (LFEs) \textbf{~\cite{SHE_2007_nature}}, that is small magnitude earthquakes (M $\sim$ 1) which dominant frequency is clearly low (1-10 Hz) compared with that of ordinary tiny earthquakes (up to 20 Hz).
-The source of the tremor and the LFEs is located on the plate boundary \textbf{~\cite{SHE_2006,BOS_2012,AUD_2016}}, and their focal mechanisms represent shear slip on a low-angle thrust fault dipping in the same direction as the plate interface ~\textbf{\cite{IDE_2007_GRL,BOS_2012,ROY_2014}}.
+Tremor can be explained as a swarm of low-frequency earthquakes (LFEs) ~\cite{SHE_2007_nature}, that is small magnitude earthquakes (M $\sim$ 1) \textbf{whose} dominant frequency is clearly low (1-10 Hz) compared with ordinary tiny earthquakes (up to 20 Hz).
+The source of the tremor and the LFEs is located on the plate boundary ~\cite{SHE_2006,BOS_2012,AUD_2016}, and their focal mechanisms represent shear slip on a low-angle thrust fault dipping in the same direction as the plate interface ~\cite{IDE_2007_GRL,BOS_2012,ROY_2014}.
 LFEs are usually grouped into families of earthquakes, with all the earthquakes of a given family originating from the same small patch on the plate interface, and recurring more or less episodically in a bursty manner.
-\textbf{Dozens of earthquakes are thus recorded within a few hours or days during a burst of LFE activity, followed by weeks or months of quiet, with very few earthquakes.} In subduction zones such as Nankai and Cascadia, tectonic tremor and LFE observations are spatially and temporally correlated with slow-slip observations \textbf{~\cite{ROG_2003,OBA_2004}}.
+Dozens of earthquakes are thus recorded within a few hours or days during a burst of LFE activity, followed by weeks or months of quiet, with very few earthquakes.
+In subduction zones such as Nankai and Cascadia, tectonic tremor and LFE observations are spatially and temporally correlated with slow-slip observations ~\cite{ROG_2003,OBA_2004}.
 Due to this correlation, these paired phenomena have been called Episodic Tremor and Slip (ETS).
@@
 
-The relatively short recurrence of slow-slip and tremor events results in a rich history both in space and time and reveals potential patterns.
-These event histories have allowed scientists to see complete event cycles, which is typically not possible to explore in traditional earthquake catalogs.
+The relatively short recurrence of slow-slip and tremor episodes results in a rich history both in space and time and reveals potential patterns.
+These tremor activity histories have allowed scientists to see complete cycles, which is typically not possible to explore in traditional earthquake catalogs.
 However, most of the work on LFEs has been focused on detecting LFEs during periods of high tremor activity, grouping them into families of earthquakes, and locating the source of the LFE families.
-Longer catalogs (several years) have been established for LFE families in Mexico (two-year long catalog by ~\citeA{FRA_2014}), the San Andreas Fault (fifteen-year-long catalog by ~\citeA{SHE_2017}), Washington State (five-year-long catalog by ~\citeA{SWE_2019} and two-year-long catalog by ~\citeA{CHE_2017_JGR, CHE_2017_G3}), \textbf{Vancouver Island (ten-year-long catalog by ~\citeA{BOS_2015})}, New Zealand (eight-year-long catalog by ~\citeA{BAR_2018}), and Japan (twelve-year-long catalog by ~\citeA{NAK_2017}, eight-year-long catalog by ~\citeA{OHT_2017}, \textbf{eleven-year-long catalog by ~\citeA{KAT_2020}, and Japan Meteorological Agency (JMA) catalog since 1999 ~\cite{KAT_2003}}).
+Longer catalogs (several years) have been established for LFE families in Mexico (two-year long catalog by ~\citeA{FRA_2014}), the San Andreas Fault (fifteen-year-long catalog by ~\citeA{SHE_2017}), Washington State (five-year-long catalog by ~\citeA{SWE_2019} and two-year-long catalog by ~\citeA{CHE_2017_JGR, CHE_2017_G3}), Vancouver Island (ten-year-long catalog by ~\citeA{BOS_2015}), New Zealand (eight-year-long catalog by ~\citeA{BAR_2018}), and Japan (twelve-year-long catalog by ~\citeA{NAK_2017}, eight-year-long catalog by ~\citeA{OHT_2017}, eleven-year-long catalog by ~\citeA{KAT_2020}, and Japan Meteorological Agency (JMA) catalog since 1999 ~\cite{KAT_2003}).
 These studies have shown that the recurrence behavior of LFE families varies a lot between seismic regions, and inside the same seismic region.
@@
 Then, they recovered higher signal-to-noise LFE signals using iterative network cross-correlation.
-They found that the LFE families on the southern Cascadia Subduction Zone were located above the \textbf{plate boundary model of ~\citeA{MCC_2006}, with a large distribution of depths (28-47 km).
-However, they suggested that this may be because the plate boundary model is biased deep.} Three additional LFE families were found on two strike-slip faults, the Maacama and Bucknell Creek faults, which are part of the San Andreas Fault zone.
+They found that the LFE families on the southern Cascadia Subduction Zone were located above the plate boundary model of ~\citeA{MCC_2006}, with a large distribution of depths (28-47 km).
+However, they suggested that this may be because the plate boundary model is biased deep.
+Three additional LFE families were found on two strike-slip faults, the Maacama and Bucknell Creek faults, which are part of the San Andreas Fault zone.
 \\
@@
 Red stars are moderate ($M > 5$) nearby earthquakes.
-\textbf{The plate boundary from ~\citeA{MCC_2006} is contoured at 10-km intervals starting at 10 km depth.
+The plate boundary from ~\citeA{MCC_2006} is contoured at 10-km intervals starting at 10 km depth.
 The cross section shows the depth of the LFE families ~\cite{PLO_2015} and the plate boundary model from ~\citeA{MCC_2006} at latitude 41 N.
-MF indicates the Maacama Fault.}}
+MF indicates the Maacama Fault.
+\textbf{We highlighted with different shapes the LFE families or groups of LFE families that are discussed later in the text.
+The black square is for family A, the black triangles are for families B1 to B3, the black diamonds are for families C1 to C5, the black star is for family D, the inverted triangle is for family E, the circle is for family F, and the pentagons are for families G1 to G5.}}
 \label{pngfiguresample}
@@
 
-\textbf{Our ultimate goal is to obtain an eight-year-long LFE catalog using data from permanent seismic networks.
+Our ultimate goal is to obtain an eight-year-long LFE catalog using data from permanent seismic networks.
 The first step is to use the templates from ~\citeA{PLO_2015} and the data from the FAME experiment to get an LFE catalog for 2007-2009.
 The second step is to use the 2007-2009 FAME catalog to make templates for the seismic stations from the permanent networks.
-The third step is to use the new templates and the data from the permanent networks to get an LFE catalog for 2004-2011.} We used a matched-filter algorithm to detect LFEs.
+The third step is to use the new templates and the data from the permanent networks to get an LFE catalog for 2004-2011.
+We used a matched-filter algorithm to detect LFEs.
 For a given LFE family, we download one hour of seismic data.
@@
 However, if we stack the cross-correlation signals for all the channels and all the stations, we can see peaks appearing.
-Whenever the value of the average cross-correlation is higher than a threshold (we chose a threshold equal to eight times the median absolute deviation of the stacked cross-correlation \textbf{as was done by ~\citeA{SHE_2007_nature}}), we inferred that there is an LFE.
+Whenever the value of the average cross-correlation is higher than a threshold (we chose a threshold equal to eight times the median absolute deviation \textbf{(MAD)} of the stacked cross-correlation as was done by ~\citeA{SHE_2007_nature}), we inferred that there is an LFE.
 As two peaks separated by a short period of time may actually correspond to the same LFE, we kept only LFEs that are separated by at least one second and, when two LFEs are separated by less than one second, we keep only the one with the higher value of the stacked cross-correlation.
@@
 We first looked for LFEs during the months of March and April 2008, which correspond to the period covered by the catalog from ~\citeA{PLO_2015}, and compared our detections with the initial detections from the original catalog of 66 families.
-For 19 families, we recovered all the LFE detections initially present in the ~\citeA{PLO_2015}'s catalog.
+For 19 families, we recovered all the LFE detections initially present in the ~\citeA{PLO_2015} catalog.
 For 61 families, we recovered more than 90 \% of the initial LFE detections.
-We also added 74 \% more LFEs to the \textbf{initial number of LFEs in the catalog (when considering all 66 families)}, but most of added LFEs have a low cross-correlation value and may be false detections.
+We also added 74 \% more LFEs to the initial number of LFEs in the catalog (when considering all 66 families), but most of added LFEs have a low cross-correlation value and may be false detections.
 Figure 2 shows the cross-correlation values for the LFEs in the original catalog, and for the LFEs that we added to the catalog for family E (inverted triangle in Figure 1).
@@
 \noindent\includegraphics[width=\textwidth, trim={7.5cm 1cm 28cm 2cm},clip]{figures/hist.eps}
-\caption{Cross-correlation values for LFEs added in the catalog for family E (inverted triangle in Figure 1) (left) and cross-correlation values for LFEs in the original catalog from ~\citeA{PLO_2015} (right).
+\caption{Cross-correlation values for LFEs added in the catalog for family E (left) and cross-correlation values for LFEs in the original catalog from ~\citeA{PLO_2015} (right).
 There were no missing LFEs for this family.}
@@
 We then looked for LFEs during the period from July 2007 to June 2009, which correspond to the period when the FAME experiment was operating.
-Using a threshold equal to eight times the median absolute deviation of the stacked cross-correlation may produce false detections, therefore we filtered the LFE detection times before visualizing the two-year-long catalog.
-As the number of seismic stations recording may change with time as the stations were progressively installed during Summer and Fall 2007, and then progressively removed during May and June 2009, we kept only LFE detections for which the product of the \textbf{stacked} cross-correlation value by the number of \textbf{channels} recording at that time is higher than a threshold.
-\textbf{We will explain later in the text how the threshold is chosen}.
-The threshold is different for each LFE family, \textbf{but is constant over time for a given LFE family}.
+Using a threshold equal to eight times the \textbf{MAD} of the stacked cross-correlation may produce false detections, therefore we filtered the LFE detection times before visualizing the two-year-long catalog.
+Because the number of seismic stations recording may change with time as the stations were progressively installed during Summer and Fall 2007, and then progressively removed during May and June 2009, we kept only LFE detections for which the product of the stacked cross-correlation value by the number of channels recording at that time is higher than a threshold.
+We will explain later in the text how the threshold is chosen.
+The threshold is different for each LFE family, but is constant over time for a given LFE family.
 The resulting LFE catalog for the period 2007-2009 is shown in Figure 3.
 For comparison, we also plotted the tremor detection times from ~\citeA{BOY_2015}.
-\textbf{Filtering the catalog has removed about 84 \% of the LFEs, compared to the initial catalog where LFEs were detected using the 8 * MAD threshold for the cross-correlation.
-As a reference, we plotted in the Supplementary Material (Figure S1) the catalog without filtering the LFEs and the number of channels recording as a function of time (Figure S3).} \\
+Filtering the catalog has removed about 84 \% of the LFEs, compared to the initial catalog where LFEs were detected using the 8 * MAD threshold for the cross-correlation.
+As a reference, we plotted in the Supplementary Material (Figure S1) the catalog without filtering the LFEs and the number of channels recording as a function of time (Figure S3).
+\\
 
@@
 \noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/tremor_nb_FAME_3.eps}
-\caption{LFE and tremor detections as a function of time and latitude.
+\caption{\textbf{Tremor and LFEs detected using the data from the FAME experiment} as a function of time and latitude.
 Red dots represent tremor detections from the catalog of ~\citeA{BOY_2015}.
-Black dots represent days where LFEs are detected for a given LFE family.
-The size of the black dots are proportional to the number of LFEs detected during this day.
+Black dots represent days \textbf{when} LFEs are detected for a given LFE family.
+The size of \textbf{each} black dot \textbf{is} proportional to the number of LFEs detected during this day.
 The double-headed grey arrow represents the time period when the FAME experiment was operating at full capacity.
@@
 The LFE families located south on the strike-slip fault from the San Andreas Fault system have much shorter recurrence intervals than the LFE families located on the subduction zone.
-Additionally, one LFE family located on the southern end of the subduction zone \textbf{(family A at 40.09N and 34.9km depth)} has also shorter recurrence intervals than families located farther north, and behaves more similarly to the strike-slip fault families.
+Additionally, one LFE family located on the southern end of the subduction zone (family A at 40.09N and 34.9km depth) has also shorter recurrence intervals than families located farther north, and behaves more similarly to the strike-slip fault families.
 \\
@@
 To increase the cross-correlation values between the templates and the data, we thus reduced the length of the templates to 25 to 40 seconds, depending on the maximum distance from the source to the stations.
-\textbf{The 2007-2009 FAME catalog has thus been established with cross correlations over one-minute-long templates while the 2004-2011 networks catalog has been established with cross correlations over shorter templates with average duration equal to 30 seconds.} We did not use stations more than 100 kilometers away from the epicenter of an LFE family, as the template would be unlikely to have a good signal-to-noise ratio.
-We then used this new, shorter templates for the permanent stations to make an LFE catalog for the period 2007-2009.
+The 2007-2009 FAME catalog has thus been established with cross correlations over one-minute-long templates while the 2004-2011 networks catalog has been established with cross correlations over shorter templates with average duration equal to 30 seconds.
+We then used these new, shorter templates for the permanent stations to make an LFE catalog for the period 2007-2009.
 \\
@@
 \noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/templates.eps}
-\caption{Low-frequency earthquake template for station WDC and family A (square in Figure 1) for the three channels BHE, BHN and BHZ (left to right).
+\caption{Low-frequency earthquake template for station WDC and family A for the three channels BHE, BHN and BHZ (left to right).
 We can clearly see a P-wave arrival and an S-wave arrival about 7 seconds later.
@@
 As we may have many false detections, we try to eliminate some of them by assuming that LFEs present in both catalogs are always true detections.
-Then we define two thresholds: the first threshold is chosen such that half the LFE detections above the threshold in the FAME catalog are also in the network catalog, the second threshold is chosen such that half the LFE detections above the threshold \textbf{(and occurring during 2007-2009)} in the network catalog are also in the FAME catalog.
+Then we define two thresholds \textbf{for each LFE family}: the first threshold is chosen such that half the LFE detections above the threshold in the FAME catalog are also in the network catalog, the second threshold is chosen such that half the LFE detections above the threshold (and occurring during 2007-2009) in the network catalog are also in the FAME catalog.
 If we filter the catalogs and keep only detections above the thresholds, we are now confident that at least half of the LFE detections are true detections.
-\textbf{Thus there are two thresholds per LFE family (given in Table S3 of the Supplementary Material).} As the number of stations recording may vary over time (especially for the permanent networks catalog), we keep only the LFE detections such that the associated cross correlation multiplied by the number of channels recording at that time is higher than the threshold.
+Thus there are two thresholds per LFE family (given in Table S3 of the Supplementary Material).
+As the number of stations recording may vary over time (especially for the permanent networks catalog), we keep only the LFE detections such that the associated cross correlation multiplied by the number of channels recording at that time is higher than the threshold.
 Thus, if there are few stations recordings at some time, the cross correlation must be higher for the LFE to be considered as a true detection.
@@
 Examples are given in Figure 5 for families A (square in Figure 1) and E (inverted triangle in Figure 1).
-Although the number of LFEs during each \textbf{cluster of LFEs} may not be the same, we clearly see for family E that the timing of the clusters are the same for both catalogs.
-Family A has much shorter recurrence times but most \textbf{clusters of LFEs are present in both catalogs as well: forty clusters are present in both catalogs, three clusters are present in the FAME catalog but not in the networks catalog and one cluster is present in the networks catalog but not in the FAME catalog.} \\
+\textbf{In the following, we speak of an LFE cluster when many LFEs are detected for a given family in a short period of time, we speak of LFE episode when many LFEs are detected for several families and LFE activity is propagating from one family to another along the strike of the plate boundary.} Although the number of LFEs during each cluster of LFEs may not be the same, we clearly see for family E that the timing of the clusters are the same for both catalogs.
+Family A has much shorter recurrence times but most clusters of LFEs are present in both catalogs as well: forty clusters are present in both catalogs, three clusters are present in the FAME catalog but not in the networks catalog and one cluster is present in the networks catalog but not in the FAME catalog.
+\\
 
@@
 \noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/cumulative.eps}
-\caption{Normalized cumulative number of LFEs over the period July 2007-July 2009 for the FAME catalog (red) and the network catalog (blue) for family A (square in Figure 1) and family E (inverted triangle in Figure 1).
-The cumulative number of LFEs has been divided by the total number of LFEs so that both curves start at 0 and end at 1, in order to get a better match between the LFE bursts in both catalogs.}
+\caption{Normalized cumulative number of LFEs over the period July 2007-July 2009 for the FAME catalog (red) and the network catalog (blue) for family A and family E.
+The cumulative number of LFEs has been divided by the total number of LFEs so that both curves start at 0 and end at 1, in order to get a better match between the LFE \textbf{clusters} in both catalogs.}
 \label{pngfiguresample}
@@
 In the following, we focus on the period 2004-2011.
-In November 2011, several one-component stations stopped recording and the number of available stations started decreasing, which is why we did not look for LFE after that date.
+In November 2011, several one-component stations stopped recording and the number of available stations started decreasing, which is why we did not look for LFEs after that date.
 The resulting LFE catalog for the period 2004-2011 is shown in Figure 6.
@@
 Figure 7 shows the details of six big ETS events in 2004, 2005, 2006, 2007 and 2008.
-\textbf{The catalog shown in Figure 6 has been filtered using the threshold computed above.
+The catalog shown in Figure 6 has been filtered using the threshold computed above.
 Filtering the catalog has removed about 63 \% of the LFEs, compared to the initial catalog where LFEs were detected using the 8 * MAD threshold for the cross-correlation.
-As a reference, we plotted in the Supplementary Material (Figure S2) the catalog without filtering the LFEs and the number of channels recording as a function of time (Figure S4).} \\
+As a reference, we plotted in the Supplementary Material (Figure S2) the catalog without filtering the LFEs and the number of channels recording as a function of time (Figure S4).
+\\
 
@@
 \noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/tremor_nb_perm_3.eps}
-\caption{LFE and tremor detections as a function of time and latitude.
+\caption{\textbf{Tremor and LFEs detected using the data from the permanent seismic networks} as a function of time and latitude.
 Red dots represent tremor detections from the catalog of ~\citeA{BOY_2015}.
-Black dots represent days where LFEs are detected for a given LFE family.
-The size of the black dots are proportional to the number of LFEs detected during this day.
+Black dots represent days \textbf{when} LFEs are detected for a given LFE family.
+The size of \textbf{each} black dot \textbf{is} proportional to the number of LFEs detected during this day.
 For clarity, we do not show the LFEs for the days when there are less than three LFEs.}
@@
 Red dots represent tremor detections from the catalog of ~\citeA{BOY_2015}.
-Black dots represent days where LFEs are detected for a given LFE family.
-The size of the black dots are proportional to the number of LFEs detected during this day.
+Black dots represent days \textbf{when} LFEs are detected for a given LFE family.
+The size of \textbf{each} black dot \textbf{is} proportional to the number of LFEs detected during this day.
 For clarity, we do not show the LFEs for the days when there are less than three LFEs.
-\textbf{The tremor catalog of ~\citeA{BOY_2015} starts in 2005.
-This is why no tremor detections can be shown for the two ETS events in 2004.}}
+The tremor catalog of ~\citeA{BOY_2015} starts in 2005.
+\textbf{So there are} no tremor detections for the two ETS events in 2004.}
 \label{pngfiguresample}
@@
 
-We were able to detect LFE clusters propagating from North to South or from South to North whenever there is a tremor episode in the ~\citeA{BOY_2015} catalog.
+We were able to detect LFE episodes propagating from North to South or from South to North whenever there is a tremor episode in the ~\citeA{BOY_2015} catalog.
 We were also able to detect several LFE episodes in 2004-2005 before the beginning of the ~\citeA{BOY_2015} catalog.
@@
 
-It is known than tectonic tremor can be triggered by surface waves from distant and regional earthquakes, as has been observed in Cascadia ~\cite{RUB_2009}, the San Andreas ~\cite{PEN_2009, GUI_2010}, and Nankai \textbf{~\cite{MIY_2008,HAN_2014}}.
+It is known \textbf{that} tectonic tremor can be triggered by surface waves from distant and regional earthquakes, as has been observed in Cascadia ~\cite{RUB_2009}, the San Andreas ~\cite{PEN_2009, GUI_2010}, and Nankai ~\cite{MIY_2008,HAN_2014}.
 LFE activity on the San Andreas fault also increased during several months after the 2004 Parkfield earthquake ~\cite{SHE_2017}.
@@
 The characteristics of the earthquakes we looked at are given in Table 2.
-We also looked at distant earthquakes with large magnitude, which  characteristics are given in Table 3.
-\\
+We also looked at \textbf{five large, distant earthquakes (Table 3).} \\
 
@@
 
-In northern Cascadia, it has been observed that there is an increase in activity downdip of the plate boundary compared to up dip, both for tremor ~\cite{WEC_2011} and LFEs ~\cite{SWE_2019}.
+In northern Cascadia, there is an increase in activity downdip of the plate boundary compared to up dip, both for tremor ~\cite{WEC_2011} and LFEs ~\cite{SWE_2019}.
 We want to verify whether we can see an increase of LFE activity for the downdip LFE families compared to the updip LFE families.
-Most families in the northern and central part of the study area are well aligned along the strike direction, however families in the southern part of the subduction zone are more distant from each other.
-We first look at three families aligned at latitude about 40.4N (group B, triangles in Figure 1) and show the number of LFEs per day in the left column of Figure 8.
-We then look at five families aligned at latitude about 40.7N (group C, diamonds in Figure 1) and show the number of LFEs per day in the middle column of Figure 8.
-Finally, we look at five families aligned at latitude about 41.05N (group G, pentagons in Figure 1) and show the number of LFEs per day in the right column of Figure 8.
-For all three sets of families, LFE clusters are more frequent for the easternmost family than for the westernmost family, as was also the case in northern Cascadia ~\cite{SWE_2019}.
+Most families in the northern and central part of the study area are well aligned along the strike direction, however families in the southern part of the subduction zone are more \textbf{distributed in the dip direction}.
+For example, we consider 3 groups of LFE families labeled as B, C and G (triangles, diamonds and pentagons in Figure 1).
+Each group has 3-5 families at about the same along-strike position, but varying in the dip direction.
+For each of the three groups there is a very clear pattern of many more LFE clusters for the down-dip (eastern) families than for the updip (western) families (Figure 8), as was also the case in northern Cascadia ~\cite{SWE_2019}.
 It is more difficult to compare cluster size and swarm duration as the number of stations and the quality of the templates are different for each family, and may have a strong influence on the number of LFEs detected.
-To summarize the findings, we plot in Figure 9 the \textbf{average time between} LFE clusters as a function of the distance in the eastern direction from the \textbf{western} limit of the tremor.
-\textbf{We assume that there is an LFE cluster every time that at least five LFEs are recorded during a given day.
-If two clusters are separated by less than five days, we assume that this is a single cluster.} We clearly see that the \textbf{average time between LFE clusters} decreases with the down dip distance.
-The southernmost family A is also added in Figure 9, but does not fit the general trend.\\
+To summarize the findings, we plot in Figure 9 the average time between LFE clusters as a function of the distance in the eastern direction from the western limit of the tremor.
+We \textbf{define} an LFE cluster \textbf{as} at least five LFEs recorded during a given day \textbf{for a given LFE family}.
+If two clusters are separated by less than five days, we assume that this is a single cluster.
+We clearly see that the average time between LFE clusters decreases with the down dip distance.
+The southernmost family A is also \textbf{plotted} in Figure 9, but does not fit the general trend.\\
 
@@
 \noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/set_daily_LFEs.eps}
-\caption{Left: Daily number of LFEs over the period 2004-2011 for the three LFE families in group C (triangles in Figure 1).
-Middle: Daily number of LFEs for the five LFE families in group D (diamonds in Figure 1).
-Right: Daily number of LFEs for the five LFE families in group E (pentagons in Figure 1).
+\caption{Daily number of LFEs over the period 2004-2011 for the three LFE families in group B \textbf{(left in this figure, triangles in Figure 1)}, for the five LFE families in group C \textbf{(middle in this figure, diamonds in Figure 1)} and the five LFE families in group G \textbf{(right in this figure, pentagons in Figure 1)}.
 Down-dip families (lower rows) typically have far more LFE swarms that up-dip families (upper rows).}
@@
 \noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/nb_LFE_events.eps}
-\caption{\textbf{Average time between} LFE clusters as a function of distance in the eastern direction from the \textbf{westward} limit of tremor for the three LFE families in group B (triangles in Figure 1), the five LFE families in group C (diamonds in Figure 1), and the five LFE families in group G (pentagons in Figure 1).
-Family A (square in Figure 1) has much \textbf{shorter time intervals between } LFE clusters.}
+\caption{Average time between LFE clusters as a function of distance in the eastern direction from the westward limit of tremor for the three LFE families in group B, the five LFE families in group C, and the five LFE families in group G.
+Family A has much shorter time intervals between LFE clusters.}
 \label{pngfiguresample}
@@
 
-The occurrence and amplitude of tectonic tremor can be modulated by small stress changes (about 1 kPa) associated with ocean or solid earth tides \textbf{~\cite{SHE_2007_G3,HOU_2011,HOU_2015}}.
+The occurrence and amplitude of tectonic tremor can be modulated by small stress changes (about 1 kPa) associated with ocean or solid earth tides ~\cite{SHE_2007_G3,HOU_2011,HOU_2015}.
 Sensitivity of LFE families activity to tidal stress changes has also been observed in northern Cascadia ~\cite{ROY_2015}, and on the San Andreas fault ~\cite{THO_2012}.
@@
 where $\Delta \tau$ is the change in shear stress on the fault plane in the slip direction, $\Delta \sigma$ is the change in fault normal stress (positive is tensile), $\mu$ is the coefficient of intrinsic friction, $\Delta \sigma_m$ is the change in mean stress and $B$ is the Skempton's coefficient ~\cite{HOU_2015}.
-We take the values $\mu = 0.1$ and $B = 0.5$ for the friction and the Skempton's coefficient, \textbf{as was done by ~\citeA{HOU_2015}}.
+We take the values $\mu = 0.1$ and $B = 0.5$ for the friction and the Skempton's coefficient, as was done by ~\citeA{HOU_2015}.
 We then divided the values of tidal Coulomb stress change into 20 stress bins and computed for each LFE family the number of LFEs occurring at a time when the value of the stress was in a given bin.
@@
 We thus choose to only consider the later part of the 2008 ETS event, using only LFEs that occurred between 1.5 and 11.5 days after the arrival of the tremor front.
-As there are only a few LFEs, it is not always obvious to see the influence of tidal stress on LFE activity.
+As there are only a few LFEs \textbf{in many of the families}, the influence of tidal stress on LFE activity \textbf{is not always clear}.
 However, Figure 10 shows the number of LFEs occurring during each stress bin (blue bars) and the expected number of LFEs (black line) for six families with a relatively high number of LFEs.
-For most of the families, a positive Coulomb stress change (promoting shear failure) is associated with an increase in LFE activity.
+For most of the families, a positive Coulomb stress change (promoting shear failure) is associated with an increase in LFE activity \textbf{, as is the case in northern Cascadia ~\cite{HOU_2015}}.
 However, this is not the case for the southernmost LFE family A, for which a negative Coulomb stress change is associated with an increase in LFE activity.
@@
 We clearly see that these LFEs tend to occur during times when predicted tidal Coulomb stress is discouraging slip on the plate boundary.
-\textbf{We tried to relocate this LFE family using new templates obtained from LFEs present in both the 2007-2009 FAME catalog and the 2004-2011 networks catalog.
-We locate the family using S minus P times for each station, or using P-P times between stations, or using a combination of both.
+We tried to relocate this LFE family using new templates obtained from LFEs present in both the 2007-2009 FAME catalog and the 2004-2011 networks catalog.
+We locate the family using S minus P times for each station, or using P-P times between \textbf{pairs of} stations, or using a combination of both.
 The family may be located 30 to 50 kilometers east from the initial location given by ~\citeA{PLO_2015}.
@@
 We hypothesize that LFE family A may not be located on the subduction zone and may be on a nearby crustal fault.
-If this was the case, the fault plane assumed for the tidal stress calculation would not be appropriate, which would explain the different pattern for this LFE family.
-The LFE families located on the San Andreas fault by ~\citeA{SHE_2017} have a depth of 15 to 30 kilometers, so the depth of the LFE family A is compatible with a location on a crustal fault.}
+If this was the case, the fault plane assumed for the tidal stress calculation would not be appropriate, which \textbf{could} explain the different pattern for this LFE family.
+The LFE families located on the San Andreas fault by ~\citeA{SHE_2017} have a depth of 15 to 30 kilometers, so the depth of the LFE family A is compatible with a location on a crustal fault.
 
@@
 
-In this study, we used the templates obtained by ~\citeA{PLO_2015} using data recorded by the FAME network in Northern California during an episode of high tremor activity in April 2008, and we extended their catalog to the whole two years (2007-2009) during which the seismic stations were installed.
-We then used the two-year-long catalog to create templates for stations from the permanent seismic networks, and used the seismic data recorded by these stations to extend the catalog before and after the FAME experiment.
-We observe LFEs every time that there is tectonic tremor on the tremor catalog from Boyarko et al.
-(2015), and several additional smaller LFE episodes.
-Whereas the LFE families from the subduction zone are mainly active during the big Episodic Tremor and Slip events, the southernmost family is more active, with repeating events about once a month.
-Downdip families are also more active than up dip families.
-Tidal stress changes seem to be correlated with LFE activity in the later part of the 2008 ETS event.
+We used the \textbf{waveform} templates obtained by ~\citeA{PLO_2015} using data recorded by the FAME network in Northern California during an episode of high tremor activity in April 2008, and we extended their catalog to the whole two years (2007-2009) during which the seismic stations were installed.
+We then used the two-year-long catalog to create templates for stations from the permanent seismic networks, and used the seismic data recorded by these stations to extend the catalog before and after the FAME experiment \textbf{to an eight-year duration (2004-2011)}.
+We observe \textbf{abundant} LFEs every time that there is tectonic tremor on the tremor catalog from Boyarko et al.
+(2015), and several additional smaller LFE episodes as well as two new longer LFE episodes in 2004 that predate the ~\citeA{BOY_2015} catalog.
+\textbf{The recurrence intervals of LFE clusters are systematically longer for updip (west) families than for families that are downdip (east), as has been observed in Northern Cascadia ~\cite{SWE_2019}.
+LFEs occur far more frequently during encouraging tidal Coulomb stresses than during times of discouraging stress during the April 2008 ETS.
+The effect is strongest starting 1.5 days after the rupture front has passed a given family.
+The behavior has been seen in northern Cascadia as well ~\cite{HOU_2015}.
+The southernmost LFE family, near the southern edge of the slab is unusual in that it is updip, yet has the shortest recurrence interval of all the families, and it occurs much more often during discouraging tidal stresses than during encouraging stress.
+Perhaps this family is mislocated and is on a crustal strike-slip fault, or on the edge of the slab rather than on the subduction interface.}
 
@@
 The first figure was done using GMT ~\cite{WES_1991}.
-\textbf{All the downloading and preprocessing operations on the seismic waveforms are done with the Python package obspy.} The Python scripts used to analyze the data and make the figures can be found on the first author's Github account, accessible through Zenodo ~\cite{ariane_ducellier_2022_5962414}.
+All the downloading and preprocessing operations on the seismic waveforms are done with the Python package obspy.
+The Python scripts used to analyze the data and make the figures can be found on the first author's Github account, accessible through Zenodo ~\cite{ariane_ducellier_2022_5962414}.
 

### 2022-03-09 data/Ducellier/plot_tremor_nbLFEs.py

@@ -13,8 +13,8 @@ from math import floor
 from date import ymdhms2day
 
 # Time boundaries
-xmin = 2007.5
-xmax = 2009.5
+xmin = 2004.0
+xmax = 2012.0
 
 # Space boundaries
 latmin = 39.4
@@ -23,6 +23,7 @@ latmax = 41.8
 # Read tremor file
 tremor = pd.read_csv('../tremor/tremor.xyddtt', sep=' ', header=None)
 tremor.columns = ['longitude', 'latitude', 'downdip', 'alongstrike', 'year', 'epoch']
+tremor = tremor.loc[(tremor['year'] >= xmin) & (tremor['year'] <= xmax)]
 year_tremor = tremor['year']
 lat_tremor = tremor['latitude']
 
@@ -53,20 +54,20 @@ kept_LFEs = 0
 for i in range(0, np.shape(templates)[0]):
 
     # Plot only good data
-    if threshold['threshold_FAME'].iloc[i] > 0.0:
+    if threshold['threshold_perm'].iloc[i] > 0.0:
 
         # Get latitude
         latitude = templates[i][2]
 
         # Open LFE catalog
         namedir = 'catalogs/' + templates[i][0].astype(str)
-        namefile = namedir + '/catalog_2007_2009.pkl'
+        namefile = namedir + '/catalog_2004_2011.pkl'
         df = pickle.load(open(namefile, 'rb'))
 
         all_LFEs = all_LFEs + len(df)
 
         # Filter LFEs
-#        df = df.loc[df['cc'] * df['nchannel'] >= threshold['threshold_FAME'].iloc[i]]
+#        df = df.loc[df['cc'] * df['nchannel'] >= threshold['threshold_perm'].iloc[i]]
 
         kept_LFEs = kept_LFEs + len(df)
 
@@ -89,17 +90,17 @@ for i in range(0, np.shape(templates)[0]):
         # Plot LFEs
         time = time[nbLFEs > 3]
         nbLFEs = nbLFEs[nbLFEs > 3]
-        plt.scatter(time, np.repeat(latitude, np.shape(time)[0]), s=1 + nbLFEs * 5, c='k')
+        plt.scatter(time, np.repeat(latitude, np.shape(time)[0]), s=1 + nbLFEs * 5, c='k', label='Numbers of LFEs')
[…]

### 2022-03-21 paper/agujournaltemplate.tex
Submit second revision

@@
 In this study, we extend the LFE catalog obtained by ~\citeA{PLO_2015} during an episode of high tremor activity in  April 2008, to the 8-year period 2004-2011.
-All of the tremor in the ~\citeA{BOY_2015} catalog south of 42 degrees North has associated LFE activity, but we have identified several smaller clusters of LFEs without associated tremor activity, and extend their catalog forward and backward by a total of about 3 years.
+All of the tremor in the ~\citeA{BOY_2015} catalog south of 42 degrees North has associated LFE activity, but we have identified several smaller episodes of LFEs without associated tremor activity, and extend their catalog forward and backward by a total of about 3 years.
 As in northern Cascadia, the down-dip LFE families have recurrence intervals several times smaller than the up-dip families.
-For the April, 2008 Episodic Tremor and Slip event, the best recorded LFE families exhibit a strong tidal Coulomb stress sensitivity starting 1.5 days after the rupture front passes by each LFE family.
+For the April 2008 Episodic Tremor and Slip event, the best recorded LFE families exhibit a strong tidal Coulomb stress sensitivity starting 1.5 days after the rupture front passes by each LFE family.
 The southernmost LFE family, which has been interpreted to be on the subduction plate boundary, near the up-dip limit of tremor, has a very short recurrence time.
@@
 Low-frequency earthquakes (LFEs) are small magnitude earthquakes, with typical magnitude less than 2, and reduced amplitudes at frequencies greater than 10 Hz relative to ordinary small earthquakes.
-They are usually grouped into families of events, with all the earthquakes of a given family originating from the same small patch on the plate interface.
+They are usually grouped into families, with all the earthquakes of a given family originating from the same small patch on the plate interface.
 LFEs tend to happen in bursts, with dozen of earthquakes occurring within a few days, followed by weeks or months of quiet.
@@
 It is characterized by a long (several seconds to many minutes), low amplitude seismic signal, emergent onsets, and an absence of clear impulsive phases.
-Tremor can be explained as a swarm of low-frequency earthquakes (LFEs) ~\cite{SHE_2007_nature}, that is small magnitude earthquakes (M $\sim$ 1) which dominant frequency is clearly low (1-10 Hz) compared with that of ordinary tiny earthquakes (up to 20 Hz).
+Tremor can be explained as a swarm of low-frequency earthquakes (LFEs) ~\cite{SHE_2007_nature}, that is small magnitude earthquakes (M $\sim$ 1) whose dominant frequency is clearly low (1-10 Hz) compared with ordinary tiny earthquakes (up to 20 Hz).
 The source of the tremor and the LFEs is located on the plate boundary ~\cite{SHE_2006,BOS_2012,AUD_2016}, and their focal mechanisms represent shear slip on a low-angle thrust fault dipping in the same direction as the plate interface ~\cite{IDE_2007_GRL,BOS_2012,ROY_2014}.
@@
 
-The relatively short recurrence of slow-slip and tremor events results in a rich history both in space and time and reveals potential patterns.
-These event histories have allowed scientists to see complete event cycles, which is typically not possible to explore in traditional earthquake catalogs.
+The relatively short recurrence of slow-slip and tremor episodes results in a rich history both in space and time and reveals potential patterns.
+These tremor activity histories have allowed scientists to see complete cycles, which is typically not possible to explore in traditional earthquake catalogs.
 However, most of the work on LFEs has been focused on detecting LFEs during periods of high tremor activity, grouping them into families of earthquakes, and locating the source of the LFE families.
@@
 The cross section shows the depth of the LFE families ~\cite{PLO_2015} and the plate boundary model from ~\citeA{MCC_2006} at latitude 41 N.
-MF indicates the Maacama Fault.}
+MF indicates the Maacama Fault.
+We highlighted with different shapes the LFE families or groups of LFE families that are discussed later in the text.
+The black square is for family A, the black triangles are for families B1 to B3, the black diamonds are for families C1 to C5, the black star is for family D, the inverted triangle is for family E, the circle is for family F, and the pentagons are for families G1 to G5.}
 \label{pngfiguresample}
@@
 However, if we stack the cross-correlation signals for all the channels and all the stations, we can see peaks appearing.
-Whenever the value of the average cross-correlation is higher than a threshold (we chose a threshold equal to eight times the median absolute deviation of the stacked cross-correlation as was done by ~\citeA{SHE_2007_nature}), we inferred that there is an LFE.
+Whenever the value of the average cross-correlation is higher than a threshold (we chose a threshold equal to eight times the median absolute deviation (MAD) of the stacked cross-correlation as was done by ~\citeA{SHE_2007_nature}), we inferred that there is an LFE.
 As two peaks separated by a short period of time may actually correspond to the same LFE, we kept only LFEs that are separated by at least one second and, when two LFEs are separated by less than one second, we keep only the one with the higher value of the stacked cross-correlation.
@@
 We first looked for LFEs during the months of March and April 2008, which correspond to the period covered by the catalog from ~\citeA{PLO_2015}, and compared our detections with the initial detections from the original catalog of 66 families.
-For 19 families, we recovered all the LFE detections initially present in the ~\citeA{PLO_2015}'s catalog.
+For 19 families, we recovered all the LFE detections initially present in the ~\citeA{PLO_2015} catalog.
 For 61 families, we recovered more than 90 \% of the initial LFE detections.
@@
 \begin{figure}
-\noindent\includegraphics[width=\textwidth, trim={7.5cm 1cm 28cm 2cm},clip]{figures/hist.eps}
-\caption{Cross-correlation values for LFEs added in the catalog for family E (inverted triangle in Figure 1) (left) and cross-correlation values for LFEs in the original catalog from ~\citeA{PLO_2015} (right).
+\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 25.5cm 0cm},clip]{figures/hist.eps}
+\caption{Cross-correlation values for LFEs added in the catalog for family E (left) and cross-correlation values for LFEs in the original catalog from ~\citeA{PLO_2015} (right).
 There were no missing LFEs for this family.}
@@
 We then looked for LFEs during the period from July 2007 to June 2009, which correspond to the period when the FAME experiment was operating.
-Using a threshold equal to eight times the median absolute deviation of the stacked cross-correlation may produce false detections, therefore we filtered the LFE detection times before visualizing the two-year-long catalog.
-As the number of seismic stations recording may change with time as the stations were progressively installed during Summer and Fall 2007, and then progressively removed during May and June 2009, we kept only LFE detections for which the product of the stacked cross-correlation value by the number of channels recording at that time is higher than a threshold.
+Using a threshold equal to eight times the MAD of the stacked cross-correlation may produce false detections, therefore we filtered the LFE detection times before visualizing the two-year-long catalog.
+Because the number of seismic stations recording may change with time as the stations were progressively installed during Summer and Fall 2007, and then progressively removed during May and June 2009, we kept only LFE detections for which the product of the stacked cross-correlation value by the number of channels recording at that time is higher than a threshold.
 We will explain later in the text how the threshold is chosen.
@@
 \noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/tremor_nb_FAME_3.eps}
-\caption{LFE and tremor detections as a function of time and latitude.
+\caption{Tremor and LFEs detected using the data from the FAME experiment as a function of time and latitude.
 Red dots represent tremor detections from the catalog of ~\citeA{BOY_2015}.
-Black dots represent days where LFEs are detected for a given LFE family.
-The size of the black dots are proportional to the number of LFEs detected during this day.
+Black dots represent days when LFEs are detected for a given LFE family.
+The size of each black dot is proportional to the number of LFEs detected during this day.
 The double-headed grey arrow represents the time period when the FAME experiment was operating at full capacity.
@@
 The LFE families located south on the strike-slip fault from the San Andreas Fault system have much shorter recurrence intervals than the LFE families located on the subduction zone.
-Additionally, one LFE family located on the southern end of the subduction zone (family A at 40.09N and 34.9km depth) has also shorter recurrence intervals than families located farther north, and behaves more similarly to the strike-slip fault families.
+Additionally, one LFE family located on the southern end of the subduction zone (family A at 40.09N and 34.9km depth) also has shorter recurrence intervals than families located farther north, and behaves more similarly to the strike-slip fault families.
 \\
@@
 The 2007-2009 FAME catalog has thus been established with cross correlations over one-minute-long templates while the 2004-2011 networks catalog has been established with cross correlations over shorter templates with average duration equal to 30 seconds.
-We did not use stations more than 100 kilometers away from the epicenter of an LFE family, as the template would be unlikely to have a good signal-to-noise ratio.
-We then used this new, shorter templates for the permanent stations to make an LFE catalog for the period 2007-2009.
+We then used these new, shorter templates for the permanent stations to make an LFE catalog for the period 2007-2009.
 \\
@@
 
-\section{Results}
+%\section{Results}
 
@@
 As we may have many false detections, we try to eliminate some of them by assuming that LFEs present in both catalogs are always true detections.
-Then we define two thresholds: the first threshold is chosen such that half the LFE detections above the threshold in the FAME catalog are also in the network catalog, the second threshold is chosen such that half the LFE detections above the threshold (and occurring during 2007-2009) in the network catalog are also in the FAME catalog.
+Then we define two thresholds for each LFE family: the first threshold is chosen such that half the LFE detections above the threshold in the FAME catalog are also in the network catalog, the second threshold is chosen such that half the LFE detections above the threshold (and occurring during 2007-2009) in the network catalog are also in the FAME catalog.
 If we filter the catalogs and keep only detections above the thresholds, we are now confident that at least half of the LFE detections are true detections.
@@
 Examples are given in Figure 5 for families A (square in Figure 1) and E (inverted triangle in Figure 1).
+In the following, we speak of an LFE cluster when many LFEs are detected for a given family in a short period of time, we speak of LFE episode when many LFEs are detected for several families and LFE activity is propagating from one family to another along the strike of the plate boundary.
 Although the number of LFEs during each cluster of LFEs may not be the same, we clearly see for family E that the timing of the clusters are the same for both catalogs.
@@
 \noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/cumulative.eps}
-\caption{Normalized cumulative number of LFEs over the period July 2007-July 2009 for the FAME catalog (red) and the network catalog (blue) for family A (square in Figure 1) and family E (inverted triangle in Figure 1).
-The cumulative number of LFEs has been divided by the total number of LFEs so that both curves start at 0 and end at 1, in order to get a better match between the LFE bursts in both catalogs.}
+\caption{Normalized cumulative number of LFEs over the period July 2007-July 2009 for the FAME catalog (red) and the network catalog (blue) for family A and family E.
+The cumulative number of LFEs has been divided by the total number of LFEs so that both curves start at 0 and end at 1, in order to get a better match between the LFE clusters in both catalogs.}
 \label{pngfiguresample}
@@
 \noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/tremor_nb_perm_3.eps}
-\caption{LFE and tremor detections as a function of time and latitude.
+\caption{Tremor and LFEs detected using the data from the permanent seismic networks as a function of time and latitude.
 Red dots represent tremor detections from the catalog of ~\citeA{BOY_2015}.
-Black dots represent days where LFEs are detected for a given LFE family.
-The size of the black dots are proportional to the number of LFEs detected during this day.
+Black dots represent days when LFEs are detected for a given LFE family.
+The size of each black dot is proportional to the number of LFEs detected during this day.
 For clarity, we do not show the LFEs for the days when there are less than three LFEs.}
@@
 Red dots represent tremor detections from the catalog of ~\citeA{BOY_2015}.
-Black dots represent days where LFEs are detected for a given LFE family.
-The size of the black dots are proportional to the number of LFEs detected during this day.
+Black dots represent days when LFEs are detected for a given LFE family.
+The size of each black dot is proportional to the number of LFEs detected during this day.
 For clarity, we do not show the LFEs for the days when there are less than three LFEs.
 The tremor catalog of ~\citeA{BOY_2015} starts in 2005.
-This is why no tremor detections can be shown for the two ETS events in 2004.}
+So there are no tremor detections for the two ETS events in 2004.}
 \label{pngfiguresample}
@@
 
-It is known than tectonic tremor can be triggered by surface waves from distant and regional earthquakes, as has been observed in Cascadia ~\cite{RUB_2009}, the San Andreas ~\cite{PEN_2009, GUI_2010}, and Nankai ~\cite{MIY_2008,HAN_2014}.
+It is known that tectonic tremor can be triggered by surface waves from distant and regional earthquakes, as has been observed in Cascadia ~\cite{RUB_2009}, the San Andreas ~\cite{PEN_2009, GUI_2010}, and Nankai ~\cite{MIY_2008,HAN_2014}.
 LFE activity on the San Andreas fault also increased during several months after the 2004 Parkfield earthquake ~\cite{SHE_2017}.
@@
 The characteristics of the earthquakes we looked at are given in Table 2.
-We also looked at distant earthquakes with large magnitude, which  characteristics are given in Table 3.
+We also looked at five large, distant earthquakes (Table 3).
 \\
@@
 
-In northern Cascadia, it has been observed that there is an increase in activity downdip of the plate boundary compared to up dip, both for tremor ~\cite{WEC_2011} and LFEs ~\cite{SWE_2019}.
+In northern Cascadia, there is an increase in activity downdip of the plate boundary compared to up dip, both for tremor ~\cite{WEC_2011} and LFEs ~\cite{SWE_2019}.
 We want to verify whether we can see an increase of LFE activity for the downdip LFE families compared to the updip LFE families.
-Most families in the northern and central part of the study area are well aligned along the strike direction, however families in the southern part of the subduction zone are more distant from each other.
-We first look at three families aligned at latitude about 40.4N (group B, triangles in Figure 1) and show the number of LFEs per day in the left column of Figure 8.
-We then look at five families aligned at latitude about 40.7N (group C, diamonds in Figure 1) and show the number of LFEs per day in the middle column of Figure 8.
-Finally, we look at five families aligned at latitude about 41.05N (group G, pentagons in Figure 1) and show the number of LFEs per day in the right column of Figure 8.
-For all three sets of families, LFE clusters are more frequent for the easternmost family than for the westernmost family, as was also the case in northern Cascadia ~\cite{SWE_2019}.
+Most families in the northern and central part of the study area are well aligned along the strike direction, however families in the southern part of the subduction zone are more distributed in the dip direction.
+For example, we consider 3 groups of LFE families labeled as B, C and G (triangles, diamonds and pentagons in Figure 1).
+Each group has 3-5 families at about the same along-strike position, but varying in the dip direction.
+For each of the three groups there is a very clear pattern of many more LFE clusters for the down-dip (eastern) families than for the updip (western) families (Figure 8), as was also the case in northern Cascadia ~\cite{SWE_2019}.
 It is more difficult to compare cluster size and swarm duration as the number of stations and the quality of the templates are different for each family, and may have a strong influence on the number of LFEs detected.
 To summarize the findings, we plot in Figure 9 the average time between LFE clusters as a function of the distance in the eastern direction from the western limit of the tremor.
-We assume that there is an LFE cluster every time that at least five LFEs are recorded during a given day.
+We define an LFE cluster as at least five LFEs recorded during a given day for a given LFE family.
 If two clusters are separated by less than five days, we assume that this is a single cluster.
 We clearly see that the average time between LFE clusters decreases with the down dip distance.
-The southernmost family A is also added in Figure 9, but does not fit the general trend.\\
+The southernmost family A is also plotted in Figure 9, but does not fit the general trend.\\
 
@@
 \noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/set_daily_LFEs.eps}
-\caption{Left: Daily number of LFEs over the period 2004-2011 for the three LFE families in group C (triangles in Figure 1).
-Middle: Daily number of LFEs for the five LFE families in group D (diamonds in Figure 1).
-Right: Daily number of LFEs for the five LFE families in group E (pentagons in Figure 1).
+\caption{Daily number of LFEs over the period 2004-2011 for the three LFE families in group B (left in this figure, triangles in Figure 1), for the five LFE families in group C (middle in this figure, diamonds in Figure 1) and the five LFE families in group G (right in this figure, pentagons in Figure 1).
 Down-dip families (lower rows) typically have far more LFE swarms that up-dip families (upper rows).}
@@
 \noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/nb_LFE_events.eps}
-\caption{Average time between LFE clusters as a function of distance in the eastern direction from the westward limit of tremor for the three LFE families in group B (triangles in Figure 1), the five LFE families in group C (diamonds in Figure 1), and the five LFE families in group G (pentagons in Figure 1).
-Family A (square in Figure 1) has much shorter time intervals between LFE clusters.}
+\caption{Average time between LFE clusters as a function of distance in the eastern direction from the westward limit of tremor for the three LFE families in group B, the five LFE families in group C, and the five LFE families in group G.
+Family A has much shorter time intervals between LFE clusters.}
 \label{pngfiguresample}
@@
 We thus choose to only consider the later part of the 2008 ETS event, using only LFEs that occurred between 1.5 and 11.5 days after the arrival of the tremor front.
-As there are only a few LFEs, it is not always obvious to see the influence of tidal stress on LFE activity.
+As there are only a few LFEs in many of the families, the influence of tidal stress on LFE activity is not always clear.
 However, Figure 10 shows the number of LFEs occurring during each stress bin (blue bars) and the expected number of LFEs (black line) for six families with a relatively high number of LFEs.
-For most of the families, a positive Coulomb stress change (promoting shear failure) is associated with an increase in LFE activity.
+For most of the families, a positive Coulomb stress change (promoting shear failure) is associated with an increase in LFE activity, as is the case in northern Cascadia ~\cite{HOU_2015}.
+\\
+
 However, this is not the case for the southernmost LFE family A, for which a negative Coulomb stress change is associated with an increase in LFE activity.
@@
 We tried to relocate this LFE family using new templates obtained from LFEs present in both the 2007-2009 FAME catalog and the 2004-2011 networks catalog.
-We locate the family using S minus P times for each station, or using P-P times between stations, or using a combination of both.
+We locate the family using S minus P times for each station, or using P-P times between pairs of stations, or using a combination of both.
 The family may be located 30 to 50 kilometers east from the initial location given by ~\citeA{PLO_2015}.
@@
 We hypothesize that LFE family A may not be located on the subduction zone and may be on a nearby crustal fault.
-If this was the case, the fault plane assumed for the tidal stress calculation would not be appropriate, which would explain the different pattern for this LFE family.
+If this was the case, the fault plane assumed for the tidal stress calculation would not be appropriate, which could explain the different pattern for this LFE family.
 The LFE families located on the San Andreas fault by ~\citeA{SHE_2017} have a depth of 15 to 30 kilometers, so the depth of the LFE family A is compatible with a location on a crustal fault.
@@
 
-In this study, we used the templates obtained by ~\citeA{PLO_2015} using data recorded by the FAME network in Northern California during an episode of high tremor activity in April 2008, and we extended their catalog to the whole two years (2007-2009) during which the seismic stations were installed.
-We then used the two-year-long catalog to create templates for stations from the permanent seismic networks, and used the seismic data recorded by these stations to extend the catalog before and after the FAME experiment.
-We observe LFEs every time that there is tectonic tremor on the tremor catalog from Boyarko et al.
-(2015), and several additional smaller LFE episodes.
-Whereas the LFE families from the subduction zone are mainly active during the big Episodic Tremor and Slip events, the southernmost family is more active, with repeating events about once a month.
-Downdip families are also more active than up dip families.
-Tidal stress changes seem to be correlated with LFE activity in the later part of the 2008 ETS event.
+We used the waveform templates obtained by ~\citeA{PLO_2015} using data recorded by the FAME network in Northern California during an episode of high tremor activity in April 2008, and we extended their catalog to the whole two years (2007-2009) during which the seismic stations were installed.
+We then used the two-year-long catalog to create templates for stations from the permanent seismic networks, and used the seismic data recorded by these stations to extend the catalog before and after the FAME experiment to an eight-year duration (2004-2011).
+We observe abundant LFEs every time that there is tectonic tremor on the tremor catalog from Boyarko et al.
+(2015), and several additional smaller LFE episodes as well as two new longer LFE episodes in 2004 that predate the ~\citeA{BOY_2015} catalog.
+The recurrence intervals of LFE clusters are systematically longer for updip (west) families than for families that are downdip (east), as has been observed in Northern Cascadia ~\cite{SWE_2019}.
+LFEs occur far more frequently during encouraging tidal Coulomb stresses than during times of discouraging stress during the April 2008 ETS.
+The effect is strongest starting 1.5 days after the rupture front has passed a given family.
+The behavior has been seen in northern Cascadia as well ~\cite{HOU_2015}.
+The southernmost LFE family, near the southern edge of the slab is unusual in that it is updip, yet has the shortest recurrence interval of all the families, and it occurs much more often during discouraging tidal stresses than during encouraging stress.
+Perhaps this family is mislocated and is on a crustal strike-slip fault, or on the edge of the slab rather than on the subduction interface.
 

### 2022-03-21 paper/agujournaltemplate_highlighted.tex
Submit second revision

@@
 \begin{figure}
-\noindent\includegraphics[width=\textwidth, trim={7.5cm 1cm 28cm 2cm},clip]{figures/hist.eps}
+\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 25.5cm 0cm},clip]{figures/hist.eps}
 \caption{Cross-correlation values for LFEs added in the catalog for family E (left) and cross-correlation values for LFEs in the original catalog from ~\citeA{PLO_2015} (right).
@@
 The LFE families located south on the strike-slip fault from the San Andreas Fault system have much shorter recurrence intervals than the LFE families located on the subduction zone.
-Additionally, one LFE family located on the southern end of the subduction zone (family A at 40.09N and 34.9km depth) has also shorter recurrence intervals than families located farther north, and behaves more similarly to the strike-slip fault families.
+Additionally, one LFE family located on the southern end of the subduction zone (family A at 40.09N and 34.9km depth) \textbf{also has} shorter recurrence intervals than families located farther north, and behaves more similarly to the strike-slip fault families.
 \\
@@
 For most of the families, a positive Coulomb stress change (promoting shear failure) is associated with an increase in LFE activity \textbf{, as is the case in northern Cascadia ~\cite{HOU_2015}}.
+\\
+
 However, this is not the case for the southernmost LFE family A, for which a negative Coulomb stress change is associated with an increase in LFE activity.

### 2022-03-21 data/Ducellier/plot_every_LFE.py

@@ -1,0 +1,105 @@
+"""
+This script looks at the catalog from southern Cascadia (2007-2009) and plots
+for each family the daily number of LFEs in function of time
+"""
+
+import matplotlib.pylab as pylab
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+import pickle
+
+from datetime import datetime, timedelta
+from math import cos, floor, pi, sin, sqrt
+
+params = {'legend.fontsize': 24, \
+          'xtick.labelsize':24, \
+          'ytick.labelsize':24}
+pylab.rcParams.update(params)
+
+# Earth's radius and ellipticity
+#a = 6378.136
+#e = 0.006694470
+
+# Conversion lat-lon into kilometers
+#lat0 = 40.281
+#lon0 = -124.433
+#dx = (pi / 180.0) * a * cos(lat0 * pi / 180.0) / sqrt(1.0 - e * e * \
+#    sin(lat0 * pi / 180.0) * sin(lat0 * pi / 180.0))
+#dy = (3.6 * pi / 648.0) * a * (1.0 - e * e) / ((1.0 - e * e * sin(lat0 * \
+#    pi / 180.0) * sin(lat0 * pi / 180.0)) ** 1.5)
+
+# List of LFE families
+templates = np.loadtxt('../Plourde_2015/templates_list.txt', \
+    dtype={'names': ('name', 'family', 'lat', 'lon', 'depth', 'eH', \
+    'eZ', 'nb'), \
+         'formats': ('S13', 'S3', np.float, np.float, np.float, \
+    np.float, np.float, np.int)}, \
+    skiprows=1)
+
+# Threshold for filtering the catalog
+threshold = pd.read_csv('threshold_cc.txt', sep=r'\s{1,}', header=None, engine='python')
+threshold.columns = ['family', 'threshold_FAME', 'threshold_perm']
+
+# Beginning and end of the period we are looking at
+tbegin = datetime(2011, 3, 11, 5, 46, 24)
+tend = datetime(2011, 3, 11, 11, 46, 24)
+teq = datetime(2011, 3, 11, 5, 46, 24)
+
+tmin = tbegin - teq
+xmin = tmin.days * 24 + tmin.seconds / 3600.0
+tmax = tend - teq
+xmax = tmax.days * 24 + tmax.seconds / 3600.0
+
+# Loop on templates
+for i in range(0, np.shape(templates)[0]):
+
+    # Plot only good data
[…]

### 2022-03-21 data/Ducellier/plot_nb_events.py

@@ -18,6 +18,9 @@ pylab.rcParams.update(params)
 events = pd.read_csv('LFEdistribution_perm/nb_LFE_events.txt', sep=r'\s{1,}', header=None, engine='python')
 events.columns = ['group', 'name', 'lon', 'lat', 'x', 'y', 'nb', 'rt']
 
+event_B3 = events.loc[events['name'] == 'B3']
+events = events.loc[events['name'] != 'B3']
+
 groups = events['group'].unique()
 
 plt.figure(1, figsize=(8, 8))
@@ -26,6 +29,8 @@ cycol = cycle('bgrcmk')
 for group in groups:
     events_sub = events.loc[events['group'] == group]
     color = next(cycol)
+    if group == 'B':
+        color_B = color
     plt.scatter(events_sub['x'], events_sub['rt'], c=color, s=100)
     for i in range(0, len(events_sub)):
         if events_sub['name'].iloc[i] in ['C2', 'C4']:
@@ -45,10 +50,14 @@ for group in groups:
                 (events_sub['x'].iloc[i] + 1, events_sub['rt'].iloc[i]), \
                 fontsize=24, color=color)
 
+plt.arrow(event_B3['x'].iloc[0], 275, 0, 20, width=0.3, color=color_B)
+plt.annotate(event_B3['name'].iloc[0] + ' (' + str(int(event_B3['rt'].iloc[0])) + ')', \
+    (event_B3['x'].iloc[0] + 1, 275), fontsize=24, color=color_B)
+
 plt.xlabel('Distance in the east direction (km)', fontsize=24)
 plt.ylabel('Recurrence time (days)', fontsize=24)
 plt.xlim([2, 52])
-plt.ylim([0, 500])
+plt.ylim([0, 300])
 plt.tight_layout()
 plt.savefig('LFEdistribution_perm/nb_LFE_events.eps', format='eps')
 plt.close(1)

### 2022-03-21 data/Ducellier/plot_tremor_nbLFEs.py

@@ -13,8 +13,13 @@ from math import floor
 from date import ymdhms2day
 
 # Time boundaries
-xmin = 2004.0
-xmax = 2012.0
+#xmin = 2004.0
+#xmax = 2012.0
+
+xmin = (2008, 4, 27, 6, 28, 1)
+xmax = (2008, 5, 27, 6, 28, 1)
+xmin = ymdhms2day(xmin[0], xmin[1], xmin[2], xmin[3], xmin[4], xmin[5])
+xmax = ymdhms2day(xmax[0], xmax[1], xmax[2], xmax[3], xmax[4], xmax[5])
 
 # Space boundaries
 latmin = 39.4
@@ -67,7 +72,7 @@ for i in range(0, np.shape(templates)[0]):
         all_LFEs = all_LFEs + len(df)
 
         # Filter LFEs
-#        df = df.loc[df['cc'] * df['nchannel'] >= threshold['threshold_perm'].iloc[i]]
+        df = df.loc[df['cc'] * df['nchannel'] >= threshold['threshold_perm'].iloc[i]]
 
         kept_LFEs = kept_LFEs + len(df)
 
@@ -112,6 +117,7 @@ plt.annotate('F', (xmax + 0.06 * (xmax - xmin), 41.02000), fontsize=24, color='g
 plt.annotate('G', (xmax + 0.08 * (xmax - xmin), 41.10000), fontsize=24, color='grey')
 
 # End figure
+plt.axvline(0.5 * (xmin + xmax), linewidth=2, color='grey')
 plt.xlim([xmin, xmax + 0.2 * (xmax - xmin)])
 plt.ylim([39.1, latmax])
 plt.xlabel('Time (years)', fontsize=24)
@@ -126,7 +132,5 @@ for (size, label) in zip(msizes, mlabels):
 plt.legend(handles=markers, frameon=False, title='Number of LFEs', loc=4, title_fontsize=24)
 
 plt.tight_layout()
-plt.savefig('LFEdistribution_perm/unfiltered.eps', format='eps')
+plt.savefig('LFEdistribution_perm/zoom_teq5.eps', format='eps')
 plt.close(1)
-
-print(all_LFEs, kept_LFEs)

### 2022-03-21 src/compare_catalog.py

@@ -167,8 +167,8 @@ def compare_catalog(filename):
     # Difference between LFEs added in our catalog
     # and LFEs present in both catalogs
     plt.figure(1, figsize=(30, 10))
-    params = {'xtick.labelsize':16,
-              'ytick.labelsize':16}
+    params = {'xtick.labelsize':24,
+              'ytick.labelsize':24}
     pylab.rcParams.update(params) 
     ax1 = plt.subplot(131)
     plt.hist(df_added['cc'], \
@@ -176,6 +176,7 @@ def compare_catalog(filename):
         0.1, 0.11, 0.12, 0.13, 0.14, 0.15, 0.16, 0.17, 0.18, 0.19, 0.20, \
         0.21, 0.22, 0.23, 0.24, 0.25, 0.26, 0.27, 0.28, 0.29, 0.30, 0.31, \
         0.32, 0.33])
+    plt.ylim([0, 40])
     plt.xlabel('Cross-correlation value', fontsize=24)
     plt.ylabel('Number of LFEs', fontsize=24)
     plt.title('LFEs added in our catalog', fontsize=30)
@@ -185,6 +186,7 @@ def compare_catalog(filename):
         0.1, 0.11, 0.12, 0.13, 0.14, 0.15, 0.16, 0.17, 0.18, 0.19, 0.20, \
         0.21, 0.22, 0.23, 0.24, 0.25, 0.26, 0.27, 0.28, 0.29, 0.30, 0.31, \
         0.32, 0.33])
+    plt.ylim([0, 40])
     plt.xlabel('Cross-correlation value', fontsize=24)
     plt.ylabel('Number of LFEs', fontsize=24)
     plt.title('LFEs present in both catalogs', fontsize=30)
@@ -194,9 +196,11 @@ def compare_catalog(filename):
         0.1, 0.11, 0.12, 0.13, 0.14, 0.15, 0.16, 0.17, 0.18, 0.19, 0.20, \
         0.21, 0.22, 0.23, 0.24, 0.25, 0.26, 0.27, 0.28, 0.29, 0.30, 0.31, \
         0.32, 0.33])
+    plt.ylim([0, 40])
     plt.xlabel('Cross-correlation value', fontsize=24)
     plt.ylabel('Number of LFEs', fontsize=24)
     plt.title('LFEs missing in our catalog', fontsize=30)
+    plt.tight_layout()
[…]

### 2022-03-21 paper/agujournaltemplate.tex
Add reference Zenodo

@@
 All the downloading and preprocessing operations on the seismic waveforms are done with the Python package obspy.
-The Python scripts used to analyze the data and make the figures can be found on the first author's Github account, accessible through Zenodo ~\cite{ariane_ducellier_2022_5962414}.
+The Python scripts used to analyze the data and make the figures can be found on the first author's Github account, accessible through Zenodo ~\cite{ariane_ducellier_2022_6374239}.
 
